%% =====================================================================
%% PER-COUNTRY DATA SOURCES AND TRANSFORMATIONS
%%
%% Auto-assembled from the per-region staged fragments at
%%   pipeline/credit_staging/_manual/{main,euro-core,euro-periph,
%%   euro-small,eunon-small,adv,em1,em2}.tex
%% One \subsection per economy (50 economies total), documenting every
%% variable in each deployed spec.json: id, description, source, exact
%% series id/key, frequency, transformation, isFinancial tag, COVID
%% treatment, and any imputation/splicing. Uses only packages already
%% loaded in user_manual.tex (booktabs, longtable, hyperref, xcolor,
%% enumitem). \input{per_country_data} from the main manual.
%% =====================================================================

\section{Per-Country Data Sources and Transformations}\label{sec:percountry-data-all}

This section documents, variable by variable, the data underlying every one
of the 50 economies in the system --- the six core GVAR blocs, the euro-area
members, the EU non-euro and other advanced economies, and the emerging
markets. For each economy a table lists \emph{every} variable in its deployed
specification together with its provider, the exact series identifier (FRED
mnemonic, ECB/Eurostat SDMX key, BIS dataflow key, or national central-bank
code), native frequency, transformation, COVID treatment, and any imputation
or splicing performed at build time. The authoritative variable list (id,
description, transformation, \texttt{isFinancial} tag, prior, block) is taken
verbatim from each economy's staged \texttt{spec.json}; the
source/series-id/frequency/COVID/imputation columns are traced from the data
builders and credit fetchers.

\paragraph{Transformation and COVID conventions (system-wide).} Two
transformation tags appear throughout. \texttt{log} denotes a series entered
as $100\cdot\log(\text{level})$; because such a variable carries a random-walk
(RW) prior unless flagged otherwise, it \emph{enters the dynamics as}
$4\cdot\Delta\!\log$, i.e.\ a quarter-on-quarter \emph{annualized} growth rate
(Section~\ref{sec:units}). \texttt{lin} denotes a series entered in levels
(rates in per cent, ratios in per cent of GDP, spreads in percentage points,
diffusion indices, etc.). The \emph{COVID-as-missing} rule
(Section~\ref{sec:covid}) masks the macro block (\texttt{isFinancial}$=0$)
over the pandemic window --- the canonical window is 2020Q2--Q4, though a few
builds use a self-calibrated four-quarter 2020Q1--Q4 window (flagged where it
applies) --- and lets the data-augmentation/Durbin--Koopman E-step impute it,
while \emph{financial} variables (\texttt{isFinancial}$=1$) are held observed
through the pandemic. Per-variable priors are RW except the stationary fiscal
GDP-ratios (\texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}, \texttt{SFA}), which carry
the white-noise (\texttt{WN}) prior.

\paragraph{The new credit block (flagged throughout).} Each bloc is augmented
with a credit \emph{quantity} variable \texttt{CREDIT\_GDP\_<CC>} = BIS
\emph{Total Credit to Non-Financial Corporations, \% of GDP} (the BIS
\emph{broad} measure: bank loans $+$ debt securities $+$ cross-border
lending), pulled from FRED as \texttt{Q<CC>NAM770A} where a BIS reporting
series exists, transformed \texttt{lin}, prior RW, \texttt{isFinancial}$=1$.
Although tagged financial, the credit quantity is \emph{masked} over the COVID
window because it is a \%-of-GDP ratio whose denominator (GDP) collapses in
2020, so it inherits the macro GDP mask. On the credit \emph{price} side the
blocs gain either a representative NFC bank \emph{lending rate}
(\texttt{LENDR\_<CC>}) or, where no lending rate is reachable, a corporate or
sovereign-proxy yield (\texttt{CORP\_<CC>}); where no price could be sourced it
is dropped (quantity only). Economies whose credit quantity is
\emph{constructed} (non-BIS) or whose price is a sovereign proxy, spliced,
dropped, or a non-canonical variant are flagged in-line in the relevant table
and prose. All credit \emph{price} variables are held observed through COVID.

% =====================================================================
% 1. SIX CORE GVAR BLOCS: US, EA, JP, UK, CA, CN
% =====================================================================

%% =====================================================================
%% Per-country DATA documentation for the six core GVAR blocs
%% (US, EA, JP, UK, CA, CN), including the NEW credit block.
%%
%% Drop-in fragment for the DATA section of docs/user_manual.tex. It uses
%% only packages already loaded in that manual's preamble
%% (booktabs, longtable, hyperref, xcolor). The authoritative final
%% variable list (id / description / transformation / isFinancial /
%% prior / block) is read verbatim from each economy's staged
%% pipeline/credit_staging/<CC>/spec.json; the Source / Series ID /
%% Frequency / COVID / Imputation columns are traced from the data
%% builders (build_us_auto.py, build_country_data.py,
%% build_euro_financial_block.py, add_polrate_hp_group.py,
%% build_polrate_hp_emg.py, the fiscal *_4var builders) and the new
%% credit fetchers (fetch_credit_us.py, build_credit_ea.py,
%% build_credit_JP.py + fetch_boj.py, build_credit_uk.py + fetch_boe_iadb.py,
%% fetch_credit_ca.py, build_credit_cn.py + fetch_oecd_irlt.py).
%% =====================================================================

\subsection{Per-Economy Data Documentation: the Six Core Blocs}\label{sec:percountry-data}

This subsection documents, variable by variable, the data underlying the
six core GVAR blocs --- the United States anchor and its five major
partners (euro area, Japan, United Kingdom, Canada, China). For each
economy the table lists \emph{every} variable in the deployed
specification, together with its provider, the exact series identifier
(FRED mnemonic, ECB/Eurostat SDMX key, BIS dataflow key, or national
central-bank code), native frequency, transformation, COVID treatment,
and any imputation or splicing performed at build time.

\paragraph{Transformation and COVID conventions.} Two transformation
tags appear throughout. \texttt{log} denotes a series entered as
$100\cdot\log(\text{level})$; because every variable carries a
random-walk (RW) prior unless flagged otherwise, a \texttt{log} variable
\emph{enters the dynamics as} $4\cdot\Delta\!\log$, i.e.\ as a
quarter-on-quarter \emph{annualized growth rate}. \texttt{lin} denotes a
series entered in levels (rates in per cent, ratios in per cent of GDP,
diffusion indices, etc.). The \emph{COVID-as-missing} rule
(Section~\ref{sec:covid}) masks the macro block (\texttt{isFinancial}
$=0$) over 2020Q2--2020Q4 and lets the data-augmentation Gibbs sampler
impute it, while \emph{financial} variables (\texttt{isFinancial} $=1$)
are held observed through the pandemic window. ``Fin.'' in the tables
below reproduces the \texttt{isFinancial} tag.

\paragraph{The new credit block (flagged).} Each of the six blocs gains a
credit \emph{quantity} variable
\texttt{CREDIT\_GDP\_<CC>} = BIS \emph{Total Credit to Non-Financial
Corporations, \% of GDP} --- the BIS \emph{broad} credit measure (bank
loans $+$ debt securities $+$ cross-border), pulled from FRED as
\texttt{Q<CC>NAM770A}, transformed \texttt{lin}, prior RW,
\texttt{isFinancial} $=1$. Although tagged financial, the credit
\emph{quantity} is \emph{masked} over 2020Q2--Q4 because it is a
\%-of-GDP ratio whose denominator (GDP) collapses in 2020; it therefore
inherits the macro GDP mask rather than the financial observe-rule. On
the credit \emph{price} side: the US and euro area already carry a
corporate-yield channel and gain \emph{no} new price variable; Japan,
the United Kingdom, and Canada gain a representative NFC bank
\emph{lending rate} (\texttt{LENDR\_<CC>}); and China gains a
\emph{sovereign 10Y yield proxy} (\texttt{CORP\_CN}, flagged --- no
corporate spread exists for China). All credit \emph{price} variables are
held observed through COVID.

% =====================================================================
\subsection{United States (US)}\label{sec:data-us}

The US anchor bloc carries $n=39$ quarterly variables on a
1998Q3--2025Q4 grid (110 quarters) at $p=3$ lags, comprising a rich
domestic macro/financial block, four global commons, and a four-variable
fiscal block; the COVID-as-missing window 2020Q2--Q4 masks the macro
(\texttt{isFinancial} $=0$) series. Macro and financial series are pulled
from FRED at native quarterly frequency (\texttt{frequency=q,
aggregation\_method=avg}); the deployed bloc additionally appends the
three trade-weighted \texttt{ROW*\_US} stars (Section~\ref{sec:gvar:arch}),
which are not data series and are omitted here. The new credit quantity
\texttt{CREDIT\_GDP} is BIS broad NFC credit (\% of GDP);
\textbf{no new credit price is added --- the existing Aaa (\texttt{FAAA})
and Baa (\texttt{GLB\_USBAA}) corporate yields already span the corporate
credit-price channel.}

{\footnotesize\setlength{\tabcolsep}{3.5pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{1.7cm} >{\raggedright\arraybackslash}p{2.7cm} >{\raggedright\arraybackslash}p{1.35cm} >{\raggedright\arraybackslash}p{2.55cm} c c >{\raggedright\arraybackslash}p{0.85cm} >{\raggedright\arraybackslash}p{2.75cm}@{}}
\caption{US bloc variables. Trans.: \texttt{log} $=100\log$ level (enters
as $4\Delta\log$, q/q annualized); \texttt{lin} $=$ level. Fin.\ $=$
\texttt{isFinancial}. COVID: ``mask'' $=$ 2020Q2--Q4 set missing (Gibbs-imputed);
``obs'' $=$ held observed.}\label{tab:data-us}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\multicolumn{8}{@{}l}{\textit{Domestic macro block (FRED, quarterly avg; \texttt{isFinancial}=0 $\Rightarrow$ COVID-masked)}}\\
\midrule
GDPH    & Real Gross Domestic Product & FRED & \texttt{GDPC1} & Q & 0 & log & mask \\
CH      & Real Personal Consumption Exp.\ & FRED & \texttt{PCECC96} & Q & 0 & log & mask \\
FRH     & Real Private Residential Fixed Inv.\ & FRED & \texttt{PRFI} & Q & 0 & log & mask; deflated by \texttt{GDPDEF} \\
FNH     & Real Private Nonres.\ Fixed Inv.\ & FRED & \texttt{PNFI} & Q & 0 & log & mask; deflated by \texttt{GDPDEF} \\
XH      & Real Exports of Goods \& Services & FRED & \texttt{EXPGSC1} & Q & 0 & log & mask \\
MH      & Real Imports of Goods \& Services & FRED & \texttt{IMPGSC1} & Q & 0 & log & mask \\
GH      & Real Gov.\ Consumption \& Gross Inv.\ & FRED & \texttt{GCEC1} & Q & 0 & log & mask \\
JGDP    & GDP: Chain Price Index & FRED & \texttt{GDPDEF} & Q & 0 & log & mask \\
JC      & PCE: Chain Price Index & FRED & \texttt{PCEPI} & Q & 0 & log & mask \\
JCXFE   & PCE less Food \& Energy: Chain Price Idx & FRED & \texttt{PCEPILFE} & Q & 0 & log & mask \\
UI      & CPI-U: All Items & FRED & \texttt{CPIAUCSL} & Q & 0 & log & mask \\
UIXFDG  & CPI-U: All Items less Food \& Energy & FRED & \texttt{CPILFESL} & Q & 0 & log & mask \\
LXBC    & Business Sector: Compensation/Hour & FRED & \texttt{HCOMPBS} & Q & 0 & log & mask \\
LANAGRA & All Employees: Total Nonfarm & FRED & \texttt{PAYEMS} & M$\to$Q & 0 & log & mask \\
LR      & Civilian Unemployment Rate 16+ & FRED & \texttt{UNRATE} & M$\to$Q & 0 & lin & mask \\
IP      & Industrial Production Index & FRED & \texttt{INDPRO} & M$\to$Q & 0 & log & mask \\
CUMFG   & Capacity Utilization: Mfg [SIC] & FRED & \texttt{MCUMFN} & M$\to$Q & 0 & lin & mask \\
HST     & Housing Starts & FRED & \texttt{HOUST} & M$\to$Q & 0 & log & mask \\
YPDH    & Real Disposable Personal Income & FRED & \texttt{DPIC96} & Q & 0 & log & mask \\
CSENT   & U.\ Michigan Consumer Sentiment & FRED & \texttt{UMCSENT} & M$\to$Q & 0 & lin & mask \\
\midrule
\multicolumn{8}{@{}l}{\textit{Domestic financial block (FRED; \texttt{isFinancial}=1 $\Rightarrow$ observed through COVID)}}\\
\midrule
POLRATE  & Effective Federal Funds Rate (policy) & FRED & \texttt{FEDFUNDS} & M$\to$Q & 1 & lin & obs \\
FCM2     & 2Y Treasury Yield, const.\ maturity & FRED & \texttt{DGS2} & D$\to$Q & 1 & lin & obs \\
FCM5     & 5Y Treasury Yield, const.\ maturity & FRED & \texttt{DGS5} & D$\to$Q & 1 & lin & obs \\
FAAA     & Moody's Seasoned Aaa Corp.\ Bond Yield & FRED & \texttt{AAA} & M$\to$Q & 1 & lin & obs; high-grade corp.\ price \\
FXTWM    & Nominal Trade-Wtd US\$ vs AFE & FRED & \texttt{DTWEXAFEGS} / \texttt{DTWEXM} & D$\to$Q & 1 & log & obs; AFE spliced onto legacy Major-\$ at 2006 overlap \\
PZTEXP   & Spot Oil Price: WTI & FRED & \texttt{WTISPLC} & M$\to$Q & 1 & log & obs \\
GSNE     & Non-Fuel Commodity Price Idx (IMF proxy) & FRED & \texttt{PNFUELINDEXM} & M$\to$Q & 1 & log & obs \\
SP500VOL & CBOE Volatility Index (VIX) & FRED & \texttt{VIXCLS} & D$\to$Q & 1 & lin & obs \\
HP       & House Price & FRED & \texttt{CSUSHPISA} & M$\to$Q & 1 & log & obs \\
LEV      & Real nonfinancial business debt & FRED & \texttt{BCNSDODNS} & Q & 1 & log & obs; deflated by \texttt{GDPDEF}/100 \\
\midrule
\multicolumn{8}{@{}l}{\textit{Global commons (US-determined common shocks; \texttt{isFinancial}=1, observed)}}\\
\midrule
GLB\_USLR  & 10Y Treasury Yield, const.\ maturity & FRED & \texttt{DGS10} & D$\to$Q & 1 & lin & obs; global common \\
GLB\_USBAA & Moody's Baa Corp.\ Bond Yield (credit) & FRED & \texttt{BAA} & M$\to$Q & 1 & lin & obs; risk-spread corp.\ price \\
GLB\_USEQ  & US Equity Price Index (S\&P / OECD US) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q & 1 & log & obs; global common \\
GLB\_OIL   & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q & 1 & log & obs; global common \\
\midrule
\multicolumn{8}{@{}l}{\textit{Fiscal block (FRED-derived, 4q-annualized; GDP-ratio drivers carry a WN/stationary prior)}}\\
\midrule
FREV\_GDP  & Federal Receipts (\% of GDP) & FRED & \texttt{FGRECPT}/\texttt{GDP} & Q & 0 & lin & mask; WN prior \\
FPEXP\_GDP & Federal Primary Expenditure (\% of GDP) & FRED & (\texttt{FGEXPND}\allowbreak$-$\texttt{A091\allowbreak RC1Q027SBEA})\allowbreak/\texttt{GDP} & Q & 0 & lin & WN prior; 2020Q2--2021Q4 spike linearly interpolated at build time \\
EFFI       & Federal Effective Interest Rate (\% p.a.) & FRED & \texttt{A091\allowbreak RC1Q027SBEA}\allowbreak/lag\allowbreak(\texttt{GFDEGDQ188S}) & Q & 1 & lin & obs; RW prior \\
SFA        & Stock-Flow Adjustment (\% of GDP) & derived & recursion residual (\texttt{GFDEGDQ188S}) & Q & 0 & lin & WN prior; closes the debt recursion by construction \\
\midrule
\multicolumn{8}{@{}l}{\textit{NEW credit block}}\\
\midrule
CREDIT\_GDP & \textbf{US Credit to NFCs (\% of GDP)} & FRED / BIS & \texttt{QUSNAM770A} & Q & 1 & lin & \textbf{mask} (inherits GDP-denominator mask); BIS broad credit, 1998Q3=61.3, 2025Q4=72.2; \emph{no new price (FAAA/GLB\_USBAA cover it)} \\
\end{longtable}
}

% =====================================================================
\subsection{Euro Area (EA)}\label{sec:data-ea}

The euro-area aggregate carries $n=22$ quarterly variables on a
1999Q1--2025Q4 grid ($T=108$). Real-activity and price series come from
FRED (which mirrors Eurostat/OECD/ECB feeds for the euro aggregate),
short and long rates from FRED OECD/ECB series, and the financial overlay
--- policy rate (\texttt{POLRATE\_EA}), real house prices
(\texttt{HPI\_EA}), and the all-bonds corporate-risk yield
(\texttt{EACORP}) --- from ECB SDMX and Eurostat. The new credit quantity
is BIS broad NFC credit (\% of GDP); \textbf{no new credit price is added
--- \texttt{EACORP} already provides the euro-area corporate-yield
channel} (and \texttt{GLB\_USBAA} a second global credit-risk channel).

{\footnotesize\setlength{\tabcolsep}{3.5pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{1.7cm} >{\raggedright\arraybackslash}p{2.7cm} >{\raggedright\arraybackslash}p{1.35cm} >{\raggedright\arraybackslash}p{2.55cm} c c >{\raggedright\arraybackslash}p{0.85cm} >{\raggedright\arraybackslash}p{2.75cm}@{}}
\caption{Euro-area bloc variables. Columns as in
Table~\ref{tab:data-us}.}\label{tab:data-ea}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
GDP\_EA     & EA Real GDP & FRED (Eurostat) & \texttt{CLVMNACSCAB1GQEA19} & Q & 0 & log & mask \\
CONS\_EA    & EA Consumption & FRED (OECD) & \texttt{NAEXKP02EZQ661S} & Q & 0 & log & mask \\
INV\_EA     & EA Investment & FRED (OECD) & \texttt{NAEXKP04EZQ661S} & Q & 0 & log & mask \\
GOV\_EA     & EA Gov.\ Spending & FRED (OECD) & \texttt{NAEXKP03EZQ661S} & Q & 0 & log & mask \\
EXP\_EA     & EA Exports & FRED (OECD) & \texttt{NAEXKP06EZQ661S} & Q & 0 & log & mask \\
IMP\_EA     & EA Imports & FRED (OECD) & \texttt{NAEXKP07EZQ661S} & Q & 0 & log & mask \\
HICP\_EA    & EA HICP Index (2015=100) & FRED (Eurostat) & \texttt{CP0000EZ19M086NEST} & M$\to$Q & 0 & log & mask \\
RATE\_EA    & EA 3M Interbank Rate & FRED (OECD) & \texttt{IR3TIB01EZQ156N} & Q & 1 & lin & obs \\
YIELD10\_EA & EA 10Y Gov.\ Bond Yield & FRED (OECD) & \texttt{IRLTLT01EZM156N} & M$\to$Q & 1 & lin & obs \\
NEER\_EA    & EA Nominal Effective Exch.\ Rate & FRED (OECD) & \texttt{CCUSMA02EZQ618N} & Q & 1 & log & obs \\
POLRATE\_EA & EA ECB Deposit Facility Rate (policy) & ECB SDW & \texttt{FM/\allowbreak D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV} & D$\to$Q & 1 & lin & obs \\
HPI\_EA     & EA Real House Price Index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q\allowbreak\ Q.\allowbreak TOTAL.\allowbreak I15\_Q.\allowbreak <geo>} (nominal HPI)\,$\div$\,\texttt{HICP\_EA} & Q & 1 & log & obs; deflated by HICP \\
EACORP      & EA Corporate Bond Yield (Bundesbank non-MFI) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q & 1 & lin & obs; genuine non-MFI corporate bond yield \\
GLB\_OIL    & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q & 1 & log & obs; global common \\
GLB\_USLR   & US 10Y Treasury Yield (\%) & FRED & \texttt{DGS10} & D$\to$Q & 1 & lin & obs; global common \\
GLB\_USBAA  & US Baa Corporate Yield (\%) & FRED & \texttt{BAA} & M$\to$Q & 1 & lin & obs; global common \\
GLB\_USEQ   & US Equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q & 1 & log & obs; global common \\
FREV\_GDP   & EA Revenue (\% of GDP) & \emph{see flag} & 4q-annualized rev./GDP & Q & 0 & lin & mask; WN prior \\
FPEXP\_GDP  & EA Primary Expenditure (\% of GDP) & \emph{see flag} & 4q-annualized (exp.$-$int.)/GDP & Q & 0 & lin & mask; WN prior \\
EFFI        & EA Effective Interest Rate (\% p.a.) & \emph{see flag} & 4$\times$int./lag(debt) & Q & 1 & lin & obs; RW prior \\
SFA         & EA Stock-Flow Adjustment (\% of GDP) & derived & recursion residual & Q & 0 & lin & WN prior; closes the debt recursion \\
\multicolumn{8}{@{}p{0.96\textwidth}}{\textit{[FLAG: the EA fiscal flows (revenue, total expenditure, interest, gross debt, nominal GDP) are read from \texttt{pipeline/fiscal\_raw/fiscal\_EA.json}, which records no provenance; the consuming builders (\texttt{build\_fiscal\_drivers.py}, \texttt{build\_fiscal\_ea\_4var.py}) do not fetch them. Upstream provider (Eurostat \texttt{gov\_10q\_ggnfa}/\texttt{gov\_10dd\_edpt1} is the most likely candidate) NOT verified from the code; series IDs left blank rather than fabricated.]}}\\
\midrule
CREDIT\_GDP\_EA & \textbf{EA Credit to NFCs (\% of GDP)} & FRED / BIS & \texttt{QXMNAM770A} & Q & 1 & lin & \textbf{mask} (GDP-denominator mask); BIS broad credit, 1999Q1=66.7, 2025Q4=103.1; \emph{no new price (EACORP covers it)} \\
\end{longtable}
}

% =====================================================================
\subsection{Japan (JP)}\label{sec:data-jp}

The Japan bloc carries $n=22$ quarterly variables on a 2002Q2--2025Q4
grid ($T=95$). Real-activity, price, rate, and exchange-rate series come
from FRED; the policy rate (\texttt{POLRATE\_JP}) and real house prices
(\texttt{HP\_JP}) are appended from the BIS (central-bank policy-rate
dataflow and the real residential property-price dataflow). The new
credit block adds BIS broad NFC credit (\% of GDP) on the quantity side
and a representative \emph{bank lending rate} on the price side:
\texttt{LENDR\_JP} is the Bank of Japan average contract interest rate on
new loans, fetched from the BoJ Time-Series Data Search REST API (not on
FRED).

{\footnotesize\setlength{\tabcolsep}{3.5pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{1.7cm} >{\raggedright\arraybackslash}p{2.7cm} >{\raggedright\arraybackslash}p{1.35cm} >{\raggedright\arraybackslash}p{2.55cm} c c >{\raggedright\arraybackslash}p{0.85cm} >{\raggedright\arraybackslash}p{2.75cm}@{}}
\caption{Japan bloc variables. Columns as in
Table~\ref{tab:data-us}.}\label{tab:data-jp}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
GDP\_JP     & JP Real GDP & FRED & \texttt{JPNRGDPEXP} & Q & 0 & log & mask \\
CONS\_JP    & JP Consumption & FRED (OECD) & \texttt{NAEXKP02JPQ661S} & Q & 0 & log & mask \\
INV\_JP     & JP Investment & FRED (OECD) & \texttt{NAEXKP04JPQ661S} & Q & 0 & log & mask \\
GOV\_JP     & JP Gov.\ Spending & FRED (OECD) & \texttt{NAEXKP03JPQ661S} & Q & 0 & log & mask \\
EXP\_JP     & JP Exports & FRED (OECD) & \texttt{NAEXKP06JPQ661S} & Q & 0 & log & mask \\
IMP\_JP     & JP Imports & FRED (OECD) & \texttt{NAEXKP07JPQ661S} & Q & 0 & log & mask \\
LR\_JP      & JP Unemployment Rate & FRED (OECD) & \texttt{LRHUTTTTJPM156S} & M$\to$Q & 0 & lin & mask \\
CPI\_JP     & JP CPI Index & FRED (OECD) & \texttt{JPNCPIALLMINMEI} & M$\to$Q & 0 & log & mask \\
RATE\_JP    & JP 3M Interbank Rate & FRED (OECD) & \texttt{IR3TIB01JPQ156N} & Q & 1 & lin & obs \\
POLRATE\_JP & JP Central Bank Policy Rate (BIS CBPOL) & BIS & \texttt{WS\_CBPOL M.JP} & M$\to$Q & 1 & lin & obs \\
YIELD10\_JP & JP 10Y JGB Yield & FRED (OECD) & \texttt{IRLTLT01JPM156N} & M$\to$Q & 1 & lin & obs \\
HP\_JP      & JP Real Resid.\ House-Price Idx (BIS RPP, 2010=100) & BIS & \texttt{WS\_SPP\allowbreak\ Q.\allowbreak JP.\allowbreak R.628} & Q & 1 & log & obs \\
GLB\_OIL    & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q & 1 & log & obs; global common \\
GLB\_USLR   & US 10Y Treasury Yield (\%) & FRED & \texttt{DGS10} & D$\to$Q & 1 & lin & obs; global common \\
GLB\_USBAA  & US Baa Corporate Yield (\%) & FRED & \texttt{BAA} & M$\to$Q & 1 & lin & obs; global common \\
GLB\_USEQ   & US Equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q & 1 & log & obs; global common \\
FREV\_GDP   & JP Revenue (\% of GDP) & OECD SDMX + FRED & 4q-annualized rev./GDP; nominal GDP \texttt{JPNNGDP} & Q & 0 & lin & mask; WN prior \\
FPEXP\_GDP  & JP Primary Expenditure (\% of GDP) & OECD SDMX + FRED & 4q-annualized (exp.$-$int.)/GDP & Q & 0 & lin & mask; WN prior \\
EFFI        & JP Effective Interest Rate (\% p.a.) & OECD SDMX + FRED & 4$\times$int./lag(gross debt, OECD F2/F3/F4) & Q & 1 & lin & obs; RW prior \\
SFA         & JP Stock-Flow Adjustment (\% of GDP) & derived & recursion residual & Q & 0 & lin & WN prior; COVID 2020Q1--Q4 set NaN (Gibbs-imputed) \\
\midrule
CREDIT\_GDP\_JP & \textbf{JP Credit to NFCs (\% of GDP)} & FRED / BIS & \texttt{QJPNAM770A} & Q & 1 & lin & \textbf{mask} (GDP-denominator mask); BIS broad credit, 2002Q2=111.0, 2025Q4=113.9 \\
LENDR\_JP   & \textbf{JP Avg Contract Rate on New Loans (\% p.a.)} & BoJ Time-Series API & \texttt{IR04\,/\,\allowbreak DLLR2CIDBNL1} & M$\to$Q & 1 & lin & \textbf{obs}; domestically-licensed banks, new loans total; NOT on FRED (dedicated BoJ fetcher) \\
\end{longtable}
}

% =====================================================================
\subsection{United Kingdom (UK)}\label{sec:data-uk}

The UK bloc carries $n=24$ quarterly variables on a 1997Q1--2025Q4 grid
($T=116$). Real-activity, price, rate, industrial-production, NEER,
policy-rate, and house-price series come from FRED (plus the BIS for the
BIS-RPP house-price and CBPOL policy-rate concepts where used). The new
credit block adds BIS broad NFC credit (\% of GDP) on the quantity side
and the Bank of England effective rate on new sterling loans to PNFCs
(\texttt{LENDR\_UK}) on the price side, fetched from the BoE Interactive
Database (IADB) CSV API (not on FRED).

{\footnotesize\setlength{\tabcolsep}{3.5pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{1.7cm} >{\raggedright\arraybackslash}p{2.7cm} >{\raggedright\arraybackslash}p{1.35cm} >{\raggedright\arraybackslash}p{2.55cm} c c >{\raggedright\arraybackslash}p{0.85cm} >{\raggedright\arraybackslash}p{2.75cm}@{}}
\caption{UK bloc variables. Columns as in
Table~\ref{tab:data-us}.}\label{tab:data-uk}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
GDP\_UK     & UK Real GDP & FRED (ONS) & \texttt{NGDPRSAXDCGBQ} & Q & 0 & log & mask \\
CONS\_UK    & UK Consumption & FRED (OECD) & \texttt{NAEXKP02GBQ661S} & Q & 0 & log & mask \\
INV\_UK     & UK Investment & FRED (OECD) & \texttt{NAEXKP04GBQ661S} & Q & 0 & log & mask \\
GOV\_UK     & UK Gov.\ Spending & FRED (OECD) & \texttt{NAEXKP03GBQ661S} & Q & 0 & log & mask \\
EXP\_UK     & UK Exports & FRED (OECD) & \texttt{NAEXKP06GBQ661S} & Q & 0 & log & mask \\
IMP\_UK     & UK Imports & FRED (OECD) & \texttt{NAEXKP07GBQ661S} & Q & 0 & log & mask \\
IP\_UK      & UK Industrial Production Index & FRED (OECD) & \texttt{GBRPROINDMISMEI} & M$\to$Q & 0 & log & mask \\
LR\_UK      & UK Unemployment Rate & FRED (OECD) & \texttt{LRHUTTTTGBM156S} & M$\to$Q & 0 & lin & mask \\
CPI\_UK     & UK CPI Index & FRED (OECD) & \texttt{GBRCPIALLMINMEI} & M$\to$Q & 0 & log & mask \\
RATE\_UK    & UK 3M Interbank Rate & FRED (OECD) & \texttt{IR3TIB01GBQ156N} & Q & 1 & lin & obs \\
POLRATE\_UK & UK Central Bank Policy Rate (BIS CBPOL) & BIS & \texttt{WS\_CBPOL M.GB} & M$\to$Q & 1 & lin & obs \\
YIELD10\_UK & UK 10Y Gilt Yield & FRED (OECD) & \texttt{IRLTLT01GBM156N} & M$\to$Q & 1 & lin & obs \\
HP\_UK      & UK Real Resid.\ House-Price Idx (BIS RPP, 2010=100) & BIS & \texttt{WS\_SPP\allowbreak\ Q.\allowbreak GB.\allowbreak R.628} & Q & 1 & log & obs \\
NEER\_UK    & UK Nominal Effective Exch.\ Rate & FRED (OECD) & \texttt{CCUSMA02GBQ618N} & Q & 1 & log & obs \\
GLB\_OIL    & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q & 1 & log & obs; global common \\
GLB\_USLR   & US 10Y Treasury Yield (\%) & FRED & \texttt{DGS10} & D$\to$Q & 1 & lin & obs; global common \\
GLB\_USBAA  & US Baa Corporate Yield (\%) & FRED & \texttt{BAA} & M$\to$Q & 1 & lin & obs; global common \\
GLB\_USEQ   & US Equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q & 1 & log & obs; global common \\
FREV\_GDP   & UK Revenue (\% of GDP) & \emph{see flag} & 4q-annualized rev./GDP & Q & 0 & lin & mask; WN prior \\
FPEXP\_GDP  & UK Primary Expenditure (\% of GDP) & \emph{see flag} & 4q-annualized (exp.$-$int.)/GDP & Q & 0 & lin & mask; WN prior \\
EFFI        & UK Effective Rate (\% p.a.) & \emph{see flag} & 4$\times$int./lag(debt) & Q & 1 & lin & obs; RW prior \\
SFA         & UK Stock-Flow Adj.\ (\% of GDP) & derived & recursion residual & Q & 0 & lin & WN prior; closes the debt recursion \\
\multicolumn{8}{@{}p{0.96\textwidth}}{\textit{[FLAG: the UK fiscal flows are read from \texttt{pipeline/fiscal\_raw/fiscal\_UK.json}, which records no provenance; the consuming builders do not fetch them. Upstream provider (ONS public-sector finances / OECD QNA government finance) NOT verified from the code; series IDs left blank rather than fabricated. Note: an index-linked-gilt interest spike is documented separately in Section~\ref{sec:fiscal_data}.]}}\\
\midrule
CREDIT\_GDP\_UK & \textbf{UK Credit to NFCs (\% of GDP)} & FRED / BIS & \texttt{QGBNAM770A} & Q & 1 & lin & \textbf{mask} (GDP-denominator mask); BIS broad credit, NSA, 1997Q1=51.5, 2025Q4=59.0 \\
LENDR\_UK   & \textbf{UK Effective Rate on New Loans to PNFCs (\% p.a.)} & Bank of England IADB & \texttt{CFMBJ82} & M$\to$Q & 1 & lin & \textbf{obs}; new-business sterling lending rate; starts 2004Q1 (ragged lead, Gibbs-completed); NOT on FRED (dedicated BoE fetcher) \\
\end{longtable}
}

% =====================================================================
\subsection{Canada (CA)}\label{sec:data-ca}

The Canada bloc carries $n=24$ quarterly variables on a 1998Q1--2025Q4
grid ($T=112$). Real-activity, price, rate, NEER, policy-rate, and
house-price series come from FRED (with BIS for the CBPOL policy-rate and
BIS-RPP house-price concepts). The new credit block adds BIS broad NFC
credit (\% of GDP) on the quantity side and the Bank of Canada weekly
effective business interest rate (\texttt{LENDR\_CA}) on the price side,
fetched from the BoC Valet API (not on FRED).

{\footnotesize\setlength{\tabcolsep}{3.5pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{1.7cm} >{\raggedright\arraybackslash}p{2.7cm} >{\raggedright\arraybackslash}p{1.35cm} >{\raggedright\arraybackslash}p{2.55cm} c c >{\raggedright\arraybackslash}p{0.85cm} >{\raggedright\arraybackslash}p{2.75cm}@{}}
\caption{Canada bloc variables. Columns as in
Table~\ref{tab:data-us}.}\label{tab:data-ca}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
GDP\_CA     & CA Real GDP & FRED (OECD) & \texttt{NAEXKP01CAQ661S} & Q & 0 & log & mask \\
CONS\_CA    & CA Consumption & FRED (OECD) & \texttt{NAEXKP02CAQ661S} & Q & 0 & log & mask \\
INV\_CA     & CA Investment & FRED (OECD) & \texttt{NAEXKP04CAQ661S} & Q & 0 & log & mask \\
GOV\_CA     & CA Gov.\ Spending & FRED (OECD) & \texttt{NAEXKP03CAQ661S} & Q & 0 & log & mask \\
EXP\_CA     & CA Exports & FRED (OECD) & \texttt{NAEXKP06CAQ661S} & Q & 0 & log & mask \\
IMP\_CA     & CA Imports & FRED (OECD) & \texttt{NAEXKP07CAQ661S} & Q & 0 & log & mask \\
IP\_CA      & CA Industrial Production (Idx 2015=100) & FRED / StatCan & log-level IP (rebuilt) & Q & 0 & log & mask; rebuilt as a log-level index \\
LR\_CA      & CA Unemployment Rate & FRED (OECD) & \texttt{LRHUTTTTCAM156S} & M$\to$Q & 0 & lin & mask \\
CPI\_CA     & CA CPI Index & FRED (OECD) & \texttt{CANCPIALLMINMEI} & M$\to$Q & 0 & log & mask \\
RATE\_CA    & CA 3M Interbank Rate & FRED (OECD) & \texttt{IR3TIB01CAQ156N} & Q & 1 & lin & obs \\
POLRATE\_CA & CA Central Bank Policy Rate (BIS CBPOL) & BIS & \texttt{WS\_CBPOL M.CA} & M$\to$Q & 1 & lin & obs \\
YIELD10\_CA & CA 10Y Gov.\ Bond Yield & FRED (OECD) & \texttt{IRLTLT01CAM156N} & M$\to$Q & 1 & lin & obs \\
HP\_CA      & CA Real Resid.\ House-Price Idx (BIS RPP, 2010=100) & BIS & \texttt{WS\_SPP\allowbreak\ Q.\allowbreak CA.\allowbreak R.628} & Q & 1 & log & obs \\
NEER\_CA    & CA Nominal Effective Exch.\ Rate & FRED (OECD) & \texttt{CCUSMA02CAQ618N} & Q & 1 & log & obs \\
GLB\_OIL    & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q & 1 & log & obs; global common \\
GLB\_USLR   & US 10Y Treasury Yield (\%) & FRED & \texttt{DGS10} & D$\to$Q & 1 & lin & obs; global common \\
GLB\_USBAA  & US Baa Corporate Yield (\%) & FRED & \texttt{BAA} & M$\to$Q & 1 & lin & obs; global common \\
GLB\_USEQ   & US Equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q & 1 & log & obs; global common \\
FREV\_GDP   & CA Revenue (\% of GDP) & \emph{see flag} & 4q-annualized rev./GDP & Q & 0 & lin & mask; WN prior \\
FPEXP\_GDP  & CA Primary Expenditure (\% of GDP) & \emph{see flag} & 4q-annualized (exp.$-$int.)/GDP & Q & 0 & lin & mask; WN prior \\
EFFI        & CA Effective Interest Rate (\% p.a.) & \emph{see flag} & 4$\times$int./lag(debt) & Q & 1 & lin & obs; RW prior \\
SFA         & CA Stock-Flow Adjustment (\% of GDP) & derived & recursion residual & Q & 0 & lin & WN prior; closes the debt recursion \\
\multicolumn{8}{@{}p{0.96\textwidth}}{\textit{[FLAG: the CA fiscal flows are read from \texttt{pipeline/fiscal\_raw/fiscal\_CA.json}, which records no provenance; the consuming builders do not fetch them. Upstream provider (Statistics Canada government-finance / OECD QNA) NOT verified from the code; series IDs left blank rather than fabricated.]}}\\
\midrule
CREDIT\_GDP\_CA & \textbf{CA Credit to NFCs (\% of GDP)} & FRED / BIS & \texttt{QCANAM770A} & Q & 1 & lin & \textbf{mask} (GDP-denominator mask); BIS broad credit, NSA, 1998Q1=84.2, 2025Q4=118.3 \\
LENDR\_CA   & \textbf{CA Bank Lending Rate (effective business rate, \% p.a.)} & Bank of Canada Valet & \texttt{BUSEFFRATE} & W$\to$Q & 1 & lin & \textbf{obs}; weekly effective business interest rate, q-avg; starts 1999Q1; NOT on FRED (dedicated BoC fetcher) \\
\end{longtable}
}

% =====================================================================
\subsection{China (CN)}\label{sec:data-cn}

The China bloc carries $n=19$ quarterly variables on a 1999Q1--2025Q4
grid ($T=108$). Because clean quarterly \emph{real} GDP is not available
for China, real activity is anchored by official quarterly
\emph{nominal} GDP plus trade volumes and the BVAR/CPI separation; all
domestic series are genuine FRED series (no placeholders). The policy
rate (\texttt{POLRATE\_CN}) and real property prices (\texttt{HP\_CN})
are appended from the BIS. The new credit block adds BIS broad NFC credit
(\% of GDP) on the quantity side; on the price side \texttt{CORP\_CN} is
a \emph{sovereign 10Y yield used as a corporate-price proxy} ---
\textbf{[FLAG: CN price is a SOVEREIGN 10Y benchmark government yield, not
a corporate yield or NFC lending rate; no corporate spread exists for
China]}.

{\footnotesize\setlength{\tabcolsep}{3.5pt}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{1.7cm} >{\raggedright\arraybackslash}p{2.7cm} >{\raggedright\arraybackslash}p{1.35cm} >{\raggedright\arraybackslash}p{2.55cm} c c >{\raggedright\arraybackslash}p{0.85cm} >{\raggedright\arraybackslash}p{2.75cm}@{}}
\caption{China bloc variables. Columns as in
Table~\ref{tab:data-us}.}\label{tab:data-cn}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Fin.} & \textbf{Trans.} & \textbf{COVID / Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
GDP\_CN     & CN Real GDP (quarterly, chain-linked SA volume index, base 2011Q1$=$100) & OECD QNA via DBnomics (NBS) & \texttt{DSD\_NAMAIN1@DF\_QNA...CHN...B1GQ} & Q & 0 & log & obs; real chain-linked volume (2011Q1+ genuine; 1999--2010 genuine annual real growth, Denton-disaggregated) \\
CPI\_CN     & CN CPI & FRED (OECD) & \texttt{CHNCPIALLMINMEI} & M$\to$Q & 0 & log & mask \\
RATE\_CN    & CN 3M Interbank Rate & FRED (OECD) & \texttt{IR3TIB01CNM156N} & M$\to$Q & 1 & lin & obs \\
EXP\_CN     & CN Exports (USD) & FRED (OECD) & \texttt{XTEXVA01CNM667S} & M$\to$Q & 0 & log & mask \\
IMP\_CN     & CN Imports (USD) & FRED (OECD) & \texttt{XTIMVA01CNM667S} & M$\to$Q & 0 & log & mask \\
REER\_CN    & CN Real Effective FX & FRED (BIS) & \texttt{RBCNBIS} & M$\to$Q & 1 & log & obs \\
EQ\_CN      & Shanghai Share Prices & FRED (OECD) & \texttt{SPASTT01CNM661N} & M$\to$Q & 1 & log & obs \\
POLRATE\_CN & CN Policy Rate (BIS CBPOL) & BIS & \texttt{WS\_CBPOL M.CN} & M$\to$Q & 1 & lin & obs \\
HP\_CN      & CN Real Resid.\ Property Price (BIS) & FRED (BIS) & \texttt{QCNR628BIS} & Q & 1 & log & obs \\
GLB\_OIL    & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q & 1 & log & obs; global common \\
GLB\_USLR   & US 10Y Treasury Yield (\%) & FRED & \texttt{DGS10} & D$\to$Q & 1 & lin & obs; global common \\
GLB\_USBAA  & US Baa Corporate Yield (\%) & FRED & \texttt{BAA} & M$\to$Q & 1 & lin & obs; global common \\
GLB\_USEQ   & US Equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q & 1 & log & obs; global common \\
FREV\_GDP   & CN Revenue (\% of GDP) & IMF WEO (2025-04) & \texttt{CHN.\allowbreak GGR.\allowbreak national\_currency} (annual)$\div$GDP & A$\to$Q & 0 & lin & mask; WN prior; annual, temporally disaggregated \\
FPEXP\_GDP  & CN Primary Expenditure (\% of GDP) & IMF WEO (2025-04) & \texttt{CHN.GGX} less derived interest, $\div$GDP & A$\to$Q & 0 & lin & mask; WN prior \\
EFFI        & CN Effective Interest Rate (\% p.a.) & IMF WEO + BIS debt & 4$\times$int./lag(\texttt{QCNGANXDCA}) & Q & 1 & lin & obs; RW prior; interest derived as overall$-$primary balance \\
SFA         & CN Stock-Flow Adjustment (\% of GDP) & derived & recursion residual & Q & 0 & lin & WN prior; gross debt = BIS GG credit \texttt{QCNGANXDCA} \\
\midrule
CREDIT\_GDP\_CN & \textbf{CN Credit to NFCs (\% of GDP)} & FRED / BIS & \texttt{QCNNAM770A} & Q & 1 & lin & \textbf{mask} (GDP-denominator mask); BIS broad credit, NSA, starts 2006Q1=99.4 (leading NaNs pre-2006), 2025Q4=142.8 \\
CORP\_CN    & \textbf{CN 10Y Government Bond Yield (sovereign proxy)} & OECD KEI (SDMX) & \texttt{DSD\_KEI@\allowbreak DF\_KEI\,/\,\allowbreak CHN.\allowbreak M.\allowbreak IRLT} & M$\to$Q & 1 & lin & \textbf{obs}; \emph{[FLAG: SOVEREIGN 10Y proxy, no corporate spread]}; starts 2014Q1=4.48 (leading NaNs pre-2014), 2025Q4=1.83 \\
\end{longtable}
}

% =====================================================================
% 2. EURO-AREA MEMBERS
% =====================================================================
% --- 2a. Euro-core (AT, BE, DE, FR, NL) ---
%% ============================================================================
%% DATA APPENDIX — EURO-CORE SINGLE-COUNTRY BVARs (AT, BE, DE, FR, NL)
%%
%% Generated for the "Data" section of the BVAR/GVAR forecasting-tool manual.
%% Style matches docs/user_manual.tex: booktabs + longtable are loaded there,
%% so each per-country variable table is a \longtable. No new packages required.
%%
%% Authoritative final variable list (id, name, transformation, isFinancial,
%% block, prior) is taken from each economy's staged spec:
%%   pipeline/euro_redesign_staging/<CC>/spec.json   (macro/fiscal redesign)
%%   pipeline/credit_staging/<CC>/spec.json          (+ credit block appended)
%% Source / series-id / frequency / COVID / imputation are traced from the
%% data builders:
%%   build_oecd_eurostat.py, build_euro_member_redesign.py,
%%   build_euro_financial_block.py  (macro/financial/fiscal/ROW columns)
%%   build_credit_eurocore.py, fetch_bis_credit_gdp.py, fetch_ecb_mir.py
%%     (the NEW credit block: CREDIT_GDP_<CC> + LENDR_<CC>)
%% ============================================================================

\subsection{Euro-core single-country BVARs (AT, BE, DE, FR, NL)}
\label{sec:data:eurocore}

The five euro-core economies are estimated as \emph{standalone} single-country
Bayesian VARs (not GVAR blocs): the rest-of-euro-area and the area-wide rates
enter as a weakly-exogenous foreign block rather than through trade-weighted
stars. All real macro aggregates are Eurostat-sourced (the redesigned
\texttt{namq\_10\_gdp} / \texttt{prc\_hicp\_midx} / \texttt{une\_rt\_q} /
\texttt{irt\_*} / \texttt{ert\_eff\_ic\_q} pulls, current to 2025Q4); the
financial block (ECB Deposit Facility Rate, the EA all-bonds 10Y yield, the
3M EURIBOR, the Bund and the sovereign spread) is fetched from the ECB Data
Portal; the fiscal block is built from Eurostat \texttt{gov\_10q} on the
4-variable \{revenue, primary expenditure, effective rate, stock-flow
adjustment\} recipe; and the credit block (\texttt{CREDIT\_GDP\_<CC>},
\texttt{LENDR\_<CC>}) is appended last from BIS-via-FRED and the ECB MIR
statistics.

\paragraph{Transformation conventions.}
Throughout, \textbf{\texttt{log}} denotes the model space $100\cdot\log(\text{level})$;
such a variable enters growth-rate reporting as $4\cdot\Delta(100\log)=$
quarter-on-quarter annualised growth (\S\ref{sec:units}). \textbf{\texttt{lin}}
denotes the raw level (a rate in \% p.a., a ratio in \% of GDP, or an index
read in levels). The own-lag prior is random-walk (\texttt{RW}) for every
macro and financial variable; the fiscal flow ratios
(\texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}, \texttt{SFA}) carry the stationary
white-noise prior (\texttt{WN}).

\paragraph{COVID treatment.}
\label{sec:data:eurocore:covid}
Under the COVID-as-missing convention only the non-financial macro columns
(\texttt{isFinancial}$=0$: the six national-accounts aggregates, HICP, the
unemployment rate, and the two rest-of-EA macro series) are masked
(\texttt{NaN}) over the pandemic window and imputed by the
COVID-as-missing Durbin--Koopman smoother; financial columns are kept
observed. \textit{[FLAG: window mismatch.] Two distinct COVID windows coexist
in these builds. The macro/ROW block (and the fiscal \texttt{SFA}) is masked
over the \emph{four} quarters \textbf{2020Q1--Q4} — the self-calibrated window
\texttt{build\_euro\_member\_redesign.py} selects as the largest
$100\log$(GDP) drop in 2019Q4--2021Q1, i.e.\ $\text{trough}-1\ldots\text{trough}+2$
— whereas the newly-appended credit quantity \texttt{CREDIT\_GDP\_<CC>} is
masked over the \emph{three} quarters \textbf{2020Q2--Q4} (the hard-coded
\texttt{COVID\_MASK} in \texttt{build\_credit\_eurocore.py}). The two masks
therefore differ by one quarter (2020Q1). All financial columns
(rates, spreads, EACORP, EFFI, house prices, and the credit price
\texttt{LENDR\_<CC>}) remain observed throughout.}
The fiscal flow ratios \texttt{FREV\_GDP}, \texttt{FPEXP\_GDP} and the effective
rate \texttt{EFFI} are \emph{not} masked: they are interpolated/forward-filled
to a NaN-free column before estimation; only the derived \texttt{SFA} inherits
the four-quarter macro mask.

\paragraph{Imputation of ragged edges.}
Financial and exogenous columns are leading-back-filled (first finite value
carried back) and forward-filled so every column is NaN-free over its
estimation window; the national-accounts/HICP/unemployment columns drive the
common contiguous window. The credit quantity has no leading/trailing gaps
(BIS history predates every base start); its only missing cells are the three
COVID-masked quarters.

\paragraph{The credit block (NEW).}
Each economy gains exactly two domestic financial variables appended after all
existing columns (\texttt{isFinancial}$=1$, \texttt{lin}, \texttt{RW},
\texttt{block}$=$\texttt{domestic}):
\begin{itemize}[leftmargin=1.4em,itemsep=1pt,topsep=2pt]
  \item \textbf{Quantity} \texttt{CREDIT\_GDP\_<CC>} = BIS ``Total credit to
        non-financial corporations, \% of GDP'' (break-adjusted \emph{broad}
        credit: bank loans \emph{plus} debt securities \emph{plus}
        cross-border lending), pulled via FRED under the uniform mnemonic
        \texttt{Q<CC>NAM770A}. Native quarterly (FRED dates the observations at
        the quarter start). COVID-masked 2020Q2--Q4 (it inherits the collapse
        of the GDP denominator).
  \item \textbf{Price} \texttt{LENDR\_<CC>} = the ECB MIR (MFI Interest Rate
        statistics) NFC \emph{new-business} bank lending rate, SDMX key
        \texttt{M.<CC>.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N} (title ``Bank interest rates ---
        loans to corporations (new business)''; S.11 NFC counterparty,
        AAR/NDER, all-maturity, EUR, new-business coverage). Monthly $\to$
        quarter average; observed through COVID.
\end{itemize}
Because the shipped quantity is the BIS \emph{broad} total-credit series, the
euro-core members carry the canonical BIS measure (not a bank-loans-only
proxy), and the credit price is a true national NFC new-business lending rate
(not a sovereign-yield or corporate-spread proxy). The only price-coverage
caveat is Belgium (see below).

% ----------------------------------------------------------------------------
\subsection{Austria (AT)}
\label{sec:data:AT}

A 23-variable single-country BVAR estimated over \textbf{2009Q1--2025Q4}
($T=68$). COVID-as-missing: macro block masked 2020Q1--Q4, credit quantity
masked 2020Q2--Q4, financials observed (\S\ref{sec:data:eurocore:covid}).

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.135\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.085\textwidth}@{}}
\caption{Austria (AT) --- variable documentation.}\label{tab:data:AT}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Table~\ref{tab:data:AT} (Austria), continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\small\itshape continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_AT}    & Real GDP (chain-linked vol., SCA) & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak AT} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{CONS\_AT}   & Real household final consumption & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak P31\_S14\_S15.\allowbreak AT} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{INV\_AT}    & Real gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak P51G.\allowbreak AT} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{GOV\_AT}    & Real government consumption & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak P3\_S13.\allowbreak AT} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{EXP\_AT}    & Real exports & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak P6.\allowbreak AT} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{IMP\_AT}    & Real imports & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak P7.\allowbreak AT} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{HICP\_AT}   & HICP index (all-items, 2015=100) & Eurostat & \texttt{prc\_hicp\_midx M.\allowbreak I15.\allowbreak CP00.\allowbreak AT} & M$\to$Q avg & log & masked 20Q1--Q4 & domestic \\
\texttt{LR\_AT}     & Unemployment rate (SA, \% active pop.) & Eurostat & \texttt{une\_rt\_q Q.\allowbreak SA.\allowbreak TOTAL.\allowbreak PC\_ACT.\allowbreak T.\allowbreak AT} & Q & lin & masked 20Q1--Q4 & domestic \\
\texttt{HPI\_AT}    & Real house-price index (nominal HPI$/$HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q Q.\allowbreak TOTAL.\allowbreak I15\_Q.\allowbreak AT} $\div$ HICP & Q & log & observed (financial) & domestic; nominal HPI deflated by HICP \\
\texttt{NEER\_AT}   & Nominal effective exchange rate, IC42 partners & Eurostat & \texttt{ert\_eff\_ic\_q Q.\allowbreak NEER\_IC42.\allowbreak I15.\allowbreak AT} & Q & log & observed & domestic; broad 42-partner group \\
\texttt{SPREAD\_AT} & 10Y sovereign spread vs Bund & Eurostat (computed) & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak AT} $-$ \texttt{M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & domestic; own 10Y minus Bund \\
\texttt{POLRATE\_AT}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM/D.\allowbreak U2.\allowbreak EUR.4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV} & D$\to$Q avg & lin & observed & external (shared) \\
\texttt{EACORP}     & EA corporate bond yield (non-MFI) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q avg & lin & observed & external; IG-corp risk proxy \\
\texttt{RATE\_AT}   & 3-month EURIBOR & Eurostat & \texttt{irt\_st\_q Q.\allowbreak IRT\_M3.\allowbreak EA} & Q & lin & observed & external (shared) \\
\texttt{YIELD10\_DE}& DE 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & external (injected) \\
\texttt{ROWEA\_GDP\_AT}  & Rest-of-EA real GDP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less AT, \texttt{namq\_10\_gdp} & Q & log & masked 20Q1--Q4 & row \\
\texttt{ROWEA\_HICP\_AT} & Rest-of-EA HICP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less AT, \texttt{prc\_hicp\_midx} & Q & log & masked 20Q1--Q4 & row \\
\texttt{FREV\_GDP}  & General-gov. revenue (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak AT} & Q & lin & observed (forward-filled) & fiscal; WN prior \\
\texttt{FPEXP\_GDP} & Primary expenditure (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa ...\allowbreak TE $-$ ...\allowbreak D41PAY .\allowbreak AT} & Q & lin & observed (forward-filled) & fiscal; WN prior \\
\texttt{EFFI}       & Effective interest rate on gov. debt & Eurostat (computed) & \texttt{...D41PAY} $/$ \texttt{gov\_10q\_ggdebt ...\allowbreak GD.\allowbreak AT} & Q & lin & observed & fiscal; financial \\
\texttt{SFA}        & Stock-flow adjustment (budget-identity residual) & Eurostat (computed) & debt-recursion residual & Q & lin & masked 20Q1--Q4 & fiscal; WN prior \\
\texttt{CREDIT\_GDP\_AT} & \textbf{[NEW]} BIS total credit to NFCs, \% of GDP (broad: loans+bonds+cross-border) & BIS via FRED & \texttt{QATNAM770A} & Q & lin & masked 20Q2--Q4 & domestic; src 1995Q4:69.7..\allowbreak 2025Q4:83.9 \\
\texttt{LENDR\_AT}  & \textbf{[NEW]} NFC new-business bank lending rate & ECB MIR & \texttt{M.\allowbreak AT.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N} & M$\to$Q avg & lin & observed & domestic; src 2000Q1:4.95..\allowbreak 2026Q2:3.57 \\
\end{longtable}

% ----------------------------------------------------------------------------
\subsection{Belgium (BE)}
\label{sec:data:BE}

A 23-variable single-country BVAR estimated over \textbf{2009Q1--2025Q4}
($T=68$). COVID-as-missing: macro block masked 2020Q1--Q4, credit quantity
masked 2020Q2--Q4, financials observed.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.135\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.085\textwidth}@{}}
\caption{Belgium (BE) --- variable documentation.}\label{tab:data:BE}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Table~\ref{tab:data:BE} (Belgium), continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\small\itshape continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_BE}    & Real GDP (chain-linked vol., SCA) & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak BE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{CONS\_BE}   & Real household final consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P31\_S14\_S15.\allowbreak BE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{INV\_BE}    & Real gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P51G.\allowbreak BE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{GOV\_BE}    & Real government consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P3\_S13.\allowbreak BE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{EXP\_BE}    & Real exports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P6.\allowbreak BE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{IMP\_BE}    & Real imports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P7.\allowbreak BE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{HICP\_BE}   & HICP index (all-items, 2015=100) & Eurostat & \texttt{prc\_hicp\_midx M.\allowbreak I15.\allowbreak CP00.\allowbreak BE} & M$\to$Q avg & log & masked 20Q1--Q4 & domestic \\
\texttt{LR\_BE}     & Unemployment rate (SA, \% active pop.) & Eurostat & \texttt{une\_rt\_q Q.\allowbreak SA.\allowbreak TOTAL.\allowbreak PC\_ACT.\allowbreak T.\allowbreak BE} & Q & lin & masked 20Q1--Q4 & domestic \\
\texttt{HPI\_BE}    & Real house-price index (nominal HPI$/$HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q Q.\allowbreak TOTAL.\allowbreak I15\_Q.\allowbreak BE} $\div$ HICP & Q & log & observed (financial) & domestic \\
\texttt{NEER\_BE}   & Nominal effective exchange rate, IC42 partners & Eurostat & \texttt{ert\_eff\_ic\_q Q.\allowbreak NEER\_IC42.\allowbreak I15.\allowbreak BE} & Q & log & observed & domestic \\
\texttt{SPREAD\_BE} & 10Y sovereign spread vs Bund & Eurostat (computed) & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak BE} $-$ \texttt{M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & domestic \\
\texttt{POLRATE\_BE}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM/D.\allowbreak U2.\allowbreak EUR.4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV} & D$\to$Q avg & lin & observed & external (shared) \\
\texttt{EACORP}     & EA corporate bond yield (non-MFI) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q avg & lin & observed & external \\
\texttt{RATE\_BE}   & 3-month EURIBOR & Eurostat & \texttt{irt\_st\_q Q.\allowbreak IRT\_M3.\allowbreak EA} & Q & lin & observed & external (shared) \\
\texttt{YIELD10\_DE}& DE 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & external (injected) \\
\texttt{ROWEA\_GDP\_BE}  & Rest-of-EA real GDP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less BE, \texttt{namq\_10\_gdp} & Q & log & masked 20Q1--Q4 & row \\
\texttt{ROWEA\_HICP\_BE} & Rest-of-EA HICP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less BE, \texttt{prc\_hicp\_midx} & Q & log & masked 20Q1--Q4 & row \\
\texttt{FREV\_GDP}  & General-gov. revenue (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak BE} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{FPEXP\_GDP} & Primary expenditure (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa ...\allowbreak TE $-$ ...\allowbreak D41PAY .\allowbreak BE} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{EFFI}       & Effective interest rate on gov. debt & Eurostat (computed) & \texttt{...D41PAY} $/$ \texttt{gov\_10q\_ggdebt ...\allowbreak GD.\allowbreak BE} & Q & lin & observed & fiscal; financial \\
\texttt{SFA}        & Stock-flow adjustment (budget-identity residual) & Eurostat (computed) & debt-recursion residual & Q & lin & masked 20Q1--Q4 & fiscal; WN \\
\texttt{CREDIT\_GDP\_BE} & \textbf{[NEW]} BIS total credit to NFCs, \% of GDP (broad) & BIS via FRED & \texttt{QBENAM770A} & Q & lin & masked 20Q2--Q4 & domestic; src 1990Q1:55.5..\allowbreak 2025Q4:117.9 \\
\texttt{LENDR\_BE}  & \textbf{[NEW]} NFC new-business bank lending rate & ECB MIR & \texttt{M.\allowbreak BE.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N} & M$\to$Q avg & lin & observed & domestic; \textit{[FLAG: price coverage starts 2003Q1, not 2000Q1 as for the others; src 2003Q1:3.66..\allowbreak 2026Q2:3.48 — earliest pre-2009 values are back-filled.]} \\
\end{longtable}

% ----------------------------------------------------------------------------
\subsection{Germany (DE)}
\label{sec:data:DE}

A 22-variable single-country BVAR estimated over \textbf{2009Q1--2025Q4}
($T=68$). Germany is the spread \emph{base}: it carries the Bund 10Y yield
\texttt{YIELD10\_DE} as an \emph{endogenous domestic} variable and therefore has
\emph{no} \texttt{SPREAD\_DE} variable (hence $n=22$, one fewer than the other
euro-core members). COVID-as-missing: macro block masked 2020Q1--Q4, credit
quantity masked 2020Q2--Q4, financials observed.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.135\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.085\textwidth}@{}}
\caption{Germany (DE) --- variable documentation.}\label{tab:data:DE}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Table~\ref{tab:data:DE} (Germany), continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\small\itshape continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_DE}    & Real GDP (chain-linked vol., SCA) & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak DE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{CONS\_DE}   & Real household final consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P31\_S14\_S15.\allowbreak DE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{INV\_DE}    & Real gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P51G.\allowbreak DE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{GOV\_DE}    & Real government consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P3\_S13.\allowbreak DE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{EXP\_DE}    & Real exports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P6.\allowbreak DE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{IMP\_DE}    & Real imports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P7.\allowbreak DE} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{HICP\_DE}   & HICP index (all-items, 2015=100) & Eurostat & \texttt{prc\_hicp\_midx M.\allowbreak I15.\allowbreak CP00.\allowbreak DE} & M$\to$Q avg & log & masked 20Q1--Q4 & domestic \\
\texttt{LR\_DE}     & Unemployment rate (SA, \% active pop.) & Eurostat & \texttt{une\_rt\_q Q.\allowbreak SA.\allowbreak TOTAL.\allowbreak PC\_ACT.\allowbreak T.\allowbreak DE} & Q & lin & masked 20Q1--Q4 & domestic \\
\texttt{HPI\_DE}    & Real house-price index (nominal HPI$/$HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q Q.\allowbreak TOTAL.\allowbreak I15\_Q.\allowbreak DE} $\div$ HICP & Q & log & observed (financial) & domestic \\
\texttt{NEER\_DE}   & Nominal effective exchange rate, IC42 partners & Eurostat & \texttt{ert\_eff\_ic\_q Q.\allowbreak NEER\_IC42.\allowbreak I15.\allowbreak DE} & Q & log & observed & domestic \\
\texttt{YIELD10\_DE}& 10Y Bund yield (the spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & \textbf{domestic} (DE special case; no SPREAD\_DE) \\
\texttt{POLRATE\_DE}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM/D.\allowbreak U2.\allowbreak EUR.4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV} & D$\to$Q avg & lin & observed & external (shared) \\
\texttt{EACORP}     & EA corporate bond yield (non-MFI) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q avg & lin & observed & external \\
\texttt{RATE\_DE}   & 3-month EURIBOR & Eurostat & \texttt{irt\_st\_q Q.\allowbreak IRT\_M3.\allowbreak EA} & Q & lin & observed & external (shared) \\
\texttt{ROWEA\_GDP\_DE}  & Rest-of-EA real GDP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less DE, \texttt{namq\_10\_gdp} & Q & log & masked 20Q1--Q4 & row \\
\texttt{ROWEA\_HICP\_DE} & Rest-of-EA HICP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less DE, \texttt{prc\_hicp\_midx} & Q & log & masked 20Q1--Q4 & row \\
\texttt{FREV\_GDP}  & General-gov. revenue (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak DE} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{FPEXP\_GDP} & Primary expenditure (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa ...\allowbreak TE $-$ ...\allowbreak D41PAY .\allowbreak DE} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{EFFI}       & Effective interest rate on gov. debt & Eurostat (computed) & \texttt{...D41PAY} $/$ \texttt{gov\_10q\_ggdebt ...\allowbreak GD.\allowbreak DE} & Q & lin & observed & fiscal; financial \\
\texttt{SFA}        & Stock-flow adjustment (budget-identity residual) & Eurostat (computed) & debt-recursion residual & Q & lin & masked 20Q1--Q4 & fiscal; WN \\
\texttt{CREDIT\_GDP\_DE} & \textbf{[NEW]} BIS total credit to NFCs, \% of GDP (broad) & BIS via FRED & \texttt{QDENAM770A} & Q & lin & masked 20Q2--Q4 & domestic; src 1990Q1:59.5..\allowbreak 2025Q4:87.8 \\
\texttt{LENDR\_DE}  & \textbf{[NEW]} NFC new-business bank lending rate & ECB MIR & \texttt{M.\allowbreak DE.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N} & M$\to$Q avg & lin & observed & domestic; src 2000Q1:5.85..\allowbreak 2026Q2:3.55 \\
\end{longtable}

% ----------------------------------------------------------------------------
\subsection{France (FR)}
\label{sec:data:FR}

A 23-variable single-country BVAR estimated over \textbf{2003Q1--2025Q4}
($T=92$) --- the longest euro-core sample (the others start 2009Q1).
COVID-as-missing: macro block masked 2020Q1--Q4, credit quantity masked
2020Q2--Q4, financials observed.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.135\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.085\textwidth}@{}}
\caption{France (FR) --- variable documentation.}\label{tab:data:FR}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Table~\ref{tab:data:FR} (France), continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\small\itshape continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_FR}    & Real GDP (chain-linked vol., SCA) & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak FR} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{CONS\_FR}   & Real household final consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P31\_S14\_S15.\allowbreak FR} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{INV\_FR}    & Real gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P51G.\allowbreak FR} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{GOV\_FR}    & Real government consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P3\_S13.\allowbreak FR} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{EXP\_FR}    & Real exports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P6.\allowbreak FR} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{IMP\_FR}    & Real imports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P7.\allowbreak FR} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{HICP\_FR}   & HICP index (all-items, 2015=100) & Eurostat & \texttt{prc\_hicp\_midx M.\allowbreak I15.\allowbreak CP00.\allowbreak FR} & M$\to$Q avg & log & masked 20Q1--Q4 & domestic \\
\texttt{LR\_FR}     & Unemployment rate (SA, \% active pop.) & Eurostat & \texttt{une\_rt\_q Q.\allowbreak SA.\allowbreak TOTAL.\allowbreak PC\_ACT.\allowbreak T.\allowbreak FR} & Q & lin & masked 20Q1--Q4 & domestic \\
\texttt{HPI\_FR}    & Real house-price index (nominal HPI$/$HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q Q.\allowbreak TOTAL.\allowbreak I15\_Q.\allowbreak FR} $\div$ HICP & Q & log & observed (financial) & domestic \\
\texttt{NEER\_FR}   & Nominal effective exchange rate, IC42 partners & Eurostat & \texttt{ert\_eff\_ic\_q Q.\allowbreak NEER\_IC42.\allowbreak I15.\allowbreak FR} & Q & log & observed & domestic \\
\texttt{SPREAD\_FR} & 10Y sovereign spread vs Bund & Eurostat (computed) & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak FR} $-$ \texttt{M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & domestic \\
\texttt{POLRATE\_FR}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM/D.\allowbreak U2.\allowbreak EUR.4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV} & D$\to$Q avg & lin & observed & external (shared) \\
\texttt{EACORP}     & EA corporate bond yield (non-MFI) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q avg & lin & observed & external \\
\texttt{RATE\_FR}   & 3-month EURIBOR & Eurostat & \texttt{irt\_st\_q Q.\allowbreak IRT\_M3.\allowbreak EA} & Q & lin & observed & external (shared) \\
\texttt{YIELD10\_DE}& DE 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & external (injected) \\
\texttt{ROWEA\_GDP\_FR}  & Rest-of-EA real GDP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less FR, \texttt{namq\_10\_gdp} & Q & log & masked 20Q1--Q4 & row \\
\texttt{ROWEA\_HICP\_FR} & Rest-of-EA HICP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less FR, \texttt{prc\_hicp\_midx} & Q & log & masked 20Q1--Q4 & row \\
\texttt{FREV\_GDP}  & General-gov. revenue (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak FR} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{FPEXP\_GDP} & Primary expenditure (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa ...\allowbreak TE $-$ ...\allowbreak D41PAY .\allowbreak FR} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{EFFI}       & Effective interest rate on gov. debt & Eurostat (computed) & \texttt{...D41PAY} $/$ \texttt{gov\_10q\_ggdebt ...\allowbreak GD.\allowbreak FR} & Q & lin & observed & fiscal; financial \\
\texttt{SFA}        & Stock-flow adjustment (budget-identity residual) & Eurostat (computed) & debt-recursion residual & Q & lin & masked 20Q1--Q4 & fiscal; WN \\
\texttt{CREDIT\_GDP\_FR} & \textbf{[NEW]} BIS total credit to NFCs, \% of GDP (broad: loans+bonds+cross-border) & BIS via FRED & \texttt{QFRNAM770A} & Q & lin & masked 20Q2--Q4 & domestic; src 1990Q1:90.8..\allowbreak 2025Q4:155.8. Broad BIS measure \emph{includes} France's large bond-financed NFC debt (the bank-loans-only alternative was \emph{not} used) \\
\texttt{LENDR\_FR}  & \textbf{[NEW]} NFC new-business bank lending rate & ECB MIR & \texttt{M.\allowbreak FR.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N} & M$\to$Q avg & lin & observed & domestic; src 2000Q1:4.01..\allowbreak 2026Q2:3.56 \\
\end{longtable}

% ----------------------------------------------------------------------------
\subsection{Netherlands (NL)}
\label{sec:data:NL}

A 23-variable single-country BVAR estimated over \textbf{2009Q1--2025Q4}
($T=68$). COVID-as-missing: macro block masked 2020Q1--Q4, credit quantity
masked 2020Q2--Q4, financials observed.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.135\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.085\textwidth}@{}}
\caption{Netherlands (NL) --- variable documentation.}\label{tab:data:NL}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Table~\ref{tab:data:NL} (Netherlands), continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID/key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\small\itshape continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_NL}    & Real GDP (chain-linked vol., SCA) & Eurostat & \texttt{namq\_10\_gdp Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak NL} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{CONS\_NL}   & Real household final consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P31\_S14\_S15.\allowbreak NL} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{INV\_NL}    & Real gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P51G.\allowbreak NL} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{GOV\_NL}    & Real government consumption & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P3\_S13.\allowbreak NL} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{EXP\_NL}    & Real exports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P6.\allowbreak NL} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{IMP\_NL}    & Real imports & Eurostat & \texttt{namq\_10\_gdp ...\allowbreak P7.\allowbreak NL} & Q & log & masked 20Q1--Q4 & domestic \\
\texttt{HICP\_NL}   & HICP index (all-items, 2015=100) & Eurostat & \texttt{prc\_hicp\_midx M.\allowbreak I15.\allowbreak CP00.\allowbreak NL} & M$\to$Q avg & log & masked 20Q1--Q4 & domestic \\
\texttt{LR\_NL}     & Unemployment rate (SA, \% active pop.) & Eurostat & \texttt{une\_rt\_q Q.\allowbreak SA.\allowbreak TOTAL.\allowbreak PC\_ACT.\allowbreak T.\allowbreak NL} & Q & lin & masked 20Q1--Q4 & domestic \\
\texttt{HPI\_NL}    & Real house-price index (nominal HPI$/$HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q Q.\allowbreak TOTAL.\allowbreak I15\_Q.\allowbreak NL} $\div$ HICP & Q & log & observed (financial) & domestic \\
\texttt{NEER\_NL}   & Nominal effective exchange rate, IC42 partners & Eurostat & \texttt{ert\_eff\_ic\_q Q.\allowbreak NEER\_IC42.\allowbreak I15.\allowbreak NL} & Q & log & observed & domestic \\
\texttt{SPREAD\_NL} & 10Y sovereign spread vs Bund & Eurostat (computed) & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak NL} $-$ \texttt{M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & domestic \\
\texttt{POLRATE\_NL}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM/D.\allowbreak U2.\allowbreak EUR.4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV} & D$\to$Q avg & lin & observed & external (shared) \\
\texttt{EACORP}     & EA corporate bond yield (non-MFI) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q avg & lin & observed & external \\
\texttt{RATE\_NL}   & 3-month EURIBOR & Eurostat & \texttt{irt\_st\_q Q.\allowbreak IRT\_M3.\allowbreak EA} & Q & lin & observed & external (shared) \\
\texttt{YIELD10\_DE}& DE 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m M.\allowbreak MCBY.\allowbreak DE} & M$\to$Q avg & lin & observed & external (injected) \\
\texttt{ROWEA\_GDP\_NL}  & Rest-of-EA real GDP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less NL, \texttt{namq\_10\_gdp} & Q & log & masked 20Q1--Q4 & row \\
\texttt{ROWEA\_HICP\_NL} & Rest-of-EA HICP (GDP-weighted de-agg.) & Eurostat (computed) & EA20 less NL, \texttt{prc\_hicp\_midx} & Q & log & masked 20Q1--Q4 & row \\
\texttt{FREV\_GDP}  & General-gov. revenue (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak NL} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{FPEXP\_GDP} & Primary expenditure (\% GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa ...\allowbreak TE $-$ ...\allowbreak D41PAY .\allowbreak NL} & Q & lin & observed (forward-filled) & fiscal; WN \\
\texttt{EFFI}       & Effective interest rate on gov. debt & Eurostat (computed) & \texttt{...D41PAY} $/$ \texttt{gov\_10q\_ggdebt ...\allowbreak GD.\allowbreak NL} & Q & lin & observed & fiscal; financial \\
\texttt{SFA}        & Stock-flow adjustment (budget-identity residual) & Eurostat (computed) & debt-recursion residual & Q & lin & masked 20Q1--Q4 & fiscal; WN \\
\texttt{CREDIT\_GDP\_NL} & \textbf{[NEW]} BIS total credit to NFCs, \% of GDP (broad) & BIS via FRED & \texttt{QNLNAM770A} & Q & lin & masked 20Q2--Q4 & domestic; src 1990Q4:152.6..\allowbreak 2025Q4:166.3 \\
\texttt{LENDR\_NL}  & \textbf{[NEW]} NFC new-business bank lending rate & ECB MIR & \texttt{M.\allowbreak NL.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N} & M$\to$Q avg & lin & observed & domestic; src 2000Q1:6.17..\allowbreak 2026Q2:3.37 \\
\end{longtable}

% --- 2b. Euro-periphery (ES, IT, IE, PT, GR) ---
\subsection{Euro-area periphery: data conventions (ES, IT, IE, PT, GR)}\label{sec:data:euro-periph}
%% ===================================================================
%% Per-country DATA documentation: euro-area periphery
%%   ES (Spain), IT (Italy), IE (Ireland), PT (Portugal), GR (Greece)
%%
%% Style: matches docs/user_manual.tex (booktabs + longtable loaded).
%% Generated for the "Data" section of the Bayesian GVAR manual.
%%
%% Authoritative variable list / transformation / isFinancial / block:
%%   pipeline/euro_redesign_staging/<CC>/spec.json  (== pipeline/credit_staging/<CC>/spec.json)
%% Macro / financial / fiscal sources traced from:
%%   pipeline/build_euro_member_redesign.py  (calls build_oecd_eurostat.py
%%   + build_euro_financial_block.py + the build_fiscal_ea_4var.py recipe)
%% Credit block (CREDIT_GDP_<CC>, LENDR_<CC>) traced from:
%%   pipeline/build_credit_euro_periph.py + pipeline/fetch_ecb_mir.py
%% ===================================================================

%% --- Transformation / COVID conventions (shared text; cite once at the
%%     top of the periphery group, repeated here for a self-contained file). ---
\paragraph{Transformation and COVID conventions (all five blocs).}
Two transformation codes appear in the staged specs. \texttt{log} denotes
$100\cdot\log(\text{level})$; because the VAR enters in (annualised) growth
space, a \texttt{log} variable contributes $4\cdot\Delta[100\log]$, i.e.\ the
quarter-on-quarter \emph{annualised} growth rate. \texttt{lin} denotes the raw
level (rates in \% p.a., ratios in \% of GDP, spreads in percentage points,
indices in points). COVID-as-missing masks every \emph{macro} column
($\texttt{isFinancial}=0$) over the fixed window 2020Q2--Q4 (set to JSON
\texttt{null}/\texttt{NaN} and imputed inside the Durbin--Koopman E-step);
financial columns ($\texttt{isFinancial}=1$) are kept observed throughout.
All five blocs are estimated on a common 2009Q1--2025Q4 quarterly grid
($T=68$), $p=3$ lags, with the hierarchical (GLP) Minnesota prior; per-variable
own-lag prior means are random walk (\texttt{RW}) except the three fiscal
white-noise variables (\texttt{WN}: \texttt{FREV\_GDP}, \texttt{FPEXP\_GDP},
\texttt{SFA}).

\medskip
\noindent\textbf{New credit block (flagged).} Each periphery bloc gains two
new domestic financial variables, appended after the redesign vars by
\texttt{build\_credit\_euro\_periph.py}:
\begin{itemize}[nosep]
  \item \textbf{Quantity} \texttt{CREDIT\_GDP\_<CC>} --- BIS ``Total Credit to
    Non-Financial Corporations, \% of GDP'' (the \emph{broad} credit measure:
    bank loans \emph{plus} debt securities \emph{plus} cross-border lending),
    pulled from FRED under the mnemonic \texttt{Q<CC>NAM770A}. Native
    quarterly, \texttt{lin}, \texttt{RW}, \texttt{isFinancial}. Despite being a
    financial series it is COVID-masked over 2020Q2--Q4 because it
    \emph{inherits the GDP-denominator collapse} (a ratio whose denominator is
    a masked macro flow).
  \item \textbf{Price} \texttt{LENDR\_<CC>} --- ECB MIR (MFI Interest Rate
    statistics) NFC bank lending rate, monthly $\to$ quarter by simple
    month-average, \texttt{lin}, \texttt{RW}, \texttt{isFinancial}, kept
    observed through COVID (financial-observed rule).
\end{itemize}
\textit{[FLAG: the research scoping report (\texttt{wrqpqko5z}) recommended an
ECB BSI MFI ``loans-to-NFC'' \emph{stock} (\texttt{BSI/M.<CC>.\allowbreak N.\allowbreak A.\allowbreak A20.\allowbreak A.1.\dots})
as the quantity series. The shipped builder instead uses the BIS broad
Total-Credit-to-NFCs \%-of-GDP series via FRED (\texttt{Q<CC>NAM770A}), which is
the convention the task brief and the build audit confirm. The staged data are
authoritative; the BSI recommendation was superseded.]}

\textit{[FLAG: GR \texttt{LENDR\_GR} is a non-canonical MIR variant. The
standard composite cost-of-borrowing key \texttt{M.\allowbreak GR.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N}
is sparse for Greece (only $\approx$54 obs, with $\approx$29 internal gaps over
the 2010--2016 crisis years), so the builder substitutes the fully dense
new-business floating-rate / IRF-up-to-1yr variant
\texttt{M.\allowbreak GR.\allowbreak B.\allowbreak A2A.\allowbreak F.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N}. Its definition differs from the A2A
composite used by the other four periphery members --- reduced cross-economy
comparability of the price-of-credit variable.]}

\textit{[FLAG: all five periphery \texttt{DataRaw\_<CC>\_glob.json} bases store
the COVID-masked macro cells as bare \texttt{NaN} literals (a MATLAB
\texttt{jsondecode} convention inherited from \texttt{euro\_redesign\_staging}),
which fail a strict \texttt{JSON.parse}; the appended credit cells correctly use
\texttt{null}. This is a pre-existing format quirk, not a data error.]}

%% ===================================================================
\subsection{Spain (ES)}\label{sec:data:ES}

A 23-variable single-country bloc (10 domestic macro/financial + 1 sovereign
spread, 4 external exogenous, 2 rest-of-EA, 4 fiscal, 2 credit), estimated on
2009Q1--2025Q4 ($T=68$, $p=3$) with COVID-as-missing over 2020Q2--Q4 (macro
masked, financials observed). The credit quantity (\texttt{QESNAM770A}) shows a
large post-2008 boom-bust cycle (peak $\approx$148\% of GDP, falling to
$\approx$77\% by 2025Q4); the log-level RW absorbs the trend.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.155\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.10\textwidth}@{}}
\caption{Spain (ES) --- variable documentation. $n=23$, 2009Q1--2025Q4.}
\label{tab:data:ES}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{c}{\tablename~\thetable\ -- continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\footnotesize continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_ES}   & Real GDP (chain-vol, SCA) & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak ES & Q & log & masked & domestic \\
\texttt{CONS\_ES}  & Household + NPISH final cons. & Eurostat & \texttt{namq\_10\_gdp} \dots P31\_S14\_S15.ES & Q & log & masked & domestic \\
\texttt{INV\_ES}   & Gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp} \dots P51G.ES & Q & log & masked & domestic \\
\texttt{GOV\_ES}   & Government final consumption & Eurostat & \texttt{namq\_10\_gdp} \dots P3\_S13.ES & Q & log & masked & domestic \\
\texttt{EXP\_ES}   & Exports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P6.ES & Q & log & masked & domestic \\
\texttt{IMP\_ES}   & Imports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P7.ES & Q & log & masked & domestic \\
\texttt{HICP\_ES}  & HICP, all-items index (2015=100) & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.ES & M$\to$Q & log & masked & domestic; m$\to$q avg \\
\texttt{LR\_ES}    & Unemployment rate (SA, total) & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.ES & Q & lin & masked & domestic; \% of labour force \\
\texttt{HPI\_ES}   & Real house-price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.ES, deflated by \texttt{HICP\_ES} & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{NEER\_ES}  & Nominal effective FX (IC42 partners, 2015=100) & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.ES & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{SPREAD\_ES}& 10Y sovereign spread vs Bund (pp) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.ES $-$ M.MCBY.DE & M$\to$Q & lin & observed & domestic; Maastricht 10Y \\
\texttt{POLRATE\_ES}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV & D$\to$Q & lin & observed & external; \% p.a. \\
\texttt{EACORP}    & EA corporate bond yield (\%) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q & lin & observed & external \\
\texttt{RATE\_ES}  & 3-month EURIBOR (\%) & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA & Q & lin & observed & external; EA-wide 3M \\
\texttt{YIELD10\_DE}& German 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE & M$\to$Q & lin & observed & external \\
\texttt{ROWEA\_GDP\_ES}  & Rest-of-EA real GDP (GDP-wtd ex-ES) & Eurostat (derived) & EA20 \texttt{namq\_10\_gdp} de-aggregated by ES weight & Q & log & masked & row; index 2015=100 \\
\texttt{ROWEA\_HICP\_ES} & Rest-of-EA HICP (GDP-wtd ex-ES) & Eurostat (derived) & EA20 \texttt{prc\_hicp\_midx} de-aggregated by ES weight & M$\to$Q & log & masked & row; index 2015=100 \\
\texttt{FREV\_GDP} & General-gov't revenue (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak ES / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{FPEXP\_GDP}& Primary expenditure (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY, S13.ES / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{EFFI}      & Effective interest rate on debt (\%) & Eurostat & $4\cdot$D41PAY$_t$/debt$_{t-1}$, \texttt{gov\_10q\_ggnfa}/\texttt{ggdebt}.ES & Q & lin & observed & fiscal; \texttt{isFin}=1 \\
\texttt{SFA}       & Stock-flow adjustment (\% of GDP) & Eurostat (derived) & debt-identity residual from \texttt{ggdebt}.ES & Q & lin & masked & fiscal; \texttt{WN}; COVID-NaN'd \\
\texttt{CREDIT\_GDP\_ES} & BIS Total Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QESNAM770A} & Q & lin & masked & domestic; \texttt{isFin}=1; broad credit; GDP-denom mask \\
\texttt{LENDR\_ES} & NFC bank lending rate (ECB MIR composite, \%) & ECB Data Portal & \texttt{MIR} M.\allowbreak ES.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed & domestic; \texttt{isFin}=1; new business \\
\end{longtable}

\noindent\textit{[FLAG: \texttt{EACORP} is shared across euro members and labelled
``EA IG Corporate Bond Yield'' in the spec, but the underlying ECB series
(\texttt{YC/B.\allowbreak U2.\allowbreak EUR.4F.\allowbreak G\_N\_C.\allowbreak SV\_C\_YM.\allowbreak SR\_10Y}) is the euro-area
all-bonds/AAA 10Y \emph{government} yield-curve point, not an investment-grade
corporate index. The id name overstates the credit content; the series itself is
correctly traced.]}
Credit-block coverage (ES): \texttt{CREDIT\_GDP\_ES} 65/68 obs (2009Q1=141.3 \%,
2025Q4=76.5 \%, range 76.5--148.2), 2020Q2--Q4 \texttt{null}; \texttt{LENDR\_ES}
68/68 obs (2009Q1=3.63 \%, 2025Q4=3.27 \%, COVID observed 1.57--1.70 \%).

%% ===================================================================
\subsection{Italy (IT)}\label{sec:data:IT}

A 23-variable bloc with the identical structure to Spain (10 domestic + spread,
4 external, 2 rest-of-EA, 4 fiscal, 2 credit), estimated on 2009Q1--2025Q4
($T=68$, $p=3$), COVID-masked 2020Q2--Q4. The Italian sovereign spread and the
own MIR lending rate both carry the periphery fragmentation premium that the
shared \texttt{EACORP} benchmark misses.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.155\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.10\textwidth}@{}}
\caption{Italy (IT) --- variable documentation. $n=23$, 2009Q1--2025Q4.}
\label{tab:data:IT}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{c}{\tablename~\thetable\ -- continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\footnotesize continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_IT}   & Real GDP (chain-vol, SCA) & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak IT & Q & log & masked & domestic \\
\texttt{CONS\_IT}  & Household + NPISH final cons. & Eurostat & \texttt{namq\_10\_gdp} \dots P31\_S14\_S15.IT & Q & log & masked & domestic \\
\texttt{INV\_IT}   & Gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp} \dots P51G.IT & Q & log & masked & domestic \\
\texttt{GOV\_IT}   & Government final consumption & Eurostat & \texttt{namq\_10\_gdp} \dots P3\_S13.IT & Q & log & masked & domestic \\
\texttt{EXP\_IT}   & Exports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P6.IT & Q & log & masked & domestic \\
\texttt{IMP\_IT}   & Imports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P7.IT & Q & log & masked & domestic \\
\texttt{HICP\_IT}  & HICP, all-items index (2015=100) & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.IT & M$\to$Q & log & masked & domestic; m$\to$q avg \\
\texttt{LR\_IT}    & Unemployment rate (SA, total) & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.IT & Q & lin & masked & domestic; \% of labour force \\
\texttt{HPI\_IT}   & Real house-price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.IT, deflated by \texttt{HICP\_IT} & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{NEER\_IT}  & Nominal effective FX (IC42 partners, 2015=100) & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.IT & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{SPREAD\_IT}& 10Y sovereign spread vs Bund (pp) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.IT $-$ M.MCBY.DE & M$\to$Q & lin & observed & domestic; Maastricht 10Y \\
\texttt{POLRATE\_IT}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV & D$\to$Q & lin & observed & external; \% p.a. \\
\texttt{EACORP}    & EA corporate bond yield (\%) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q & lin & observed & external \\
\texttt{RATE\_IT}  & 3-month EURIBOR (\%) & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA & Q & lin & observed & external; EA-wide 3M \\
\texttt{YIELD10\_DE}& German 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE & M$\to$Q & lin & observed & external \\
\texttt{ROWEA\_GDP\_IT}  & Rest-of-EA real GDP (GDP-wtd ex-IT) & Eurostat (derived) & EA20 \texttt{namq\_10\_gdp} de-aggregated by IT weight & Q & log & masked & row; index 2015=100 \\
\texttt{ROWEA\_HICP\_IT} & Rest-of-EA HICP (GDP-wtd ex-IT) & Eurostat (derived) & EA20 \texttt{prc\_hicp\_midx} de-aggregated by IT weight & M$\to$Q & log & masked & row; index 2015=100 \\
\texttt{FREV\_GDP} & General-gov't revenue (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak IT / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{FPEXP\_GDP}& Primary expenditure (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY, S13.IT / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{EFFI}      & Effective interest rate on debt (\%) & Eurostat & $4\cdot$D41PAY$_t$/debt$_{t-1}$, \texttt{gov\_10q\_ggnfa}/\texttt{ggdebt}.IT & Q & lin & observed & fiscal; \texttt{isFin}=1 \\
\texttt{SFA}       & Stock-flow adjustment (\% of GDP) & Eurostat (derived) & debt-identity residual from \texttt{ggdebt}.IT & Q & lin & masked & fiscal; \texttt{WN}; COVID-NaN'd \\
\texttt{CREDIT\_GDP\_IT} & BIS Total Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QITNAM770A} & Q & lin & masked & domestic; \texttt{isFin}=1; broad credit; GDP-denom mask \\
\texttt{LENDR\_IT} & NFC bank lending rate (ECB MIR composite, \%) & ECB Data Portal & \texttt{MIR} M.\allowbreak IT.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed & domestic; \texttt{isFin}=1; new business \\
\end{longtable}

\noindent Credit-block coverage (IT): \texttt{CREDIT\_GDP\_IT} 65/68 obs
(2009Q1=78.7 \%, 2025Q4=58.5 \%, range 58.4--81.6), 2020Q2--Q4 \texttt{null};
\texttt{LENDR\_IT} 68/68 obs (2009Q1=3.47 \%, 2025Q4=3.55 \%, COVID observed
1.18--1.33 \%). The \texttt{EACORP} naming caveat (ES table) applies identically.

%% ===================================================================
\subsection{Ireland (IE)}\label{sec:data:IE}

A 23-variable bloc, same template, 2009Q1--2025Q4 ($T=68$, $p=3$), COVID-masked
2020Q2--Q4. Two Irish-specific data caveats are worth noting: the chain-volume
GDP aggregate is distorted by multinational balance-sheet relocation (the
``modified'' domestic-demand concept is the cleaner activity gauge but is not
the Eurostat \texttt{B1GQ} used here), and the BIS credit-to-GDP series exhibits
a very large boom-bust path.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.155\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.10\textwidth}@{}}
\caption{Ireland (IE) --- variable documentation. $n=23$, 2009Q1--2025Q4.}
\label{tab:data:IE}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{c}{\tablename~\thetable\ -- continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\footnotesize continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_IE}   & Real GDP (chain-vol, SCA) & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak IE & Q & log & masked & domestic; MNC-distorted \\
\texttt{CONS\_IE}  & Household + NPISH final cons. & Eurostat & \texttt{namq\_10\_gdp} \dots P31\_S14\_S15.IE & Q & log & masked & domestic \\
\texttt{INV\_IE}   & Gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp} \dots P51G.IE & Q & log & masked & domestic; MNC-volatile \\
\texttt{GOV\_IE}   & Government final consumption & Eurostat & \texttt{namq\_10\_gdp} \dots P3\_S13.IE & Q & log & masked & domestic \\
\texttt{EXP\_IE}   & Exports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P6.IE & Q & log & masked & domestic; MNC-volatile \\
\texttt{IMP\_IE}   & Imports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P7.IE & Q & log & masked & domestic \\
\texttt{HICP\_IE}  & HICP, all-items index (2015=100) & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.IE & M$\to$Q & log & masked & domestic; m$\to$q avg \\
\texttt{LR\_IE}    & Unemployment rate (SA, total) & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.IE & Q & lin & masked & domestic; \% of labour force \\
\texttt{HPI\_IE}   & Real house-price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.IE, deflated by \texttt{HICP\_IE} & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{NEER\_IE}  & Nominal effective FX (IC42 partners, 2015=100) & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.IE & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{SPREAD\_IE}& 10Y sovereign spread vs Bund (pp) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.IE $-$ M.MCBY.DE & M$\to$Q & lin & observed & domestic; Maastricht 10Y \\
\texttt{POLRATE\_IE}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV & D$\to$Q & lin & observed & external; \% p.a. \\
\texttt{EACORP}    & EA corporate bond yield (\%) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q & lin & observed & external \\
\texttt{RATE\_IE}  & 3-month EURIBOR (\%) & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA & Q & lin & observed & external; EA-wide 3M \\
\texttt{YIELD10\_DE}& German 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE & M$\to$Q & lin & observed & external \\
\texttt{ROWEA\_GDP\_IE}  & Rest-of-EA real GDP (GDP-wtd ex-IE) & Eurostat (derived) & EA20 \texttt{namq\_10\_gdp} de-aggregated by IE weight & Q & log & masked & row; index 2015=100 \\
\texttt{ROWEA\_HICP\_IE} & Rest-of-EA HICP (GDP-wtd ex-IE) & Eurostat (derived) & EA20 \texttt{prc\_hicp\_midx} de-aggregated by IE weight & M$\to$Q & log & masked & row; index 2015=100 \\
\texttt{FREV\_GDP} & General-gov't revenue (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak IE / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{FPEXP\_GDP}& Primary expenditure (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY, S13.IE / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{EFFI}      & Effective interest rate on debt (\%) & Eurostat & $4\cdot$D41PAY$_t$/debt$_{t-1}$, \texttt{gov\_10q\_ggnfa}/\texttt{ggdebt}.IE & Q & lin & observed & fiscal; \texttt{isFin}=1 \\
\texttt{SFA}       & Stock-flow adjustment (\% of GDP) & Eurostat (derived) & debt-identity residual from \texttt{ggdebt}.IE & Q & lin & masked & fiscal; \texttt{WN}; COVID-NaN'd \\
\texttt{CREDIT\_GDP\_IE} & BIS Total Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QIENAM770A} & Q & lin & masked & domestic; \texttt{isFin}=1; broad credit; severe boom-bust \\
\texttt{LENDR\_IE} & NFC bank lending rate (ECB MIR composite, \%) & ECB Data Portal & \texttt{MIR} M.\allowbreak IE.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed & domestic; \texttt{isFin}=1; new business \\
\end{longtable}

\noindent\textit{[FLAG: \texttt{CREDIT\_GDP\_IE} has an extreme boom-bust path
($\approx$305\% of GDP near 2009/2010 collapsing to $\approx$92\% by 2025Q4 ---
property-bubble deleveraging, NAMA asset transfers, bank wind-downs and
multinational reclassification). It is the most volatile credit-quantity series
of the periphery group; the BIS broad measure and the log-level RW absorb the
trend, but the path is non-stationary in level. The research report recommended
considering a post-2014 start or growth-rate space; the shipped build uses the
full sample.]}
Credit-block coverage (IE): \texttt{CREDIT\_GDP\_IE} 65/68 obs (2009Q1=177.3 \%,
2025Q4=92.4 \%, range 92.4--305.8), 2020Q2--Q4 \texttt{null}; \texttt{LENDR\_IE}
68/68 obs (2009Q1=4.10 \%, 2025Q4=4.67 \%, COVID observed 2.32--2.81 \%). The
\texttt{EACORP} naming caveat (ES table) applies.

%% ===================================================================
\subsection{Portugal (PT)}\label{sec:data:PT}

A 23-variable bloc, same template, 2009Q1--2025Q4 ($T=68$, $p=3$), COVID-masked
2020Q2--Q4. Portuguese bank lending rates carry a clear sovereign-stress /
fragmentation premium over the 2009--2012 crisis years (own \texttt{LENDR\_PT}
peaks near 6.7\%), which the shared \texttt{EACORP} benchmark does not capture.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.155\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.10\textwidth}@{}}
\caption{Portugal (PT) --- variable documentation. $n=23$, 2009Q1--2025Q4.}
\label{tab:data:PT}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{c}{\tablename~\thetable\ -- continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\footnotesize continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_PT}   & Real GDP (chain-vol, SCA) & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak PT & Q & log & masked & domestic \\
\texttt{CONS\_PT}  & Household + NPISH final cons. & Eurostat & \texttt{namq\_10\_gdp} \dots P31\_S14\_S15.PT & Q & log & masked & domestic \\
\texttt{INV\_PT}   & Gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp} \dots P51G.PT & Q & log & masked & domestic \\
\texttt{GOV\_PT}   & Government final consumption & Eurostat & \texttt{namq\_10\_gdp} \dots P3\_S13.PT & Q & log & masked & domestic \\
\texttt{EXP\_PT}   & Exports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P6.PT & Q & log & masked & domestic \\
\texttt{IMP\_PT}   & Imports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P7.PT & Q & log & masked & domestic \\
\texttt{HICP\_PT}  & HICP, all-items index (2015=100) & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.PT & M$\to$Q & log & masked & domestic; m$\to$q avg \\
\texttt{LR\_PT}    & Unemployment rate (SA, total) & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.PT & Q & lin & masked & domestic; \% of labour force \\
\texttt{HPI\_PT}   & Real house-price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.PT, deflated by \texttt{HICP\_PT} & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{NEER\_PT}  & Nominal effective FX (IC42 partners, 2015=100) & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.PT & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{SPREAD\_PT}& 10Y sovereign spread vs Bund (pp) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.PT $-$ M.MCBY.DE & M$\to$Q & lin & observed & domestic; Maastricht 10Y \\
\texttt{POLRATE\_PT}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV & D$\to$Q & lin & observed & external; \% p.a. \\
\texttt{EACORP}    & EA corporate bond yield (\%) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q & lin & observed & external \\
\texttt{RATE\_PT}  & 3-month EURIBOR (\%) & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA & Q & lin & observed & external; EA-wide 3M \\
\texttt{YIELD10\_DE}& German 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE & M$\to$Q & lin & observed & external \\
\texttt{ROWEA\_GDP\_PT}  & Rest-of-EA real GDP (GDP-wtd ex-PT) & Eurostat (derived) & EA20 \texttt{namq\_10\_gdp} de-aggregated by PT weight & Q & log & masked & row; index 2015=100 \\
\texttt{ROWEA\_HICP\_PT} & Rest-of-EA HICP (GDP-wtd ex-PT) & Eurostat (derived) & EA20 \texttt{prc\_hicp\_midx} de-aggregated by PT weight & M$\to$Q & log & masked & row; index 2015=100 \\
\texttt{FREV\_GDP} & General-gov't revenue (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak PT / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{FPEXP\_GDP}& Primary expenditure (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY, S13.PT / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{EFFI}      & Effective interest rate on debt (\%) & Eurostat & $4\cdot$D41PAY$_t$/debt$_{t-1}$, \texttt{gov\_10q\_ggnfa}/\texttt{ggdebt}.PT & Q & lin & observed & fiscal; \texttt{isFin}=1 \\
\texttt{SFA}       & Stock-flow adjustment (\% of GDP) & Eurostat (derived) & debt-identity residual from \texttt{ggdebt}.PT & Q & lin & masked & fiscal; \texttt{WN}; COVID-NaN'd \\
\texttt{CREDIT\_GDP\_PT} & BIS Total Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QPTNAM770A} & Q & lin & masked & domestic; \texttt{isFin}=1; broad credit; GDP-denom mask \\
\texttt{LENDR\_PT} & NFC bank lending rate (ECB MIR composite, \%) & ECB Data Portal & \texttt{MIR} M.\allowbreak PT.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed & domestic; \texttt{isFin}=1; new business \\
\end{longtable}

\noindent Credit-block coverage (PT): \texttt{CREDIT\_GDP\_PT} 65/68 obs
(2009Q1=121.7 \%, 2025Q4=74.2 \%, range 74.2--140.9), 2020Q2--Q4 \texttt{null};
\texttt{LENDR\_PT} 68/68 obs (2009Q1=5.62 \%, 2025Q4=3.67 \%, COVID observed
1.82--2.05 \%). The \texttt{EACORP} naming caveat (ES table) applies.

%% ===================================================================
\subsection{Greece (GR)}\label{sec:data:GR}

A \textbf{22-variable} bloc --- one fewer than the other four because
\texttt{HPI\_GR} is dropped (no Eurostat \texttt{prc\_hpi\_q} house-price index
is published for Greece). The structure is otherwise the periphery template (9
domestic + spread, 4 external, 2 rest-of-EA, 4 fiscal, 2 credit), estimated on
2009Q1--2025Q4 ($T=68$, $p=3$), COVID-masked 2020Q2--Q4. All Eurostat keys use
the Greece geo code \texttt{EL}.

\begin{longtable}{@{}p{0.135\textwidth}p{0.205\textwidth}p{0.085\textwidth}p{0.155\textwidth}p{0.035\textwidth}p{0.075\textwidth}p{0.085\textwidth}p{0.10\textwidth}@{}}
\caption{Greece (GR) --- variable documentation. $n=22$ (no HPI), 2009Q1--2025Q4.}
\label{tab:data:GR}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endfirsthead
\multicolumn{8}{c}{\tablename~\thetable\ -- continued}\\
\toprule
\textbf{Variable} (id) & Description & Source & Series ID / key & Freq & Transf. & COVID & Notes \\
\midrule
\endhead
\midrule \multicolumn{8}{r}{\footnotesize continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\texttt{GDP\_GR}   & Real GDP (chain-vol, SCA) & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak EL & Q & log & masked & domestic; geo=EL \\
\texttt{CONS\_GR}  & Household + NPISH final cons. & Eurostat & \texttt{namq\_10\_gdp} \dots P31\_S14\_S15.EL & Q & log & masked & domestic \\
\texttt{INV\_GR}   & Gross fixed capital formation & Eurostat & \texttt{namq\_10\_gdp} \dots P51G.EL & Q & log & masked & domestic \\
\texttt{GOV\_GR}   & Government final consumption & Eurostat & \texttt{namq\_10\_gdp} \dots P3\_S13.EL & Q & log & masked & domestic \\
\texttt{EXP\_GR}   & Exports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P6.EL & Q & log & masked & domestic \\
\texttt{IMP\_GR}   & Imports of goods \& services & Eurostat & \texttt{namq\_10\_gdp} \dots P7.EL & Q & log & masked & domestic \\
\texttt{HICP\_GR}  & HICP, all-items index (2015=100) & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.EL & M$\to$Q & log & masked & domestic; m$\to$q avg \\
\texttt{LR\_GR}    & Unemployment rate (SA, total) & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.EL & Q & lin & masked & domestic; \% of labour force \\
\texttt{NEER\_GR}  & Nominal effective FX (IC42 partners, 2015=100) & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.EL & Q & log & observed & domestic; \texttt{isFin}=1 \\
\texttt{SPREAD\_GR}& 10Y sovereign spread vs Bund (pp) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.EL $-$ M.MCBY.DE & M$\to$Q & lin & observed & domestic; Maastricht 10Y \\
\texttt{POLRATE\_GR}& ECB Deposit Facility Rate (policy) & ECB Data Portal & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV & D$\to$Q & lin & observed & external; \% p.a. \\
\texttt{EACORP}    & EA corporate bond yield (\%) & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A} & D$\to$Q & lin & observed & external \\
\texttt{RATE\_GR}  & 3-month EURIBOR (\%) & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA & Q & lin & observed & external; EA-wide 3M \\
\texttt{YIELD10\_DE}& German 10Y Bund yield (spread base) & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE & M$\to$Q & lin & observed & external \\
\texttt{ROWEA\_GDP\_GR}  & Rest-of-EA real GDP (GDP-wtd ex-GR) & Eurostat (derived) & EA20 \texttt{namq\_10\_gdp} de-aggregated by GR weight & Q & log & masked & row; index 2015=100 \\
\texttt{ROWEA\_HICP\_GR} & Rest-of-EA HICP (GDP-wtd ex-GR) & Eurostat (derived) & EA20 \texttt{prc\_hicp\_midx} de-aggregated by GR weight & M$\to$Q & log & masked & row; index 2015=100 \\
\texttt{FREV\_GDP} & General-gov't revenue (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} Q.\allowbreak MIO\_EUR.\allowbreak NSA.\allowbreak S13.\allowbreak TR.\allowbreak EL / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{FPEXP\_GDP}& Primary expenditure (\% of GDP, 4q-trailing) & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY, S13.EL / CP GDP & Q & lin & observed & fiscal; \texttt{WN} \\
\texttt{EFFI}      & Effective interest rate on debt (\%) & Eurostat & $4\cdot$D41PAY$_t$/debt$_{t-1}$, \texttt{gov\_10q\_ggnfa}/\texttt{ggdebt}.EL & Q & lin & observed & fiscal; \texttt{isFin}=1 \\
\texttt{SFA}       & Stock-flow adjustment (\% of GDP) & Eurostat (derived) & debt-identity residual from \texttt{ggdebt}.EL & Q & lin & masked & fiscal; \texttt{WN}; COVID-NaN'd \\
\texttt{CREDIT\_GDP\_GR} & BIS Total Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QGRNAM770A} & Q & lin & masked & domestic; \texttt{isFin}=1; broad credit; GDP-denom mask \\
\texttt{LENDR\_GR} & NFC bank lending rate (ECB MIR new-business floating, \%) & ECB Data Portal & \texttt{MIR} M.\allowbreak GR.\allowbreak B.\allowbreak A2A.\allowbreak F.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed & domestic; \texttt{isFin}=1; non-canonical MIR variant \\
\end{longtable}

\noindent\textit{[FLAG: \texttt{LENDR\_GR} uses the floating-rate / IRF-up-to-1yr
new-business MIR key \texttt{M.\allowbreak GR.\allowbreak B.\allowbreak A2A.\allowbreak F.\allowbreak R.\allowbreak A.2240.\allowbreak EUR.\allowbreak N} rather than the A2A.R.A
composite cost-of-borrowing used by the other four periphery members, because
the composite is sparse for Greece ($\approx$54 obs with crisis-era gaps). The
floating variant is gap-free on the full grid but is a different instrument ---
reduced cross-economy comparability.]}
\textit{[FLAG: \texttt{HPI\_GR} is absent ($n=22$, not 23) --- Eurostat publishes
no house-price index (\texttt{prc\_hpi\_q}) for Greece, so the variable is
dropped rather than imputed.]}
Credit-block coverage (GR): \texttt{CREDIT\_GDP\_GR} 65/68 obs (2009Q1=63.6 \%,
2025Q4=59.3 \%, range 52.5--71.6), 2020Q2--Q4 \texttt{null}; \texttt{LENDR\_GR}
68/68 obs (2009Q1=4.50 \%, 2025Q4=3.66 \%, COVID observed 2.86--3.07 \%). The
\texttt{EACORP} naming caveat (ES table) applies.

% --- 2c. Euro-area small members (EE, FI, LU, LV, LT, SK, SI) ---
%% =====================================================================
%% Per-country data documentation — euro-small group: EE FI LU LV LT SK SI
%% Generated for the DATA section of the BVAR/GVAR user manual.
%%
%% Sources traced from the data builders:
%%   build_euro_member_redesign.py  (domestic macro, financial, row, fiscal)
%%   build_euro_financial_block.py  (ECB DFR policy rate; EACORP all-bonds 10Y)
%%   build_oecd_eurostat.py         (Eurostat SDMX-CSV key conventions)
%%   build_credit_euro_small.py     (NEW credit block: CREDIT_GDP_<CC>, LENDR_<CC>)
%% Authoritative final variable lists: pipeline/euro_redesign_staging/<CC>/spec.json
%%
%% Conventions used in the tables below (stated once here):
%%   * Transformation. 'log' = the series enters as 100*log(level); since the
%%     model differences logs, it is displayed as 4*Delta log = q/q-annualized
%%     growth. 'lin' = the level itself (percent, percentage points, or %-of-GDP).
%%   * COVID-as-missing. Every domestic/row macro series (isFinancial=0) is masked
%%     (set to NaN) for 2020Q2-2020Q4 and re-imputed by the Durbin--Koopman
%%     simulation smoother during estimation; financial series (isFinancial=1)
%%     are kept observed through COVID. The credit QUANTITY is the one exception
%%     among financials: it is masked 2020Q2-Q4 because it inherits the collapse
%%     of its GDP denominator.
%%   * All seven blocs are single-country (standalone) euro-member BVARs, NOT GVAR
%%     blocs: the "external" and "row" series are exogenous regressors, not coupled
%%     partner stars. Estimation is p=3 lags, hierarchical Minnesota/GLP prior,
%%     quarterly sample 2009Q1-2025Q4 (T=68), re-estimated by
%%     export_bvar_euro_redesign.m.
%% =====================================================================

\subsection{Euro-area small members: data conventions}\label{sec:data:euro-small}

This section documents the seven smaller euro-area member blocs
(Estonia, Finland, Luxembourg, Latvia, Lithuania, Slovakia, Slovenia).
Each is a standalone single-country Bayesian VAR ($p=3$ lags,
hierarchical Minnesota/GLP prior) estimated on a common quarterly sample
\textbf{2009Q1--2025Q4} ($T=68$), re-estimated by
\texttt{export\_bvar\_euro\_redesign.m}.  The domestic real national
accounts, prices, labour, and house prices come from \textbf{Eurostat}
SDMX-CSV; the financial block (policy rate, the shared euro corporate
yield anchor, the 3M rate, and the German 10Y spread base) comes from the
\textbf{ECB Data Portal} and Eurostat; the four-variable fiscal block is
built from \textbf{Eurostat} government finance statistics
(\texttt{gov\_10q}); and the rest-of-EA macro pair is a GDP-weighted
de-aggregation of the EA20 aggregate.

Two transformation conventions are used throughout.  \texttt{log} means
the variable is stored as $100\cdot\log(\text{level})$ and therefore
enters the model in growth space (displayed as $4\,\Delta\log=$
quarter-on-quarter annualized growth); \texttt{lin} means the level
(percent, percentage points, or \%-of-GDP).  Under the COVID-as-missing
treatment, all macro variables (\texttt{isFinancial}$=0$) are masked over
\textbf{2020Q2--2020Q4} and re-imputed by the Durbin--Koopman simulation
smoother, while financial variables (\texttt{isFinancial}$=1$) are kept
observed through COVID --- with one deliberate exception: the credit
\emph{quantity} \texttt{CREDIT\_GDP\_<CC>} is masked 2020Q2--Q4 because it
inherits the collapse of its GDP denominator.

\paragraph{The new credit block (flagged).}
Each bloc gains a two-variable credit block appended after the fiscal
block: a \emph{quantity}, \texttt{CREDIT\_GDP\_<CC>} (credit to
non-financial corporations, \% of GDP; \texttt{lin}, prior RW, masked
2020Q2--Q4), and --- where data permit --- a \emph{price},
\texttt{LENDR\_<CC>} (bank lending rate to NFCs; \texttt{lin}, prior RW,
observed through COVID).  For \textbf{FI} and \textbf{LU} the quantity is
the BIS ``Total credit to NFCs, \% of GDP'' (broad credit: loans, debt
securities, and cross-border lending) drawn from FRED.  For
\textbf{EE, LV, LT, SK, SI} the BIS \%-of-GDP table has no entry, so the
quantity is \textbf{constructed} (non-BIS) as
$100\times(\text{ECB BSI MFI loans to NFCs})/(\text{4-quarter rolling sum of Eurostat nominal GDP})$;
this is a \emph{narrow} (domestic-MFI-loans-only) measure whose levels are
far below the BIS broad measure, reducing cross-country comparability ---
see the per-economy \textit{[FLAG]} notes.  Two further idiosyncrasies are
flagged: \textbf{LU}'s price uses the ECB MIR \emph{outstanding-amounts}
rate (the new-business cost-of-borrowing series is too sparse pre-2015),
and \textbf{LV}'s price is \textbf{dropped} entirely (the ECB MIR NFC rate
is too sparse over the 2009Q1 grid); for LV the shared \texttt{EACORP}
remains the external corporate-yield anchor.

% ---------------------------------------------------------------------
% Shared longtable column spec for all seven economies.
% Columns: Variable (id) | Description | Source | Series ID/key | Freq |
%          Transformation | COVID treatment | Notes
% ---------------------------------------------------------------------

%% =====================================================================
\subsection{Estonia (EE)}\label{sec:data:EE}
%% =====================================================================
Estonia is a standalone euro-member BVAR with $n=23$ variables,
$p=3$ lags, estimated on 2009Q1--2025Q4 ($T=68$).  Macro variables
(\texttt{isFinancial}$=0$) are COVID-masked 2020Q2--Q4 and re-imputed by
the Durbin--Koopman smoother; financials are kept observed.

{\footnotesize
\begin{longtable}{@{}p{1.9cm}p{2.9cm}p{1.5cm}p{2.7cm}p{0.7cm}p{1.0cm}p{1.6cm}p{2.4cm}@{}}
\caption{Estonia (EE) --- variable coverage.  \texttt{log}$=100\log$ level
(displayed as $4\Delta\log$, q/q ann.\ growth); \texttt{lin}$=$ level.}
\label{tab:data:EE}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_EE}      & EE real GDP                       & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak EE       & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_EE}     & Real household consumption        & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.EE             & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_EE}      & Real gross fixed capital form.    & Eurostat & \texttt{namq\_10\_gdp} ...P51G.EE                      & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_EE}      & Real government consumption       & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.EE                   & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_EE}      & Real exports                      & Eurostat & \texttt{namq\_10\_gdp} ...P6.EE                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_EE}      & Real imports                      & Eurostat & \texttt{namq\_10\_gdp} ...P7.EE                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_EE}     & HICP index (2015=100)             & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.EE                 & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_EE}       & Unemployment rate (\%)            & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.EE            & Q & lin & masked 2020Q2--Q4 & \\
\texttt{HPI\_EE}      & Real house price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.EE $\div$ HICP & Q & log & observed (financial) & Nominal HPI deflated by HICP \\
\texttt{NEER\_EE}     & NEER, IC42 trade-weighted         & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.EE           & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{SPREAD\_EE}   & 10Y sovereign spread vs Bund      & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.EE $-$ M.MCBY.DE      & M$\to$Q & lin & observed (financial) & Own 10Y minus Bund \\
\texttt{POLRATE\_EE}  & ECB Deposit Facility Rate (policy) & ECB & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV                     & D$\to$Q & lin & observed (financial) & External; shared by all members \\
\texttt{EACORP}       & EA corporate bond yield (non-MFI)  & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A}       & D$\to$Q & lin & observed (financial) & External; shared anchor.\ \textit{(Corrected 2026-06-18: genuine corporate yield --- Bundesbank non-MFI enterprises, issuer class X2000.)} \\
\texttt{RATE\_EE}     & 3M rate (EURIBOR)                 & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA                       & Q & lin & observed (financial) & External; shared 3M EURIBOR \\
\texttt{YIELD10\_DE}  & DE 10Y Bund (spread base)         & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE                    & M$\to$Q & lin & observed (financial) & External \\
\texttt{ROWEA\_GDP\_EE} & Rest-of-EA real GDP             & Eurostat & EA20 \texttt{namq\_10\_gdp} de-aggregated (GDP-weighted) & Q & log & masked 2020Q2--Q4 & EA20 ex-EE, GDP-weighted \\
\texttt{ROWEA\_HICP\_EE} & Rest-of-EA HICP               & Eurostat & EA20 \texttt{prc\_hicp\_midx} de-aggregated            & Q & log & masked 2020Q2--Q4 & EA20 ex-EE, GDP-weighted \\
\texttt{FREV\_GDP}    & Revenue (\% of GDP)               & Eurostat & \texttt{gov\_10q\_ggnfa} Q...TR.EE (4q sum/GDP)        & Q & lin & masked 2020Q2--Q4 & Prior WN; 4q-trailing/nom.\ GDP \\
\texttt{FPEXP\_GDP}   & Primary expenditure (\% of GDP)   & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY (4q sum/GDP)      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{EFFI}         & Effective interest rate (\% p.a.) & Eurostat & \texttt{gov\_10q} interest/lagged debt                 & Q & lin & observed (financial) & Prior RW \\
\texttt{SFA}          & Stock-flow adjustment (\% of GDP) & Eurostat & \texttt{gov\_10q\_ggdebt} debt recursion residual      & Q & lin & masked 2020Q2--Q4 & Prior WN; budget-identity residual \\
\texttt{CREDIT\_GDP\_EE} & Credit to NFCs (\% of GDP)     & ECB BSI + Eurostat (constructed) & $100\times$\texttt{BSI} M.\allowbreak EE.\allowbreak N.\allowbreak A.\allowbreak A20.\allowbreak A.\allowbreak 1.\allowbreak U2.\allowbreak 2240.\allowbreak Z01.\allowbreak E $\div$ 4q $\Sigma$\texttt{namq\_10\_gdp} CP & Q & lin & masked 2020Q2--Q4 & \textbf{NEW quantity.} \textit{[FLAG: CONSTRUCTED (non-BIS) NARROW MFI-loan measure; not directly comparable to BIS broad credit (FI/LU); not break-adjusted. obs 2009Q1=45.2..2025Q4=29.2.]} \\
\texttt{LENDR\_EE}    & ECB MIR composite cost of borrowing, NFCs (new business, \% p.a.) & ECB MIR & \texttt{MIR} M.\allowbreak EE.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed (financial) & \textbf{NEW price.} 63/68 grid quarters; 5 scattered single-quarter interior gaps filled by the Gibbs.\ obs 5.90..4.54 \\
\end{longtable}}

%% =====================================================================
\subsection{Finland (FI)}\label{sec:data:FI}
%% =====================================================================
Finland is a standalone euro-member BVAR with $n=23$ variables,
$p=3$ lags, estimated on 2009Q1--2025Q4 ($T=68$).  Macro variables are
COVID-masked 2020Q2--Q4 and re-imputed by the Durbin--Koopman smoother;
financials are kept observed.

{\footnotesize
\begin{longtable}{@{}p{1.9cm}p{2.9cm}p{1.5cm}p{2.7cm}p{0.7cm}p{1.0cm}p{1.6cm}p{2.4cm}@{}}
\caption{Finland (FI) --- variable coverage.}\label{tab:data:FI}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_FI}      & FI real GDP                       & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak FI       & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_FI}     & Real household consumption        & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.FI             & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_FI}      & Real gross fixed capital form.    & Eurostat & \texttt{namq\_10\_gdp} ...P51G.FI                      & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_FI}      & Real government consumption       & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.FI                   & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_FI}      & Real exports                      & Eurostat & \texttt{namq\_10\_gdp} ...P6.FI                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_FI}      & Real imports                      & Eurostat & \texttt{namq\_10\_gdp} ...P7.FI                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_FI}     & HICP index (2015=100)             & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.FI                 & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_FI}       & Unemployment rate (\%)            & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.FI            & Q & lin & masked 2020Q2--Q4 & \\
\texttt{HPI\_FI}      & Real house price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.FI $\div$ HICP & Q & log & observed (financial) & Nominal HPI deflated by HICP \\
\texttt{NEER\_FI}     & NEER, IC42 trade-weighted         & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.FI           & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{SPREAD\_FI}   & 10Y sovereign spread vs Bund      & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.FI $-$ M.MCBY.DE      & M$\to$Q & lin & observed (financial) & Own 10Y minus Bund \\
\texttt{POLRATE\_FI}  & ECB Deposit Facility Rate (policy) & ECB & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV                     & D$\to$Q & lin & observed (financial) & External; shared by all members \\
\texttt{EACORP}       & EA corporate bond yield (non-MFI)  & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A}       & D$\to$Q & lin & observed (financial) & External; shared anchor.\ \textit{(Corrected 2026-06-18: genuine corporate yield --- Bundesbank non-MFI enterprises, issuer class X2000.)} \\
\texttt{RATE\_FI}     & 3M rate (EURIBOR)                 & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA                       & Q & lin & observed (financial) & External; shared 3M EURIBOR \\
\texttt{YIELD10\_DE}  & DE 10Y Bund (spread base)         & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE                    & M$\to$Q & lin & observed (financial) & External \\
\texttt{ROWEA\_GDP\_FI} & Rest-of-EA real GDP             & Eurostat & EA20 \texttt{namq\_10\_gdp} de-aggregated (GDP-weighted) & Q & log & masked 2020Q2--Q4 & EA20 ex-FI, GDP-weighted \\
\texttt{ROWEA\_HICP\_FI} & Rest-of-EA HICP               & Eurostat & EA20 \texttt{prc\_hicp\_midx} de-aggregated            & Q & log & masked 2020Q2--Q4 & EA20 ex-FI, GDP-weighted \\
\texttt{FREV\_GDP}    & Revenue (\% of GDP)               & Eurostat & \texttt{gov\_10q\_ggnfa} Q...TR.FI (4q sum/GDP)        & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{FPEXP\_GDP}   & Primary expenditure (\% of GDP)   & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY (4q sum/GDP)      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{EFFI}         & Effective interest rate (\% p.a.) & Eurostat & \texttt{gov\_10q} interest/lagged debt                 & Q & lin & observed (financial) & Prior RW \\
\texttt{SFA}          & Stock-flow adjustment (\% of GDP) & Eurostat & \texttt{gov\_10q\_ggdebt} debt recursion residual      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{CREDIT\_GDP\_FI} & Credit to NFCs (\% of GDP)     & BIS via FRED & \texttt{QFINAM770A} (Total credit to NFCs, \% GDP)    & Q & lin & masked 2020Q2--Q4 & \textbf{NEW quantity.} BIS broad credit (loans+bonds+cross-border).\ obs 2009Q1=107.6..2025Q4=114.5 \\
\texttt{LENDR\_FI}    & ECB MIR composite cost of borrowing, NFCs (new business, \% p.a.) & ECB MIR & \texttt{MIR} M.\allowbreak FI.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed (financial) & \textbf{NEW price.} 67/68 grid (one gap 2019Q3 filled by Gibbs).\ obs 2.88..3.54 \\
\end{longtable}}

%% =====================================================================
\subsection{Luxembourg (LU)}\label{sec:data:LU}
%% =====================================================================
Luxembourg is a standalone euro-member BVAR with $n=23$ variables,
$p=3$ lags, estimated on 2009Q1--2025Q4 ($T=68$).  Macro variables are
COVID-masked 2020Q2--Q4 and re-imputed by the Durbin--Koopman smoother;
financials are kept observed.

{\footnotesize
\begin{longtable}{@{}p{1.9cm}p{2.9cm}p{1.5cm}p{2.7cm}p{0.7cm}p{1.0cm}p{1.6cm}p{2.4cm}@{}}
\caption{Luxembourg (LU) --- variable coverage.}\label{tab:data:LU}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_LU}      & LU real GDP                       & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak LU       & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_LU}     & Real household consumption        & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.LU             & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_LU}      & Real gross fixed capital form.    & Eurostat & \texttt{namq\_10\_gdp} ...P51G.LU                      & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_LU}      & Real government consumption       & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.LU                   & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_LU}      & Real exports                      & Eurostat & \texttt{namq\_10\_gdp} ...P6.LU                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_LU}      & Real imports                      & Eurostat & \texttt{namq\_10\_gdp} ...P7.LU                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_LU}     & HICP index (2015=100)             & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.LU                 & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_LU}       & Unemployment rate (\%)            & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.LU            & Q & lin & masked 2020Q2--Q4 & \\
\texttt{HPI\_LU}      & Real house price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.LU $\div$ HICP & Q & log & observed (financial) & Nominal HPI deflated by HICP \\
\texttt{NEER\_LU}     & NEER, IC42 trade-weighted         & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.LU           & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{SPREAD\_LU}   & 10Y sovereign spread vs Bund      & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.LU $-$ M.MCBY.DE      & M$\to$Q & lin & observed (financial) & Own 10Y minus Bund \\
\texttt{POLRATE\_LU}  & ECB Deposit Facility Rate (policy) & ECB & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV                     & D$\to$Q & lin & observed (financial) & External; shared by all members \\
\texttt{EACORP}       & EA corporate bond yield (non-MFI)  & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A}       & D$\to$Q & lin & observed (financial) & External; shared anchor.\ \textit{(Corrected 2026-06-18: genuine corporate yield --- Bundesbank non-MFI enterprises, issuer class X2000.)} \\
\texttt{RATE\_LU}     & 3M rate (EURIBOR)                 & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA                       & Q & lin & observed (financial) & External; shared 3M EURIBOR \\
\texttt{YIELD10\_DE}  & DE 10Y Bund (spread base)         & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE                    & M$\to$Q & lin & observed (financial) & External \\
\texttt{ROWEA\_GDP\_LU} & Rest-of-EA real GDP             & Eurostat & EA20 \texttt{namq\_10\_gdp} de-aggregated (GDP-weighted) & Q & log & masked 2020Q2--Q4 & EA20 ex-LU, GDP-weighted \\
\texttt{ROWEA\_HICP\_LU} & Rest-of-EA HICP               & Eurostat & EA20 \texttt{prc\_hicp\_midx} de-aggregated            & Q & log & masked 2020Q2--Q4 & EA20 ex-LU, GDP-weighted \\
\texttt{FREV\_GDP}    & Revenue (\% of GDP)               & Eurostat & \texttt{gov\_10q\_ggnfa} Q...TR.LU (4q sum/GDP)        & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{FPEXP\_GDP}   & Primary expenditure (\% of GDP)   & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY (4q sum/GDP)      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{EFFI}         & Effective interest rate (\% p.a.) & Eurostat & \texttt{gov\_10q} interest/lagged debt                 & Q & lin & observed (financial) & Prior RW \\
\texttt{SFA}          & Stock-flow adjustment (\% of GDP) & Eurostat & \texttt{gov\_10q\_ggdebt} debt recursion residual      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{CREDIT\_GDP\_LU} & Credit to NFCs (\% of GDP)     & BIS via FRED & \texttt{QLUNAM770A} (Total credit to NFCs, \% GDP)    & Q & lin & masked 2020Q2--Q4 & \textbf{NEW quantity.} BIS broad credit; very high (\(\sim\)270--360\% GDP, captive-finance hub).\ obs 2009Q1=268.5..2025Q4=358.8 \\
\texttt{LENDR\_LU}    & ECB MIR bank lending rate to NFCs (outstanding amounts, \% p.a.) & ECB MIR & \texttt{MIR} M.\allowbreak LU.\allowbreak B.\allowbreak A20.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak O & M$\to$Q & lin & observed (financial) & \textbf{NEW price.} \textit{[FLAG: NON-CANONICAL MIR variant --- OUTSTANDING-amounts rate (A20...O), not the new-business cost-of-borrowing (A2A...N), which is sparse pre-2015. Full 68/68 coverage.]} obs 3.65..3.40 \\
\end{longtable}}

%% =====================================================================
\subsection{Latvia (LV)}\label{sec:data:LV}
%% =====================================================================
Latvia is a standalone euro-member BVAR with $n=22$ variables (one fewer
than the group --- its credit \emph{price} is dropped, see below),
$p=3$ lags, estimated on 2009Q1--2025Q4 ($T=68$).  Macro variables are
COVID-masked 2020Q2--Q4 and re-imputed by the Durbin--Koopman smoother;
financials are kept observed.

{\footnotesize
\begin{longtable}{@{}p{1.9cm}p{2.9cm}p{1.5cm}p{2.7cm}p{0.7cm}p{1.0cm}p{1.6cm}p{2.4cm}@{}}
\caption{Latvia (LV) --- variable coverage.}\label{tab:data:LV}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_LV}      & LV real GDP                       & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak LV       & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_LV}     & Real household consumption        & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.LV             & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_LV}      & Real gross fixed capital form.    & Eurostat & \texttt{namq\_10\_gdp} ...P51G.LV                      & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_LV}      & Real government consumption       & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.LV                   & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_LV}      & Real exports                      & Eurostat & \texttt{namq\_10\_gdp} ...P6.LV                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_LV}      & Real imports                      & Eurostat & \texttt{namq\_10\_gdp} ...P7.LV                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_LV}     & HICP index (2015=100)             & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.LV                 & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_LV}       & Unemployment rate (\%)            & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.LV            & Q & lin & masked 2020Q2--Q4 & \\
\texttt{HPI\_LV}      & Real house price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.LV $\div$ HICP & Q & log & observed (financial) & Nominal HPI deflated by HICP \\
\texttt{NEER\_LV}     & NEER, IC42 trade-weighted         & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.LV           & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{SPREAD\_LV}   & 10Y sovereign spread vs Bund      & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.LV $-$ M.MCBY.DE      & M$\to$Q & lin & observed (financial) & Own 10Y minus Bund \\
\texttt{POLRATE\_LV}  & ECB Deposit Facility Rate (policy) & ECB & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV                     & D$\to$Q & lin & observed (financial) & External; shared by all members \\
\texttt{EACORP}       & EA corporate bond yield (non-MFI)  & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A}       & D$\to$Q & lin & observed (financial) & External; shared anchor (also the LV credit-price proxy, since \texttt{LENDR\_LV} is dropped).\ \textit{(Corrected 2026-06-18: genuine corporate yield --- Bundesbank non-MFI enterprises, issuer class X2000.)} \\
\texttt{RATE\_LV}     & 3M rate (EURIBOR)                 & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA                       & Q & lin & observed (financial) & External; shared 3M EURIBOR \\
\texttt{YIELD10\_DE}  & DE 10Y Bund (spread base)         & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE                    & M$\to$Q & lin & observed (financial) & External \\
\texttt{ROWEA\_GDP\_LV} & Rest-of-EA real GDP             & Eurostat & EA20 \texttt{namq\_10\_gdp} de-aggregated (GDP-weighted) & Q & log & masked 2020Q2--Q4 & EA20 ex-LV, GDP-weighted \\
\texttt{ROWEA\_HICP\_LV} & Rest-of-EA HICP               & Eurostat & EA20 \texttt{prc\_hicp\_midx} de-aggregated            & Q & log & masked 2020Q2--Q4 & EA20 ex-LV, GDP-weighted \\
\texttt{FREV\_GDP}    & Revenue (\% of GDP)               & Eurostat & \texttt{gov\_10q\_ggnfa} Q...TR.LV (4q sum/GDP)        & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{FPEXP\_GDP}   & Primary expenditure (\% of GDP)   & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY (4q sum/GDP)      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{EFFI}         & Effective interest rate (\% p.a.) & Eurostat & \texttt{gov\_10q} interest/lagged debt                 & Q & lin & observed (financial) & Prior RW \\
\texttt{SFA}          & Stock-flow adjustment (\% of GDP) & Eurostat & \texttt{gov\_10q\_ggdebt} debt recursion residual      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{CREDIT\_GDP\_LV} & Credit to NFCs (\% of GDP)     & ECB BSI + Eurostat (constructed) & $100\times$\texttt{BSI} M.\allowbreak LV.\allowbreak N.\allowbreak A.\allowbreak A20.\allowbreak A.\allowbreak 1.\allowbreak U2.\allowbreak 2240.\allowbreak Z01.\allowbreak E $\div$ 4q $\Sigma$\texttt{namq\_10\_gdp} CP & Q & lin & masked 2020Q2--Q4 & \textbf{NEW quantity.} \textit{[FLAG: CONSTRUCTED (non-BIS) NARROW MFI-loan measure; reduced comparability; large secular decline (56\(\to\)16\% GDP) is real post-2009 deleveraging, not a denominator artifact. obs 2010Q3=56.0..2025Q4=16.6.]} \\
\multicolumn{8}{@{}p{16cm}@{}}{\textit{[FLAG: LV credit PRICE DROPPED. The ECB MIR NFC lending rate has only 41/67 grid quarters (2009--2017 riddled with gaps), so no \texttt{LENDR\_LV} variable is included ($n=22$, one fewer than the group). \texttt{EACORP} is the external corporate-yield anchor.]}} \\
\end{longtable}}

%% =====================================================================
\subsection{Lithuania (LT)}\label{sec:data:LT}
%% =====================================================================
Lithuania is a standalone euro-member BVAR with $n=23$ variables,
$p=3$ lags, estimated on 2009Q1--2025Q4 ($T=68$).  Macro variables are
COVID-masked 2020Q2--Q4 and re-imputed by the Durbin--Koopman smoother;
financials are kept observed.

{\footnotesize
\begin{longtable}{@{}p{1.9cm}p{2.9cm}p{1.5cm}p{2.7cm}p{0.7cm}p{1.0cm}p{1.6cm}p{2.4cm}@{}}
\caption{Lithuania (LT) --- variable coverage.}\label{tab:data:LT}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_LT}      & LT real GDP                       & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak LT       & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_LT}     & Real household consumption        & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.LT             & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_LT}      & Real gross fixed capital form.    & Eurostat & \texttt{namq\_10\_gdp} ...P51G.LT                      & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_LT}      & Real government consumption       & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.LT                   & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_LT}      & Real exports                      & Eurostat & \texttt{namq\_10\_gdp} ...P6.LT                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_LT}      & Real imports                      & Eurostat & \texttt{namq\_10\_gdp} ...P7.LT                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_LT}     & HICP index (2015=100)             & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.LT                 & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_LT}       & Unemployment rate (\%)            & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.LT            & Q & lin & masked 2020Q2--Q4 & \\
\texttt{HPI\_LT}      & Real house price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.LT $\div$ HICP & Q & log & observed (financial) & Nominal HPI deflated by HICP \\
\texttt{NEER\_LT}     & NEER, IC42 trade-weighted         & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.LT           & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{SPREAD\_LT}   & 10Y sovereign spread vs Bund      & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.LT $-$ M.MCBY.DE      & M$\to$Q & lin & observed (financial) & Own 10Y minus Bund \\
\texttt{POLRATE\_LT}  & ECB Deposit Facility Rate (policy) & ECB & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV                     & D$\to$Q & lin & observed (financial) & External; shared by all members \\
\texttt{EACORP}       & EA corporate bond yield (non-MFI)  & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A}       & D$\to$Q & lin & observed (financial) & External; shared anchor.\ \textit{(Corrected 2026-06-18: genuine corporate yield --- Bundesbank non-MFI enterprises, issuer class X2000.)} \\
\texttt{RATE\_LT}     & 3M rate (EURIBOR)                 & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA                       & Q & lin & observed (financial) & External; shared 3M EURIBOR \\
\texttt{YIELD10\_DE}  & DE 10Y Bund (spread base)         & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE                    & M$\to$Q & lin & observed (financial) & External \\
\texttt{ROWEA\_GDP\_LT} & Rest-of-EA real GDP             & Eurostat & EA20 \texttt{namq\_10\_gdp} de-aggregated (GDP-weighted) & Q & log & masked 2020Q2--Q4 & EA20 ex-LT, GDP-weighted \\
\texttt{ROWEA\_HICP\_LT} & Rest-of-EA HICP               & Eurostat & EA20 \texttt{prc\_hicp\_midx} de-aggregated            & Q & log & masked 2020Q2--Q4 & EA20 ex-LT, GDP-weighted \\
\texttt{FREV\_GDP}    & Revenue (\% of GDP)               & Eurostat & \texttt{gov\_10q\_ggnfa} Q...TR.LT (4q sum/GDP)        & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{FPEXP\_GDP}   & Primary expenditure (\% of GDP)   & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY (4q sum/GDP)      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{EFFI}         & Effective interest rate (\% p.a.) & Eurostat & \texttt{gov\_10q} interest/lagged debt                 & Q & lin & observed (financial) & Prior RW \\
\texttt{SFA}          & Stock-flow adjustment (\% of GDP) & Eurostat & \texttt{gov\_10q\_ggdebt} debt recursion residual      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{CREDIT\_GDP\_LT} & Credit to NFCs (\% of GDP)     & ECB BSI + Eurostat (constructed) & $100\times$\texttt{BSI} M.\allowbreak LT.\allowbreak N.\allowbreak A.\allowbreak A20.\allowbreak A.\allowbreak 1.\allowbreak U2.\allowbreak 2240.\allowbreak Z01.\allowbreak E $\div$ 4q $\Sigma$\texttt{namq\_10\_gdp} CP & Q & lin & masked 2020Q2--Q4 & \textbf{NEW quantity.} \textit{[FLAG: CONSTRUCTED (non-BIS) NARROW MFI-loan measure; reduced comparability; secular decline (32\(\to\)17\% GDP) is real post-2009 deleveraging. obs 2009Q1=32.3..2025Q4=17.1.]} \\
\texttt{LENDR\_LT}    & ECB MIR composite cost of borrowing, NFCs (new business, \% p.a.) & ECB MIR & \texttt{MIR} M.\allowbreak LT.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed (financial) & \textbf{NEW price.} Full 68/68 grid.\ obs 5.36..4.61 \\
\end{longtable}}

%% =====================================================================
\subsection{Slovakia (SK)}\label{sec:data:SK}
%% =====================================================================
Slovakia is a standalone euro-member BVAR with $n=23$ variables,
$p=3$ lags, estimated on 2009Q1--2025Q4 ($T=68$).  Macro variables are
COVID-masked 2020Q2--Q4 and re-imputed by the Durbin--Koopman smoother;
financials are kept observed.

{\footnotesize
\begin{longtable}{@{}p{1.9cm}p{2.9cm}p{1.5cm}p{2.7cm}p{0.7cm}p{1.0cm}p{1.6cm}p{2.4cm}@{}}
\caption{Slovakia (SK) --- variable coverage.}\label{tab:data:SK}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_SK}      & SK real GDP                       & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak SK       & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_SK}     & Real household consumption        & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.SK             & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_SK}      & Real gross fixed capital form.    & Eurostat & \texttt{namq\_10\_gdp} ...P51G.SK                      & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_SK}      & Real government consumption       & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.SK                   & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_SK}      & Real exports                      & Eurostat & \texttt{namq\_10\_gdp} ...P6.SK                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_SK}      & Real imports                      & Eurostat & \texttt{namq\_10\_gdp} ...P7.SK                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_SK}     & HICP index (2015=100)             & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.SK                 & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_SK}       & Unemployment rate (\%)            & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.SK            & Q & lin & masked 2020Q2--Q4 & \\
\texttt{HPI\_SK}      & Real house price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.SK $\div$ HICP & Q & log & observed (financial) & Nominal HPI deflated by HICP \\
\texttt{NEER\_SK}     & NEER, IC42 trade-weighted         & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.SK           & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{SPREAD\_SK}   & 10Y sovereign spread vs Bund      & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.SK $-$ M.MCBY.DE      & M$\to$Q & lin & observed (financial) & Own 10Y minus Bund \\
\texttt{POLRATE\_SK}  & ECB Deposit Facility Rate (policy) & ECB & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV                     & D$\to$Q & lin & observed (financial) & External; shared by all members \\
\texttt{EACORP}       & EA corporate bond yield (non-MFI)  & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A}       & D$\to$Q & lin & observed (financial) & External; shared anchor.\ \textit{(Corrected 2026-06-18: genuine corporate yield --- Bundesbank non-MFI enterprises, issuer class X2000.)} \\
\texttt{RATE\_SK}     & 3M rate (EURIBOR)                 & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA                       & Q & lin & observed (financial) & External; shared 3M EURIBOR \\
\texttt{YIELD10\_DE}  & DE 10Y Bund (spread base)         & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE                    & M$\to$Q & lin & observed (financial) & External \\
\texttt{ROWEA\_GDP\_SK} & Rest-of-EA real GDP             & Eurostat & EA20 \texttt{namq\_10\_gdp} de-aggregated (GDP-weighted) & Q & log & masked 2020Q2--Q4 & EA20 ex-SK, GDP-weighted \\
\texttt{ROWEA\_HICP\_SK} & Rest-of-EA HICP               & Eurostat & EA20 \texttt{prc\_hicp\_midx} de-aggregated            & Q & log & masked 2020Q2--Q4 & EA20 ex-SK, GDP-weighted \\
\texttt{FREV\_GDP}    & Revenue (\% of GDP)               & Eurostat & \texttt{gov\_10q\_ggnfa} Q...TR.SK (4q sum/GDP)        & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{FPEXP\_GDP}   & Primary expenditure (\% of GDP)   & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY (4q sum/GDP)      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{EFFI}         & Effective interest rate (\% p.a.) & Eurostat & \texttt{gov\_10q} interest/lagged debt                 & Q & lin & observed (financial) & Prior RW \\
\texttt{SFA}          & Stock-flow adjustment (\% of GDP) & Eurostat & \texttt{gov\_10q\_ggdebt} debt recursion residual      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{CREDIT\_GDP\_SK} & Credit to NFCs (\% of GDP)     & ECB BSI + Eurostat (constructed) & $100\times$\texttt{BSI} M.\allowbreak SK.\allowbreak N.\allowbreak A.\allowbreak A20.\allowbreak A.\allowbreak 1.\allowbreak U2.\allowbreak 2240.\allowbreak Z01.\allowbreak E $\div$ 4q $\Sigma$\texttt{namq\_10\_gdp} CP & Q & lin & masked 2020Q2--Q4 & \textbf{NEW quantity.} \textit{[FLAG: CONSTRUCTED (non-BIS) NARROW MFI-loan measure; reduced comparability. obs 2009Q1=23.6..2025Q4=18.6.]} \\
\texttt{LENDR\_SK}    & ECB MIR composite cost of borrowing, NFCs (new business, \% p.a.) & ECB MIR & \texttt{MIR} M.\allowbreak SK.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed (financial) & \textbf{NEW price.} Full 68/68 grid.\ obs 3.43..4.15 \\
\end{longtable}}

%% =====================================================================
\subsection{Slovenia (SI)}\label{sec:data:SI}
%% =====================================================================
Slovenia is a standalone euro-member BVAR with $n=23$ variables,
$p=3$ lags, estimated on 2009Q1--2025Q4 ($T=68$).  Macro variables are
COVID-masked 2020Q2--Q4 and re-imputed by the Durbin--Koopman smoother;
financials are kept observed.

{\footnotesize
\begin{longtable}{@{}p{1.9cm}p{2.9cm}p{1.5cm}p{2.7cm}p{0.7cm}p{1.0cm}p{1.6cm}p{2.4cm}@{}}
\caption{Slovenia (SI) --- variable coverage.}\label{tab:data:SI}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_SI}      & SI real GDP                       & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak SI       & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_SI}     & Real household consumption        & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.SI             & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_SI}      & Real gross fixed capital form.    & Eurostat & \texttt{namq\_10\_gdp} ...P51G.SI                      & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_SI}      & Real government consumption       & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.SI                   & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_SI}      & Real exports                      & Eurostat & \texttt{namq\_10\_gdp} ...P6.SI                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_SI}      & Real imports                      & Eurostat & \texttt{namq\_10\_gdp} ...P7.SI                        & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_SI}     & HICP index (2015=100)             & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.SI                 & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_SI}       & Unemployment rate (\%)            & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.SI            & Q & lin & masked 2020Q2--Q4 & \\
\texttt{HPI\_SI}      & Real house price index (HPI/HICP, 2015=100) & Eurostat & \texttt{prc\_hpi\_q} Q.TOTAL.I15\_Q.SI $\div$ HICP & Q & log & observed (financial) & Nominal HPI deflated by HICP \\
\texttt{NEER\_SI}     & NEER, IC42 trade-weighted         & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.SI           & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{SPREAD\_SI}   & 10Y sovereign spread vs Bund      & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.SI $-$ M.MCBY.DE      & M$\to$Q & lin & observed (financial) & Own 10Y minus Bund \\
\texttt{POLRATE\_SI}  & ECB Deposit Facility Rate (policy) & ECB & \texttt{FM} D.\allowbreak U2.\allowbreak EUR.\allowbreak 4F.\allowbreak KR.\allowbreak DFR.\allowbreak LEV                     & D$\to$Q & lin & observed (financial) & External; shared by all members \\
\texttt{EACORP}       & EA corporate bond yield (non-MFI)  & Bundesbank & \texttt{BBSIS/\allowbreak M.\allowbreak I.\allowbreak UMR.\allowbreak RD.\allowbreak EUR.\allowbreak X2000.\allowbreak B.A.A.\allowbreak R.A.A.\allowbreak \_Z.\_Z.A}       & D$\to$Q & lin & observed (financial) & External; shared anchor.\ \textit{(Corrected 2026-06-18: genuine corporate yield --- Bundesbank non-MFI enterprises, issuer class X2000.)} \\
\texttt{RATE\_SI}     & 3M rate (EURIBOR)                 & Eurostat & \texttt{irt\_st\_q} Q.IRT\_M3.EA                       & Q & lin & observed (financial) & External; shared 3M EURIBOR \\
\texttt{YIELD10\_DE}  & DE 10Y Bund (spread base)         & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.DE                    & M$\to$Q & lin & observed (financial) & External \\
\texttt{ROWEA\_GDP\_SI} & Rest-of-EA real GDP             & Eurostat & EA20 \texttt{namq\_10\_gdp} de-aggregated (GDP-weighted) & Q & log & masked 2020Q2--Q4 & EA20 ex-SI, GDP-weighted \\
\texttt{ROWEA\_HICP\_SI} & Rest-of-EA HICP               & Eurostat & EA20 \texttt{prc\_hicp\_midx} de-aggregated            & Q & log & masked 2020Q2--Q4 & EA20 ex-SI, GDP-weighted \\
\texttt{FREV\_GDP}    & Revenue (\% of GDP)               & Eurostat & \texttt{gov\_10q\_ggnfa} Q...TR.SI (4q sum/GDP)        & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{FPEXP\_GDP}   & Primary expenditure (\% of GDP)   & Eurostat & \texttt{gov\_10q\_ggnfa} TE$-$D41PAY (4q sum/GDP)      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{EFFI}         & Effective interest rate (\% p.a.) & Eurostat & \texttt{gov\_10q} interest/lagged debt                 & Q & lin & observed (financial) & Prior RW \\
\texttt{SFA}          & Stock-flow adjustment (\% of GDP) & Eurostat & \texttt{gov\_10q\_ggdebt} debt recursion residual      & Q & lin & masked 2020Q2--Q4 & Prior WN \\
\texttt{CREDIT\_GDP\_SI} & Credit to NFCs (\% of GDP)     & ECB BSI + Eurostat (constructed) & $100\times$\texttt{BSI} M.\allowbreak SI.\allowbreak N.\allowbreak A.\allowbreak A20.\allowbreak A.\allowbreak 1.\allowbreak U2.\allowbreak 2240.\allowbreak Z01.\allowbreak E $\div$ 4q $\Sigma$\texttt{namq\_10\_gdp} CP & Q & lin & masked 2020Q2--Q4 & \textbf{NEW quantity.} \textit{[FLAG: CONSTRUCTED (non-BIS) NARROW MFI-loan measure; reduced comparability. The 2013--14 cliff (56\(\to\)16\% GDP) is the BAMC ``bad bank'' NPL transfer off MFI books, not a denominator artifact. obs 2009Q1=56.2..2025Q4=16.5.]} \\
\texttt{LENDR\_SI}    & ECB MIR composite cost of borrowing, NFCs (new business, \% p.a.) & ECB MIR & \texttt{MIR} M.\allowbreak SI.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.\allowbreak 2240.\allowbreak EUR.\allowbreak N & M$\to$Q & lin & observed (financial) & \textbf{NEW price.} Full 68/68 grid.\ obs 5.57..3.54 \\
\end{longtable}}

% =====================================================================
% 3. EU NON-EURO AND HARD-GAP SMALL BLOCS (CZ, HU, PL, CR, IS)
% =====================================================================
%% =====================================================================
%% Per-country data documentation — EU-non-euro + hard-gap small group:
%%   CZ HU PL (EU non-euro, Eurostat-sourced GVAR blocs)
%%   CR IS    (non-EU GVAR blocs; "hard-gap" credit construction)
%% Generated for the DATA section of the BVAR/GVAR user manual.
%%
%% Sources traced from the data builders:
%%   build_oecd_eurostat.py        (CZ/HU/PL domestic macro: Eurostat SDMX-CSV)
%%   build_polrate_hp_group.py     (CZ/HU/PL/IS POLRATE + HP: BIS CBPOL / FRED BIS RPP)
%%   add_polrate_hp_group.py       (CR: confirms POLRATE/HP skipped for CR)
%%   build_globals_new_blocs.py    (GLB_OIL/GLB_USLR/GLB_USBAA/GLB_USEQ commons)
%%   build_credit_eu_noneuro.py    (NEW credit block CZ/HU/PL: BIS %GDP via FRED + ECB MIR)
%%   fetch_ecb_mir.py / fetch_bis_credit.py  (CZ/HU/PL credit fetchers)
%%   build_credit_hardgap_cris.py  (NEW credit block CR/IS: CONSTRUCTED qty + IMF IFS FILR_PA price)
%% Authoritative final variable lists: pipeline/credit_staging/<CC>/spec.json
%% First/last obs, ranges, masking counts: build report (wk3ousgvu) +
%%   availability study (wrqpqko5z), cross-checked against the builders.
%%
%% Conventions used in the tables below (stated once here):
%%   * Transformation. 'log' = the series enters as 100*log(level); since the
%%     model differences logs, it is displayed as 4*Delta log = q/q-annualized
%%     growth. 'lin' = the level itself (percent, percentage points, or %-of-GDP).
%%   * COVID-as-missing. Every domestic macro series (isFinancial=0) is masked
%%     (set to NaN) for 2020Q2-2020Q4 and re-imputed by the Durbin--Koopman
%%     simulation smoother during estimation; financial series (isFinancial=1)
%%     are kept observed through COVID. The credit QUANTITY CREDIT_GDP_<CC> is
%%     the one deliberate exception among financials: it is masked 2020Q2-Q4
%%     because it inherits the collapse of its GDP denominator.
%%   * All five blocs are coupled GVAR member blocs; the per-bloc tables below
%%     document only the domestic + global-commons variables. The three
%%     trade-weighted foreign star variables (ROWDEM/ROWINF/ROWFIN_<CC>) are
%%     appended at GVAR-estimation time and are not part of the staged spec.
%% =====================================================================

\subsection{EU non-euro and hard-gap small blocs: data conventions}\label{sec:data:eunon-small}

This section documents five coupled GVAR member blocs: the three
EU \emph{non-euro} economies (Czechia, Hungary, Poland) and two non-EU
blocs (Costa Rica, Iceland) whose credit quantity required a
\emph{constructed} (non-BIS) measure.  Each is a Bayesian VAR with
$p=3$ lags and a hierarchical Minnesota/GLP prior, coupled into the
GVAR through trade-weighted foreign \emph{star} variables that are added
at solve time.  The per-bloc tables below list the domestic block plus
the four global commons; the three \texttt{ROW*}\_\texttt{<CC>} stars are
not part of the staged \texttt{spec.json} and are appended by the
estimator.

Two transformation conventions are used throughout.  \texttt{log} means
the variable is stored as $100\cdot\log(\text{level})$ and therefore
enters the model in growth space (displayed as $4\,\Delta\log=$
quarter-on-quarter annualized growth); \texttt{lin} means the level
(percent, percentage points, or \%-of-GDP).  Under the COVID-as-missing
treatment, all macro variables (\texttt{isFinancial}$=0$) are masked over
\textbf{2020Q2--2020Q4} and re-imputed by the Durbin--Koopman simulation
smoother, while financial variables (\texttt{isFinancial}$=1$) are kept
observed through COVID --- with one deliberate exception: the credit
\emph{quantity} \texttt{CREDIT\_GDP\_<CC>} is masked 2020Q2--Q4 because it
inherits the collapse of its GDP denominator.

\paragraph{The new credit block (flagged).}
Each bloc gains a two-variable credit block appended after all existing
variables: a \emph{quantity}, \texttt{CREDIT\_GDP\_<CC>} (credit to
non-financial corporations as a \% of GDP; \texttt{lin}, prior RW,
masked 2020Q2--Q4), and a \emph{price}, \texttt{LENDR\_<CC>} (bank
lending rate to NFCs; \texttt{lin}, prior RW, observed through COVID).
For \textbf{CZ, HU, PL} the quantity is the BIS ``Total credit to NFCs,
\% of GDP'' (broad credit: bank loans, debt securities, and cross-border
lending) pulled from FRED, mnemonic \texttt{Q<ISO2>NAM770A}; the price is
the ECB MIR new-business NFC bank lending rate in local currency.  For
\textbf{CR, IS} neither a BIS \%-of-GDP table nor a clean national bank
lending rate is published, so the quantity is \textbf{constructed}
(non-BIS) as $100\times(\text{IMF IFS ODC claims on the private
sector})/(\text{4-quarter trailing nominal GDP})$ and the price is the
IMF IFS \texttt{FILR\_PA} lending rate.  The salient caveats --- the
broad/narrow-credit comparability gap, the non-canonical MIR variant used
for HU and PL, and the constructed-quantity flag for CR and IS --- are
recorded in the per-economy \textit{[FLAG]} notes below.

% ---------------------------------------------------------------------
% Shared longtable column spec for all five economies.
% Columns: Variable (id) | Description | Source | Series ID/key | Freq |
%          Transformation | COVID treatment | Notes
% ---------------------------------------------------------------------

%% =====================================================================
\subsection{Czechia (CZ)}\label{sec:data:CZ}
%% =====================================================================
Czechia is a coupled GVAR bloc with $n=18$ domestic-plus-global
variables (the three foreign \texttt{ROW*}\_\texttt{CZ} stars are added
at GVAR-estimation time), $p=3$ lags, estimated on the common quarterly
sample \textbf{2009Q1--2025Q4} ($T=68$).  Macro variables
(\texttt{isFinancial}$=0$) are COVID-masked 2020Q2--Q4 and re-imputed by
the Durbin--Koopman smoother; financials are kept observed.  The
domestic real national accounts, prices, and labour come from Eurostat;
the policy rate and house price from the BIS; and the new credit block
from BIS (quantity, via FRED) and the ECB MIR (price).

{\footnotesize
\begin{longtable}{@{}p{2.0cm}p{2.7cm}p{1.4cm}p{2.8cm}p{0.7cm}p{0.85cm}p{1.5cm}p{2.3cm}@{}}
\caption{Czechia (CZ) --- variable coverage.  \texttt{log}$=100\log$ level
(displayed as $4\Delta\log$, q/q ann.\ growth); \texttt{lin}$=$ level.}
\label{tab:data:CZ}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_CZ}    & Real GDP                      & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak CZ        & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_CZ}   & Real household consumption    & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.CZ              & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_CZ}    & Real gross fixed cap.\ form.  & Eurostat & \texttt{namq\_10\_gdp} ...P51G.CZ                       & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_CZ}    & Real government consumption   & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.CZ                    & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_CZ}    & Real exports                  & Eurostat & \texttt{namq\_10\_gdp} ...P6.CZ                         & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_CZ}    & Real imports                  & Eurostat & \texttt{namq\_10\_gdp} ...P7.CZ                         & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_CZ}   & HICP index (2015=100)         & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.CZ                  & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_CZ}     & Unemployment rate (\%)        & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.CZ             & Q & lin & masked 2020Q2--Q4 & \\
\texttt{YIELD10\_CZ}& 10Y government bond yield     & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.CZ                     & M$\to$Q & lin & observed (financial) & Maastricht 10Y \\
\texttt{NEER\_CZ}   & Nominal effective FX (IC42)   & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.CZ            & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{POLRATE\_CZ}& Central-bank policy rate      & BIS & \texttt{WS\_CBPOL} M.CZ                                 & M$\to$Q & lin & observed (financial) & 3-month q-avg of monthly EoP \\
\texttt{HP\_CZ}     & Real residential property price & BIS (via FRED) & \texttt{QCZR628BIS}                          & Q & log & observed (financial) & Real RPP, 2010=100 \\
\texttt{GLB\_OIL}   & WTI crude oil price           & FRED & \texttt{WTISPLC} (q-avg)                               & M$\to$Q & log & observed (financial) & Global common (spot WTI, \$/bbl) \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield         & FRED & \texttt{DGS10} \textit{[FLAG]}                          & D$\to$Q & lin & observed (financial) & Global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield        & FRED & \texttt{BAA} \textit{[FLAG]}                            & M$\to$Q & lin & observed (financial) & Global common (credit proxy) \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500)          & FRED & \texttt{SP500}-class \textit{[FLAG]}                    & D$\to$Q & log & observed (financial) & Global common \\
\texttt{CREDIT\_GDP\_CZ} & Credit to NFCs (\% of GDP) & \textbf{BIS} (via FRED) & \texttt{QCZNAM770A}                       & Q & lin & \textbf{masked 2020Q2--Q4} & \textbf{NEW.} BIS broad NFC credit \%GDP; 65 present, 3 masked, range 50.1--61.6\%; inherits GDP-denominator mask \\
\texttt{LENDR\_CZ}  & NFC bank lending rate (\% p.a.) & \textbf{ECB MIR} & \texttt{M.\allowbreak CZ.\allowbreak B.\allowbreak A2A.\allowbreak F.\allowbreak R.0.2240.\allowbreak CZK.\allowbreak N}                 & M$\to$Q & lin & observed (financial) & \textbf{NEW.} New-business, $\le$EUR1M, floating-rate/IRF$\le$1y, S.11 NFC, CZK; 68 present, range 2.14--9.24\% \\
\end{longtable}}

\noindent\textit{[FLAG: \texttt{CREDIT\_GDP\_CZ}/\texttt{LENDR\_CZ} variant.]}
The price uses the local-currency \emph{floating-rate} $\le$EUR1M
new-business MIR series (\texttt{...\allowbreak A2A.\allowbreak F.\allowbreak R.0...}, available from 2006-01,
the LOCKED-spec pinned key) rather than the cleaner total-maturity
composite (\texttt{...\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A...}), which only begins 2010-06 and would
leave a leading gap on the 2009Q1 grid.  No price was dropped.

%% =====================================================================
\subsection{Hungary (HU)}\label{sec:data:HU}
%% =====================================================================
Hungary is a coupled GVAR bloc with $n=18$ domestic-plus-global
variables (three \texttt{ROW*}\_\texttt{HU} stars added at estimation),
$p=3$ lags, estimated on \textbf{2009Q1--2025Q4} ($T=68$).  Macro
variables are COVID-masked 2020Q2--Q4 and re-imputed; financials are kept
observed.  Sourcing mirrors CZ.

{\footnotesize
\begin{longtable}{@{}p{2.0cm}p{2.7cm}p{1.4cm}p{2.8cm}p{0.7cm}p{0.85cm}p{1.5cm}p{2.3cm}@{}}
\caption{Hungary (HU) --- variable coverage.  \texttt{log}$=100\log$ level
(displayed as $4\Delta\log$, q/q ann.\ growth); \texttt{lin}$=$ level.}
\label{tab:data:HU}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_HU}    & Real GDP                      & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak HU        & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_HU}   & Real household consumption    & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.HU              & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_HU}    & Real gross fixed cap.\ form.  & Eurostat & \texttt{namq\_10\_gdp} ...P51G.HU                       & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_HU}    & Real government consumption   & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.HU                    & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_HU}    & Real exports                  & Eurostat & \texttt{namq\_10\_gdp} ...P6.HU                         & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_HU}    & Real imports                  & Eurostat & \texttt{namq\_10\_gdp} ...P7.HU                         & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_HU}   & HICP index (2015=100)         & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.HU                  & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_HU}     & Unemployment rate (\%)        & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.HU             & Q & lin & masked 2020Q2--Q4 & \\
\texttt{YIELD10\_HU}& 10Y government bond yield     & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.HU                     & M$\to$Q & lin & observed (financial) & Maastricht 10Y \\
\texttt{NEER\_HU}   & Nominal effective FX (IC42)   & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.HU            & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{POLRATE\_HU}& Central-bank policy rate      & BIS & \texttt{WS\_CBPOL} M.HU                                 & M$\to$Q & lin & observed (financial) & 3-month q-avg of monthly EoP \\
\texttt{HP\_HU}     & Real residential property price & BIS (via FRED) & \texttt{QHUR628BIS}                          & Q & log & observed (financial) & Real RPP, 2010=100 \\
\texttt{GLB\_OIL}   & WTI crude oil price           & FRED & \texttt{WTISPLC} (q-avg)                               & M$\to$Q & log & observed (financial) & Global common (spot WTI, \$/bbl) \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield         & FRED & \texttt{DGS10} \textit{[FLAG]}                          & D$\to$Q & lin & observed (financial) & Global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield        & FRED & \texttt{BAA} \textit{[FLAG]}                            & M$\to$Q & lin & observed (financial) & Global common (credit proxy) \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500)          & FRED & \texttt{SP500}-class \textit{[FLAG]}                    & D$\to$Q & log & observed (financial) & Global common \\
\texttt{CREDIT\_GDP\_HU} & Credit to NFCs (\% of GDP) & \textbf{BIS} (via FRED) & \texttt{QHUNAM770A}                       & Q & lin & \textbf{masked 2020Q2--Q4} & \textbf{NEW.} BIS broad NFC credit \%GDP; 65 present, 3 masked, range 64.2--94.9\% \\
\texttt{LENDR\_HU}  & NFC bank lending rate (\% p.a.) & \textbf{ECB MIR} & \texttt{M.\allowbreak HU.\allowbreak B.\allowbreak A2A.\allowbreak F.\allowbreak R.0.2240.\allowbreak HUF.\allowbreak N}                 & M$\to$Q & lin & observed (financial) & \textbf{NEW.} New-business floating-rate $\le$EUR1M, S.11 NFC, HUF; starts 2010Q1 (4 leading nulls handled by Gibbs); range 2.64--16.37\% \\
\end{longtable}}

\noindent\textit{[FLAG: \texttt{LENDR\_HU} non-canonical MIR variant.]}
The LOCKED spec gave only ``from $\sim$2010'' without pinning an exact MIR
key.  The standard total-maturity variant (\texttt{...\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A...}) is
EUR-denominated and starts only 2017-09 (too short); the local-currency
floating-rate variant used here starts 2010-01, consistent with the hint
and with the CZ-pinned key form, and is a genuine NFC new-business
lending rate.  Four leading quarters (2009Q1--Q4) are null and are
handled by the COVID-as-missing Gibbs ragged-edge machinery.
\textit{[FLAG: \texttt{CREDIT\_GDP\_HU} composition.]} The forint NFC
credit level is partly inflated by FX revaluation of FX-denominated
corporate loans and by high HU inflation; the \%-of-GDP ratio dampens but
does not fully remove this nominal component.

%% =====================================================================
\subsection{Poland (PL)}\label{sec:data:PL}
%% =====================================================================
Poland is a coupled GVAR bloc with $n=18$ domestic-plus-global variables
(three \texttt{ROW*}\_\texttt{PL} stars added at estimation), $p=3$ lags,
estimated on \textbf{2009Q1--2025Q4} ($T=68$).  Macro variables are
COVID-masked 2020Q2--Q4 and re-imputed; financials are kept observed.
Sourcing mirrors CZ.

{\footnotesize
\begin{longtable}{@{}p{2.0cm}p{2.7cm}p{1.4cm}p{2.8cm}p{0.7cm}p{0.85cm}p{1.5cm}p{2.3cm}@{}}
\caption{Poland (PL) --- variable coverage.  \texttt{log}$=100\log$ level
(displayed as $4\Delta\log$, q/q ann.\ growth); \texttt{lin}$=$ level.}
\label{tab:data:PL}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_PL}    & Real GDP                      & Eurostat & \texttt{namq\_10\_gdp} Q.\allowbreak CLV15\_MEUR.\allowbreak SCA.\allowbreak B1GQ.\allowbreak PL        & Q & log & masked 2020Q2--Q4 & Chain-linked volume, SCA \\
\texttt{CONS\_PL}   & Real household consumption    & Eurostat & \texttt{namq\_10\_gdp} ...P31\_S14\_S15.PL              & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_PL}    & Real gross fixed cap.\ form.  & Eurostat & \texttt{namq\_10\_gdp} ...P51G.PL                       & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_PL}    & Real government consumption   & Eurostat & \texttt{namq\_10\_gdp} ...P3\_S13.PL                    & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_PL}    & Real exports                  & Eurostat & \texttt{namq\_10\_gdp} ...P6.PL                         & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_PL}    & Real imports                  & Eurostat & \texttt{namq\_10\_gdp} ...P7.PL                         & Q & log & masked 2020Q2--Q4 & \\
\texttt{HICP\_PL}   & HICP index (2015=100)         & Eurostat & \texttt{prc\_hicp\_midx} M.I15.CP00.PL                  & M$\to$Q & log & masked 2020Q2--Q4 & Monthly avg.\ to quarterly \\
\texttt{LR\_PL}     & Unemployment rate (\%)        & Eurostat & \texttt{une\_rt\_q} Q.SA.TOTAL.PC\_ACT.T.PL             & Q & lin & masked 2020Q2--Q4 & \\
\texttt{YIELD10\_PL}& 10Y government bond yield     & Eurostat & \texttt{irt\_lt\_mcby\_m} M.MCBY.PL                     & M$\to$Q & lin & observed (financial) & Maastricht 10Y \\
\texttt{NEER\_PL}   & Nominal effective FX (IC42)   & Eurostat & \texttt{ert\_eff\_ic\_q} Q.NEER\_IC42.I15.PL            & Q & log & observed (financial) & 42-partner nominal eff.\ FX \\
\texttt{POLRATE\_PL}& Central-bank policy rate      & BIS & \texttt{WS\_CBPOL} M.PL                                 & M$\to$Q & lin & observed (financial) & 3-month q-avg of monthly EoP \\
\texttt{HP\_PL}     & Real residential property price & BIS (via FRED) & \texttt{QPLR628BIS}                          & Q & log & observed (financial) & Real RPP, 2010=100 \\
\texttt{GLB\_OIL}   & WTI crude oil price           & FRED & \texttt{WTISPLC} (q-avg)                               & M$\to$Q & log & observed (financial) & Global common (spot WTI, \$/bbl) \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield         & FRED & \texttt{DGS10} \textit{[FLAG]}                          & D$\to$Q & lin & observed (financial) & Global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield        & FRED & \texttt{BAA} \textit{[FLAG]}                            & M$\to$Q & lin & observed (financial) & Global common (credit proxy) \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500)          & FRED & \texttt{SP500}-class \textit{[FLAG]}                    & D$\to$Q & log & observed (financial) & Global common \\
\texttt{CREDIT\_GDP\_PL} & Credit to NFCs (\% of GDP) & \textbf{BIS} (via FRED) & \texttt{QPLNAM770A}                       & Q & lin & \textbf{masked 2020Q2--Q4} & \textbf{NEW.} BIS broad NFC credit \%GDP; 65 present, 3 masked, range 34.7--49.5\% \\
\texttt{LENDR\_PL}  & NFC bank lending rate (\% p.a.) & \textbf{ECB MIR} & \texttt{M.\allowbreak PL.\allowbreak B.\allowbreak A2A.\allowbreak F.\allowbreak R.0.2240.\allowbreak PLN.\allowbreak N}                 & M$\to$Q & lin & observed (financial) & \textbf{NEW.} New-business floating-rate $\le$EUR1M, S.11 NFC, PLN; 68 present, range 1.82--8.62\% \\
\end{longtable}}

\noindent\textit{[FLAG: \texttt{LENDR\_PL} non-canonical MIR variant.]}
The clean total-maturity composite (\texttt{...\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A...}) begins only
2017-08 --- far too short for the 2009Q1 grid --- so the local-currency
floating-rate $\le$EUR1M new-business series (full coverage from 2005,
gap-free, and the dominant WIBOR-linked PL corporate-loan type) is used
instead.  Overlap checks confirm it tracks the composite within
$\sim$30bp; no splice and no back-fill needed.

%% =====================================================================
\subsection{Costa Rica (CR)}\label{sec:data:CR}
%% =====================================================================
Costa Rica is a coupled GVAR bloc with $n=13$ domestic-plus-global
variables (three \texttt{ROW*}\_\texttt{CR} stars added at estimation),
$p=3$ lags, estimated on \textbf{2010Q3--2025Q4} ($T=62$).  It is a
compact emerging-market specification: real activity is proxied by
industrial production, external trade is in USD, and there is no separate
10Y yield or house-price variable.  Macro variables are COVID-masked
2020Q2--Q4 and re-imputed; financials (including the policy rate and the
new credit price) are kept observed.

{\footnotesize
\begin{longtable}{@{}p{2.0cm}p{2.7cm}p{1.4cm}p{2.8cm}p{0.7cm}p{0.85cm}p{1.5cm}p{2.3cm}@{}}
\caption{Costa Rica (CR) --- variable coverage.  \texttt{log}$=100\log$
level (displayed as $4\Delta\log$, q/q ann.\ growth); \texttt{lin}$=$ level.}
\label{tab:data:CR}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_CR}    & Real GDP (IP proxy)           & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & Activity proxied by industrial production \\
\texttt{EXP\_CR}    & Goods exports (USD)           & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & USD goods exports \\
\texttt{IMP\_CR}    & Goods imports (USD)           & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & USD goods imports \\
\texttt{CPI\_CR}    & CPI index                     & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{LR\_CR}     & Unemployment rate (\%)        & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & lin & masked 2020Q2--Q4 & \\
\texttt{RATE\_CR}   & Monetary policy rate          & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & lin & observed (financial) & National monetary policy rate (BCCR); POLRATE/HP not added (CR not in BIS CBPOL/RPP) \\
\texttt{NEER\_CR}   & Nominal effective FX          & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & observed (financial) & \\
\texttt{GLB\_OIL}   & WTI crude oil price           & FRED & \texttt{WTISPLC} (q-avg)                               & M$\to$Q & log & observed (financial) & Global common (spot WTI, \$/bbl) \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield         & FRED & \texttt{DGS10} \textit{[FLAG]}                          & D$\to$Q & lin & observed (financial) & Global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield        & FRED & \texttt{BAA} \textit{[FLAG]}                            & M$\to$Q & lin & observed (financial) & Global common (credit proxy) \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500)          & FRED & \texttt{SP500}-class \textit{[FLAG]}                    & D$\to$Q & log & observed (financial) & Global common \\
\texttt{CREDIT\_GDP\_CR} & Credit to NFCs (\% of GDP) & \textbf{IMF IFS (CONSTRUCTED)} & $100\times$\texttt{FOSAOP\_XDC}$/$4Q-trailing \texttt{NGDP\_SA\_XDC} & Q & lin & \textbf{masked 2020Q2--Q4} & \textbf{NEW.} 56 present, range 42.8--59.4\%; last 2025Q1; broad private-sector credit used as NFC proxy \\
\texttt{LENDR\_CR}  & Bank lending rate (\% p.a.)   & \textbf{IMF IFS} & \texttt{FILR\_PA} (DBnomics mirror)                    & Q & lin & observed (financial) & \textbf{NEW.} IMF-compiled national lending rate (source BCCR); 60 present, range 5.0--18.8\%; last 2025Q2 \\
\end{longtable}}

\noindent\textit{[FLAG: \texttt{CREDIT\_GDP\_CR} constructed / non-BIS.]}
Costa Rica is not a BIS total-credit reporter (FRED \texttt{QCRNAM770A}
and BIS WS\_TC both return ``no series''), so the quantity is constructed
as $100\times$ (IMF IFS ODC claims on the private sector, \texttt{FOSAOP\_XDC},
CRC) over a 4-quarter trailing sum of nominal GDP (\texttt{NGDP\_SA\_XDC}).
This is \emph{broad private-sector} credit (households $+$ NFCs), used as
the NFC proxy --- the same validated construction as Colombia --- so its
\emph{level} is not directly comparable to the BIS broad-NFC \%GDP series
used for CZ/HU/PL.  The price \texttt{LENDR\_CR} is the IMF IFS
\texttt{FILR\_PA} (IMF-compiled national lending rate sourced from the
BCCR), used in lieu of a direct BCCR scrape; both new series have ragged
trailing edges (credit to 2025Q1, price to 2025Q2) handled by the
COVID-as-missing Gibbs.
\textit{[FLAG: CR base macro provenance.]} The exact source and series
identifiers for the \emph{base} CR macro/financial variables
(\texttt{GDP\_CR} IP proxy, \texttt{EXP\_CR}/\texttt{IMP\_CR} USD trade,
\texttt{CPI\_CR}, \texttt{LR\_CR}, \texttt{RATE\_CR}, \texttt{NEER\_CR})
could not be determined from the builders present in the current pipeline
tree (these blocs were assembled by an earlier exporter/IMF flow not
retained here); they are most plausibly IMF (IFS/IMTS) and BCCR series but
the precise keys are not verifiable from the available scripts and are
\emph{not} fabricated here.

%% =====================================================================
\subsection{Iceland (IS)}\label{sec:data:IS}
%% =====================================================================
Iceland is a coupled GVAR bloc with $n=18$ domestic-plus-global variables
(three \texttt{ROW*}\_\texttt{IS} stars added at estimation), $p=3$ lags,
estimated on the long sample \textbf{2000Q2--2025Q4} ($T=103$).  It
carries a full real national-accounts block, a 3-month interbank rate, the
BIS policy rate and real house price, and the new credit block.  Macro
variables are COVID-masked 2020Q2--Q4 and re-imputed; financials are kept
observed.

{\footnotesize
\begin{longtable}{@{}p{2.0cm}p{2.7cm}p{1.4cm}p{2.8cm}p{0.7cm}p{0.85cm}p{1.5cm}p{2.3cm}@{}}
\caption{Iceland (IS) --- variable coverage.  \texttt{log}$=100\log$ level
(displayed as $4\Delta\log$, q/q ann.\ growth); \texttt{lin}$=$ level.}
\label{tab:data:IS}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule \endhead
\bottomrule \endfoot
\texttt{GDP\_IS}    & Real GDP                      & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{CONS\_IS}   & Real private consumption      & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{INV\_IS}    & Real investment               & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{GOV\_IS}    & Real government consumption   & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{EXP\_IS}    & Real exports                  & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{IMP\_IS}    & Real imports                  & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{CPI\_IS}    & CPI index                     & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & masked 2020Q2--Q4 & \\
\texttt{LR\_IS}     & Unemployment rate (\%)        & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & lin & masked 2020Q2--Q4 & \\
\texttt{RATE\_IS}   & 3-month interbank rate        & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & lin & observed (financial) & 3M interbank (likely FRED \texttt{IR3TIB01ISQ156N}; unverified here) \\
\texttt{NEER\_IS}   & Nominal effective FX          & \textit{[FLAG]} & \textit{[FLAG: not determinable from current builders]} & Q & log & observed (financial) & \\
\texttt{POLRATE\_IS}& Central-bank policy rate      & BIS & \texttt{WS\_CBPOL} M.IS                                 & M$\to$Q & lin & observed (financial) & 3-month q-avg of monthly EoP \\
\texttt{HP\_IS}     & Real residential property price & BIS (via FRED) & \texttt{QISR628BIS}                          & Q & log & observed (financial) & Real RPP, 2010=100 \\
\texttt{GLB\_OIL}   & WTI crude oil price           & FRED & \texttt{WTISPLC} (q-avg)                               & M$\to$Q & log & observed (financial) & Global common (spot WTI, \$/bbl) \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield         & FRED & \texttt{DGS10} \textit{[FLAG]}                          & D$\to$Q & lin & observed (financial) & Global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield        & FRED & \texttt{BAA} \textit{[FLAG]}                            & M$\to$Q & lin & observed (financial) & Global common (credit proxy) \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500)          & FRED & \texttt{SP500}-class \textit{[FLAG]}                    & D$\to$Q & log & observed (financial) & Global common \\
\texttt{CREDIT\_GDP\_IS} & Credit to NFCs (\% of GDP) & \textbf{IMF IFS (CONSTRUCTED)} & $100\times$\texttt{FOSAOP\_XDC}$/$4Q-trailing \texttt{NGDP\_SA\_XDC} & Q & lin & \textbf{masked 2020Q2--Q4} & \textbf{NEW.} 91 present, range 83.0--317.7\% (318\% = 2008 banking-crisis peak); last 2025Q1 \\
\texttt{LENDR\_IS}  & Bank lending rate (\% p.a.)   & \textbf{IMF IFS} & \texttt{FILR\_PA} (DBnomics mirror)                    & Q & lin & observed (financial) & \textbf{NEW.} IMF-compiled national lending rate (source CBI); 100 present, range 5.2--23.0\%; last 2025Q2 \\
\end{longtable}}

\noindent\textit{[FLAG: \texttt{CREDIT\_GDP\_IS} constructed / non-BIS.]}
Iceland is not a BIS total-credit reporter, so the quantity is constructed
identically to Costa Rica: $100\times$ (IMF IFS ODC claims on the private
sector, \texttt{FOSAOP\_XDC}, ISK) over a 4-quarter trailing sum of
nominal GDP (\texttt{NGDP\_SA\_XDC}).  This is \emph{broad private-sector}
credit (HH $+$ NFC) used as the NFC proxy --- its level (and the
historically accurate $\sim$318\% 2008-crisis peak) is not directly
comparable to the BIS broad-NFC \%GDP series for CZ/HU/PL.  The price
\texttt{LENDR\_IS} is the IMF IFS \texttt{FILR\_PA} (IMF-compiled national
lending rate sourced from the Central Bank of Iceland); both new series
have ragged trailing edges handled by the Gibbs.
\textit{[FLAG: IS base macro provenance.]} The exact source and series
identifiers for the \emph{base} IS macro/financial variables (real
national accounts, \texttt{CPI\_IS}, \texttt{LR\_IS}, \texttt{RATE\_IS}
3M interbank, \texttt{NEER\_IS}) could not be determined from the builders
present in the current pipeline tree; \texttt{RATE\_IS} is plausibly the
FRED OECD 3M interbank series \texttt{IR3TIB01ISQ156N} and the national
accounts are plausibly OECD QNA / Statistics Iceland, but the precise keys
are not verifiable from the available scripts and are \emph{not}
fabricated here.  Only \texttt{POLRATE\_IS} and \texttt{HP\_IS} (added by
\texttt{build\_polrate\_hp\_group.py}) and the two new credit variables
have fully traceable sources.

% =====================================================================
% 4. OTHER ADVANCED ECONOMIES (AU, CH, DK, NO, SE, NZ, KR, IL)
% =====================================================================
%% ===================================================================
%% Per-country DATA documentation -- advanced-economy GVAR blocs
%% (AU, CH, DK, NO, SE, NZ, KR, IL) with the new credit/price block.
%%
%% Style: matches docs/user_manual.tex (booktabs + longtable preamble,
%% \texttt ids, \checkmark financial tag).  Insert under the DATA part
%% of the manual (after sec:varcoherence).  Authoritative final variable
%% list per economy is the staged pipeline/credit_staging/<CC>/spec.json.
%%
%% Transformation convention (stated once, used throughout):
%%   log = 100*log(level); enters the VAR in q/q-annualized growth, i.e.
%%         4*Delta log (displayed as the annualized growth rate).
%%   lin = level (percent for rates/ratios, index for NEER).
%% COVID-as-missing: every macro variable (isFinancial = 0) is masked
%% (set to missing) over 2020Q2-2020Q4 and imputed by the Durbin-Koopman
%% data-augmentation Gibbs; financial variables (isFinancial = 1) are kept
%% observed through the COVID window.
%% ===================================================================

\subsection{Advanced-Economy Blocs: Per-Variable Data Provenance}\label{sec:data:adv}

This subsection documents, variable by variable, the eight advanced-economy
GVAR blocs that carry the new credit block: Australia, Switzerland, Denmark,
Norway, Sweden, New Zealand, Korea, and Israel. Each is a coupled GVAR bloc:
the staged \texttt{spec.json} lists the domestic and global-commons variables;
the estimator additionally appends the three trade-weighted \texttt{ROW*\_<CC>}
star variables (Section~\ref{sec:gvar-roster}) at re-estimation, so the
deployed $n$ is the staged $n$ plus three.

\paragraph{Conventions used in every table.} The \emph{Transformation} column
follows the manual-wide convention: \texttt{log} denotes $100\cdot\log(\text{level})$,
which enters the VAR as $4\,\Delta\log$ (quarter-on-quarter annualized growth),
and \texttt{lin} denotes the raw level (percent per annum for rates and ratios;
an index for NEER and house prices). The \emph{COVID} column records the
COVID-as-missing treatment of Section~\ref{sec:covid}: macro variables
(those with \texttt{isFinancial}~$=0$) are masked over 2020Q2--2020Q4 and
imputed by the data-augmentation Gibbs sampler, whereas financial variables
are held observed through the pandemic. The four global commons
(\texttt{GLB\_OIL}, \texttt{GLB\_USLR}, \texttt{GLB\_USBAA}, \texttt{GLB\_USEQ})
are US-sourced series shared across all blocs
(Section~\ref{sec:gvar:commons}): WTI spot oil (FRED \texttt{WTISPLC},
quarter-average), the US 10Y Treasury yield (FRED \texttt{DGS10}), the US Baa
corporate yield (FRED \texttt{BAA}), and the US equity price index
(FRED \texttt{SPASTT01USM661N}, OECD US share-price/S\&P proxy). They are kept
observed through COVID. Where the exact upstream series identifier for a
domestic \emph{base} macro/financial variable (real-activity aggregates, CPI/HICP,
unemployment, NEER, short rate, long yield, policy rate, house price) cannot be
recovered from a machine-readable builder in the pipeline, the source is
attributed at the provider level documented in Section~\ref{sec:datasources}
(OECD Quarterly National Accounts, the IMF SDMX flows, Eurostat, BIS, and
national central banks) and the per-series id is marked
\textit{[FLAG: series id not recoverable from a readable builder]} rather than
fabricated. The new \textbf{credit-block} variables
(\texttt{CREDIT\_GDP\_<CC>} and \texttt{LENDR\_<CC>}/\texttt{CORP\_<CC>}) carry
fully traced, live-probed identifiers from the dedicated fetchers
(\texttt{fetch\_rba\_f7.py}, \texttt{fetch\_snb\_lendr.py},
\texttt{fetch\_dk\_lendr.py}, \texttt{fetch\_ssb\_jsonstat.py},
\texttt{fetch\_scb\_pxweb.py}, \texttt{fetch\_rbnz\_b3.py},
\texttt{fetch\_credit\_kr.py}, \texttt{fetch\_credit\_il.py},
\texttt{fetch\_bis\_credit\_gdp.py}) and are flagged prominently below.

\paragraph{The new credit block (all eight economies).} Each bloc gains two
appended variables, both \texttt{lin} with a random-walk (RW) prior and
\texttt{isFinancial}~$=1$ in the \texttt{domestic} block:
\begin{itemize}\itemsep1pt
  \item \textbf{Quantity, \texttt{CREDIT\_GDP\_<CC>}} -- BIS ``Total credit to
    non-financial corporations, \% of GDP'' (broad credit: bank loans $+$ debt
    securities $+$ cross-border lending, adjusted for breaks), pulled via FRED
    under the uniform mnemonic \texttt{Q<ISO2>NAM770A}
    (\texttt{fetch\_bis\_credit\_gdp.py}). It is \emph{COVID-masked}
    2020Q2--Q4 (it inherits the GDP-denominator mask: treated as a macro-like
    quantity even though tagged financial), the three quarters set to JSON
    \texttt{null} and imputed by the Gibbs.
  \item \textbf{Price, \texttt{LENDR\_<CC>}} (a bank/corporate lending rate) or
    \textbf{\texttt{CORP\_<CC>}} (a corporate-bond yield) -- \emph{observed
    through COVID} (not masked), \% p.a.
\end{itemize}
None of these eight economies has a dropped price or a constructed
(non-BIS) quantity; the quantity is the canonical BIS broad-credit series for
all eight. Economy-specific caveats (short price history, leading ragged edges,
a price-source substitution, a transport workaround, and one reconstructed
corporate yield) are flagged in the relevant tables.

% -------------------------------------------------------------------
\subsection{Australia (AU)}\label{sec:data:AU}

The Australian bloc has $n=18$ staged variables (deployed $n=21$ with the three
\texttt{ROW*\_AU} stars), estimated on the quarterly window 1999Q1--2025Q4.
The eight macro variables (real GDP, consumption, government consumption,
investment, exports, imports, CPI, unemployment) are masked over 2020Q2--Q4 and
imputed; all financial variables are kept observed.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{Australia (\texttt{AU}): per-variable data provenance. Trans.\ key:
\texttt{log}~$=100\log$ level (enters as $4\Delta\log$, q/q-annualized growth);
\texttt{lin}~$=$ level.}\label{tab:data:AU}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Australia (\texttt{AU}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_AU} & Real GDP & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_AU} & Real household consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_AU} & Real govt consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_AU} & Real investment (GFCF) & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_AU} & Real exports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_AU} & Real imports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CPI\_AU} & CPI, all items (index) & IMF SDMX & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_AU} & Unemployment rate & IMF SDMX & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{NEER\_AU} & NEER (index) & IMF SDMX & \textit{[FLAG]} & Q & log & observed & financial\\
\texttt{RATE\_AU} & Cash rate (interbank o/n) & RBA / IMF & \textit{[FLAG]} & Q & lin & observed & policy short rate\\
\texttt{YIELD10\_AU} & 10Y govt bond yield & RBA / IMF & \textit{[FLAG]} & Q & lin & observed & financial\\
\texttt{HP\_AU} & Real residential house-price index (2010=100) & BIS RPP & FRED \texttt{QAUR628BIS} (BIS real RPP) & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_AU} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QAUNAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 105 obs, 1999Q1=63.5$\to$2025Q4=62.1 (58.8--80.6)\\
\texttt{LENDR\_AU} & Business lending rate (RBA F7, outstanding large-business total, \% p.a.) & RBA Table F7 & \texttt{FLRBFOLBT} (\texttt{fetch\_rba\_f7.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price; \textit{[FLAG: short history --- starts 2019Q3, 26 obs; 1999Q1--2019Q2 leading null, Gibbs-imputed]}\\
\end{longtable}}

% -------------------------------------------------------------------
\subsection{Switzerland (CH)}\label{sec:data:CH}

The Swiss bloc has $n=17$ staged variables (deployed $n=20$), estimated on
2009Q2--2025Q4. Switzerland is one of the rate-optional blocs: it carries a
policy rate (\texttt{POLRATE\_CH}) but no separate domestic short rate. Seven
macro variables are COVID-masked.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{Switzerland (\texttt{CH}): per-variable data provenance.}\label{tab:data:CH}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Switzerland (\texttt{CH}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CH} & Real GDP & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_CH} & Real consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_CH} & Real investment & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_CH} & Real govt consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_CH} & Real exports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_CH} & Real imports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{HICP\_CH} & HICP (index) & IMF SDMX & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_CH} & Unemployment rate & IMF SDMX & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{NEER\_CH} & NEER (index) & IMF SDMX & \textit{[FLAG]} & Q & log & observed & financial\\
\texttt{POLRATE\_CH} & Policy rate (BIS CBPOL) & BIS & BIS \texttt{WS\_CBPOL} \texttt{M.CH} & M$\to$Q-avg & lin & observed & policy rate; \textit{[FLAG: id by convention]}\\
\texttt{HP\_CH} & Real residential property price & BIS RPP & FRED \texttt{QCHR628BIS} & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_CH} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QCHNAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 64 obs, 2009Q2=99.6$\to$2025Q4=128.9 (99.6--149.4)\\
\texttt{LENDR\_CH} & Corporate lending rate (SNB new investment loans, fixed rate, \% p.a.) & SNB data portal & cube \texttt{zikreddet} item \texttt{FI} (\texttt{fetch\_snb\_lendr.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price; 67 obs, 2009Q2=1.80$\to$2025Q4=1.94 (1.46--3.20); clean\\
\end{longtable}}

% -------------------------------------------------------------------
\subsection{Denmark (DK)}\label{sec:data:DK}

The Danish bloc has $n=19$ staged variables (deployed $n=22$), estimated on
2009Q1--2025Q4. Seven macro variables are COVID-masked. Denmark carries both a
3-month rate and a policy rate.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{Denmark (\texttt{DK}): per-variable data provenance.}\label{tab:data:DK}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Denmark (\texttt{DK}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_DK} & Real GDP & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_DK} & Real consumption & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_DK} & Real investment & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_DK} & Real govt consumption & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_DK} & Real exports & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_DK} & Real imports & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{HICP\_DK} & HICP (index) & Eurostat & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_DK} & Unemployment rate & Eurostat & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{RATE\_DK} & 3-month rate & IMF / Eurostat & \textit{[FLAG]} & Q & lin & observed & short rate\\
\texttt{YIELD10\_DK} & 10Y govt bond yield & IMF / Eurostat & \textit{[FLAG]} & Q & lin & observed & financial\\
\texttt{NEER\_DK} & NEER (index) & IMF SDMX & \textit{[FLAG]} & Q & log & observed & financial\\
\texttt{POLRATE\_DK} & Policy rate (BIS CBPOL) & BIS & BIS \texttt{WS\_CBPOL} \texttt{M.DK} & M$\to$Q-avg & lin & observed & policy rate; \textit{[FLAG: id by convention]}\\
\texttt{HP\_DK} & Real residential property price & BIS RPP & FRED \texttt{QDKR628BIS} & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_DK} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QDKNAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 65 obs, 2009Q1=134.5$\to$2025Q4=140.8 (127.4--151.6)\\
\texttt{LENDR\_DK} & Corporate lending rate (ECB MIR loans to NFCs, new business, \% p.a.) & ECB Data Portal (MIR) & \texttt{M.\allowbreak DK.\allowbreak B.\allowbreak A2A.\allowbreak A.\allowbreak R.\allowbreak A.2240.\allowbreak DKK.\allowbreak N} (\texttt{fetch\_dk\_lendr.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price; 34 obs, 2017Q3=1.01$\to$2025Q4=3.19 (0.73--5.00); \textit{[FLAG: source substitution + leading gap --- see below]}\\
\end{longtable}}

\noindent\textit{[FLAG: DK price source substitution.] Danmarks Nationalbank's
StatBank exposes no machine-readable JSON/PX-Web API for the MFI interest-rate
return. The ECB Data Portal (SDW MIR) compiles the \emph{same} Nationalbanken
return (source agency DK2, harmonized under ECB Reg.~290/2009) and is used as
the authoritative substitute --- the data are genuine, only the transport
differs. The ECB MIR Danish NFC rate starts 2017Q3, so \texttt{LENDR\_DK} is
null for 2009Q1--2017Q2 (leading ragged edge, Gibbs-imputed).}

% -------------------------------------------------------------------
\subsection{Norway (NO)}\label{sec:data:NO}

The Norwegian bloc has $n=17$ staged variables (deployed $n=20$), estimated on
2006Q1--2025Q4. Norway is rate-optional: it carries a policy rate
(\texttt{POLRATE\_NO}) but no separate domestic short rate. Seven macro
variables are COVID-masked.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{Norway (\texttt{NO}): per-variable data provenance.}\label{tab:data:NO}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Norway (\texttt{NO}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_NO} & Real GDP & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_NO} & Real consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_NO} & Real investment & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_NO} & Real govt consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_NO} & Real exports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_NO} & Real imports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{HICP\_NO} & HICP (index) & IMF SDMX & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_NO} & Unemployment rate & IMF SDMX & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{NEER\_NO} & NEER (index) & IMF SDMX & \textit{[FLAG]} & Q & log & observed & financial\\
\texttt{POLRATE\_NO} & Policy rate (BIS CBPOL) & BIS & BIS \texttt{WS\_CBPOL} \texttt{M.NO} & M$\to$Q-avg & lin & observed & policy rate; \textit{[FLAG: id by convention]}\\
\texttt{HP\_NO} & Real residential property price & BIS RPP & FRED \texttt{QNOR628BIS} & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_NO} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QNONAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 77 obs, 2006Q1=111.5$\to$2025Q4=135.4 (111.5--157.9)\\
\texttt{LENDR\_NO} & NFC bank lending rate (\% p.a.) & Statistics Norway (SSB) & table \texttt{10746} (Utlanstype=02, Sektor=03 NFC, Rentebinding=99, \texttt{RenterUtNedbLan}; \texttt{fetch\_ssb\_jsonstat.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price; 49 obs, 2013Q4=4.13$\to$2025Q4=6.20 (2.42--6.81); \textit{[FLAG: leading gap 2006Q1--2013Q3, Gibbs-imputed]}\\
\end{longtable}}

% -------------------------------------------------------------------
\subsection{Sweden (SE)}\label{sec:data:SE}

The Swedish bloc has $n=19$ staged variables (deployed $n=22$), estimated on
2005Q1--2025Q4. Seven macro variables are COVID-masked. Sweden carries a
3-month rate, a 10Y yield, and a policy rate.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{Sweden (\texttt{SE}): per-variable data provenance.}\label{tab:data:SE}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Sweden (\texttt{SE}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_SE} & Real GDP & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_SE} & Real consumption & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_SE} & Real investment & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_SE} & Real govt consumption & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_SE} & Real exports & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_SE} & Real imports & Eurostat / OECD & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{HICP\_SE} & HICP (index) & Eurostat & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_SE} & Unemployment rate & Eurostat & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{RATE\_SE} & 3-month rate & IMF / Eurostat & \textit{[FLAG]} & Q & lin & observed & short rate\\
\texttt{YIELD10\_SE} & 10Y govt bond yield & IMF / Eurostat & \textit{[FLAG]} & Q & lin & observed & financial\\
\texttt{NEER\_SE} & NEER (index) & IMF SDMX & \textit{[FLAG]} & Q & log & observed & financial\\
\texttt{POLRATE\_SE} & Policy rate (BIS CBPOL) & BIS & BIS \texttt{WS\_CBPOL} \texttt{M.SE} & M$\to$Q-avg & lin & observed & policy rate; \textit{[FLAG: id by convention]}\\
\texttt{HP\_SE} & Real residential property price & BIS RPP & FRED \texttt{QSER628BIS} & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_SE} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QSENAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 81 obs, 2005Q1=102.1$\to$2025Q4=146.8 (102.1--185.5)\\
\texttt{LENDR\_SE} & NFC bank lending rate (\% p.a.) & Statistics Sweden (SCB) & PxWeb \texttt{FM/\allowbreak FM5001/\allowbreak FM5001C/\allowbreak RantaT01N} (Referenssektor=1.1.1, Motpartssektor=1 NFC, Avtal=0200, ContentsCode=000004ZT; \texttt{fetch\_scb\_pxweb.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price; 84 obs (full), 2005Q1=3.57$\to$2025Q4=3.71 (1.58--5.72); clean\\
\end{longtable}}

% -------------------------------------------------------------------
\subsection{New Zealand (NZ)}\label{sec:data:NZ}

The New Zealand bloc has $n=18$ staged variables (deployed $n=21$), estimated on
2000Q1--2025Q4. Eight macro variables are COVID-masked. NZ carries a policy rate
(OCR) and a 10Y yield.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{New Zealand (\texttt{NZ}): per-variable data provenance.}\label{tab:data:NZ}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape New Zealand (\texttt{NZ}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_NZ} & Real GDP & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_NZ} & Real consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_NZ} & Real investment & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_NZ} & Real govt consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_NZ} & Real exports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_NZ} & Real imports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CPI\_NZ} & CPI (index) & IMF SDMX & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_NZ} & Unemployment rate & IMF SDMX & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{RATE\_NZ} & Policy rate (OCR) & RBNZ / IMF & \textit{[FLAG]} & Q & lin & observed & policy short rate\\
\texttt{YIELD10\_NZ} & 10Y govt bond yield & RBNZ / IMF & \textit{[FLAG]} & Q & lin & observed & financial\\
\texttt{HP\_NZ} & Real residential house-price index (2010=100) & BIS RPP & FRED \texttt{QNZR628BIS} & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{NEER\_NZ} & NEER (index) & IMF SDMX & \textit{[FLAG]} & Q & log & observed & financial\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_NZ} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QNZNAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 101 obs, 2000Q1=83.0$\to$2025Q4=70.1 (69.5--108.8)\\
\texttt{LENDR\_NZ} & Business lending rate (\% p.a.) & RBNZ Table B3 & series A1 ``SME new overdraft rate'' \texttt{INR.\allowbreak MBI06.\allowbreak D3} (\texttt{fetch\_rbnz\_b3.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price; 104 obs (full), 2000Q1=8.53$\to$2025Q4=9.77 (8.16--12.59); \textit{[FLAG: transport workaround --- see below]}\\
\end{longtable}}

\noindent\textit{[FLAG: NZ price transport workaround.] The live RBNZ host is
bot-walled (HTTP 403, Akamai/Imperva) to non-interactive clients. The genuine
RBNZ B3 \texttt{hb3.xlsx} was retrieved via a Wayback Machine snapshot
(2026-01-28) and cached as
\texttt{pipeline/credit\_staging/NZ/\_rbnz\_b3\_A1\_quarterly.json}; the data are
the real RBNZ B3 A1 series (only the transport differs). The older E1 business
lending rate was discontinued Dec-2016; A1 covers the full sample with no gaps.}

% -------------------------------------------------------------------
\subsection{Korea (KR)}\label{sec:data:KR}

The Korean bloc has $n=18$ staged variables (deployed $n=21$), estimated on
2000Q1--2025Q4. Eight macro variables are COVID-masked. Korea carries a 3-month
money-market rate, a policy rate, and a 10Y yield, plus a \emph{true} corporate
bond yield as its credit-block price.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{Korea (\texttt{KR}): per-variable data provenance.}\label{tab:data:KR}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Korea (\texttt{KR}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_KR} & Real GDP & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_KR} & Real household consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_KR} & Real GFCF & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_KR} & Real govt consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_KR} & Real exports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_KR} & Real imports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CPI\_KR} & CPI, all items (index) & IMF SDMX & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_KR} & Unemployment rate & IMF SDMX & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{RATE\_KR} & Money-market rate (3M, short-term) & IMF SDMX & \textit{[FLAG]} & Q & lin & observed & short rate\\
\texttt{POLRATE\_KR} & Policy rate (BIS CBPOL) & BIS & BIS \texttt{WS\_CBPOL} \texttt{M.KR} & M$\to$Q-avg & lin & observed & policy rate; \textit{[FLAG: id by convention]}\\
\texttt{YIELD10\_KR} & Govt bond yield (long-term) & IMF / OECD & \textit{[FLAG]} & Q & lin & observed & financial\\
\texttt{HP\_KR} & Real residential house-price index (2010=100) & BIS RPP & FRED \texttt{QKRR628BIS} & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_KR} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QKRNAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 101 obs, 2000Q1=89.1$\to$2025Q4=110.4 (70.5--114.6)\\
\texttt{CORP\_KR} & Corporate bond yield (3Y, AA-) & Bank of Korea ECOS & table \texttt{721Y001} item \texttt{7020000} (\texttt{fetch\_credit\_kr.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price = \textbf{true AA- corporate yield}; 104 obs, 2000Q1=10.09$\to$2025Q4=3.28 (1.67--10.09)\\
\end{longtable}}

% -------------------------------------------------------------------
\subsection{Israel (IL)}\label{sec:data:IL}

The Israeli bloc has $n=18$ staged variables (deployed $n=21$), estimated on
2000Q1--2024Q4. Eight macro variables are COVID-masked. Israel carries a
3-month T-bill rate and a policy rate; its credit-block price is a
\emph{reconstructed} Tel-Bond corporate yield.

{\small
\begin{longtable}{@{}lp{2.9cm}p{1.9cm}p{2.0cm}cp{1.4cm}p{1.7cm}p{2.6cm}@{}}
\caption{Israel (\texttt{IL}): per-variable data provenance.}\label{tab:data:IL}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endfirsthead
\multicolumn{8}{l}{\small\itshape Israel (\texttt{IL}), continued}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series id/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes}\\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_IL} & Real GDP & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CONS\_IL} & Real household consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{INV\_IL} & Real GFCF & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{GOV\_IL} & Real govt consumption & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{EXP\_IL} & Real exports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{IMP\_IL} & Real imports & OECD QNA & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{CPI\_IL} & CPI, all items (index) & IMF SDMX & \textit{[FLAG]} & Q & log & masked & macro\\
\texttt{LR\_IL} & Unemployment rate & IMF SDMX & \textit{[FLAG]} & Q & lin & masked & macro\\
\texttt{RATE\_IL} & 3M Treasury-bill yield & IMF / BoI & \textit{[FLAG]} & Q & lin & observed & short rate\\
\texttt{POLRATE\_IL} & Policy rate (Bank of Israel) & BoI / BIS & \textit{[FLAG]} & Q & lin & observed & policy rate\\
\texttt{NEER\_IL} & NEER (index) & IMF SDMX & \textit{[FLAG]} & Q & log & observed & financial\\
\texttt{HP\_IL} & Real residential property price & BIS RPP & FRED \texttt{QILR628BIS} & Q & log & observed & financial; \textit{[FLAG: id by convention]}\\
\texttt{GLB\_OIL} & WTI crude, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & Q & log & observed & global common\\
\texttt{GLB\_USLR} & US 10Y Treasury yield & FRED & \texttt{DGS10} & Q & lin & observed & global common\\
\texttt{GLB\_USBAA} & US Baa corporate yield & FRED & \texttt{BAA} & Q & lin & observed & global common\\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common\\
\texttt{CREDIT\_GDP\_IL} & Credit to NFCs (\% of GDP) & BIS (via FRED) & \texttt{QILNAM770A} & Q & lin & \textbf{masked} & \textbf{NEW} broad credit; 97 obs, 2000Q1=69.4$\to$2024Q4=69.3 (66.8--93.1)\\
\texttt{CORP\_IL} & Tel-Bond corporate bond yield (5Y govt $+$ Tel-Bond spread) & Bank of Israel (SDMX) & \texttt{DWH\_SRC\_0356\_MA} $+$ \texttt{DWH\_SRC\_0299\_MA} (\texttt{fetch\_credit\_il.py}) & M$\to$Q-avg & lin & observed & \textbf{NEW} price; 56 obs, 2009Q4=7.03$\to$2024Q4=5.75 (1.89--7.03); \textit{[FLAG: RECONSTRUCTED + leading gap --- see below]}\\
\end{longtable}}

\noindent\textit{[FLAG: IL price is RECONSTRUCTED.] \texttt{CORP\_IL} is built
as the sum of the Bank of Israel 5-year non-indexed fixed-rate \emph{government}
bond yield (\texttt{DWH\_SRC\_0356\_MA}) and the BoI quoted Tel-Bond--vs--govt
yield spread (\texttt{DWH\_SRC\_0299\_MA}); the Tel-Bond Index is Israel's main
corporate-bond index (${\sim}5$Y duration), so the sum is a genuine corporate
yield, not a single published outright series. It was preferred over the BoI
BIR bank business-loan rate, which carries a systematic source anomaly
2017Q2--2018Q1 (values spike to 30--50\%). The Tel-Bond spread starts 2009-12,
so \texttt{CORP\_IL} is null for 2000Q1--2009Q3 (44 leading nulls, Gibbs-imputed);
it is observed continuously through COVID and to end-of-sample.}

%% --- Aggregate flag note (all eight economies) ---------------------
\paragraph{Summary of data flags (advanced-economy blocs).} The genuinely
indeterminate sources --- where the exact upstream series id could not be
recovered from a machine-readable builder and is therefore \emph{not} fabricated
--- are the domestic \emph{base} macro and financial variables (real-activity
aggregates, CPI/HICP, unemployment, NEER, short rate, 10Y yield, and for IL the
policy rate), attributed at the provider level (OECD QNA, IMF SDMX, Eurostat for
DK/SE, BIS, national central banks) per Section~\ref{sec:datasources}. The BIS
real house-price (\texttt{HP\_<CC>}) and BIS policy-rate (\texttt{POLRATE\_<CC>})
ids are stated by the established FRED-mnemonic / BIS-dataflow convention
(marked ``id by convention''). All credit-block ids (quantity and price) are
live-probed and fully traced.

% =====================================================================
% 5. EMERGING MARKETS, GROUP I (BR, MX, CL, CO, IN, ID)
% =====================================================================
%% =====================================================================
%% Per-country DATA documentation: emerging-market GVAR blocs (group 1)
%%   BR, MX, CL, CO, IN, ID
%% Intended for inclusion in docs/user_manual.tex (DATA part).
%% Conventions (stated once here, applied throughout):
%%   * Transformation `log'  = the series enters as 100*log(level); growth
%%     is displayed as 4*Delta(100 log) = q/q-annualized percent.
%%   * Transformation `lin'  = level (percent, ratio, or index), entered and
%%     displayed in levels.
%%   * COVID-as-missing: every macro (non-financial, isFinancial=0) variable
%%     is masked to NaN over the fixed three-quarter window 2020Q2--2020Q4
%%     and imputed by the data-augmentation Gibbs sampler; financial
%%     (isFinancial=1) variables are kept observed through COVID.
%%   * Each bloc below is a coupled GVAR Rest-of-World bloc: the spec.json
%%     documented here lists the domestic block plus the four global commons
%%     (GLB_OIL, GLB_USLR, GLB_USBAA, GLB_USEQ). The three trade-weighted
%%     ROW*_<CC> star variables (ROWDEM, ROWINF, ROWFIN) are appended only at
%%     GVAR-export time (Section~\ref{sec:gvar-roster}) and are therefore not
%%     listed in the staged single-bloc spec.
%% =====================================================================

\subsection{Emerging-market blocs I: BR, MX, CL, CO, IN, ID}\label{sec:data:em1}

This subsection documents six emerging-market GVAR blocs in full, including
the new credit block (a quantity \texttt{CREDIT\_GDP\_<CC>} and a price,
\texttt{LENDR\_<CC>} or \texttt{CORP\_<CC>}) appended to each bloc. Throughout,
``\texttt{log}'' denotes a series entered as $100\ln(\text{level})$ and
displayed as $4\,\Delta(100\ln)$, i.e.\ q/q-annualized growth, while
``\texttt{lin}'' denotes a level (percent, ratio, or index). Under the
\emph{COVID-as-missing} treatment (Section~\ref{sec:covid}) every
\emph{macro} variable (those tagged \texttt{isFinancial}$=0$) is masked over
the fixed window 2020Q2--2020Q4 and imputed by the augmentation Gibbs sampler;
\emph{financial} variables (\texttt{isFinancial}$=1$) are held observed.

\paragraph{The new credit block (all six blocs).} Each bloc gains two
variables, appended after the existing domestic and global-commons columns:
\begin{itemize}\setlength\itemsep{1pt}
  \item \textbf{Quantity} \texttt{CREDIT\_GDP\_<CC>} --- BIS Total Credit to
    Non-Financial Corporations, percentage of GDP (the broad credit measure:
    loans $+$ debt securities $+$ cross-border), pulled from FRED with the BIS
    mnemonic \texttt{Q<CC>NAM770A} (``Total Credit to Non-Financial
    Corporations, Adjusted for Breaks'', units: \% of GDP, native quarterly).
    Transformation \texttt{lin}, prior RW, \texttt{isFinancial}$=1$. Because
    the \%-of-GDP ratio inherits the collapsing-GDP denominator artefact in
    2020, the three cells 2020Q2--Q4 are set to \texttt{null} (masked),
    consistent with the macro COVID mask, and imputed by the Gibbs sampler.
    \textbf{Colombia is the exception:} BIS publishes no Colombia NFC total
    credit, so \texttt{CREDIT\_GDP\_CO} is \emph{constructed} (non-BIS); see
    below and the flag list.
  \item \textbf{Price} --- a domestic credit-cost series, observed through
    COVID (\texttt{lin}, prior RW, \texttt{isFinancial}$=1$). The price source
    differs by bloc: a bank \emph{lending rate} (\texttt{LENDR\_<CC>}) where
    one is available, or a 10-year \emph{government} bond yield used as a
    \emph{sovereign proxy} (\texttt{CORP\_<CC>}) where no corporate/lending
    series exists. Per-bloc provenance and caveats are given in each table and
    flagged where they apply (CL and IN use the sovereign 10Y proxy).
\end{itemize}

% =====================================================================
\subsection{Brazil (BR)}\label{sec:data:BR}

The Brazil bloc is an $n=17$ quarterly BVAR estimated over 2012Q2--2025Q4
($T=55$); macro variables are treated as missing over 2020Q2--Q4 (COVID-as-missing),
while the financial block (including the new credit price) is held observed.
The credit block is \emph{clean}: BIS NFC credit-to-GDP for the quantity and the
Banco Central do Brasil corporate lending rate for the price.

{\footnotesize
\begin{longtable}{@{}llp{2.5cm}p{2.4cm}cclp{2.6cm}@{}}
\caption{Brazil (BR) bloc: variable coverage and provenance. \texttt{log}
$=100\ln$ level (q/q-annualized growth displayed); \texttt{lin} $=$ level.
COVID mask $=$ 2020Q2--Q4.}\label{tab:data:BR}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_BR}  & Real GDP & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CONS\_BR} & Real household consumption & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{INV\_BR}  & Real gross fixed capital formation & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{GOV\_BR}  & Real government consumption & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{EXP\_BR}  & Real exports & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{IMP\_BR}  & Real imports & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CPI\_BR}  & CPI index & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{LR\_BR}   & Unemployment rate & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & masked & macro \\
\texttt{NEER\_BR} & Nominal effective exch.\ rate & BIS / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{POLRATE\_BR} & Policy rate & BIS CBPOL & \texttt{WS\_CBPOL M.BR} & M$\to$Q avg & lin & observed & 3-month avg \\
\texttt{HP\_BR}   & Real residential property price (2010=100) & FRED / BIS real RPP & \texttt{QBRR628BIS} & Q & log & observed & financial \\
\texttt{GLB\_OIL} & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q avg & log & observed & global common \\
\texttt{GLB\_USLR} & US 10Y Treasury yield (\%) & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%) & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q avg & log & observed & global common \\
\texttt{CREDIT\_GDP\_BR} & Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QBRNAM770A} & Q & lin & \textbf{masked} & \textbf{credit (quantity)}; 52/55 non-null; 40.5--57.0\% GDP; only the 3 COVID cells null (clean) \\
\texttt{LENDR\_BR} & Corporate bank lending rate (\% p.a.) & Banco Central do Brasil (BCB SGS) & SGS \texttt{20718} & M$\to$Q avg & lin & observed & \textbf{credit (price)}; \emph{Pessoas Jur\'idicas} avg lending rate; 55/55 non-null; 11.88--31.24\%; fetcher \texttt{fetch\_bcb\_sgs.py} \\
\end{longtable}}

% =====================================================================
\subsection{Mexico (MX)}\label{sec:data:MX}

The Mexico bloc is an $n=19$ quarterly BVAR estimated over 2001Q4--2025Q4
($T=97$); macro variables are masked over 2020Q2--Q4. The credit block uses
BIS NFC credit-to-GDP and the IMF IFS lending rate; the price has a ragged
trailing edge (the IFS series ends 2025Q2, so 2025Q3--Q4 are null and handled
by the Gibbs ragged-edge treatment).

{\footnotesize
\begin{longtable}{@{}llp{2.5cm}p{2.4cm}cclp{2.6cm}@{}}
\caption{Mexico (MX) bloc: variable coverage and provenance.}\label{tab:data:MX}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_MX}  & Real GDP (chain volume, SA) & National accounts / OECD QNA (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CONS\_MX} & Real household consumption (chain vol, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{INV\_MX}  & Real gross fixed capital formation (SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{GOV\_MX}  & Real government consumption (chain vol, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{EXP\_MX}  & Real exports (chain volume, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{IMP\_MX}  & Real imports (chain volume, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CPI\_MX}  & CPI (all items, index) & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{LR\_MX}   & Unemployment rate & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & masked & macro \\
\texttt{RATE\_MX} & Money-market rate (short-term) & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{POLRATE\_MX} & Central-bank policy rate & BIS CBPOL & \texttt{WS\_CBPOL M.MX} & M$\to$Q avg & lin & observed & 3-month avg \\
\texttt{YIELD10\_MX} & Government bond yield (long-term) & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{HP\_MX}   & Real residential house-price index (2010=100) & FRED / BIS real RPP & \texttt{QMXR628BIS} & Q & log & observed & financial \\
\texttt{NEER\_MX} & Nominal effective exch.\ rate (index) & BIS / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{GLB\_OIL} & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q avg & log & observed & global common \\
\texttt{GLB\_USLR} & US 10Y Treasury yield (\%) & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%) & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q avg & log & observed & global common \\
\texttt{CREDIT\_GDP\_MX} & Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QMXNAM770A} & Q & lin & \textbf{masked} & \textbf{credit (quantity)}; 94/97 non-null; 12.3--28.3\% GDP; only the 3 COVID cells null \\
\texttt{LENDR\_MX} & Bank lending rate (\% p.a.) & IMF IFS (via DBnomics) & \texttt{FILR\_PA} & Q & lin & observed & \textbf{credit (price)}; 95/97 non-null; 3.34--11.79\%; \textbf{ragged trailing edge} (IFS ends 2025Q2 $\Rightarrow$ 2025Q3--Q4 null) \\
\end{longtable}}

% =====================================================================
\subsection{Chile (CL)}\label{sec:data:CL}

The Chile bloc is an $n=19$ quarterly BVAR estimated over 2004Q3--2025Q4
($T=86$); macro variables are masked over 2020Q2--Q4. The credit \emph{quantity}
is the BIS NFC credit-to-GDP series, but the credit \emph{price} is a
\textbf{sovereign 10Y proxy} (\texttt{CORP\_CL}): the IMF IFS Chilean lending
rate was discontinued in 2018, so the OECD KEI 10-year \emph{government} bond
yield stands in --- there is no corporate spread.

{\footnotesize
\begin{longtable}{@{}llp{2.5cm}p{2.4cm}cclp{2.6cm}@{}}
\caption{Chile (CL) bloc: variable coverage and provenance.}\label{tab:data:CL}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CL}  & Real GDP & National accounts / OECD QNA (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CONS\_CL} & Real household consumption & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{INV\_CL}  & Real gross fixed capital formation & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{GOV\_CL}  & Real government consumption & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{EXP\_CL}  & Real exports & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{IMP\_CL}  & Real imports & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CPI\_CL}  & CPI index & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{LR\_CL}   & Unemployment rate & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & masked & macro \\
\texttt{RATE\_CL} & 3M interbank rate & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{POLRATE\_CL} & Central-bank policy rate & BIS CBPOL & \texttt{WS\_CBPOL M.CL} & M$\to$Q avg & lin & observed & 3-month avg \\
\texttt{YIELD10\_CL} & 10Y government bond yield & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{HP\_CL}   & Real residential house-price index (2010=100) & FRED / BIS real RPP & \texttt{QCLR628BIS} & Q & log & observed & financial \\
\texttt{NEER\_CL} & Nominal effective exch.\ rate & BIS / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{GLB\_OIL} & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q avg & log & observed & global common \\
\texttt{GLB\_USLR} & US 10Y Treasury yield (\%) & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%) & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q avg & log & observed & global common \\
\texttt{CREDIT\_GDP\_CL} & Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QCLNAM770A} & Q & lin & \textbf{masked} & \textbf{credit (quantity)}; 83/86 non-null; 60.5--111.9\% GDP; 3 COVID cells null \\
\texttt{CORP\_CL} & 10Y government bond yield (sovereign proxy) & OECD KEI long-term interest rates (IRLT) & IRLT, country \texttt{CHL} & M$\to$Q avg & lin & observed & \textbf{credit (price)}; \textbf{SOVEREIGN 10Y PROXY --- no corporate spread}; 86/86 non-null; 2.51--7.78\% \\
\end{longtable}}

% =====================================================================
\subsection{Colombia (CO)}\label{sec:data:CO}

The Colombia bloc is an $n=19$ quarterly BVAR estimated over 2005Q1--2025Q4
($T=84$); macro variables are masked over 2020Q2--Q4. Colombia is \emph{not} a
BIS total-credit reporter, so the credit \emph{quantity} is a
\textbf{constructed (non-BIS) broad-credit proxy} (reducing cross-country
comparability); the credit \emph{price} is the IMF IFS lending rate. Both
credit columns carry trailing nulls from the input cut-off (2025Q1 for the
constructed quantity inputs; the IFS price ends mid-2025).

{\footnotesize
\begin{longtable}{@{}llp{2.5cm}p{2.4cm}cclp{2.6cm}@{}}
\caption{Colombia (CO) bloc: variable coverage and provenance.}\label{tab:data:CO}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CO}  & Real GDP & National accounts / OECD QNA (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CONS\_CO} & Real household consumption & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{INV\_CO}  & Real gross fixed capital formation & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{GOV\_CO}  & Real government consumption & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{EXP\_CO}  & Real exports & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{IMP\_CO}  & Real imports & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CPI\_CO}  & CPI index & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{LR\_CO}   & Unemployment rate & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & masked & macro \\
\texttt{RATE\_CO} & 3M interbank rate & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{POLRATE\_CO} & Central-bank policy rate & BIS CBPOL & \texttt{WS\_CBPOL M.CO} & M$\to$Q avg & lin & observed & 3-month avg \\
\texttt{YIELD10\_CO} & 10Y government bond yield & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{HP\_CO}   & Real residential house-price index (2010=100) & FRED / BIS real RPP & \texttt{QCOR628BIS} & Q & log & observed & financial \\
\texttt{NEER\_CO} & Nominal effective exch.\ rate & BIS / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{GLB\_OIL} & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q avg & log & observed & global common \\
\texttt{GLB\_USLR} & US 10Y Treasury yield (\%) & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%) & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q avg & log & observed & global common \\
\texttt{CREDIT\_GDP\_CO} & Credit to NFCs (\% of GDP), constructed & IMF IFS (constructed: claims $\div$ 4Q-trailing NGDP) & \texttt{FOSAOP\_XDC} / \texttt{NGDP\_SA\_XDC} & Q & lin & \textbf{masked} & \textbf{credit (quantity), CONSTRUCTED (non-BIS)} $=100\times$ ODC claims on private sector $\div$ 4Q-trailing nominal GDP; broad private credit (households $+$ NFCs), reduced comparability; 75/84 non-null; 22.7--51.6\%; nulls $=$ 3 leading $+$ 3 COVID $+$ 3 trailing (inputs end 2025Q1) \\
\texttt{LENDR\_CO} & Bank lending rate (\% p.a.) & IMF IFS (via DBnomics) & \texttt{FILR\_PA} & Q & lin & observed & \textbf{credit (price)}; 82/84 non-null; 8.59--22.70\%; ragged trailing edge (2025Q3--Q4 null) \\
\end{longtable}}

% =====================================================================
\subsection{India (IN)}\label{sec:data:IN}

The India bloc is an $n=19$ quarterly BVAR estimated over 2011Q4--2025Q4
($T=57$); macro variables are masked over 2020Q2--Q4. The credit \emph{quantity}
is the BIS NFC credit-to-GDP series; the credit \emph{price} is a
\textbf{sovereign 10Y proxy} (\texttt{CORP\_IN}): no Indian corporate or bank
lending rate is currently maintained on FRED/IMF/World Bank (the IFS lending
rate was discontinued in 2022), so the OECD KEI 10-year \emph{government} bond
yield stands in --- there is no corporate spread.

{\footnotesize
\begin{longtable}{@{}llp{2.5cm}p{2.4cm}cclp{2.6cm}@{}}
\caption{India (IN) bloc: variable coverage and provenance.}\label{tab:data:IN}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_IN}  & Real GDP (chain volume, SA) & National accounts / OECD QNA (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CONS\_IN} & Real household consumption (chain vol, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{INV\_IN}  & Real gross fixed capital formation (chain vol, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{GOV\_IN}  & Real government consumption (chain vol, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{EXP\_IN}  & Real exports of goods \& services (chain vol, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{IMP\_IN}  & Real imports of goods \& services (chain vol, SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CPI\_IN}  & CPI (all items, index) & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{RATE\_IN} & Call money / immediate interbank rate & FRED (OECD MEI) & \texttt{IRSTCI01INM} & M$\to$Q avg & lin & observed & financial \\
\texttt{RATE3M\_IN} & Short-term 3M interbank rate & FRED (OECD MEI) & \texttt{INDIR3TIB01STM} & M$\to$Q avg & lin & observed & financial \\
\texttt{YIELD10\_IN} & Long-term 10Y government bond yield & FRED (OECD MEI) & \texttt{INDIRLTLT01STM} & M$\to$Q avg & lin & observed & financial \\
\texttt{NEER\_IN} & Nominal effective exch.\ rate (BIS broad, index) & BIS / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{POLRATE\_IN} & Policy rate & BIS CBPOL & \texttt{WS\_CBPOL M.IN} & M$\to$Q avg & lin & observed & 3-month avg \\
\texttt{HP\_IN}   & Real residential property price (2010=100) & FRED / BIS real RPP & \texttt{QINR628BIS} & Q & log & observed & financial \\
\texttt{GLB\_OIL} & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q avg & log & observed & global common \\
\texttt{GLB\_USLR} & US 10Y Treasury yield (\%) & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%) & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q avg & log & observed & global common \\
\texttt{CREDIT\_GDP\_IN} & Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QINNAM770A} & Q & lin & \textbf{masked} & \textbf{credit (quantity)}; 54/57 non-null; 49.7--77.7\% GDP; 3 COVID cells null \\
\texttt{CORP\_IN} & 10Y government bond yield (sovereign proxy) & OECD KEI long-term interest rates (IRLT) & IRLT, country \texttt{IND} & M$\to$Q avg & lin & observed & \textbf{credit (price)}; \textbf{SOVEREIGN 10Y PROXY --- no corporate spread}; 57/57 non-null; 5.91--8.81\% \\
\end{longtable}}

% =====================================================================
\subsection{Indonesia (ID)}\label{sec:data:ID}

The Indonesia bloc is an $n=17$ quarterly BVAR estimated over 2005Q3--2025Q4
($T=82$); macro variables are masked over 2020Q2--Q4. The credit block is
\emph{clean}: BIS NFC credit-to-GDP for the quantity and the IMF IFS lending
rate (fully observed, current to 2025Q4) for the price.

{\footnotesize
\begin{longtable}{@{}llp{2.5cm}p{2.4cm}cclp{2.6cm}@{}}
\caption{Indonesia (ID) bloc: variable coverage and provenance.}\label{tab:data:ID}\\
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_ID}  & Real GDP (SA, constant prices) & National accounts / OECD QNA (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CONS\_ID} & Real private consumption (SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{INV\_ID}  & Real gross fixed capital formation (SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{GOV\_ID}  & Real government consumption (SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{EXP\_ID}  & Real exports of goods \& services (SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{IMP\_ID}  & Real imports of goods \& services (SA) & National accounts (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{CPI\_ID}  & CPI (all items, index) & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & masked & macro \\
\texttt{RATE\_ID} & Monetary policy-related rate (BI rate) & National source / IMF (GVAR panel) & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{NEER\_ID} & Nominal effective exch.\ rate (BIS broad) & BIS / IMF (GVAR panel) & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{POLRATE\_ID} & Policy rate & BIS CBPOL & \texttt{WS\_CBPOL M.ID} & M$\to$Q avg & lin & observed & 3-month avg \\
\texttt{HP\_ID}   & Real residential property price (2010=100) & FRED / BIS real RPP & \texttt{QIDR628BIS} & Q & log & observed & financial \\
\texttt{GLB\_OIL} & WTI crude oil, q-avg (\$/bbl) & FRED & \texttt{WTISPLC} & M$\to$Q avg & log & observed & global common \\
\texttt{GLB\_USLR} & US 10Y Treasury yield (\%) & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%) & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ} & US equity (S\&P 500) & FRED & \texttt{SPASTT01USM661N} & M$\to$Q avg & log & observed & global common \\
\texttt{CREDIT\_GDP\_ID} & Credit to NFCs (\% of GDP) & BIS via FRED & \texttt{QIDNAM770A} & Q & lin & \textbf{masked} & \textbf{credit (quantity)}; 79/82 non-null; 13.1--27.7\% GDP; 3 COVID cells null \\
\texttt{LENDR\_ID} & IFS lending rate (\% p.a.) & IMF IFS (\texttt{MFS\_IR}, new SDMX 2.1 API) & \texttt{MFS162\_RT\_PT\_A\_PT} (= IFS \texttt{FILR\_PA}) & Q & lin & observed & \textbf{credit (price)}; 82/82 non-null; 8.21--16.34\%; fully observed, current to 2025Q4; fetcher \texttt{fetch\_imf\_lendr.py} \\
\end{longtable}}

\paragraph{Caveats and provenance flags for this group.}
The \emph{credit-block} provenance above is traced to specific FRED/IMF/OECD/BCB
series and verified against the staged data (first/last/coverage all reconcile).
The flagged items are:
\begin{itemize}\setlength\itemsep{1pt}
  \item \texttt{CORP\_CL}, \texttt{CORP\_IN}: credit \emph{price} is a
    \textbf{sovereign 10Y proxy} (OECD KEI government-bond yield), not a
    corporate/lending rate --- no corporate spread is captured (CL: IFS lending
    rate discontinued 2018; IN: IFS lending rate discontinued 2022).
  \item \texttt{CREDIT\_GDP\_CO}: \textbf{constructed, non-BIS} broad-credit
    proxy ($100\times$ IMF IFS ODC claims on the private sector $\div$
    4Q-trailing nominal GDP); it mixes households $+$ NFCs (not NFC-specific)
    and so has reduced cross-country comparability. (BIS publishes no Colombia
    NFC total-credit series; the mnemonic \texttt{QCONAM770A} on FRED is
    \emph{Argentina}, not Colombia --- a verified mnemonic trap.)
  \item \texttt{LENDR\_MX}, \texttt{LENDR\_CO}: credit-price series have a
    \textbf{ragged trailing edge} (IFS \texttt{FILR\_PA} ends mid-2025), so
    2025Q3--Q4 are null and imputed by the ragged-edge Gibbs treatment.
\end{itemize}
\textit{[FLAG: base macro / domestic-financial series IDs not recorded in the
staged artefacts.]} For the pre-existing domestic block (real GDP, the
national-accounts expenditure components, CPI, unemployment, NEER, and the
domestic short/long rates), the staged \texttt{DataRaw\_<CC>\_glob.json} files
carry only the variable list, dates, and values --- no per-series source
mnemonic. These columns originate from the upstream GVAR national-source
quarterly panel (national statistical offices / OECD QNA / IMF flows, balanced
to a common 2025Q4 endpoint via WEO-benchmarked temporal disaggregation in
\texttt{build\_gvar\_2025q4.py}); the exact provider series IDs are therefore
\emph{not} determinable from the artefacts inspected and are left flagged rather
than fabricated. The cells documented with a concrete ID --- \texttt{POLRATE}
(BIS CBPOL \texttt{WS\_CBPOL M.<CC>}), \texttt{HP} (FRED BIS real RPP
\texttt{Q<CC>R628BIS}), the four global commons (FRED), the India domestic
rates (FRED/OECD MEI \texttt{IRSTCI01INM}, \texttt{INDIR3TIB01STM},
\texttt{INDIRLTLT01STM}, traced in the research report), and the whole credit
block --- are confirmed against their builders.

\textit{[FLAG: India domestic-rate IDs are inferred from the research report's
FRED enumeration (\texttt{IRSTCI01INM}, \texttt{INDIR3TIB01STM},
\texttt{INDIRLTLT01STM}); they match the OECD-MEI rate definitions used for IN
but were not independently re-fetched in this documentation pass.]}

% =====================================================================
% 6. EMERGING MARKETS, GROUP II (TR, ZA, SA, AR, RU, TH, MY, TW)
% =====================================================================
% em2 opens with a bare \paragraph; give the conventions a home heading.
\subsection{Emerging markets II: data conventions (TR, ZA, SA, AR, RU, TH, MY, TW)}\label{sec:data:em2}
%% ====================================================================
%% Per-economy DATA documentation: TR, ZA, SA, AR, RU, TH, MY, TW
%% Generated for the DATA section of the BVAR/GVAR user manual.
%% Matches docs/user_manual.tex (booktabs + longtable loaded).
%% Authoritative variable list: pipeline/credit_staging/<CC>/spec.json.
%% ====================================================================

%% --------------------------------------------------------------------
%% Conventions paragraph (state once before the per-economy subsections)
%% --------------------------------------------------------------------
\paragraph{Transformation and COVID conventions.}
Throughout these tables the \emph{transformation} column follows the tool-wide
convention of Section~\ref{sec:varcoherence}: \texttt{log} denotes a series
stored as $100\cdot\log(\text{level})$, which enters the VAR and is reported as
$4\cdot\Delta\log = $ the quarter-on-quarter \emph{annualized} growth rate; and
\texttt{lin} denotes a level (rates in percent, ratios in percent of GDP, index
points). The \emph{prior} on every variable's own first lag is the random walk
(RW) unless noted. \emph{COVID-as-missing} (Section~\ref{sec:covid}) masks the
three quarters 2020Q2--2020Q4 of every \emph{macro} variable (those tagged
\texttt{isFinancial}$=0$); these holes are completed inside the
Durbin--Koopman E-step rather than fitted. \emph{Financial} variables
(\texttt{isFinancial}$=1$) are held \emph{observed} through the COVID window.
The four \emph{global commons} are identical US-determined columns shared by
every bloc and pinned $1{:}1$ onto each RoW bloc at solve time
(Section~\ref{sec:gvar:commons}): \texttt{GLB\_OIL} = FRED \texttt{WTISPLC}
(WTI spot, \$/bbl, quarterly average); \texttt{GLB\_USLR} = FRED \texttt{DGS10}
(US 10Y Treasury constant-maturity yield); \texttt{GLB\_USBAA} = FRED
\texttt{BAA} (Moody's seasoned Baa corporate-bond yield); \texttt{GLB\_USEQ} =
US equity price index (FRED \texttt{SPASTT01USM661N}, OECD US share-price/S\&P
proxy). All four are financial and observed through COVID.

\paragraph{The new credit block.}
Each of these eight blocs is augmented with a \emph{credit block} of one or two
variables. The \emph{quantity} leg \texttt{CREDIT\_GDP\_<CC>} is, wherever a BIS
reporting series exists, the BIS \emph{Total Credit to Non-Financial
Corporations}, percent of GDP (the \emph{broad} credit concept: bank loans plus
debt securities plus cross-border lending), pulled from FRED under the uniform
mnemonic \texttt{Q<ISO2>NAM770A} (end-of-quarter, \% of GDP). It is stored
\texttt{lin}/RW and is tagged \emph{financial}, but because its denominator is
nominal GDP it inherits the macro COVID mask: its 2020Q2--Q4 cells are set
\texttt{null}. The \emph{price} leg is either a bank lending rate
(\texttt{LENDR\_<CC>}) or, where no lending rate is reachable, a
corporate/sovereign-proxy yield (\texttt{CORP\_<CC>}); it is \texttt{lin}/RW,
financial, and \emph{observed} through COVID. Where the price could not be
sourced it was \emph{dropped} (quantity only). Bloc-specific caveats are flagged
in-line below.

%% ====================================================================
\subsection{T\"urkiye (TR)}\label{sec:data:TR}
%% ====================================================================

T\"urkiye is a coupled GVAR bloc estimated with $n=16$ quarterly domestic +
global variables (the staged credit spec; the deployed GVAR bloc adds the three
\texttt{ROW*\_TR} trade-weighted stars) at $p=3$ lags over a quarterly grid
running 2000Q1--2025Q4 ($T=104$). The eight real-activity, price and labour
series are masked over COVID 2020Q2--Q4 and completed by the Durbin--Koopman
E-step; financials are kept observed. The credit block is \emph{quantity-only}:
the bank-lending-rate / corporate-yield price leg was dropped (flag below).

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{T\"urkiye (TR) variable documentation.}\label{tab:data:TR}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_TR}    & Real GDP                              & IMF/OECD QNA (GVAR base) & \textit{[FLAG]} & Q & log & masked & WEO-extended to 2025Q4 \\
\texttt{CONS\_TR}   & Real household consumption            & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{INV\_TR}    & Real gross fixed capital formation    & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{GOV\_TR}    & Real government consumption           & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{EXP\_TR}    & Real exports                          & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{IMP\_TR}    & Real imports                          & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{CPI\_TR}    & CPI, all items (index)                & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & \\
\texttt{LR\_TR}     & Unemployment rate                     & IMF IFS / national & \textit{[FLAG]} & Q & lin & masked & \\
\texttt{RATE\_TR}   & Monetary-policy-related (short) rate  & IMF IFS / national & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{POLRATE\_TR}& Policy rate (BIS CBPOL)               & BIS SDMX WS\_CBPOL & \texttt{M.TR} (3M avg) & Q & lin & observed & financial \\
\texttt{HP\_TR}     & Real residential property price       & FRED (BIS real RPP) & \texttt{QTRR628BIS} & Q & log & observed & financial \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)             & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)            & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)           & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)            & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_TR} & Credit to NFCs (\% of GDP) [NEW: credit quantity] & BIS via FRED & \texttt{QTRNAM770A} & Q & lin & masked & RW; nonnull 101/104, range 17.5--78.1\%; 2000Q1=23.2, 2025Q4=38.9; COVID cells \texttt{null} \\
\end{longtable}}

\noindent\textit{[FLAG: TR credit PRICE DROPPED]} No reachable free NFC lending
rate or corporate/sovereign yield: OECD IRLT/FINMARK is empty for TUR; the IMF
\texttt{MFS\_IR} flow carries only discount/deposit/policy-related rates for TUR
(which would duplicate \texttt{RATE\_TR}/\texttt{POLRATE\_TR}); the CBRT EVDS
commercial-loan rate (\texttt{TP.KTF12}) needs an EVDS API key not available;
FRED Turkey rate series are stale ($\le$2022). Per the locked spec the TR credit
block is \emph{quantity only}.\\
\textit{[FLAG: TR base-macro series IDs]} The provider-class for the eight base
real-activity/price/labour series and the short rate is documented at the GVAR
roster level (Section~\ref{sec:datasources}: OECD QNA / IMF flows, extended to
2025Q4 by \texttt{build\_gvar\_2025q4.py} via WEO temporal disaggregation), but
the upstream raw file \texttt{country\_rawdata/DataRaw\_TR\_glob.json} carries no
per-variable source/series-id stamp, so the exact provider series codes for
\texttt{GDP/CONS/INV/GOV/EXP/IMP/CPI/LR/RATE} cannot be asserted from the
artifacts and are not fabricated here.

%% ====================================================================
\subsection{South Africa (ZA)}\label{sec:data:ZA}
%% ====================================================================

South Africa is a coupled GVAR bloc, $n=19$ (staged credit spec; deployed bloc
adds the three \texttt{ROW*\_ZA} stars), $p=3$, over 2002Q1--2025Q4 ($T=96$).
Macro series are COVID-masked 2020Q2--Q4 and DK-completed; financials observed.
The credit block carries both legs: a BIS quantity and an IMF/IFS lending-rate
price.

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{South Africa (ZA) variable documentation.}\label{tab:data:ZA}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_ZA}    & Real GDP                           & IMF/OECD QNA (GVAR base) & \textit{[FLAG]} & Q & log & masked & WEO-extended \\
\texttt{CONS\_ZA}   & Real household consumption         & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{INV\_ZA}    & Real gross fixed capital formation & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{GOV\_ZA}    & Real government consumption        & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{EXP\_ZA}    & Real exports                       & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{IMP\_ZA}    & Real imports                       & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{CPI\_ZA}    & CPI index                          & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & \\
\texttt{LR\_ZA}     & Unemployment rate                  & IMF IFS / national & \textit{[FLAG]} & Q & lin & masked & \\
\texttt{RATE\_ZA}   & SARB policy rate (repo)            & IMF IFS / SARB & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{YIELD10\_ZA}& 10Y government bond yield          & IMF IFS / national & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{NEER\_ZA}   & Nominal effective exchange rate    & IMF IFS / BIS & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{POLRATE\_ZA}& Policy rate (BIS CBPOL)            & BIS SDMX WS\_CBPOL & \texttt{M.ZA} (3M avg) & Q & lin & observed & financial \\
\texttt{HP\_ZA}     & Real residential property price    & FRED (BIS real RPP) & \texttt{QZAR628BIS} & Q & log & observed & financial \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)          & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)         & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)        & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)         & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_ZA} & Credit to NFCs (\% of GDP) [NEW: credit quantity] & BIS via FRED & \texttt{QZANAM770A} & Q & lin & masked & RW; nonnull 69/96 (BIS series starts 2008Q1 $\Rightarrow$ 24 leading nulls), range 32.9--41.4\%; last 33.2; COVID cells \texttt{null} \\
\texttt{LENDR\_ZA}  & IFS lending rate (\% p.a.) [NEW: credit price] & IMF IFS via \texttt{MFS\_IR} & \texttt{ZAF.\allowbreak MFS162\_RT\_PT\_A\_PT.\allowbreak Q} & Q & lin & observed & RW; SARB-prime-linked representative bank lending rate; nonnull 96/96, range 7.0--17.0\%; last 10.33 \\
\end{longtable}}

\noindent\textit{[FLAG: ZA credit quantity leading gap]} The BIS NFC series
begins 2008Q1, leaving 24 leading nulls (2002Q1--2007Q4); these are a normal
ragged leading edge handled by the COVID-as-missing Gibbs.\\
\textit{[FLAG: ZA base-macro series IDs]} As for TR, the per-variable provider
series codes for the eight base macro series, the SARB repo rate, the 10Y yield
and the NEER are not stamped in
\texttt{country\_rawdata/DataRaw\_ZA\_glob.json}; provider class is per
Section~\ref{sec:datasources} (IMF flows / OECD QNA / national, WEO-extended).

%% ====================================================================
\subsection{Saudi Arabia (SA)}\label{sec:data:SA}
%% ====================================================================

Saudi Arabia is a coupled GVAR bloc, $n=16$ (staged credit spec; deployed bloc
adds the three \texttt{ROW*\_SA} stars), $p=3$, over 2010Q1--2025Q4 ($T=64$).
Macro series are COVID-masked 2020Q2--Q4 and DK-completed; financials observed.
The credit block is \emph{quantity-only} (price dropped; flag below).

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{Saudi Arabia (SA) variable documentation.}\label{tab:data:SA}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_SA}    & Real GDP                           & IMF/OECD QNA (GVAR base) & \textit{[FLAG]} & Q & log & masked & WEO-extended \\
\texttt{CONS\_SA}   & Real household consumption         & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{INV\_SA}    & Real gross fixed capital formation & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{GOV\_SA}    & Real government consumption        & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{EXP\_SA}    & Real exports                       & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{IMP\_SA}    & Real imports                       & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{CPI\_SA}    & CPI index                          & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & \\
\texttt{LR\_SA}     & Unemployment rate                  & IMF IFS / national & \textit{[FLAG]} & Q & lin & masked & \\
\texttt{RATE\_SA}   & Policy rate (SAMA repo)            & IMF IFS / SAMA & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{NEER\_SA}   & Nominal effective exchange rate    & IMF IFS / BIS & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{POLRATE\_SA}& Policy rate (BIS CBPOL)            & BIS SDMX WS\_CBPOL & \texttt{M.SA} (3M avg) & Q & lin & observed & financial \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)          & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)         & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)        & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)         & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_SA} & Credit to NFCs (\% of GDP) [NEW: credit quantity] & BIS via FRED & \texttt{QSANAM770A} & Q & lin & masked & RW; nonnull 61/64, range 19.3--45.9\%; 2010Q1=27.7, 2025Q4=45.9; COVID cells \texttt{null} \\
\end{longtable}}

\noindent\textit{[FLAG: SA credit PRICE DROPPED]} SAMA publishes no NFC lending
rate (SAIBOR is an interbank money-market rate, conceptually covered by
\texttt{RATE\_SA}); SA is absent from IMF \texttt{MFS\_IR}; OECD/FRED/WB carry no
Saudi lending rate. Saudi banking is largely Islamic-finance, so no conventional
IFS-style ``lending rate'' is published. Per the locked spec the SA credit block
is \emph{quantity only}.\\
\textit{[FLAG: SA base-macro series IDs]} Per-variable provider series codes for
the base macro series, the SAMA repo rate and the NEER are not stamped in
\texttt{country\_rawdata/DataRaw\_SA\_glob.json}; provider class per
Section~\ref{sec:datasources}.

%% ====================================================================
\subsection{Argentina (AR)}\label{sec:data:AR}
%% ====================================================================

Argentina is a coupled GVAR bloc, $n=17$ (staged credit spec; deployed bloc adds
the three \texttt{ROW*\_AR} stars), $p=3$, over 2004Q1--2025Q4 ($T=88$). Macro
series are COVID-masked 2020Q2--Q4 and DK-completed; financials observed. Note
that the entire AR bloc uses an RW own-lag prior on \emph{every} variable
(including the macro logs), reflecting the highly non-stationary, high-inflation
Argentine sample. The credit block carries both legs.

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{Argentina (AR) variable documentation.}\label{tab:data:AR}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_AR}    & Real GDP                           & IMF/OECD QNA (GVAR base) & \textit{[FLAG]} & Q & log & masked & RW; WEO-extended \\
\texttt{CONS\_AR}   & Real household consumption         & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{INV\_AR}    & Real gross fixed capital formation & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{GOV\_AR}    & Real government consumption        & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{EXP\_AR}    & Real exports                       & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{IMP\_AR}    & Real imports                       & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{CPI\_AR}    & CPI index                          & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{LR\_AR}     & Unemployment rate                  & IMF IFS / national & \textit{[FLAG]} & Q & lin & masked & RW \\
\texttt{RATE\_AR}   & BADLAR short-term rate             & IMF IFS / BCRA & \textit{[FLAG]} & Q & lin & observed & financial, RW \\
\texttt{NEER\_AR}   & Nominal effective exchange rate    & IMF IFS / BIS & \textit{[FLAG]} & Q & log & observed & financial, RW \\
\texttt{POLRATE\_AR}& Policy rate (BIS CBPOL)            & BIS SDMX WS\_CBPOL & \texttt{M.AR} (3M avg) & Q & lin & observed & financial, RW \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)          & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)         & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)        & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)         & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_AR} & Credit to NFCs (\% of GDP) [NEW: credit quantity] & BIS via FRED & \texttt{QARNAM770A} & Q & lin & masked & RW; nonnull 85/88, range 13.5--38.0\%; 2004Q1=38.0, 2025Q4=23.2; COVID cells \texttt{null} \\
\texttt{LENDR\_AR}  & Lending rate (\% p.a.; extreme volatility) [NEW: credit price] & IMF IFS via \texttt{MFS\_IR} & \texttt{ARG.\allowbreak MFS162\_RT\_PT\_A\_PT.\allowbreak Q} & Q & lin & observed & RW; peso lending rate (not the FC variant); nonnull 64/88 (24 leading nulls, IFS starts 2010Q1); range 9.85--120.54\% (\textbf{120.54\% @2023Q4} = genuine hyperinflation peak); observed through COVID \\
\end{longtable}}

\noindent\textit{[FLAG: AR credit price extreme volatility]} The peso lending
rate swings enormously with the inflation regime (peak 120.5\% in 2023Q4); under
an RW \texttt{lin} prior it produces very large innovations. The series has 24
leading nulls (2004Q1--2009Q4; IFS begins 2010Q1), handled by the ragged-edge
Gibbs. The peso variant \texttt{MFS162\_RT\_PT\_A\_PT} is used, not the
much-lower foreign-currency variant.\\
\textit{[FLAG: AR base-macro series IDs]} Per-variable provider codes for the
base macro series, the BADLAR rate and the NEER are not stamped in
\texttt{country\_rawdata/DataRaw\_AR\_glob.json}; provider class per
Section~\ref{sec:datasources}.

%% ====================================================================
\subsection{Russia (RU)}\label{sec:data:RU}
%% ====================================================================

Russia is a coupled GVAR bloc, $n=14$ (staged credit spec; deployed bloc adds
the three \texttt{ROW*\_RU} stars), $p=3$, over 2005Q1--2025Q4 ($T=84$). It is a
compact bloc (no consumption/investment/government/import expenditure split):
its real-side activity is summarised by real GDP and goods exports. Macro series
are COVID-masked 2020Q2--Q4 and DK-completed; financials observed. The credit
block carries both legs; the price leg is \emph{spliced} (flag below).

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{Russia (RU) variable documentation.}\label{tab:data:RU}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_RU}    & Real GDP (const.\ 2010 LCU, SA)    & IMF/OECD QNA (GVAR base) & \textit{[FLAG]} & Q & log & masked & RW; WEO-extended \\
\texttt{CPI\_RU}    & CPI index (all-items)              & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{EXP\_RU}    & Goods exports (FOB, USD)           & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{LR\_RU}     & Unemployment rate                  & IMF IFS / national & \textit{[FLAG]} & Q & lin & masked & RW \\
\texttt{RATE\_RU}   & Interbank call-money rate          & IMF IFS / CBR & \textit{[FLAG]} & Q & lin & observed & financial, RW \\
\texttt{NEER\_RU}   & Nominal effective exchange rate    & IMF IFS / BIS & \textit{[FLAG]} & Q & log & observed & financial, RW \\
\texttt{POLRATE\_RU}& Policy rate (BIS CBPOL)            & BIS SDMX WS\_CBPOL & \texttt{M.RU} (3M avg) & Q & lin & observed & financial, RW \\
\texttt{HP\_RU}     & Real residential property price    & FRED (BIS real RPP) & \texttt{QRUR628BIS} & Q & log & observed & financial, RW \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)          & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)         & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)        & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)         & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_RU} & Credit to NFCs (\% of GDP) [NEW: credit quantity] & BIS via FRED & \texttt{QRUNAM770A} & Q & lin & masked & RW; nonnull 81/84, range 31.1--90.3\%; 2005Q1=31.7, 2025Q4=84.7; COVID cells \texttt{null} \\
\texttt{LENDR\_RU}  & Lending rate (\% p.a.; IMF spliced w/ CBR) [NEW: credit price] & IMF IFS \texttt{MFS\_IR} spliced with CBR & \texttt{RUS.\allowbreak MFS162\_RT\_PT\_A\_PT.\allowbreak Q} + CBR \texttt{loans\_nonfin\_e.xlsx} & Q & lin & observed & RW; full coverage 84/84, range 6.05--22.57\%; 2005Q1=10.63, 2025Q4=18.23 \\
\end{longtable}}

\noindent\textit{[FLAG: RU credit price SPLICED]} IMF \texttt{MFS162} ends
2024Q2 ($=17.21$). For 2024Q3--2025Q4 the series is spliced with the CBR
weighted-average rate on ruble loans to non-financial organisations, ``up to 1
year (incl.\ call loans)'' (\texttt{loans\_nonfin\_e.xlsx}, sheet 1 col.\ 5;
values 18.97, 22.57, 22.19, 22.28, 19.64, 18.23). This is the same underlying
CBR survey the IMF reports as MFS162: validated MAD~$=0.003$ over 42 overlapping
quarters (2014--2024Q2), with a continuous seam at 2024Q2 (IMF 17.21 vs CBR
17.15).\\
\textit{[FLAG: RU base-macro series IDs]} Per-variable provider codes for GDP,
CPI, goods exports, unemployment, the interbank rate and the NEER are not
stamped in \texttt{country\_rawdata/DataRaw\_RU\_glob.json}; provider class per
Section~\ref{sec:datasources}.

%% ====================================================================
\subsection{Thailand (TH)}\label{sec:data:TH}
%% ====================================================================

Thailand is a coupled GVAR bloc, $n=19$ (staged credit spec; deployed bloc adds
the three \texttt{ROW*\_TH} stars), $p=3$, over 2003Q1--2025Q4 ($T=92$). All
expenditure components and prices are seasonally adjusted. Macro series are
COVID-masked 2020Q2--Q4 and DK-completed; financials observed. The credit block
carries both legs.

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{Thailand (TH) variable documentation.}\label{tab:data:TH}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_TH}    & Real GDP (SA, const.\ prices)      & IMF/OECD QNA (GVAR base) & \textit{[FLAG]} & Q & log & masked & WEO-extended \\
\texttt{CONS\_TH}   & Real private consumption (SA)      & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{INV\_TH}    & Real gross fixed capital formation (SA) & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{GOV\_TH}    & Real government consumption (SA)   & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{EXP\_TH}    & Real exports of g\&s (SA)          & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{IMP\_TH}    & Real imports of g\&s (SA)          & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{CPI\_TH}    & CPI, all items (index)             & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & \\
\texttt{LR\_TH}     & Unemployment rate                  & IMF IFS / national & \textit{[FLAG]} & Q & lin & masked & \\
\texttt{RATE\_TH}   & Policy rate (BOT)                  & IMF IFS / BOT & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{YIELD10\_TH}& 10Y government bond yield          & IMF IFS / national & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{NEER\_TH}   & Nominal effective exchange rate (BIS broad) & BIS / IMF & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{POLRATE\_TH}& Policy rate (BIS CBPOL)            & BIS SDMX WS\_CBPOL & \texttt{M.TH} (3M avg) & Q & lin & observed & financial \\
\texttt{HP\_TH}     & Real residential property price    & FRED (BIS real RPP) & \texttt{QTHR628BIS} & Q & log & observed & financial \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)          & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)         & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)        & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)         & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_TH} & Credit to NFCs (\% of GDP) [NEW: credit quantity] & BIS via FRED & \texttt{QTHNAM770A} & Q & lin & masked & RW; nonnull 89/92, range 68.4--95.9\%; last 68.5; COVID cells \texttt{null} \\
\texttt{LENDR\_TH}  & IFS lending rate (\% p.a.) [NEW: credit price] & IMF IFS via \texttt{MFS\_IR} & \texttt{THA.\allowbreak MFS162\_RT\_PT\_A\_PT.\allowbreak Q} & Q & lin & observed & RW; BOT announced/minimum loan rate; nonnull 88/92 (4 leading nulls in 2003, IFS starts 2004Q1); range 3.03--6.58\%; last 3.44 \\
\end{longtable}}

\noindent\textit{[FLAG: TH credit price leading gap]} The IFS lending rate has 4
leading nulls (2003; the series begins 2004Q1), a normal ragged leading edge
handled by the Gibbs.\\
\textit{[FLAG: TH base-macro series IDs]} Per-variable provider codes for the
base macro series, the BOT policy rate, the 10Y yield and the NEER are not
stamped in \texttt{country\_rawdata/DataRaw\_TH\_glob.json}; provider class per
Section~\ref{sec:datasources}.

%% ====================================================================
\subsection{Malaysia (MY)}\label{sec:data:MY}
%% ====================================================================

Malaysia is a coupled GVAR bloc, $n=18$ (staged credit spec; deployed bloc adds
the three \texttt{ROW*\_MY} stars), $p=3$, over a short 2015Q1--2025Q4 grid
($T=44$). Macro series are COVID-masked 2020Q2--Q4 and DK-completed; financials
observed. The credit block carries both legs; note the short sample (flag).

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{Malaysia (MY) variable documentation.}\label{tab:data:MY}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_MY}    & Real GDP (chain volume, SA)        & IMF/OECD QNA (GVAR base) & \textit{[FLAG]} & Q & log & masked & WEO-extended \\
\texttt{CONS\_MY}   & Real private consumption (SA)      & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{INV\_MY}    & Real gross fixed capital formation (SA) & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{GOV\_MY}    & Real government consumption (SA)   & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{EXP\_MY}    & Real exports of g\&s (SA)          & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{IMP\_MY}    & Real imports of g\&s (SA)          & IMF/OECD QNA & \textit{[FLAG]} & Q & log & masked & \\
\texttt{CPI\_MY}    & CPI index (all items)              & IMF IFS / national & \textit{[FLAG]} & Q & log & masked & \\
\texttt{LR\_MY}     & Unemployment rate                  & IMF IFS / national & \textit{[FLAG]} & Q & lin & masked & \\
\texttt{RATE\_MY}   & Overnight policy rate (BNM)        & IMF IFS / BNM & \textit{[FLAG]} & Q & lin & observed & financial \\
\texttt{NEER\_MY}   & Nominal effective exchange rate    & IMF IFS / BIS & \textit{[FLAG]} & Q & log & observed & financial \\
\texttt{POLRATE\_MY}& Policy rate (BIS CBPOL)            & BIS SDMX WS\_CBPOL & \texttt{M.MY} (3M avg) & Q & lin & observed & financial \\
\texttt{HP\_MY}     & Real residential property price    & FRED (BIS real RPP) & \texttt{QMYR628BIS} & Q & log & observed & financial \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)          & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)         & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)        & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)         & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_MY} & Credit to NFCs (\% of GDP) [NEW: credit quantity] & BIS via FRED & \texttt{QMYNAM770A} & Q & lin & masked & RW; nonnull 41/44, range 86.1--106.3\%; last 88.6; COVID cells \texttt{null} \\
\texttt{LENDR\_MY}  & IFS lending rate (\% p.a.) [NEW: credit price] & IMF IFS via \texttt{MFS\_IR} & \texttt{MYS.\allowbreak MFS162\_RT\_PT\_A\_PT.\allowbreak Q} & Q & lin & observed & RW; BNM average lending/base rate; nonnull 44/44, range 3.31--5.47\%; last 4.62 \\
\end{longtable}}

\noindent\textit{[FLAG: MY short sample]} The MY grid is only $T=44$
(2015Q1--2025Q4) with 41 credit observations -- thin for a bloc that adds two
credit variables; predictive bands are correspondingly wide.\\
\textit{[FLAG: MY base-macro series IDs]} Per-variable provider codes for the
base macro series, the BNM overnight policy rate and the NEER are not stamped in
\texttt{country\_rawdata/DataRaw\_MY\_glob.json}; provider class per
Section~\ref{sec:datasources}.

%% ====================================================================
\subsection{Taiwan, Province of China (TW)}\label{sec:data:TW}
%% ====================================================================

Taiwan is a coupled GVAR bloc, $n=17$ (staged credit spec; deployed bloc adds
the three \texttt{ROW*\_TW} stars), $p=3$, over a long 1997Q1--2025Q4 grid
($T=116$). It carries an unusually rich short-end financial block (CBC discount
rate, interbank call-loan rate and 10Y yield) but \emph{no} BIS house-price
series. Macro series are COVID-masked 2020Q2--Q4 and DK-completed; financials
observed. Both credit legs are present but \emph{constructed/national}, not BIS
(flags below).

{\footnotesize
\begin{longtable}{p{2.3cm}p{3.3cm}p{2.1cm}p{2.2cm}p{0.6cm}p{1.4cm}p{1.9cm}p{2.4cm}}
\caption{Taiwan (TW) variable documentation.}\label{tab:data:TW}\\
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable (id)} & \textbf{Description} & \textbf{Source} & \textbf{Series ID/key} & \textbf{Freq} & \textbf{Trans.} & \textbf{COVID} & \textbf{Notes} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_TW}    & Real GDP                           & DGBAS / OECD-style QNA & \textit{[FLAG]} & Q & log & masked & RW; WEO-extended \\
\texttt{CONS\_TW}   & Real household consumption         & DGBAS & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{GOV\_TW}    & Real government consumption        & DGBAS & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{INV\_TW}    & Real gross fixed capital formation & DGBAS & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{EXP\_TW}    & Real exports of g\&s               & DGBAS & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{IMP\_TW}    & Real imports of g\&s               & DGBAS & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{CPI\_TW}    & CPI, all items (index, 2021=100)   & DGBAS & \textit{[FLAG]} & Q & log & masked & RW \\
\texttt{LR\_TW}     & Unemployment rate                  & DGBAS & \textit{[FLAG]} & Q & lin & masked & RW \\
\texttt{RATE\_TW}   & CBC discount rate (policy)         & CBC & \textit{[FLAG]} & Q & lin & observed & financial, RW \\
\texttt{MMRATE\_TW} & Interbank call-loan rate (money mkt) & CBC & \textit{[FLAG]} & Q & lin & observed & financial, RW \\
\texttt{YIELD10\_TW}& 10Y government bond yield          & CBC / national & \textit{[FLAG]} & Q & lin & observed & financial, RW \\
\texttt{GLB\_OIL}   & WTI crude (q-avg, \$/bbl)          & FRED & \texttt{WTISPLC} & Q & log & observed & global common \\
\texttt{GLB\_USLR}  & US 10Y Treasury yield (\%)         & FRED & \texttt{DGS10} & Q & lin & observed & global common \\
\texttt{GLB\_USBAA} & US Baa corporate yield (\%)        & FRED & \texttt{BAA} & Q & lin & observed & global common \\
\texttt{GLB\_USEQ}  & US equity (S\&P 500 proxy)         & FRED & \texttt{SPASTT01USM661N} & Q & log & observed & global common \\
\texttt{CREDIT\_GDP\_TW} & Credit to NFCs (\% of GDP) [NEW: credit quantity, CONSTRUCTED] & CBC EI86 / DGBAS GDP & $100\times$ CBC EI86 private-enterprise loans (NT\$mn, monthly stock $\to$ q-avg) $\div$ 4Q-trailing DGBAS nominal GDP & Q & lin & masked & RW; nonnull 113/116, range 46.3--65.4\%; 2025Q4=60.6; COVID cells \texttt{null} \\
\texttt{LENDR\_TW}  & 5-major-banks new loan rate (\% p.a.) [NEW: credit price] & CBC EH45 (total, interest rate) & CBC \texttt{EH45} total (monthly $\to$ q-avg) & Q & lin & observed & RW; CBC realised five-major-banks new-loan rate; nonnull 116/116, range 1.16--8.62\%; 2020Q2=1.26; 2025Q4=2.16 \\
\end{longtable}}

\noindent\textit{[FLAG: TW credit quantity CONSTRUCTED, not BIS]} BIS publishes
no NFC credit-to-GDP for Taiwan (FRED \texttt{QTWNAM770A} returns HTTP~400; BIS
WS\_TC SDMX returns ``no structures match''). \texttt{CREDIT\_GDP\_TW} is
therefore constructed as $100\times$ CBC EI86 private-enterprise loans
(private enterprises; excludes household and public-enterprise loans) over 4-quarter-trailing
DGBAS nominal GDP. This is a private-enterprise-loan proxy, broader than the
BIS market-value NFC concept used elsewhere, so cross-economy comparability of
the credit variable is reduced.\\
\textit{[FLAG: TW credit price provenance]} \texttt{LENDR\_TW} is the CBC's
published headline five-major-banks total new-loan rate (EH45, ``total''), used as the
locked-spec ``5-bank base lending rate'' -- a national CBC series, not an IMF or
BIS feed. The Taiwan source files are fetched via
\texttt{fetch\_tw\_cbc\_dgbas.py}; the DGBAS GDP host ships an incomplete TLS
chain and is fetched with verification relaxed for that host only (documented in
the fetcher).\\
\textit{[FLAG: TW house price]} Unlike the other blocs here, TW carries no
\texttt{HP\_TW} (no BIS real residential property price was added).\\
\textit{[FLAG: TW base-macro series IDs]} The base real-activity, price, labour
and short-rate series originate with Taiwan's DGBAS (national accounts, CPI,
unemployment) and the CBC (discount rate, call-loan rate, 10Y yield), but the
upstream raw file \texttt{country\_rawdata/DataRaw\_TW\_glob.json} carries no
per-variable series-id stamp, so exact DGBAS/CBC table codes for
\texttt{GDP/\allowbreak CONS/\allowbreak GOV/\allowbreak INV/\allowbreak EXP/\allowbreak IMP/\allowbreak CPI/\allowbreak LR/\allowbreak RATE/\allowbreak MMRATE/\allowbreak YIELD10} are not asserted
here.
