\documentclass[11pt]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools}
% \usepackage{bbm}
\usepackage{graphicx}
\usepackage{pdflscape}  % landscape pages for wide tables (e.g. the coverage matrix)
\usepackage{array}      % provides \arraybackslash and >{...}p{} column specifiers
\usepackage{booktabs,longtable}
\usepackage[round,authoryear]{natbib}
\usepackage{hyperref}
\hypersetup{
  pdfpagelayout=OneColumn, pdfstartview=Fit, pdfpagemode=UseNone,
  colorlinks=true, citecolor=blue, filecolor=blue,
  linkcolor=blue, urlcolor=blue}
\usepackage{enumitem}
\usepackage{setspace}
\onehalfspacing
\usepackage{float}
\usepackage{caption}
\usepackage{xcolor}
% --- self-contained algorithm float --------------------------------
% The texlive-science algorithm/algorithm2e/algpseudocode packages are
% not guaranteed to be installed on every build host (they are absent on
% the reference Debian texlive-base image used here). To keep the manual
% self-building anywhere, we define a lightweight numbered "Algorithm N"
% float (ruled style, captioned, \ref-able, with its own list-of) on top
% of the always-present float package, plus a few pseudocode helper
% macros. Visually this matches an \usepackage[ruled]{algorithm2e} box;
% switching to a real algorithm package later requires no body changes
% beyond the environment name.
\floatstyle{ruled}
\newfloat{algorithm}{!ht}{loa}
\floatname{algorithm}{Algorithm}
\newcounter{algstep}
\newenvironment{algsteps}
  {\begin{list}{\textbf{\arabic{algstep}:}}{\usecounter{algstep}%
     \setlength{\leftmargin}{2.0em}\setlength{\labelwidth}{1.6em}%
     \setlength{\itemsep}{1.5pt}\setlength{\parsep}{0pt}%
     \setlength{\topsep}{2pt}}}
  {\end{list}}
\newcommand{\algIn}[1]{\noindent\textbf{Input:} #1\par\vspace{1pt}}
\newcommand{\algOut}[1]{\noindent\textbf{Output:} #1\par\vspace{1pt}}
\newcommand{\algInd}{\hspace*{1.4em}}
\newcommand{\algIndd}{\hspace*{2.8em}}
\newcommand{\algInddd}{\hspace*{4.2em}}
\newcommand{\algKw}[1]{\textbf{#1}}
\newcommand{\algComment}[1]{{\color{black!55}\(\triangleright\) #1}}
% -------------------------------------------------------------------
\usepackage{microtype}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,backgrounds,calc,decorations.pathreplacing,shapes.geometric}
% Disable microtype font expansion: the new TikZ figures/captions otherwise
% trigger "auto expansion is only possible with scalable fonts" on some pages.
% Character protrusion is retained.
\microtypesetup{expansion=false}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\operatorname{Cov}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\vect}{\operatorname{vec}}
\newcommand{\cmark}{{\color{green!55!black}\checkmark}}
\newcommand{\xmark}{{\color{red!70!black}\ensuremath{\times}}}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

% "important" callout box: a shaded, left-ruled frame used to flag
% must-read caveats such as the dormant fiscal feedback channels.
% mdframed handles multi-paragraph content and page breaks cleanly.
\usepackage{mdframed}
\newmdenv[
  linecolor=red!55!black,
  linewidth=2.5pt,
  leftline=true,
  rightline=false,
  topline=false,
  bottomline=false,
  innerleftmargin=10pt,
  innerrightmargin=8pt,
  innertopmargin=6pt,
  innerbottommargin=6pt,
  backgroundcolor=red!6,
  skipabove=\medskipamount,
  skipbelow=\medskipamount,
]{important}

\begin{document}

%% ================================================================
%% TITLE PAGE
%% ================================================================
\begin{titlepage}
\vspace*{3cm}
\begin{center}
{\LARGE\bfseries Monetary-Financial Model:\\[2pt] A global projection and scenario tool}\\[6pt]
{\LARGE\bfseries User Manual and Methodological Documentation}%
\footnote{The views expressed herein are those of the author and should
not be attributed to the International Monetary Fund, its Executive
Board, or its management.  This tool is provided ``as is'' without
warranty of any kind, express or implied.  The author and the IMF
disclaim all liability for any errors, omissions, or for any loss or
damage arising from its use.  Users are solely responsible for any
decisions made based on the output of this tool.}

\vspace{1.2cm}

{\large\itshape M\'aty\'as Farkas}\\[4pt]
International Monetary Fund

\vspace{1.5cm}

\today

\vspace{1.5cm}

Source code: \url{https://github.com/matyasfarkas/BVARScenarioTool}

\end{center}

\vfill
\end{titlepage}

%% ================================================================
%% ABSTRACT PAGE
%% ================================================================

\begin{center}
{\LARGE\bfseries Monetary-Financial Model:\\[2pt] A global projection and scenario tool}\\[6pt]
{\LARGE\bfseries User Manual and Methodological Documentation}
\end{center}

\vspace{0.8cm}

\begin{center}
\begin{minipage}{0.45\textwidth}\centering
M\'aty\'as Farkas\\
International Monetary Fund
\end{minipage}
\end{center}

\vspace{0.3cm}
\begin{center}
\today
\end{center}

\vspace{1cm}

\begin{center}\textbf{Abstract}\end{center}
\begin{quote}
This document describes the Monetary-Financial Model, a global
projection and scenario tool: a browser-based application for
conditional forecasting, scenario analysis, and policy
counterfactual evaluation.  The tool combines a large Bayesian vector
autoregression (BVAR) estimated with hierarchical Minnesota priors
\citep{Giannone2015} with structural impulse responses drawn from the
Macroeconomic Model Data Base
\citep[MMB;][]{WielandCwikMuellerSchmidtWolters2012,
WielandAfanasyevaYooKuete2016}.  Users condition the BVAR forecast on
arbitrary variable paths via a Durbin--Koopman simulation smoother
\citep{DurbinKoopman2002, DurbinKoopman2012}, and evaluate monetary and
fiscal policy counterfactuals using DSGE-identified impulse response
functions.  We describe the methodology employed, the implementation of
the conditional forecasting algorithms, and the three-layer architecture
that separates the unconditional baseline, the user's scenario, and the
policy counterfactual.  All computation runs client-side in the browser;
the tool requires no server infrastructure and can be deployed as a
static website.  The manual is in two parts: Part~I explains how to
\emph{use} the tool --- what you do, how you do it, and what you find
on the screen --- in plain language, assuming no econometrics; Part~II
documents the methodology in full technical detail.
\end{quote}

\vspace{0.5cm}
\noindent\textbf{Keywords}: BVARs, Conditional Forecasting, Scenario
Analysis, Kalman Filter, Durbin--Koopman Smoother, Policy
Counterfactuals, DSGE Models, MMB

\vspace{0.3cm}
\noindent\textbf{JEL classification}: C32, C53, E37, E52, E58

\vfill
\noindent\rule{\textwidth}{0.4pt}\\[4pt]
{\footnotesize $^*$The views in this paper are solely the
responsibility of the author and should not be interpreted as reflecting
the views of the International Monetary Fund or any other person
associated with the IMF.  Email: \texttt{mfarkas@imf.org}.}

\clearpage
\tableofcontents
\clearpage

%% ================================================================
%% OPENING + PART I — USING THE TOOL (task-oriented user manual)
%% ================================================================
\section{What this tool does}\label{sec:whatis}

This tool shows you quarterly forecasts for about fifty economies --- growth, inflation,
interest rates, public finances, and more --- and lets you bend them.

Click on a chart where you think inflation will be, and every other chart updates so the whole
forecast stays consistent with the estimated economics: if you push United States inflation up,
the policy rate rises, growth cools, and --- because the economies are linked through trade and
financial channels --- the euro area, Japan, and China move too. You can set where a variable
should settle in the long run, ask what a different interest-rate path would have done, and put
uncertainty bands around any of it. Everything runs in your browser; nothing to install.

Three honest rules govern everything you see:
\begin{itemize}
  \item \textbf{Data are data.} Solid history is observed. Where a country's latest quarter has
    not been published yet, the model fills the gap using everything already observed elsewhere
    --- and those filled-in points are always drawn in amber, never disguised as data.
  \item \textbf{The model is estimated once, then frozen.} Within the year, new data shift the
    starting point of the forecast but never silently change the model itself. Re-estimation
    happens once a year, on a complete final year of data.
  \item \textbf{Judgment is visible.} If you move a forecast away from what the model says ---
    a scenario, a long-run target, a policy counterfactual --- the chart says so.
\end{itemize}

\paragraph{How to use this manual.}
Part~I is the manual proper: each section tells you \emph{what you can do}, \emph{how to do it}
(step by step, naming the exact buttons), and \emph{what you will find} on the screen when you
have done it. You can read any section on its own. If you have five minutes, read
Section~\ref{sec:use-quickstart} and skip the rest until you need it.

Part~II explains how the machinery works --- the estimation, the filtering, the cross-country
system --- with the mathematics. You do not need any of it to use the tool. It is there so that
every number on the screen can be traced to a method, and every method to code and data.

\part{Using the tool}\label{part:using}

\section{Your first scenario in five minutes}\label{sec:use-quickstart}

This chapter is one continuous walk-through. You open the tool, look at one chart,
bend the United States policy rate with your mouse, watch the rest of the economy
respond, put uncertainty bands around the result, and clean up. Nothing else. Every
button and label named below appears on screen exactly as written. The full tour of
every control comes later, in \S\ref{sec:use-tour}.

\subsection{Open the tool and pick a country}

\paragraph{What you do.} Load the page and make sure you are looking at the United
States.

\paragraph{How.}
\begin{enumerate}
  \item Open the tool's web address in a modern browser. There is nothing to
    install; the model files load into the page itself, so give the first visit a
    few seconds.
  \item Look at the top bar. The \textbf{Country} dropdown already reads
    \textbf{United States} --- that is the default. If someone changed it, open the
    dropdown and pick \textbf{United States} from the \textbf{GVAR} group. That
    group lists the economies linked into the cross-country system; every other
    economy sits under \textbf{Other countries} and moves on its own.
  \item Leave everything else as it is: \textbf{Units} on \textbf{q/q ann.} and
    \textbf{Uncertainty} on \textbf{None}.
\end{enumerate}

\paragraph{What you find.} A grid of charts fills the screen --- growth, inflation,
the policy rate, public finances, credit, and more. In the left control panel a
scenario named \textbf{Scenario 1} is already active, and at the bottom of the
screen it has a tab of its own. You have not touched anything yet, so every chart
still shows the model's own view.

\subsection{Read your first chart}

\paragraph{What you do.} Learn to tell history from forecast on one chart before
you change anything.

\paragraph{How.} Find the chart titled \textbf{Inflation}, at the top left.

\paragraph{What you find.} Three things to read:
\begin{itemize}
  \item \emph{History sits on a lightly shaded background.} The solid line there is
    observed data. The x-axis is labelled with calendar years; hover over any point
    to see its exact quarter and value.
  \item \emph{The forecast is the dotted line} on the white part of the chart,
    labelled \textbf{Baseline} in the legend. The faint grey fan around it is the
    model's own uncertainty about that path --- it is there from the start, before
    you compute anything. The first forecast quarter is the latest quarter whose
    data have not been published yet; the sidebar and exports label it
    \textbf{NC} --- short for nowcast, the model's estimate of the current,
    not-yet-published quarter.
  \item \emph{Amber means model-filled.} If a series' latest quarters have not been
    published, the tail of its history is drawn as an amber dashed tail with
    open circles --- values the model filled in from everything observed elsewhere,
    never disguised as data (\S\ref{sec:use-data}).
\end{itemize}
The unit is \% q/q ann.: the change from the previous quarter, stated at an annual
rate. If you prefer the change over the same quarter a year earlier, click
\textbf{y/y} in the \textbf{Units} toggle --- then click \textbf{q/q ann.} to come
back.

\subsection{Bend the policy rate}

\paragraph{What you do.} Tell the tool: ``suppose the policy rate is higher than
the model expects one year from now --- say half a percentage point higher.''

\paragraph{How.}
\begin{enumerate}
  \item Find the chart titled \textbf{Policy Rate}, next to Inflation.
  \item Click the small \textbf{condition} button in its header. The button turns
    blue and now reads \textbf{CONDITIONED}, the panel gets a blue border, and a
    hint badge appears: \textbf{drag to adjust policy}.
  \item Press the mouse down on the forecast part of the chart, about four
    quarters in, and drag upward --- half a percentage point above the dotted
    baseline. Release.
\end{enumerate}
A shortcut for later: right-clicking an unconditioned chart does steps 2 and 3 at
once --- it conditions the variable and plants the point exactly where you clicked.

\paragraph{What you find.} A dot marks the quarter you pinned, and the scenario
line --- solid, in Scenario~1's colour --- now passes through it. While you hold
the mouse the line follows a fast preview; the full answer settles in about a
second after you release. Only the quarter you dragged is imposed; every other
quarter of the rate path is left free, and the model fills it in with the most
plausible route through your point. In the left control panel, a new entry for the
rate appears in the conditioning list, with one row per forecast quarter from
\textbf{NC} to \textbf{t+19} --- you will use those rows in
\S\ref{sec:use-scenarios}.

\subsection{Watch the rest of the economy respond}

\paragraph{What you do.} See what a tighter policy path means for everything else.

\paragraph{How.} Scroll through the grid. Compare each chart's solid scenario line
with its dotted \textbf{Baseline}.

\paragraph{What you find.} Every chart has updated, not just the one you touched.
The estimated model knows how United States variables have moved together in the
data, and it re-draws the whole forecast so it stays consistent with your pinned
rate: with a tighter path, growth typically cools, inflation eases with a lag, and
the financial variables shift too. How this works is spelled out in Part~II,
\S\ref{sec:partial}. Two notes. First, the response is the model's estimate
of typical historical co-movement, not a law. Read it as ``what usually
accompanies a higher rate,'' not ``what the rate causes.'' For a true
cause-and-effect experiment, use the policy counterfactual
(\S\ref{sec:use-counterfactual}). Second, other countries have not moved: cross-border
spillovers are off by default, so the United States moves alone until you switch
them on (\S\ref{sec:use-spillovers}).

\subsection{Put uncertainty bands around it}

\paragraph{What you do.} Ask how sure the model is about the scenario you just
drew.

\paragraph{How.}
\begin{enumerate}
  \item In the top bar, set \textbf{Uncertainty} to \textbf{Quick}.
  \item Press \textbf{Compute}. An overlay appears: \emph{Computing scenario
    uncertainty (50 draws)...} --- the model redraws its own forecast fifty times,
    each time with a different plausible version of its estimated parameters and
    shocks, and centres that range on your scenario.
\end{enumerate}

\paragraph{What you find.} A shaded band in the scenario's colour now wraps the
solid line on every chart: the middle two-thirds of the plausible outcomes.
Notice the band on the Policy Rate chart pinches shut at the quarter you dragged
--- you \emph{imposed} that value, so there is no uncertainty about it there. The
band is widest where the model is least sure, usually far out in the forecast.
\textbf{Full} does the same with 200 draws --- smoother edges, longer wait.
What the bands do and do not cover is in \S\ref{sec:use-uncertainty}, with the
machinery in Part~II, \S\ref{sec:bands}.

\subsection{Clean up}

\paragraph{What you do.} Put everything back the way you found it.

\paragraph{How.}
\begin{enumerate}
  \item In the left control panel, at the top of the \textbf{Scenario} section,
    click \textbf{Reset}. This clears the pins of the active scenario for the
    current country only --- other scenarios and other countries are untouched.
  \item Set \textbf{Uncertainty} back to \textbf{None}.
\end{enumerate}

\paragraph{What you find.} The dot is gone, the scenario line lies back on the
dotted \textbf{Baseline}, and the conditioning list in the left control panel is
empty again. You are back at the model's own view.

\subsection{Where to go next}

You have now done the core loop: pin a point, read the response, band it, reset.
The rest of Part~I builds outward from here.
\begin{itemize}
  \item \S\ref{sec:use-tour} --- the full tour: every control on the screen, top
    bar to bottom bar.
  \item \S\ref{sec:use-scenarios} --- richer scenarios: several variables and
    quarters at once, quarter-by-quarter editing, ready-made cookbook recipes,
    saving and loading.
  \item \S\ref{sec:use-spillovers} --- switch on cross-border transmission and let
    a United States scenario reach the euro area, Japan, and China.
  \item \S\ref{sec:use-longrun} --- set where a variable settles in the long run.
  \item \S\ref{sec:use-counterfactual} --- the true policy experiment: what a
    different interest-rate path would have \emph{caused}.
  \item \S\ref{sec:use-fiscal} --- revenue, spending, deficits, and debt.
  \item \S\ref{sec:use-uncertainty} --- what the bands mean, Quick versus Full,
    and what they leave out.
  \item \S\ref{sec:use-data} --- where the data come from, what the amber points
    are, and how to export everything you see.
\end{itemize}

%% ================================================================
\section{A tour of the screen}\label{sec:use-tour}\label{sec:interface}

The screen has four parts. A \emph{top bar} across the top: country choice, display units,
uncertainty, and links. A \emph{control panel} down the left side: scenarios, long-run targets,
cross-border switches, and the policy counterfactual. The \emph{chart grid} in the middle: one
chart per variable, and this is where you click and drag. A \emph{scenario bar} along the bottom:
scenario tabs and export buttons. This chapter walks through each part, and --- most importantly
--- teaches you to read one chart correctly.

\subsection{The top bar}

\subsubsection{Picking a country}

\paragraph{What you do.} You choose which economy fills the chart grid.

\paragraph{How.}
\begin{enumerate}
  \item Find the dropdown labelled \textbf{Country} in the top bar.
  \item Open it. The list has two groups: \textbf{GVAR} and \textbf{Other countries}.
  \item Click an economy. The grid redraws for that economy within a moment.
\end{enumerate}

\paragraph{What you find.} The two groups matter. Economies under \textbf{GVAR} belong to the
linked cross-country system --- the global model that ties economies together through trade and
financial channels (\S\ref{sec:gvar}) --- so a scenario you build there can spill over to
partners, and their scenarios can reach it (see \S\ref{sec:use-spillovers}). Economies under
\textbf{Other countries} are forecast on their own. Switching country never deletes your work:
each economy keeps its own scenario settings until you reset them.

\subsubsection{The rest of the bar}

Left to right, the remaining controls are:
\begin{itemize}
  \item \textbf{The app title} (\emph{Monetary-Financial Model: A global projection and
    scenario tool}), with a small ``i'' button that opens an \textbf{About} note.
  \item \textbf{Data \& coverage} --- opens the data-provenance panel, telling you for every
    variable where the numbers come from and how far the observations reach
    (\S\ref{sec:use-data}).
  \item \textbf{Three links}: \textbf{User Manual} (this document as a PDF), \textbf{Docs}
    (the full online documentation), and \textbf{Monitor} (a page showing how the latest data
    update moved every economy's forecast).
  \item \textbf{Units} --- the display-units toggle, covered below.
  \item \textbf{Uncertainty} --- a toggle with the choices \textbf{None}, \textbf{Quick}, and
    \textbf{Full} (\S\ref{sec:use-uncertainty}).
  \item \textbf{Compute} --- runs the uncertainty and long-run calculations
    (\S\ref{sec:use-uncertainty}, \S\ref{sec:use-longrun}).
\end{itemize}
\textbf{Compute} is greyed out until you either pick \textbf{Quick} or \textbf{Full}
uncertainty or set at least one long-run target.

\subsection{How to read one chart}

\paragraph{What you do.} Before you touch anything, learn what the lines and shading on a single
chart mean. Every chart in the grid follows the same grammar.

\paragraph{How.} Pick any chart --- say \textbf{Inflation} --- and look at it from left to right.

\paragraph{What you find.}
\begin{itemize}
  \item \textbf{The shaded region on the left is history.} A light background tint covers all
    quarters up to the last historical quarter. Everything to its right is forecast.
  \item \textbf{The solid coloured line is the data, then your scenario.} Inside the shaded
    region the solid line is observed history. To the right it continues as the active
    scenario's forecast. If you have not changed anything, it lies exactly on top of the
    baseline.
  \item \textbf{The amber dashed tail is model-filled, not observed.} Quarters not yet
    published are drawn amber and dashed at the end of the history line, with small open
    circles marking exactly the filled-in quarters. Hover over one and the label reads
    \emph{Model-implied nowcast (imputed)}. Solid means observed; amber dashed with open
    circles means the model's best guess. What the filling uses is explained in
    \S\ref{sec:use-data}; see also \S\ref{sec:vintage}.
  \item \textbf{The dotted grey line is the baseline.} This is what the model expects with no
    intervention from you. It is labelled \textbf{Baseline} in the legend. When you move a
    forecast, your scenario line departs from it, so the gap between solid and dotted is
    exactly what your judgment added.
  \item \textbf{The grey fan is the model's own uncertainty.} A pale grey band around the
    baseline covers the central two-thirds of the outcomes the model considers plausible ---
    roughly, ``the future usually lands inside this band.'' It is there from the start; the
    coloured band around your \emph{scenario} appears only after you press \textbf{Compute}
    (\S\ref{sec:use-uncertainty}; construction in \S\ref{sec:bands}).
  \item \textbf{The date axis.} Tick labels mark calendar years. For the exact quarter, hover
    anywhere on a line: the label shows the date and value, for example \emph{2027 Q3 · 2.10}.
    The first forecast quarter is the one right after the last historical quarter.
  \item \textbf{The header.} Each chart's title sits top-left with a \textbf{condition} button
    next to it --- click it to start steering this variable (\S\ref{sec:use-scenarios}); it
    turns into \textbf{CONDITIONED} and gives the panel a blue border once active. Charts
    computed from other charts by an accounting identity --- the change in debt-to-GDP
    ($\Delta$~Debt-to-GDP) or the external-sector charts, for example --- show a
    \textbf{derived} badge instead and cannot be steered directly. If you have moved a
    variable's long-run target off the model's estimate, its title turns amber and shows a
    small \textbf{judgement} badge with a pencil mark (\S\ref{sec:use-longrun}). While a chart
    is steerable, a hint badge appears top-right: \textbf{drag to set path} --- or, on the
    policy-rate chart, \textbf{drag to adjust policy}.
  \item \textbf{The footer.} Two small lines under each chart give the variable's definition
    and its unit, so you never have to guess what a series measures. The full variable
    catalogue is in \S\ref{sec:variables}.
\end{itemize}

One more thing you may see \emph{above} the grid on GVAR economies: a badge reporting whether
the cross-country solve you are looking at is a fast preview or the full solve, sometimes with a
\textbf{Solve full GVAR} button. Ignore it for now; \S\ref{sec:use-spillovers} explains it.

\subsection{Three ways to display the numbers}

\paragraph{What you do.} You choose the units every growth-rate chart is drawn in. The numbers
are the same forecast; only the lens changes.

\paragraph{How.}
\begin{enumerate}
  \item In the top bar, find the toggle labelled \textbf{Units}.
  \item Click one of \textbf{q/q ann.}, \textbf{y/y}, or \textbf{\% vs base}.
\end{enumerate}

\paragraph{What you find.}
\begin{itemize}
  \item \textbf{q/q ann.} shows each quarter's change from the quarter before, scaled up to a
    full year --- the ``annualised'' pace economists quote. It is the model's native unit
    (\S\ref{sec:units}) and the most responsive view: a one-quarter dip shows up as one sharp
    notch.
  \item \textbf{y/y} shows the change against the same quarter one year earlier. It is
    smoother and matches how inflation is usually reported in the press. The same forecast
    therefore looks calmer here; nothing has changed but the lens.
  \item \textbf{\% vs base} shows the \emph{difference} between your scenario and the
    baseline, centred at zero --- an impact view. A flat line at zero means your scenario
    changed nothing for that variable. This view is read-only: you cannot drag on charts while
    it is active. A second pair of buttons appears in this view only: \textbf{Level} (the
    default; the cumulative difference in the level of the series) and \textbf{Rate (IRF)}
    (the quarter-by-quarter difference, matching the convention used to compare against the
    structural policy models of \S\ref{sec:use-counterfactual}; details in
    \S\ref{sec:counterfactual}).
\end{itemize}

Two kinds of charts opt out of this toggle. Charts that are already rates --- the policy rate,
unemployment --- are always shown in \% and ignore the growth-rate lenses. And a handful
of price and index series --- the oil price, exchange-rate indices, equity and house prices ---
are always drawn as \emph{levels} (an index number, or dollars per barrel for oil), because a
level is how you think about them. On those charts, dragging sets the level itself.

\subsection{The left control panel}

The panel down the left side holds everything that is not a chart. Top to bottom:

\begin{itemize}
  \item \textbf{Scenario} --- buttons to \textbf{Reset}, \textbf{Reset all}, \textbf{Save},
    and \textbf{Load} a scenario, plus \textbf{Cookbook}, a menu of ready-made, documented
    scenarios you can load in one click. Below them, a text box to name the scenario. All of
    it is covered in \S\ref{sec:use-scenarios}.
  \item \textbf{Long-run targets} --- a collapsible panel where you set where each variable
    settles in the long run. Covered in \S\ref{sec:use-longrun}.
  \item \textbf{Cross-border spillovers} --- two on/off switches controlling whether your
    scenario and your long-run targets propagate to other economies. Covered in
    \S\ref{sec:use-spillovers}.
  \item \textbf{Policy counterfactual} --- a mode for asking what a different interest-rate or
    spending path would do, judged through a structural model of your choice. Covered in
    \S\ref{sec:use-counterfactual}.
  \item \textbf{The conditioning list} --- once you steer a variable, it appears here with a
    slider and an on/off button for each forecast quarter, and a \textbf{Show deviations} /
    \textbf{Show levels} toggle for how you type the numbers. Covered in
    \S\ref{sec:use-scenarios}.
  \item \textbf{Acknowledgments} and the disclaimer sit at the very bottom.
\end{itemize}

\subsection{The bottom bar}

\paragraph{What you do.} You manage up to four scenarios side by side and export your results.

\paragraph{How.} The bar along the bottom shows one tab per scenario --- a colour dot, the
name, and the structural model and policy rule it uses for counterfactuals. Click a tab to make
that scenario active; click its \textbf{x} to remove it. \textbf{+ Add Scenario} creates a new
one (up to four). To rename a scenario, use the name box in the left control panel, not the
tab. On the right sit four export buttons: \textbf{CSV}, \textbf{Excel}, \textbf{PNG}, and
\textbf{PDF}.

\paragraph{What you find.} Every scenario draws on every chart in its own colour, so you can
compare, say, a soft-landing path against a stagflation path on the same axes. The exports
carry the numbers behind what you see --- baseline, scenarios, and uncertainty ranges --- and
are described in \S\ref{sec:export}.

%% ================================================================
\section{Building scenarios}\label{sec:use-scenarios}

A scenario is a forecast you have bent. You pin one or more variables to a path you
believe in --- say, inflation half a point higher for the next year --- and the model
redraws every other chart so the whole picture stays consistent with the estimated
economics. This ``pin some, let the model fill in the rest'' calculation is called a
conditional forecast; the mechanics live in \S\ref{sec:partial}. This chapter shows
you every way to set pins, how to run several scenarios side by side, and how to
start over.

\subsection{Pin a variable with the mouse}

\paragraph{What you do.} You tell the tool where you think one variable is heading,
directly on its chart.

\paragraph{How.}
\begin{enumerate}
  \item Find the chart you want to steer. In its header, click \textbf{condition}.
    The button changes to \textbf{CONDITIONED} and the panel gets a blue border.
    Nothing moves yet --- you have only declared the variable steerable.
  \item Drag on the plot. A hint badge --- \textbf{drag to set path} --- appears while
    the chart is draggable. As you drag, the forecast quarter nearest your cursor is
    pinned at the height of the cursor.
  \item Or skip step 1 entirely: \emph{right-click} anywhere on the forecast region of
    an unconditioned chart. That single click conditions the variable \emph{and}
    plants a pin exactly at the quarter and value you clicked. On a chart that is
    already conditioned, right-click toggles that one quarter's pin on or off,
    placing the dot at the cursor value.
\end{enumerate}

\paragraph{What you find.} The pinned quarter shows a solid dot at your value ---
the dot snaps to the click immediately, and the full redrawn path follows a moment
later. Every other quarter of that variable, and every other chart, adjusts to stay
consistent: pin growth down and you will typically see inflation soften and the
policy rate follow. Two things cannot be dragged. Charts with a \textbf{derived}
badge are computed by an accounting identity from other variables, so you steer
their drivers instead --- except the fiscal primary-balance and debt charts, where a
drag sets a target trajectory directly (see \S\ref{sec:use-fiscal}). And nothing is
draggable in the \textbf{\% vs base} view, which is a read-only impact display.

If cross-border spillovers are switched on for a linked economy, the line follows a
quick local preview while you drag, and the cross-country solve --- the fast direct
preview, flagged by the amber \textbf{GVAR DIRECT preview} badge --- fires once when
you release the mouse. The full cross-country solve still runs only on demand, via
the \textbf{Solve full GVAR} button or \textbf{Compute}
(\S\ref{sec:use-spillovers}).

\subsection{Fine-tune quarters in the conditioning list}

\paragraph{What you do.} You set exact numbers, quarter by quarter, instead of
eyeballing a drag.

\paragraph{How.}
\begin{enumerate}
  \item Look at the conditioning list at the bottom of the left control panel. Every
    conditioned variable appears there with twenty quarter rows, labelled
    \textbf{NC}, \textbf{t+1} through \textbf{t+19}. \textbf{NC} is short for
    nowcast, the model's estimate of the current, not-yet-published quarter --- its
    read of where the economy stands right now.
  \item Click a quarter label to switch that quarter's pin on or off. Click
    \textbf{All} to switch all twenty at once.
  \item Move a quarter's slider to set its value. The slider covers roughly
    $\pm 3$ in steps of $0.1$, and the number you set is shown next to it.
  \item By default you type absolute values (say, a policy rate of $3.5$). Click
    \textbf{Show deviations} to enter distances from the baseline forecast instead
    ($+0.5$); click \textbf{Show levels} to switch back. The same pins are shown
    either way.
  \item Click \textbf{remove} next to a variable's name to take it out of the
    scenario entirely.
\end{enumerate}

\paragraph{What you find.} Only the quarters you switched on are held fixed; the
quarters that are off are filled in by the model. A single pinned quarter far out
--- say \textbf{t+8} --- gives a smooth model-chosen path to that point. Pins are
what-you-set-is-what-you-see: a pinned quarter sits exactly at your number on the
chart, always. If a pinned path looks kinked or implausible elsewhere, that is the
model telling you what your assumption costs; loosen a quarter and watch it relax.

\subsection{Condition several variables at once}

\paragraph{What you do.} You build a richer story --- for example, weaker growth
\emph{and} a lower policy rate together, to describe a downturn the central bank
leans against.

\paragraph{How.} Condition each variable as above; they stack. Every conditioned
variable gets its own block in the conditioning list, and you can pin different
quarters on each.

\paragraph{What you find.} All pins are imposed jointly, not one after the other:
the model finds the single most plausible forecast that passes through every pin at
once. Beware of fighting yourself --- pinning inflation up while pinning the policy
rate down asks for an unusual combination, and the unconditioned charts will show
you how strained it is. Fewer, well-chosen pins usually tell a cleaner story than
many.

\subsection{Run scenarios side by side}

\paragraph{What you do.} You keep up to four alternative scenarios and compare them
on the same charts.

\paragraph{How.}
\begin{enumerate}
  \item In the bar along the bottom of the screen, click \textbf{+ Add Scenario}.
    A new tab appears with its own colour dot and becomes active; the button is
    offered while you have fewer than four scenarios.
  \item Click a tab to make that scenario active. All conditioning you do --- charts,
    the conditioning list, cookbook loads --- edits the active scenario only.
  \item Rename the active scenario by typing in the \textbf{Scenario name} box at the
    top of the left control panel. The tabs have no rename control of their own.
  \item Click the small \textbf{x} on a tab to delete that scenario. The \textbf{x}
    is shown only while you have more than one.
\end{enumerate}

\paragraph{What you find.} Each scenario is drawn on every chart in its own colour
--- blue, red, green, purple, matching the dot on its tab --- with the active
scenario's line thicker. There is no hide button: all scenarios stay visible until
you delete them, so if a chart gets crowded, remove the tabs you no longer need.
Each tab also carries a small caption naming the scenario's policy-model choice,
which matters only in counterfactual mode (\S\ref{sec:use-counterfactual}).

\subsection{Start over: Reset vs.\ Reset all}

\paragraph{What you do.} You clear your work --- either just the current scenario in
the current country, or everything everywhere.

\paragraph{How.} Both buttons sit in the \textbf{Scenario} header of the left
control panel. \textbf{Reset} clears the \emph{active} scenario's pins and paths for
the \emph{current country only}. \textbf{Reset all} (in red) clears every scenario
and all cross-country conditioning in all countries; because that is drastic, it
first shows ``Clear all scenarios \& conditioning?'' and waits for you to click
\textbf{Yes, reset all} or \textbf{Cancel}.

\paragraph{What you find.} After \textbf{Reset}, the active scenario's line falls
back onto the baseline forecast here, but pins you set in other countries survive.
After \textbf{Yes, reset all}, you are back to a clean baseline everywhere. If a
scenario is worth keeping, click \textbf{Save} first --- it writes the scenario to
an Excel file that \textbf{Load} restores later (\S\ref{sec:use-data}).

\subsection{When to press Compute}

\paragraph{What you do.} Nothing, most of the time. The central scenario path
updates live with every pin --- \textbf{Compute} is never needed to see it.

\paragraph{How.} Press \textbf{Compute} in the top bar only when you want
uncertainty bands around the scenario or when you have set a long-run target; the
button's enable rule and the \textbf{Uncertainty} switch are described in the tour
(\S\ref{sec:use-tour}).

\paragraph{What you find.} Bands appear around your scenario line, showing the range
of outcomes consistent with your pins --- how to read them is
\S\ref{sec:use-uncertainty}; long-run targets are \S\ref{sec:use-longrun}. Bands do
not refresh on their own: change a pin afterwards and press \textbf{Compute} again.

\subsection{Load a ready-made scenario from the Cookbook}

\paragraph{What you do.} Instead of building pins from scratch, you load a named,
documented recipe --- an oil-price shock, an inflation surge --- as a worked
example, then adjust it.

\paragraph{How.}
\begin{enumerate}
  \item In the \textbf{Scenario} header of the left control panel, click
    \textbf{Cookbook~\raisebox{-0.2ex}{$\blacktriangledown$}}. A panel titled
    \textbf{Scenario cookbook} opens, listing the recipes available for the current
    economy.
  \item Click \textbf{Why} on a recipe to read its rationale --- what the shock is
    and why the pins are set where they are.
  \item Click one of the two load buttons. \textbf{Load naive} pins only the
    headline variable and lets the model fill in everything else --- the model's own
    read of the shock. \textbf{Load + restriction} adds short-run pins on related
    variables that shape the shock into its economically meaningful form.
  \item Adjust from there: everything a recipe loads is ordinary conditioning, so
    the sliders in the conditioning list, the quarter toggles, and chart drags all
    work on it.
\end{enumerate}

\paragraph{What you find.} Loading \emph{replaces} the active scenario's
conditioning --- your existing pins are wiped, not merged, so switch to a fresh tab
first if you want to keep them. The panel closes and the charts redraw under the
recipe's pins. Comparing \textbf{Load naive} against \textbf{Load + restriction} for
the same recipe, on two tabs, is the fastest way to see what the extra pins buy. If
a recipe names a variable this economy does not carry, an amber note lists what was
skipped; click \textbf{Dismiss} to clear it.

%% ================================================================
\section{Cross-country spillovers}\label{sec:use-spillovers}

Economies trade with each other, so a shock to one moves the others. This chapter
shows you how to make your scenario travel: you condition inflation or growth in
one country, and the forecasts for its trading partners move too. The machinery
behind this is the linked cross-country system: country models tied together by
trade-weighted links, called a GVAR (\S\ref{sec:gvar}). On screen it comes down
to two switches, one button, and a small status badge.

A quick map of who is linked. Open the \textbf{Country} dropdown in the top bar:
economies listed under the \textbf{GVAR} heading are full members of the linked
system --- conditioning any of them can reach all the others. Economies under
\textbf{Other countries} include the individual euro-area members (Germany,
France, Italy, \dots), which are a special case: they receive shocks through the
euro-area aggregate rather than through their own link (see the last subsection).

By default both spillover switches are \emph{off}. Until you turn something on or
press a solve button, a scenario moves only the country you are looking at, and
its partners stay frozen. That is deliberate: local-only is instant, it is
explicit about what has and has not been computed, and it is often all you need.

\subsection{Turning on scenario spillovers}

\paragraph{What you do.} You let your conditioning --- the points you have pinned
on the charts --- propagate across borders, so that, say, a United States growth
scenario also moves the euro area, Japan, and China.

\paragraph{How.}
\begin{enumerate}
  \item In the left control panel, find the section headed
    \textbf{Cross-border spillovers}.
  \item The first switch is \textbf{Scenario spillovers (GVAR solve)}. Click its
    On/Off pill to turn it \textbf{On}.
  \item Condition a variable as usual (\S\ref{sec:use-scenarios}): click
    \textbf{condition} on a chart and drag the forecast, or right-click to plant
    a point directly.
\end{enumerate}

\paragraph{What you find.} With the switch on, every edit to a pinned point
triggers a live cross-country computation. A status line appears above the chart
grid. While the computation runs you see a small \textbf{computing\ldots} pill
with a spinner --- the heavier recomputations can take several seconds, so the
pill tells you the app is working, not frozen. When it finishes, a badge
(marked with a small double-arrow icon) reports what was computed, for example
\textbf{GVAR DIRECT preview} with a short technical read-out (how many passes it
took, a convergence number, and how long it ran). Switch to another country in
the \textbf{Country} dropdown and you will see its forecasts shifted by your
scenario. If the switch is \emph{off} instead, the status line says \emph{local
forecast (partners frozen)} whenever you have active pins --- a plain reminder
that what you see has not travelled anywhere.

\subsection{Preview versus the complete solve}

The live result you get while editing is a \emph{preview}, and it is worth
understanding what that means.

\paragraph{What you do.} You read the badge above the charts to know how much of
the cross-country feedback is in the numbers on screen.

\paragraph{How.} Look at the badge colour and text:
\begin{itemize}
  \item An \emph{amber} badge reading \textbf{GVAR DIRECT preview} means you are
    seeing the fast first-pass answer: your shock has travelled \emph{one hop}
    to each partner, but the partners' responses have not yet fed back --- the
    echo of the echo is missing. This keeps editing responsive.
  \item A \emph{blue} badge reading \textbf{GVAR full solve} means the complete
    answer is on screen: every feedback loop between every linked economy,
    including the feedback from the rest of the world onto the United States,
    has been solved through to consistency (see \S\ref{sec:gvar:solvemode}).
\end{itemize}

\paragraph{What you find.} For small shocks the preview and the full solve are
usually close, because the second-round echoes are smaller than the first hop.
For large shocks, or when you care about the country \emph{receiving} the
spillover, run the full solve before you quote numbers. The hint text next to
the badge tells you which situation you are in: \emph{live direct-channel
preview --- click ``Solve full GVAR'' for all feedback loops} when a preview is
showing, and \emph{conditioning one bloc propagates to its trade partners} once
the full answer is up.

\subsection{The ``Solve full GVAR'' button}

\paragraph{What you do.} You compute the complete cross-country answer on
demand --- whether or not the scenario-spillover switch is on.

\paragraph{How.}
\begin{enumerate}
  \item Set up your scenario first: pin the paths you want.
  \item Click \textbf{Solve full GVAR} (the button is marked with a filled
    play-triangle icon). The button appears in two places --- in the
    \textbf{Cross-border spillovers} section of the control panel, and above the
    chart grid whenever a fuller answer than the one on screen is available.
    Pressing \textbf{Compute} in the top bar runs the same complete solve as
    part of its work.
  \item Wait for the \textbf{computing\ldots} pill to clear. The complete solve
    is the heavy option; expect it to take roughly ten seconds rather than an
    instant.
\end{enumerate}

\paragraph{What you find.} The badge turns blue and reads
\textbf{GVAR full solve}, and the button above the grid disappears --- there is
nothing more to compute for this scenario. Every linked country's charts now
show the fully consistent answer. This is the workflow to prefer if you leave
the spillover switch off: work locally and fast while you shape the scenario,
then press \textbf{Solve full GVAR} once to propagate it everywhere. Be aware
that pressing the button also turns the \textbf{Scenario spillovers (GVAR
solve)} switch \textbf{On}, so later pin edits run the live cross-country
preview; switch it back \textbf{Off} if you want to return to local-only
editing. Note also that the full solve reflects the pins as they are when you
press it; if you keep editing afterwards, press it again.

\subsection{Long-run target spillovers}

\paragraph{What you do.} You let a \emph{long-run target} --- a value you have
set for where a variable settles far out (\S\ref{sec:use-longrun}) --- shift the
long-run forecasts of the trading partners too, not just the economy you set it
on.

\paragraph{How.}
\begin{enumerate}
  \item Set a long-run target as described in \S\ref{sec:use-longrun}.
  \item In \textbf{Cross-border spillovers}, turn \textbf{On} the second switch,
    \textbf{Long-run target spillovers (GVAR constant shifts)}.
\end{enumerate}

\paragraph{What you find.} This channel is instant --- no solve button and no
computing pill. The cross-country pass-through of long-run shifts is worked out
once, ahead of time, so flipping the switch just applies it (the construction is
in \S\ref{sec:gvar:solvemode} and \S\ref{sec:driftsetter}). The receiving
country tells you what happened: the banner above its chart grid, which normally
reads \textbf{Unconditional forecast:} \emph{model-based}, turns amber and adds
\textbf{+ spillover from} followed by the names of the countries whose targets
are feeding in. Hover it for the full explanation. This keeps judgment visible:
you can always tell a partner's baseline has been tilted by targets you set
elsewhere. Note the two switches are independent --- one governs scenario pins,
the other long-run targets, and either can be on without the other.

\subsection{Euro-area members: one interest rate, one doorway}

The individual euro-area members --- Germany, France, Italy, Spain, and the
smaller members --- do not set their own interest rate. They share the European
Central Bank's policy rate, the area-wide long yield, and the area corporate
bond yield (each member also carries its own sovereign spread over the Bund).
The tool respects this: a member's model does not have its own policy channel to
move. Instead, shocks reach a member through one doorway --- the euro-area
aggregate. A United States or euro-area scenario first moves the area-wide
model. The solved area response --- the common interest rate, area growth, area
inflation --- is then fed into the member's own model, which translates it into
that member's GDP, inflation, and yields.

\paragraph{What you do.} You run, say, a United States scenario and check what
it does to Germany.

\paragraph{How.}
\begin{enumerate}
  \item Condition your scenario on the United States (or euro-area) charts.
  \item Switch the \textbf{Country} dropdown to Germany.
  \item Look above the chart grid. If the area shock has not been passed
    through yet, you see an amber note: \textbf{Cross-border spillover from the
    US/EA scenario not yet computed}, next to a
    \textbf{Solve full GVAR} button.
  \item Click \textbf{Solve full GVAR} (or press \textbf{Compute}
    in the top bar). This solves the euro-area aggregate and pushes the area
    shock into the member.
\end{enumerate}

\paragraph{What you find.} After the solve, Germany's growth, inflation, and
interest-rate charts show the scenario's imprint, transmitted through the common
euro-area block. Members never update silently in the background --- the amber
note is the tool telling you plainly that the answer on screen is still the
pre-scenario one, and the solve runs only when you ask for it. Check the note is
gone before reading member charts under a US or euro-area scenario. If you edit
the scenario again, the note reappears and you re-solve. On a member you will
not see the \textbf{GVAR} badge itself; that badge belongs to the full members
of the linked system, and the member's answer arrives through the euro-area
doorway instead.

Two caveats to close. First, spillovers only flow between economies in
the linked system --- for the exact variable-by-variable channels, see
\S\ref{sec:gvar:stars}. Second, on a linked economy the \textbf{Long-run
targets} panel always shows an amber \textbf{GVAR bloc} note warning that, with
the target-spillover switch off, partners are \emph{not} re-solved --- the
realised joint outcome may differ from the single-country picture on screen.

%% ================================================================
\section{Long-run targets}\label{sec:use-longrun}

Every forecast in this tool eventually settles down: growth returns to a trend rate,
inflation to a typical level, a fiscal ratio to its long-run average. Where each
variable settles comes from the estimated model. A \emph{long-run target} lets you
overrule that: you say where a variable should end up --- inflation at 2\%, say, or
trend growth at 1.5\% --- and the tool bends the whole forecast so it glides to your
number instead of the model's. How that bending works is explained in Part~II
(\S\ref{sec:longrun} and \S\ref{sec:driftsetter}); this chapter shows you the controls.

Two things to hold on to. First, every control starts at the model's own estimate, so
an untouched panel changes nothing --- the default view is always the raw model.
Second, targets apply \emph{instantly}: the moment you change a value, the baseline and
every scenario update. You never press \textbf{Compute} for this; that button is for
uncertainty bands and is covered in \S\ref{sec:use-uncertainty}.

\subsection{Set a target}

\paragraph{What you do.} Pick one variable and fix where it settles at the far end of
the forecast.

\paragraph{How.}
\begin{enumerate}
  \item In the left control panel, click the \textbf{Long-run targets} header (just
    below the scenario name). The panel unfolds; the chevron turns from
    $\blacktriangleright$ to open.
  \item Find the row for your variable. There is one row for every chart that can be
    targeted, in the same order as the chart grid, labelled with the chart title and
    its unit --- for example \textbf{Inflation \(\cdot\) \% q/q ann.} (quarter-on-quarter
    at an annual rate; units are explained in \S\ref{sec:units}).
  \item Set the value. Either drag the slider, or type in the number box, or use its
    arrows --- each arrow click steps the target by 0.1. The small grey
    \textbf{est} figure next to the slider is the model's own estimate, your
    reference point.
  \item To take a target back, click the row's reset-to-estimate arrow button --- it
    resets that variable to the model estimate. Setting the value exactly back to the
    estimate does the same thing: the target is removed, not stored as a coincidence.
\end{enumerate}

\paragraph{What you find.} The row highlights amber as soon as the value leaves the
estimate, the panel header gains a count such as \textbf{(1 set)}, and a green badge
appears at the foot of the panel reading \textbf{1 target \(\cdot\) exact}. ``Exact''
means what it says: the forecast is built to hit your number at the end of the horizon
by construction, not approximately. On the chart, the forecast path for that variable
now drifts toward your value instead of the model's. A \textbf{reset all to estimate}
link next to the badge clears every target at once.

\subsection{See which numbers are yours}

\paragraph{What you do.} Keep a visible record, on the charts themselves, of where you
have overruled the model.

\paragraph{How.} Nothing to click --- the flags appear on their own. Look in two
places: the chart title, and the status line above the grid.

\paragraph{What you find.} Two flags appear automatically. On the affected chart, the
title turns amber and shows a small \textbf{judgement} badge with a pencil mark; hover
it and the tooltip states your target and the model estimate side by side, in the
chart's units. Above the whole grid, the status line \textbf{Unconditional forecast:}
switches from \textbf{model-based} to \textbf{with judgement (1 variable anchored)},
counting up as you add targets. When every target is cleared, both flags disappear and
the line reads \textbf{model-based} again. This is the tool's third honest rule at
work: judgment is visible, always.

\subsection{Load the consensus anchors}

\paragraph{What you do.} Instead of setting values by hand, load a ready-made set of
publicly defensible long-run numbers for the country you are viewing --- one click.

\paragraph{How.}
\begin{enumerate}
  \item Open \textbf{Long-run targets}. If a preset exists for this country, a
    \textbf{Consensus anchors} note sits near the top of the panel, saying how many
    variables it covers.
  \item Click \textbf{Apply consensus anchors}. The button turns green and reads
    \textbf{\checkmark~Consensus applied} while your targets exactly match the preset.
  \item Click the adjacent \textbf{Clear} to drop all targets and return every
    variable to its model estimate.
\end{enumerate}

\paragraph{What you find.} The preset is deliberately minimal --- and audited. A
comprehensive review (July 2026) tested every candidate anchor against the forecast it
produces and kept only those that fix a genuine long-run bias \emph{without} distorting
the near-term path: 32 anchors across 23 economies, drawn from long-run growth,
inflation, and --- for some public-finance economies --- revenue, spending, or the
effective interest rate on debt. It never sets policy rates, unemployment, or asset
prices. Where a preset ships it is \emph{on} by default (the affected charts carry the
judgement flag, \S\ref{sec:use-longrun}); \textbf{Clear} returns the country to the raw
model. Most economies ship \emph{no} preset at all --- their long run is left entirely
model-driven, so the block simply does not appear there (Japan is one; so are the
economies whose long-run biases are too large to fix by a target and are queued for
re-estimation instead).

\subsection{Bring in an outside forecast}\label{sec:use-external}

\paragraph{What you do.} Feed the model someone else's forecast --- IMF WEO, a consensus
survey, a market curve, your own desk numbers --- as an \emph{ingredient} rather than as a
hard fact. You decide how much to trust it; the model reconciles it with everything else.

\paragraph{How.} Open \textbf{External forecasts} in the left panel. You have three ways in:
\begin{enumerate}
  \item \textbf{Load WEO} --- one click loads the IMF World Economic Outlook forecast for the
    economy you are viewing (real GDP growth and CPI inflation). WEO is annual, so each year's
    figure is applied softly to that year's four quarters and the model fills in the shape;
    WEO carries no policy rates, so the rate stays model-driven.
  \item \textbf{Export template} downloads an Excel file for this economy --- the headline
    variables across the forecast quarters, pre-filled with the model's own baseline as a
    starting point, with a Notes sheet naming the units. Overwrite the cells with your numbers
    and re-import. This is the easiest way to see exactly how a forecast should be structured.
  \item \textbf{Import forecasts\ldots} accepts that Excel file, or a small JSON
    (\texttt{data/sample\_external\_forecast.json} is a template):
\begin{quote}\small\ttfamily
\{ "source": "WEO", "bloc": "US",\\
\phantom{xx}"forecasts": \{ "GDPH": \{ "2026Q2": 2.4, "2026Q3": 2.2 \} \} \}
\end{quote}
\end{enumerate}
Whichever way you bring it in, the source appears in a list with a \textbf{trust} slider. At
\textbf{100\,\%} the forecast is pinned exactly (identical to conditioning it by hand); lower
it and the model is allowed to pull the number toward its own view --- half-way means the band
around that point is about half the model's own.

\paragraph{What you find.} Each imported point shows as a \textbf{teal diamond} with a small
error bar --- taller when you trust it less --- and every other chart moves in response,
because the outside number enters through the same estimated dynamics as any pin: an
imported growth path cools the rate, shifts inflation, and so on. A cell you have pinned by
hand always wins over an imported one. Turning the trust to zero, or pressing the source's
\textbf{✕}, removes it. This release applies imported forecasts to the \emph{viewed} economy;
the cross-country version (a WEO path for the United States moving the euro area) is planned.

\paragraph{Under the hood.} An imported forecast is a \emph{soft} conditioning: the
Durbin--Koopman smoother (Part~II, \S\ref{sec:kalman}) is run with a measurement variance on
that cell, set from the trust dial relative to the model's own predictive band --- trust
$t$ gives variance $\mathrm{predVar}\cdot(1-t)/t$, so $t\to1$ is an exact observation and
$t\to0$ is no information at all. The band therefore shrinks only \emph{partially} at a soft
pin, which is the honest thing to draw.

\paragraph{Saving the whole picture.} Because an outside forecast, your conditioning, the
long-run targets and the cross-country pins together define your view, the scenario header
carries \textbf{Export session} / \textbf{Import session}: one JSON that bundles all of it
across every country --- so a colleague opens exactly what you see, or you pick the work up
tomorrow. (The older per-scenario \textbf{Save} exports one country's conditioning to Excel.)

\subsection{Several targets at once: Per-variable or Joint}

\paragraph{What you do.} When you set two or more targets, they can interfere: pushing
inflation up also moves the interest rate, which moves growth, and so on. You choose
how the tool handles that interference.

\paragraph{How.} As soon as a second target is set, a \textbf{Multiple-target solve}
toggle appears at the top of the panel with two buttons: \textbf{Per-variable} and
\textbf{Joint}. \textbf{Per-variable} is the default.

\paragraph{What you find.} The trade-off, in plain words:
\begin{itemize}
  \item \textbf{Joint} solves all your targets together, so each one lands exactly on
    its value, knock-on effects included. This is the correct answer --- but if two
    targets are strongly related (say two interest rates the model cannot move apart
    in the long run), the solve can become unstable and the paths can blow up. If the
    charts go wild after you add a target, switch to \textbf{Per-variable}.
  \item \textbf{Per-variable} sets each target on its own, ignoring what one target's
    shift does to the others. It is stable and bounded --- but approximate: it
    understates the knock-on effects, so with several targets set, each one lands
    slightly off its stated value.
\end{itemize}
A footnote line under the toggle restates which behaviour is active. With a single
target the two modes coincide, so the toggle is hidden. The mathematics behind both
modes is in \S\ref{sec:driftsetter}.

\subsection{Greyed-out sliders}

A few variables cannot be retargeted reliably: the model's long-run response to them is
too weak for the calculation to be trustworthy. Their rows are disabled, and hovering
shows \emph{``Near-singular response --- this variable cannot be retargeted
reliably.''} This is a safety guard, not a bug --- forcing a target there would produce
an explosive or meaningless path. Target a closely related variable instead.

\subsection{Growth targets move the debt path}

Rows for real-growth variables carry an extra tag, \textbf{\(\cdot\) sets debt path}.
Setting long-run growth changes the gap between the interest rate and growth, and that
gap compounds on the stock of public debt --- so a growth target quietly reshapes the
debt-to-GDP forecast too. It is a consequence of arithmetic, not a structural fiscal
fix. The public-finance charts are covered in \S\ref{sec:use-fiscal}, and the
accounting behind them in \S\ref{sec:fiscal_identity}.

\subsection{Targets and other countries}

For an economy inside the linked cross-country system (\S\ref{sec:gvar}), the panel
shows an amber note beginning \textbf{GVAR bloc.} --- it means that, by default, your
target moves only the country you set it on; trading partners are not re-solved. To
let a long-run target travel across borders, turn on \textbf{Long-run target
spillovers (GVAR constant shifts)} --- the switch, and how imported judgment is
flagged on the receiving side, are covered in \S\ref{sec:use-spillovers}.

%% ================================================================
\section{Policy counterfactuals}\label{sec:use-counterfactual}

A scenario answers ``what if the data come in differently?'' A policy
counterfactual answers a sharper question: \emph{what if the central bank had
set interest rates differently?} You choose a theory model of how the economy
responds to policy, push the policy rate up or down quarter by quarter, and the
tool draws a second forecast --- the counterfactual --- as a dashed line next
to your scenario on every chart. The scenario line stays put; the dashed line
shows what that same scenario would have looked like under the alternative
rate path. The machinery behind this is described in \S\ref{sec:counterfactual}
and \S\ref{sec:dsge}.

One term needs defining up front. The theory models used here are DSGE models
--- economist shorthand for models where households, firms, and the central
bank are written down as decision-makers, so the model has an internal story
about \emph{why} a rate change moves inflation and output. Each model ships
with pre-computed IRFs --- impulse response functions, a ledger of how a
one-time rate move ripples through every variable over the following quarters.
The counterfactual is built by adding that ledger, scaled to your rate
adjustment, on top of your scenario.

\subsection{Turning counterfactual mode on}

\paragraph{What you do.} You switch the active scenario into counterfactual
mode so the policy controls appear.

\paragraph{How.}
\begin{enumerate}
  \item In the left control panel, find the \textbf{Policy Counterfactual}
    section.
  \item Click \textbf{Policy counterfactual}. The button turns orange and its
    label changes to \textbf{Exit counterfactual mode}; click it again at any
    time to leave.
\end{enumerate}

\paragraph{What you find.} The section expands to show four blocks:
\textbf{DSGE Model}, \textbf{Policy Rule}, \textbf{Macro response}, and the
adjustment sliders. Nothing on the charts changes yet --- the counterfactual
line only appears once you actually move the rate.

\subsection{Picking a model and a policy rule}

\paragraph{What you do.} You choose which theory model, and which interest-rate
rule inside it, translates your rate move into effects on the rest of the
economy. This choice matters: the same one-quarter rate move can have a much
larger or smaller effect under one model-and-rule pair than under another, so
treat the pass-through as model-dependent, not as a fact.

\paragraph{How.}
\begin{enumerate}
  \item Under \textbf{DSGE Model}, the current model name is shown (the
    default is \textbf{US\_SW07}, a widely used estimated model of the US
    economy). Click \textbf{Browse...} to open the model list, grouped by
    category with a count per group, or type in \textbf{Search models...} to
    filter by name or author. Click a model to select it; the list closes.
  \item Under \textbf{Policy rule}, pick a rule from the dropdown. Each entry
    shows the rule name and a short description. Rules without pre-computed
    responses for the selected model are greyed out and marked
    \textbf{(no IRFs)} --- you cannot select them.
\end{enumerate}

\paragraph{What you find.} In the default \textbf{Rule-based} mode a note
below the buttons reads ``IRFs pre-computed with the \ldots{} rule embedded in
the DSGE equilibrium'' --- meaning the rule is baked into the model's ledger of
responses, not applied afterwards. Only the model list is filtered to models
that have at least one computed rule.

\subsection{Setting the rate adjustment}

\paragraph{What you do.} You specify how much higher or lower the policy rate
should be than in your scenario, quarter by quarter, in percentage points.

\paragraph{How.} There are two equivalent ways.
\begin{enumerate}
  \item \emph{Sliders.} Under \textbf{Interest rate adjustment (pp)} you find
    twelve sliders labelled \textbf{Q1} through \textbf{Q12}, each running
    from $-2$ to $+2$ percentage points in steps of 0.05, with a signed
    readout on the right. Moving a slider sets that quarter. \textbf{Undo}
    steps back through your recent slider moves; \textbf{Reset} clears the
    whole adjustment.
  \item \emph{Drag on the chart.} With counterfactual mode on, the policy-rate
    chart shows a \textbf{drag to adjust policy} badge. Drag the forecast
    part of the rate line to where you want it; the nearest quarter takes the
    difference between your cursor and the scenario's rate as its adjustment.
\end{enumerate}

\paragraph{What you find.} Every quarter you touch --- by slider or by drag
--- becomes \emph{pinned}: the counterfactual rate holds your value there.
Quarters you never touched are left to the model: under the rule-consistent
mode below, the model's own rule decides how the rate behaves in them,
responding to the inflation and output your pinned quarters have caused.
Right-click a quarter on the policy-rate chart to toggle it between pinned
and free; releasing a quarter also zeroes its adjustment so a later re-pin
starts clean. So a single $+0.5$ in Q1 is not a five-year rate promise ---
it is a one-quarter surprise, after which policy follows the rule.

\subsection{Two ways the economy can respond}

\paragraph{What you do.} You choose who works out the consequences of the rate
move: the theory model or the forecasting model.

\paragraph{How.} Use the \textbf{Macro response} dropdown:
\begin{itemize}
  \item \textbf{DSGE/Taylor-rule (IRF-consistent)} --- the default. The theory
    model's ledger of responses dictates how inflation, output, and the rest
    react, and the unpinned rate quarters follow the model's policy rule. This
    is the mode that answers ``what does \emph{this theory} say the rate move
    would have done?''
  \item \textbf{BVAR-endogenous (let adjust)} --- no theory model. The rate
    path is handed to the estimated forecasting model as extra conditioning
    information, and it works out everything else's response from the
    historical correlations, exactly as in a scenario
    (\S\ref{sec:use-scenarios}, method in \S\ref{sec:modes}). This answers
    ``what does \emph{the data} say usually accompanies such a rate path?''
\end{itemize}

\paragraph{What you find.} The two modes can disagree, and that disagreement
is informative: theory attributes the move to a deliberate policy surprise;
the historical pattern cannot tell a surprise from a response to something
else. If the selected model-and-rule pair has no computed responses, an amber
warning appears --- ``No IRFs for \ldots{} --- using BVAR-only
re-conditioning'' --- telling you the tool has silently fallen back to the
second mode. Pick a different rule if you wanted the theory answer.

\subsection{Reading the result, and the Level \textbar{} Rate (IRF) toggle}

\paragraph{What you do.} You read the counterfactual off the charts and, if
you want, switch to a view that shows only the policy effect.

\paragraph{How.}
\begin{enumerate}
  \item Look at any chart: the counterfactual is the dashed line labelled
    \textbf{Counterfactual} on hover, drawn in a distinct rust colour next to
    your scenario line.
  \item To isolate the effect, set the \textbf{Units} toggle in the top bar to
    \textbf{\% vs base}. Charts now plot deviations from baseline, and the
    counterfactual line becomes the pure policy effect. This view is
    read-only --- you cannot drag in it.
  \item In that view only, a second toggle appears: \textbf{Level} versus
    \textbf{Rate (IRF)}. \textbf{Level} (the default) shows the cumulative
    effect on the \emph{level} of each variable --- where GDP ends up
    relative to baseline, the ``\% chg.''\ reporting convention.
    \textbf{Rate (IRF)} shows the quarter-by-quarter effect in each
    variable's native units --- the way responses are plotted in the model
    database the DSGE models come from, so you can compare the chart directly
    against published model responses.
\end{enumerate}

\paragraph{What you find.} Under a rate hike of, say, $+1$ percentage point
for one quarter, expect the dashed line to show the rate above the scenario
at the start, inflation and growth drifting below it over the following
quarters, and everything closing back towards the scenario as the effect dies
out. How large and how persistent is a property of the model and rule you
chose --- switch models and watch the dashed line change while your scenario
does not. Uncertainty bands, if computed, belong to the scenario; the
counterfactual is a single model-implied path (\S\ref{sec:uncertainty}).

\subsection{Letting the tool choose the rate path: Optimal (B\&M)}

\paragraph{What you do.} Instead of hand-crafting a rate path, you state what
the central bank should care about --- price stability versus employment ---
and the tool computes the rate path that best achieves it, using the
Barnichon--Mesters method --- it reads the best rate path directly off the
model's ledger of responses, no extra estimation (\S\ref{sec:bm}).

\paragraph{How.}
\begin{enumerate}
  \item Under \textbf{Policy Rule}, click \textbf{Optimal (B\&M)} instead of
    \textbf{Rule-based}.
  \item Move the weight slider between \textbf{Price stability} and
    \textbf{Full employment}; the readout shows the two weights, written
    $\lambda\pi$ and $\lambda y$ on screen.
  \item Set the goals with the \textbf{$\pi$* target} slider (inflation, 0 to
    5, step 0.1) and the \textbf{y* target} slider (output, $-3$ to $3$,
    step 0.1).
  \item Click \textbf{Compute optimal rate path}.
\end{enumerate}

\paragraph{What you find.} The rate-adjustment sliders fill in with the
computed path, and --- unlike a hand-set path --- \emph{every} quarter is
pinned: the optimal path is a full plan, not a one-off surprise. The dashed
counterfactual line updates as usual. If the selected model and rule have no
computed responses, an alert says so and nothing is loaded; pick another
rule first. The caption ``Barnichon \& Mesters (2023) sufficient statistics''
names the method.

\subsection{A fiscal lever too}

\paragraph{What you do.} You add a government-spending move to the
counterfactual, alongside (or instead of) the rate move.

\paragraph{How.} Below the rate sliders, find \textbf{Fiscal adjustment ---
gov spending (pp)}: twelve more sliders (\textbf{Q1}--\textbf{Q12}, $\pm 3$,
step 0.1) with their own \textbf{Undo} and \textbf{Reset}. They work exactly
like the rate sliders, scaling the model's government-spending responses on
top of your scenario.

\paragraph{What you find.} As the caption notes, this needs the selected
model to include fiscal responses --- fewer than half of the models do ---
so if the dashed line does not react, that is why. For projecting the public
finances themselves (debt, deficits), use the fiscal block instead
(\S\ref{sec:use-fiscal}).

Everything here belongs to the \emph{active} scenario. Each scenario tab
carries its own model, rule, and adjustments --- shown as a small
``model/rule'' caption on the tab --- so you can keep, say, a hawkish and a
dovish counterfactual side by side and flip between them in the bottom bar.

%% ================================================================
\section{Public finances and the external accounts}\label{sec:use-fiscal}

For the economies that carry public-finance data, the tool adds a government block to the
chart grid: what the government collects, what it spends, what it pays in interest, and where
its debt goes. For three economies it also adds an external block: trade with the rest of the
world and the country's net position toward it. This chapter shows you how to read both blocks,
how to bend the debt path, and which numbers are data and which are stated modelling assumptions.

\subsection{Reading the fiscal charts}

\paragraph{What you do.} You inspect a country's public finances: the forecast for revenue,
spending, interest costs, the budget balance, and the debt ratio.

\paragraph{How.}
\begin{enumerate}
  \item Pick a fiscal economy in the \textbf{Country} dropdown. The block exists for the
    United States, the euro area and each euro-area member, Japan, the United Kingdom, Canada,
    and China. Other countries show no fiscal charts.
  \item In the main grid, find the four estimated fiscal charts: \textbf{Revenue} and
    \textbf{Primary Expenditure} (both in \% of GDP), \textbf{Effective Interest Rate}
    (in \% per year), and \textbf{Stock-Flow Adjustment} (in \% of GDP).
  \item Below them, find the row headed \textbf{Fiscal block --- derived by accounting
    identity}. It holds three more charts: \textbf{Primary Balance}, \textbf{$\Delta$
    Debt-to-GDP}, and \textbf{Debt-to-GDP}.
\end{enumerate}

\paragraph{What you find.} The four charts in the main grid are \emph{estimated}: the model
forecasts them directly, like inflation or growth. In plain words:
\begin{itemize}
  \item \textbf{Revenue} and \textbf{Primary Expenditure} are what the government takes in and
    what it spends, excluding interest, both as a share of the economy.
  \item The \textbf{Effective Interest Rate} is the average rate the government actually pays:
    interest costs divided by the debt stock. It moves slowly, because old debt was issued at
    old rates.
  \item The \textbf{Stock-Flow Adjustment} is the bookkeeping gap between the deficit and the
    change in debt --- items such as asset sales or valuation effects that move debt without
    passing through the budget.
\end{itemize}
The three charts in the derived row are \emph{not} estimated. They are computed from the four
drivers by budget arithmetic. The \textbf{Primary Balance} is simply revenue minus primary
expenditure. The debt line is an accounting identity rolled forward: each quarter, debt grows
with the interest the government pays, shrinks as the economy grows in money terms, and falls
one-for-one with the primary surplus. The tool applies that rule quarter by quarter, starting
from the last observed debt ratio. \textbf{$\Delta$ Debt-to-GDP} shows the resulting change per
quarter. The exact arithmetic is in Part~II, \S\ref{sec:fiscal_identity}.

Three reading notes. First, the derived charts show the forecast horizon only --- the history
sits in the driver charts above. Second, the \textbf{Units} toggle in the top bar does not
change them; they are always ratios to GDP or rates. Third, \textbf{$\Delta$ Debt-to-GDP}
carries a grey \textbf{derived} badge and cannot be conditioned --- it is implied by the others.

\subsection{Move the fiscal forecast through its drivers}

\paragraph{What you do.} You impose a view on a fiscal driver --- say, revenue one point of GDP
weaker --- and read off what it does to the balance and the debt.

\paragraph{How.} Condition the driver exactly as you condition any variable
(\S\ref{sec:use-scenarios}): click \textbf{condition} on the \textbf{Revenue}, \textbf{Primary
Expenditure}, \textbf{Effective Interest Rate}, or \textbf{Stock-Flow Adjustment} chart, then
drag the line or use the sliders in the left panel.

\paragraph{What you find.} The whole model updates, and the derived row updates with it. A note
appears next to the block header --- \textbf{derived variables implicitly conditioned} ---
reminding you that once you pin any fiscal variable, the primary balance and the debt path are
pinned too, through the identity. Growth and inflation matter as much as the budget itself:
push growth down and the debt ratio rises even with unchanged fiscal numbers, because the
denominator shrinks and the gap between the interest rate and growth widens.

\subsection{Set a debt path or a primary-balance path directly}

\paragraph{What you do.} Instead of working through the drivers, you draw the outcome you want:
``debt stabilises at, say, 100\% of GDP'' or ``the primary balance reaches, say, plus one
percent of GDP by 2028'' --- and let the tool find the budget that delivers it.

\paragraph{How.}
\begin{enumerate}
  \item On the \textbf{Debt-to-GDP} or \textbf{Primary Balance} chart, click
    \textbf{condition}, or simply right-click where you want the path to pass --- that plants a
    dot exactly at the clicked quarter and value.
  \item Drag the line to shape the trajectory. The badge reads \textbf{drag to set path}. On
    these two charts, the value you drag to is the \emph{absolute} target --- 100 means 100\%
    of GDP, not a deviation.
  \item Right-click again on a quarter to pin or release it. Released quarters follow the model.
  \item To remove the target, click the \textbf{CONDITIONED} button. Note that these two
    trajectory targets live on the chart itself; they do not appear in the conditioning list
    in the left panel.
\end{enumerate}

\paragraph{What you find.} A primary-balance target is hit \emph{exactly}: it is a straight
linear condition on revenue minus expenditure, and the model finds the most plausible mix. A
debt target is \emph{approximate}, and says so. The tool inverts the debt arithmetic: it
computes the primary balance that would deliver your debt path \emph{given the model's forecast}
interest rate and growth, and pins that. But the interest rate and growth themselves respond a
little to the implied consolidation, and the tool does not iterate on that feedback. In practice
the realised debt path can miss your target --- by, say, a point or so of GDP over the horizon.
If you need the debt line exact to the decimal, this is not the instrument; if you want
a coherent consolidation scenario, it is. Details in Part~II, \S\ref{sec:fiscal_inversion}.

\subsection{Long-run fiscal targets}

Every fiscal driver can also be given a long-run destination in the \textbf{Long-run targets}
panel (\S\ref{sec:use-longrun}). Two things are specific to the fiscal block. First, the real
growth target carries the note \textbf{sets debt path}: where growth settles decides whether
the debt ratio drifts up or down, because it sets the gap between the interest rate and growth
--- it is not a structural budget fix. Second, for the main fiscal economies the
\textbf{Apply consensus anchors} button loads public long-run values for revenue, primary
expenditure, and the effective interest rate alongside growth and inflation; it is off by
default, so the raw model is what you see first.

\subsection{The external accounts}

\paragraph{What you do.} For the United States, the euro area, and China, you read the
country's balance with the rest of the world: exports minus imports, the broader current
account, and the accumulated net position.

\paragraph{How.} Select one of those three economies. Below the fiscal block, find the row
headed \textbf{External-sector block --- derived by balance-of-payments identity} with three
charts: \textbf{Trade Balance}, \textbf{Current Account}, and \textbf{NFA / GDP}, all in \% of
GDP.

\paragraph{What you find.} \textbf{Trade Balance} is exports minus imports. \textbf{Current
Account} adds the income the country earns on its net foreign assets. \textbf{NFA / GDP} is
the stock of net foreign assets --- what the country owns abroad minus what it owes abroad ---
rolled forward, quarter by quarter, from the latest published net position: each surplus adds
to it, each deficit subtracts, and exchange-rate moves revalue it. All three charts are
read-only and carry a \textbf{derived} note: to move them, condition the drivers --- the
export, import, exchange-rate, or growth charts in the country grid --- and the external row
follows. A weaker currency, for instance, revalues foreign-currency assets upward and shifts
the net position even before trade responds.

\subsection{Which numbers are modelling defaults}

Some inputs are data and some are assumptions, and the distinction matters. Data: the estimated
drivers, the starting debt ratio, and the starting net foreign asset position --- the latter
two come from published official statistics for each economy. Stated assumptions, shipped
flagged in the model files:
\begin{itemize}
  \item \textbf{The structural stock-flow adjustment.} The debt roll-forward uses a fixed
    per-quarter constant for the deficit--debt gap, not the forecast from the
    \textbf{Stock-Flow Adjustment} chart, because that forecast can be dragged to extremes by
    other conditions and would distort the debt line. The chart shows the model's forecast; the
    debt arithmetic deliberately uses the stable constant.
  \item \textbf{The return on net foreign assets}, set to about 3\% per year, which generates
    the income line inside the current account.
  \item \textbf{The share of net foreign assets exposed to the exchange rate}, set to about
    0.4, which scales the revaluation effect.
\end{itemize}
Neither of the last two is estimated; treat the level of the income and revaluation terms as
indicative and the direction of movement as the reliable part.

Finally, uncertainty: after you press \textbf{Compute} with \textbf{Quick} or \textbf{Full}
selected (\S\ref{sec:use-uncertainty}), shaded bands appear on the derived fiscal and external
charts too. Each band is built consistently: every one of the model's alternative re-solves is
pushed through the same accounting identity, so the debt band widens exactly as fast as the
underlying budget and growth uncertainty says it should. Where you have pinned a quarter of a
debt or primary-balance target, the band closes onto the line at that quarter.

%% ================================================================
\section{Uncertainty bands}\label{sec:use-uncertainty}

A forecast line is a best guess, not a promise. This chapter shows you how to read the
range around that guess, and how to put the same kind of range around a scenario you
have built yourself. There are two kinds of bands on the charts: a grey fan that is
always there, and a coloured scenario band that you compute on demand.

\subsection{The grey fan: the model's own range}

\paragraph{What you do.} You read how sure the model is about its own baseline forecast,
before you have touched anything.

\paragraph{How.}
\begin{enumerate}
  \item Nothing. The grey fan is always on. Open any chart and look at the shaded
    region around the dotted \textbf{Baseline} line in the forecast area.
\end{enumerate}

\paragraph{What you find.} The fan covers roughly the middle two-thirds of the outcomes
the model considers plausible: it runs from the 16th to the 84th percentile of the
model's simulated futures, meaning about one outcome in six falls above the fan and one
in six below. Two things to check:
\begin{itemize}
  \item The fan \emph{widens} as you look further out. Next quarter is fairly
    well pinned down; five years out much less so. That is a feature, not a flaw.
  \item The fan belongs to the \emph{baseline}. It was computed when the model was
    estimated and does not react to your clicks. When you condition a chart, the grey
    fan stays where it is --- your scenario gets its own band, described next.
\end{itemize}
How the range is built --- from repeated simulations of the estimated model, including
both coefficient and shock uncertainty --- is in \S\ref{sec:bands}.

\subsection{Putting a band around your scenario}

\paragraph{What you do.} You have pinned a path --- say, inflation half a point higher
for four quarters (\S\ref{sec:use-scenarios}) --- and you want to know how uncertain
the rest of the system's response is.

\paragraph{How.}
\begin{enumerate}
  \item In the top bar, find the \textbf{Uncertainty} toggle. It has three settings:
    \textbf{None}, \textbf{Quick}, and \textbf{Full}.
  \item Pick \textbf{Quick} or \textbf{Full}. Quick uses 50 alternative versions of
    the model; Full uses 200. An ``alternative version'' here is one set of model
    coefficients that is also consistent with the historical data --- the estimation
    does not produce a single model but a whole family of plausible ones, and the band
    samples from that family (\S\ref{sec:uncertainty}).
  \item Press \textbf{Compute}. Every chart greys out behind a message ---
    \textbf{Computing scenario uncertainty (50 draws)...} or \textbf{(200 draws)...}
    --- and comes back with the band drawn.
\end{enumerate}
Expect a wait. Quick usually takes a few seconds. Full takes proportionally longer.
The very first Compute for a country is the slowest, because the browser first has to
download that country's file of sampled coefficients (several megabytes); after that
the file is cached and only the computation remains.

\paragraph{What you find.} A band tinted in your scenario's colour appears around the
scenario line on every chart --- not just the ones you conditioned. It answers the
question: \emph{given} the path I pinned, how much could everything else still vary?
By default this band keeps the full width of the model's own forecast range and is
re-centred on your scenario path, so it is directly comparable to the grey fan.

Three caveats:
\begin{itemize}
  \item The band is a \emph{snapshot}. If you move a pin, add a variable, or change
    the conditioning after computing, the displayed band no longer matches --- press
    \textbf{Compute} again to refresh it.
  \item After switching country or switching the active scenario, treat any band still
    on screen as stale --- press \textbf{Compute} again before reading it.
  \item Setting \textbf{Uncertainty} back to \textbf{None} removes the scenario band.
    The grey baseline fan never goes away.
\end{itemize}
The \textbf{CSV} and \textbf{Excel} exports include the scenario's band columns only
after you have pressed \textbf{Compute}; until then those cells are empty
(\S\ref{sec:use-data}).

One convenience: \textbf{Compute} also lights up when you have a long-run target set,
even with uncertainty on \textbf{None} --- pressing it then switches the setting to
\textbf{Quick} automatically, because the long-run tilt needs the sampled model
versions to work with (\S\ref{sec:plr}).

\subsection{Why the band pinches shut at your pins}

\paragraph{What you find.} On a chart you have conditioned, the scenario band collapses
to zero width at every quarter you pinned, then opens up again at the quarters in
between and beyond.

This is correct behaviour, not a rendering glitch. A pinned quarter is something you
have \emph{asserted}: in your scenario, inflation in that quarter \emph{is} the value
you set, by construction. There is no uncertainty about an assumption. The uncertainty
lives in everything the assumption does not fix --- the same variable at the quarters
you left free, and every other variable at every quarter. So read a pinched band as a
reminder of what you have imposed, and the open parts as what the model still has to
say. If a band stays wide where you expected it to pinch, check the conditioning list:
the quarter may be toggled off (\textbf{NC} --- short for nowcast, the model's estimate
of the current, not-yet-published quarter --- or an unlit quarter label,
\S\ref{sec:use-scenarios}).

\subsection{Long-run targets move the bands instantly}

\paragraph{What you do.} You adjust a value in the \textbf{Long-run targets} panel ---
say, potential growth a quarter-point higher --- after having already computed a
scenario band.

\paragraph{What you find.} The forecast line \emph{and} its bands glide to the new
path together, immediately, with no recomputation and no wait. A long-run target is a
deterministic shift of the whole forecast path (\S\ref{sec:use-longrun},
\S\ref{sec:driftsetter}): it moves where the forecast is headed, not how uncertain the
model is about getting there. So both the grey fan and any computed scenario band are
simply carried along rigidly --- their widths are preserved exactly. You can drag a
long-run slider back and forth and watch line and band move as one; you never need to
press \textbf{Compute} for this. Check it yourself: note the band width at some
horizon, move a target, and confirm the width is unchanged while the centre has
shifted.

\subsection{Experimental: the per-draw cross-country band}

\paragraph{What you do.} You switch to an alternative, slower way of building the
scenario band on countries that are part of the linked cross-country system
(\S\ref{sec:use-spillovers}).

\paragraph{How.}
\begin{enumerate}
  \item Find the small \textbf{Experimental} switch in the bottom-left corner of the
    screen.
  \item Turn it on.
  \item Press \textbf{Compute}.
\end{enumerate}

\paragraph{What you find.} With the switch on, \textbf{Compute} re-solves the whole
cross-country system separately for each of the 50 or 200 alternative model versions,
producing a true conditional cloud. That cloud pinches naturally at your pins without
any overlay, but it can collapse \emph{too} tightly when only a point or two is pinned.
It is also much slower than the default. With the switch off --- the default, and the
recommended setting --- the band is the model's own forecast range shifted onto the
scenario path, as described above: full width, fast. Flipping the switch clears any
band on screen, because a band built one way must not be read as if it were built the
other; press \textbf{Compute} again after toggling. The construction details are in
\S\ref{sec:uncertainty} and \S\ref{sec:gvar:solvemode}.

%% ================================================================
\section{The data behind the charts}\label{sec:use-data}

Every chart starts with a solid line: history. This chapter tells you exactly what
that line is made of --- which quarters are published data, which are filled in by
the model, where each series comes from, and how the whole panel is kept up to date.
The rule throughout is simple: \emph{data are data}. Anything the model filled in is
drawn in amber and labelled, never disguised as an observation.

\subsection{What vintage you are looking at}

\paragraph{What you do.}
You establish the ``as of'' date of everything on screen: the last quarter of
history, and the quarter where the forecast begins.

\paragraph{How.}
\begin{enumerate}
  \item Look at any chart. The solid history line ends at the \emph{panel
    origin} --- the last quarter of history, shared by every economy; the
    forecast lines continue from there.
  \item Hover near the boundary --- the hover box shows the calendar quarter of
    each point.
  \item For the exact per-series dates, open \textbf{Data \& coverage}
    in the top bar (next subsection but one).
\end{enumerate}

\paragraph{What you find.}
At the time of writing, the panel origin is 2026~Q1: that is the last quarter of
history for every economy, and the first forecast quarter --- labelled \textbf{NC}
(short for nowcast, the model's estimate of the current, not-yet-published
quarter) in the conditioning list and in the exports --- is 2026~Q2. All economies
share this single origin. That is deliberate: the linked cross-country system
(labelled GVAR in the app, short for global vector autoregression --- see
\S\ref{sec:gvar}) couples economies row by row, so every country's history must end
on the same line. One exception: Israel's statistics arrive with a long lag,
so its charts run on Israel's own calendar, about a year behind the rest of the
panel. Details of the dating convention are in \S\ref{sec:vintage}.

\subsection{Observed history versus model-filled history}

\paragraph{What you do.}
You check whether the most recent quarters of a series are published data or values
the model filled in because the statistical office has not published them yet.

\paragraph{How.}
\begin{enumerate}
  \item Look at the end of the history line on any chart. If the last few quarters
    are drawn as an \emph{amber dashed} segment with small open circles, those
    quarters are model-filled, not published.
  \item Hover over one of the open circles. The hover box reads
    \textbf{Model-implied nowcast (imputed)}.
  \item Compare with the solid line just before it: the dashed segment starts at
    the last genuinely observed point, so you can see exactly where data end and
    filling begins.
\end{enumerate}

\paragraph{What you find.}
The amber dashed tail marks quarters that have not been published for that series.
The model fills them using everything already observed elsewhere --- the same
economy's other series and, through the trade and financial links, every other
economy's published data. (A value estimated this way for the most recent past is
called a \emph{nowcast}: a model estimate of a quarter that has already happened
but has not been reported yet.) A series with no amber tail is fully observed
through the panel origin. At this vintage only the United States is genuinely
observed at the origin; every other economy's latest quarter is model-filled, so
its series carry a short amber tail. The filling method is described in
\S\ref{sec:vintage}; how the linked system shares information across borders is in
\S\ref{sec:gvar}.

\subsection{Check where every number comes from}

\paragraph{What you do.}
For the economy you are viewing, you list every series in the model: its source,
the span of quarters it covers, its last observed quarter, and any data caveats.

\paragraph{How.}
\begin{enumerate}
  \item In the top bar, click \textbf{Data \& coverage}.
  \item A dialog opens, titled \textbf{Data \& coverage} followed by the country
    code. The header line states the last historical quarter, the last quarter at
    which \emph{all} series are observed together, and the variable count.
  \item Scan the table. The columns are \textbf{Variable}, \textbf{Source},
    \textbf{Coverage}, \textbf{Last obs}, and \textbf{Note}.
  \item Click anywhere outside the dialog, or the \textbf{\texttimes} button, to
    close it.
\end{enumerate}

\paragraph{What you find.}
A last-observed quarter drawn in amber means the series ends before the panel
origin --- exactly the series that carry an amber dashed tail on their charts. The
\textbf{Note} column carries plain-language flags: quarters around the pandemic
treated as missing during estimation (see \S\ref{sec:covid}), an interior gap in
the raw series, or a source still under review. Sources are the genuine national,
FRED, Eurostat, BIS, ECB, and IMF providers; the full source list is in
\S\ref{sec:datasources} and the cross-economy coverage matrix in
\S\ref{sec:coverage-matrix}. The view is read-only: opening it never re-pulls data
or changes anything on the charts.

\subsection{See how the latest data release moved the world}

\paragraph{What you do.}
After a data update, you ask: how did the new numbers change each economy's
estimate of the current quarter --- and which economies moved only because
\emph{someone else's} data came in?

\paragraph{How.}
\begin{enumerate}
  \item In the top bar, click \textbf{Monitor}. The \textbf{Release-impact
    monitor} opens in the same tab, with a \textbf{$\leftarrow$ back to the tool}
    link at the top.
  \item Read the intro line: it names the update quarter and lists the economies
    with their own new releases this round.
  \item Scan the headline table. Columns: \textbf{Economy}, \textbf{GDP nowcast
    revision (pp, q/q ann)}, \textbf{Inflation revision (pp)}, \textbf{Policy rate
    (pp)}, and \textbf{Channel}. Use the two buttons next to \textbf{sort by} to
    rank economies by the absolute size of the GDP or inflation revision.
  \item Click \textbf{detail} on any row to expand a per-variable table for that
    economy; click \textbf{hide} to collapse it.
\end{enumerate}

\paragraph{What you find.}
Each number is a \emph{revision}: the economy's estimate of the update quarter
after the new data, minus what the previous vintage had already predicted for that
same quarter. The \textbf{Channel} badge is the key column. \textbf{observed}
(green) means the economy's own new data drove the move --- its genuine surprise
against what was expected. \textbf{cross-block} (blue) means the economy published
nothing itself: its revision is pure cross-border transmission of other economies'
releases through the trade and financial links. Watching, say, the euro area or
Canada shift on a United States release is the linked system at work on real data
--- the same mechanism you steer by hand in \S\ref{sec:use-spillovers}. In the
per-economy detail, each variable shows its before and after values, the revision,
and how that revision carries into the first and the final forecast quarter; an
\textbf{obs} or \textbf{nowcast} badge says whether that particular cell was
published or model-filled. If a source restated its own history, the intro also
lists the \emph{accepted source revisions} for that update.

\subsection{The update cycle: quarterly shifts, annual re-estimation}

\paragraph{What you do.}
You understand what changes --- and, just as important, what does \emph{not}
change --- each time the panel is updated.

\paragraph{How.}
Nothing to click: the cycle is an operating rule, and every update leaves visible
traces you can inspect with the two views above.
\begin{enumerate}
  \item \emph{Within the year}, the panel gets quarterly \emph{data shifts}. Newly
    published quarters are pulled in for the economies with wired sources; every
    other economy's new quarter is filled by the linked system from everything
    just observed, and flagged as model-implied (the amber tails). The estimated
    model itself is untouched --- frozen exactly as estimated.
  \item \emph{Once a year}, after the previous calendar year is fully published
    for every economy, the whole system is re-estimated on that complete year of
    data. Only then do the model's estimated relationships change.
  \item \emph{Revisions are accepted and logged.} When a statistical office
    restates its history, the revised figures replace the old ones as the current
    best knowledge, and the change is recorded --- the Monitor page lists the
    accepted revisions of each update.
\end{enumerate}

\paragraph{What you find.}
After a quarterly shift, the history line is one quarter longer, the forecast
starts one quarter later, and the amber tails move with the new origin --- but the
model's behaviour, and therefore the way your scenarios respond, is unchanged. Any
movement in the forecast comes from new data, not from a silently different model.
After the annual re-estimation, the model itself is new, and the manual's technical
chapters (\S\ref{sec:vintage}, \S\ref{sec:repro}) describe how that vintage is
documented. If a chart surprises you after an update, the reading order is: hover
the tail (observed or model-filled?), open \textbf{Data \& coverage}
(did the series' last observation move?), then open \textbf{Monitor} (was it your
economy's own release, or transmission from abroad?).

\clearpage
\part{How the machinery works}\label{part:machinery}

\noindent This part documents the methods behind the screen --- the estimation, the filtering, the
cross-country system, the accounting --- with the mathematics and the references. You do not need it
to use the tool. It is here so that every number on the screen can be traced to a method, every
method to code, and every series to a source.



%% ================================================================
\section{System Overview}\label{sec:intro}

\begin{figure}[!ht]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  font=\small,
  >=Stealth,
  node distance=9mm,
  stage/.style={
    rounded corners=3pt, draw, thick, align=center,
    minimum height=15mm, minimum width=24mm, inner sep=4pt,
    fill=blue!4
  },
  data/.style={stage, fill=gray!8},
  contract/.style={stage, fill=orange!8},
  client/.style={stage, fill=green!6},
  flow/.style={->, thick, shorten >=1pt, shorten <=1pt},
  bandlbl/.style={font=\footnotesize\itshape}
]

% ---- stages, left to right ----
\node[data] (src) {Data sources\\\footnotesize FRED $\cdot$ Eurostat\\\footnotesize BIS $\cdot$ ECB\\\footnotesize 2025Q4 vintage};
\node[stage, right=of src] (est) {GVAR--EM\\estimation\\\footnotesize \texttt{cgl\_bvarV5}\\\footnotesize E/M loop};
\node[contract, right=of est] (json) {8-file JSON\\contract\\\footnotesize per bloc $+$\\\footnotesize \texttt{coupling\_default}};
\node[client, right=of json] (solve) {Closed-form\\GVAR solve\\\footnotesize affine kernels\\\footnotesize $(I{-}M)^{-1}d$};
\node[client, right=of solve] (ui) {Interactive\\UI\\\footnotesize conditioning $\cdot$\\\footnotesize counterfactual $\cdot$ fiscal};

% ---- flow arrows with labels ----
\draw[flow] (src) -- node[above, font=\footnotesize] {raw} (est);
\draw[flow] (est) -- node[above, font=\footnotesize] {export} (json);
\draw[flow] (json) -- node[above, font=\footnotesize] {fetch} (solve);
\draw[flow] (solve) -- node[above, font=\footnotesize] {paths} (ui);

% ---- under-arrows: methodological annotations ----
\node[below=2mm of est, bandlbl, text width=26mm, align=center] (estsub)
  {trade-weighted RoW stars; COVID-as-missing DK smoother};
\node[below=2mm of solve, bandlbl, text width=26mm, align=center] (solvesub)
  {Gauss--Seidel / Smith doubling; commons pinned 1:1};

% ---- background bands: offline (MATLAB) vs client (browser) ----
\begin{scope}[on background layer]
  \node[fit=(src)(est)(estsub), draw=blue!40, dashed, rounded corners=5pt,
        fill=blue!3, inner sep=7pt,
        label={[blue!55!black,font=\footnotesize\bfseries]above:Offline \quad (MATLAB)}] (offband) {};
  \node[fit=(solve)(ui)(solvesub), draw=green!45!black, dashed, rounded corners=5pt,
        fill=green!4, inner sep=7pt,
        label={[green!40!black,font=\footnotesize\bfseries]above:Client \quad (browser)}] (clband) {};
\end{scope}

\end{tikzpicture}%
}
\caption[End-to-end system architecture]{End-to-end system architecture of the EM-Bayesian Global VAR platform.
Harmonized macro-financial data (FRED, Eurostat, BIS, ECB; common 2025Q4 \emph{estimation} vintage, with
the observed panel subsequently refreshed to 2026Q1 with no re-estimation, \S\ref{sec:vintage}) feed the
\emph{offline} MATLAB GVAR--EM estimator: per-bloc Bayesian VARs (\texttt{cgl\_bvarV5}) are re-fit in an
EM loop that, at each sweep, rebuilds the trade-weighted rest-of-world ``star'' variables
(ROWDEM/ROWINF/ROWFIN) from partners' Durbin--Koopman-completed panels and re-estimates every bloc with
the 2020Q2--Q4 \emph{macro} columns masked (the foreign-rate star ROWFIN and all domestic financials kept
observed; COVID-as-missing), iterating to $\max|\Delta\text{star}|<0.03$ (cf.\ \S\ref{sec:gvar}). Each
converged bloc is serialized to the eight-file JSON contract (\texttt{spec}, \texttt{companion\_mean},
\texttt{companion\_draws}, \texttt{baseline}, \texttt{baseline\_levels}, \texttt{historical},
\texttt{historical\_levels}, \texttt{transformations}; plus \texttt{fiscal\_meta} and the precomputed
\texttt{coupling\_default.json.gz} coupling artifact). In the \emph{client} (browser), the cross-country
system is solved in closed form: the scenario delta obeys the affine fixed point $x = Mx + d$, evaluated by
Gauss--Seidel sweeps or directly via $(I-M)^{-1}d$ (Smith doubling), with global commons (US WTI oil,
US~10Y, US~BAA, US~equity) pinned 1:1 onto every RoW bloc. The interactive UI exposes conditioning,
counterfactuals, and the stock-flow fiscal block (\S\ref{sec:fiscal}).}
\label{fig:architecture}
\end{figure}
%% ================================================================

Conditional forecasting with Bayesian vector autoregressions (BVARs)
has become a standard tool in central bank forecasting and policy
analysis.  The seminal contributions of
\citet{DoanLittermanSims1984} and \citet{WaggonerZha1999}
established the methodological foundations, while
\citet{BanburaGiannoneLenza2015} extended these techniques to large
cross-sections using state-space methods.  The Monetary-Financial
Model described in this document builds on this literature to provide an
interactive, browser-based platform that makes conditional forecasting
and policy counterfactual analysis accessible without specialized
software.

The tool implements a three-layer analytical framework:
\begin{enumerate}[label=(\roman*)]
  \item \textbf{Baseline forecast:} An unconditional forecast from a
    large BVAR estimated on quarterly macroeconomic and financial data,
    following the hierarchical prior framework of \citet{Giannone2015}.
  \item \textbf{Conditional scenario:} The user conditions any subset
    of variables on desired paths; a Durbin--Koopman smoother
    \citep{DurbinKoopman2002, DurbinKoopman2012} propagates these
    constraints to all remaining variables, respecting the full
    covariance structure of the VAR.
  \item \textbf{Policy counterfactual:} An alternative monetary or
    fiscal policy path is overlaid on the scenario using impulse
    response functions from a DSGE model drawn from the Macroeconomic
    Model Data Base \citep[MMB;][]{WielandCwikMuellerSchmidtWolters2012},
    and the resulting macroeconomic responses are re-conditioned through
    the BVAR to ensure cross-variable consistency.
\end{enumerate}

The tool is designed for economists at central banks and international
institutions who need to construct and communicate conditional
projections and policy scenarios.  It runs entirely in the browser,
requiring no server-side computation, and can be deployed as a static
website on any hosting platform.

Part~II is organized as follows.  Section~\ref{sec:bvar}
describes the BVAR estimation methodology, and
Section~\ref{sec:statespace} derives the companion-form state-space
representation.  Section~\ref{sec:kalman} presents the Kalman filter
and Durbin--Koopman smoother used for conditional forecasting.
Section~\ref{sec:counterfactual} details the policy counterfactual
framework, and Section~\ref{sec:gvar} the cross-country system.
Section~\ref{sec:fiscal} covers the fiscal block and
Section~\ref{sec:longrun} the long-run targets.
Section~\ref{sec:variables} documents the data, coverage, and vintage
policy.  Section~\ref{sec:technical} discusses technical
implementation details, Section~\ref{sec:repro} reproducibility, and
Section~\ref{sec:discussion} concludes with limitations and directions
for future development.  The guide to the user interface is Part~I
(Sections~\ref{sec:use-quickstart}--\ref{sec:use-data}).

\subsection{Notation}\label{sec:notation}

Table~\ref{tab:notation} collects the symbols used throughout the manual,
grouped by the layer in which they appear (BVAR estimation, the
companion-form state space and smoother, the GVAR coupling, the fiscal
recursion, and the long-run drift setter). A plain-language \emph{Glossary} of
the named concepts---BVAR, GVAR, the trade-weighted stars, COVID-as-missing, the
stock-flow adjustment, the EM loop, the endogenous dominant unit, the long-run
drift setter, and the evaluation statistics (CRPS, Giacomini--White, $\dots$)---is
provided in Appendix~\ref{app:glossary}.

\begin{small}
\begin{longtable}{@{}p{0.16\textwidth}p{0.78\textwidth}@{}}
\caption{Notation used across the BVAR, GVAR, fiscal, and long-run layers.}
\label{tab:notation}\\
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
\endfirsthead
\multicolumn{2}{@{}l}{\footnotesize\itshape Table~\ref{tab:notation} continued from previous page}\\
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
\endhead
\midrule
\multicolumn{2}{r@{}}{\footnotesize\itshape continued on next page}\\
\endfoot
\bottomrule
\endlastfoot
\multicolumn{2}{@{}l}{\textit{BVAR estimation (Sec.~\ref{sec:bvar})}}\\
$y_t$ & $n\times 1$ vector of endogenous variables of a bloc at quarter $t$ (in estimation space). \\
$n$ & number of variables in a bloc ($n=41$ for the endogenous-US bloc). \\
$p$ & VAR lag order ($p=3$ throughout). \\
$B_\ell$ & $n\times n$ reduced-form autoregressive coefficient matrix on lag $\ell$. \\
$\varepsilon_t$ & reduced-form innovation, $\varepsilon_t\sim\mathcal{N}(0,\Sigma)$. \\
$\Sigma$ & $n\times n$ innovation covariance; posterior-mean $\hat\Sigma$. \\
$\beta$, $\hat\beta$ & stacked VAR coefficients; posterior mean. \\
$\lambda$ & overall Minnesota/GLP shrinkage (tightness) hyperparameter. \\
$\mu$ & sum-of-coefficients prior hyperparameter \citep{Giannone2015}. \\
$\psi$ & residual-variance scale of the prior (per variable). \\
$\delta_i$ & prior mean on variable $i$'s own first lag: $\delta_i=1$ (random walk, \texttt{RW}) or $\delta_i=0$ (stationary white noise, \texttt{WN}). \\
$\texttt{pos}$ & index set of the \texttt{WN} variables; sets \(\texttt{diagb}(\texttt{pos})=0\) (Sec.~\ref{sec:ownlag}). \\
$D$ & number of retained posterior draws $\{(\hat\beta^{(d)},\hat\Sigma^{(d)})\}$. \\
\midrule
\multicolumn{2}{@{}l}{\textit{State space \& smoother (Sec.~\ref{sec:statespace}--\ref{sec:kalman})}}\\
$\alpha_t$ & companion-form state vector (stacked current and lagged $y$). \\
$T,Z,Q,H$ & transition, observation, state-noise, and measurement-noise matrices. \\
$Z_t^{(o)}$ & rows of $Z$ corresponding to the \emph{observed} variables at $t$ (partial observation). \\
$\alpha_{t|t-1},P_{t|t-1}$ & one-step predicted state mean and covariance. \\
$v_t,F_t,K_t$ & innovation, innovation variance, Kalman gain. \\
$r_t,L_t$ & Durbin--Koopman backward recursion vector and transition. \\
$\alpha_{t|H}$ & smoothed (full-interval) state. \\
$\mathcal{W}$ & COVID-as-missing window (the fixed three quarters 2020Q2--Q4). \\
\midrule
\multicolumn{2}{@{}l}{\textit{GVAR coupling (Sec.~\ref{sec:gvar})}}\\
$c,j$ & bloc (economy) indices; $c$ receiver, $j$ partner. \\
$w_{cj}$ & trade weight of partner $j$ in bloc $c$'s stars, $\sum_j w_{cj}=1$. \\
$\texttt{ROWDEM},\texttt{ROWINF},\texttt{ROWFIN}$ & trade-weighted foreign demand, inflation, and financial ``star'' variables. \\
$s_{c,v,t}$ & scenario pin-delta of bloc $c$'s star $v$ at horizon $t$. \\
$g\Delta_{p,t}$ & deviation of US-determined global column $p$ (oil, US10Y, USBAA, USeq). \\
$x$ & stacked deviation state of the coupling fixed point. \\
$M$ & solve-time coupling operator; $x=Mx+d$. \\
$d$ & exogenous forcing (own-scenario pins) of the fixed point. \\
$\rho(M)$ & spectral radius of $M$ (multiplier strength; $<1$ $\Rightarrow$ contractive). \\
\midrule
\multicolumn{2}{@{}l}{\textit{Fiscal recursion (Sec.~\ref{sec:fiscal})}}\\
$d_t$ & gross public debt as a percent of GDP. \\
$\mathit{rev}_t,\mathit{pexp}_t$ & revenue and primary expenditure (\% of GDP); \texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}. \\
$i^{\text{eff}}_t$ & effective interest rate (\texttt{EFFI}, \% p.a.). \\
$\mathit{sfa}_t$ & stock-flow adjustment (\texttt{SFA}, \% of GDP). \\
$g^{n}_t$ & nominal GDP growth. \\
$\mathit{pb}_t$ & primary balance $=\mathit{rev}_t-\mathit{pexp}_t$. \\
\midrule
\multicolumn{2}{@{}l}{\textit{Long-run targets \& evaluation (Sec.~\ref{sec:longrun},~\ref{sec:empirical})}}\\
$\psi^\star_j,\psi^{\,0}_j$ & user long-run target and current terminal display forecast of variable $j$. \\
$c,\,\delta c_j$ & companion drift (constant row); shift of variable $j$'s own equation. \\
$S_h$ & partial companion-power sum $\sum_{k<h}T^{k}$; $S_h[:,j]\,\delta c_j$ is the response. \\
$\mathrm{sens}_j$ & display-unit sensitivity of $j$'s terminal forecast to a unit $\delta c_j$. \\
$h$ & forecast horizon (quarters); $h\in\{1,2,4,8\}$ in the horse-race. \\
$t_0$ & forecast origin in the recursive out-of-sample scheme. \\
$d_t$ (loss) & loss differential between two models at $t$ (overloads $d_t$; context disambiguates). \\
$\mathrm{CRPS}$ & continuous ranked probability score (primary density metric). \\
\end{longtable}
\end{small}

%% ================================================================
\section{BVAR Estimation}\label{sec:bvar}
%% ================================================================

\subsection{Reduced-Form VAR}

Consider an $n$-variable VAR($p$) in reduced form:
\begin{equation}\label{eq:var}
  y_t = c + \sum_{\ell=1}^{p} B_\ell\, y_{t-\ell} + u_t,
  \qquad u_t \sim \mathcal{N}(0, \Sigma),
\end{equation}
where $y_t \in \R^n$ is the vector of observables, $c \in \R^n$ is a
vector of intercepts, $B_1, \ldots, B_p \in \R^{n \times n}$ are the
autoregressive coefficient matrices, and $\Sigma \in \R^{n \times n}$
is the positive-definite innovation covariance matrix.  In the US
specification, $n = 41$ and $p = 3$, yielding a coefficient matrix
$\hat\beta \in \R^{124 \times 41}$ (with row~0 containing the
intercept).  The $41$ US variables include the four US-determined
\emph{global commons} (\texttt{GLB\_OIL}, \texttt{GLB\_USLR},
\texttt{GLB\_USBAA}, \texttt{GLB\_USEQ}) that the GVAR layer of
Section~\ref{sec:gvar} carries into every other bloc, the four-variable fiscal
block (Section~\ref{sec:fiscal}), and the three trade-weighted \texttt{ROW*\_US}
star variables through which the US, now an endogenous GVAR bloc, receives
Rest-of-World feedback.

\subsection{Data Transformations}

Variables enter the VAR in one of two forms:
\begin{itemize}
  \item \textbf{Log-transformed} ($\texttt{log}$): the variable is
    modeled in log levels.  Growth rates displayed to the user are
    quarter-over-quarter annualized:
    \begin{equation}\label{eq:growth}
      g_t^{\text{q/q ann.}} = 400 \times
      \bigl(\ln Y_t - \ln Y_{t-1}\bigr).
    \end{equation}
    Year-over-year growth rates are computed as:
    \begin{equation}\label{eq:yoy}
      g_t^{\text{y/y}} = 100 \times
      \bigl(\ln Y_t - \ln Y_{t-4}\bigr).
    \end{equation}
  \item \textbf{Linear} ($\texttt{lin}$): the variable enters in
    levels (e.g., interest rates in percent, unemployment rate).
    No growth-rate conversion is applied.
\end{itemize}

\subsection{Reporting Units}\label{sec:units}

The display unit is chosen per variable for interpretability, independently
of the estimation transformation:
\begin{itemize}
  \item \textbf{National-accounts / activity flows} (GDP, consumption,
    investment, trade volumes) are shown as growth (q/q annualized or y/y).
  \item \textbf{Prices} (CPI/HICP/deflators) are shown as inflation.
  \item \textbf{Rates and ratios} (policy and market rates, unemployment,
    fiscal ratios) are shown as levels in percent / percentage points.
    Unemployment-rate uncertainty bands are floored at~0 (a rate cannot be
    negative); policy and market rates are \emph{not} floored, because
    negative nominal rates do occur.
  \item \textbf{Index / FX / equity / commodity series} (the
    trade-weighted dollar \texttt{FXTWM}, US equity \texttt{GLB\_USEQ},
    house prices \texttt{HP}, oil \texttt{PZTEXP}/\texttt{GLB\_OIL}, the
    non-fuel commodity index
    \texttt{GSNE}, and the other blocs' \texttt{NEER\_EA},
    \texttt{NEER\_UK}, \texttt{NEER\_CA}, \texttt{REER\_CN},
    \texttt{EQ\_CN}) are reported as the \emph{index level}
    (e.g.\ 2010 $=100$) rather than as q/q growth: a trade-weighted
    exchange rate or equity index q/q-annualized is not an informative
    number, whereas its level is. These series remain \texttt{log} for
    estimation and are conditioned in the stored $100\ln(\text{index})$
    space; only the display is exponentiated back to the level,
    $\exp(\text{stored}/100)$, with a level-space uncertainty fan.
\end{itemize}

\subsection{Hierarchical Minnesota Prior}\label{sec:prior}

The model is estimated following \citet{Giannone2015}, who cast the
Minnesota prior \citep{Litterman1986, DoanLittermanSims1984} in a
hierarchical framework with data-driven hyperparameter selection.
The prior specification includes:
\begin{enumerate}[label=(\alph*)]
  \item The \textbf{Minnesota shrinkage} prior on $B_\ell$, centered
    on the random-walk or white-noise prior for each variable
    (depending on the variable's stationarity properties).  The
    tightness parameter $\lambda$ controls the overall degree of
    shrinkage toward the prior mean.
  \item The \textbf{sum-of-coefficients} prior
    \citep{DoanLittermanSims1984}, which shrinks toward the belief
    that a unit increase in every variable's level produces a unit
    increase in its forecast, imposing a form of cointegration.
  \item The \textbf{single-unit-root} prior, which constrains the
    system to have at most one common stochastic trend.
\end{enumerate}

The hyperparameters governing the tightness of each prior component
are treated as additional parameters and selected by maximizing the
marginal likelihood, as advocated by \citet{Giannone2015}.

Posterior draws are obtained via Markov chain Monte Carlo (MCMC).
The estimator runs a long chain with burn-in, retaining the posterior
mean $\hat\beta$ and $\hat\Sigma$ for the deterministic conditional
forecasting engine. For the browser the chain is \emph{thinned} to
$D=500$ retained draws
$\bigl\{(\hat\beta^{(d)}, \hat\Sigma^{(d)})\bigr\}_{d=1}^{D}$, the count
shipped in every bloc's \texttt{companion\_draws.json}, used for
uncertainty quantification via the simulation smoother
(Section~\ref{sec:uncertainty}). The thinned export keeps the per-bloc
draw artifact small enough to load on demand (the US file is
$\approx 34$\,MB at $D=500$, $n=41$, $p=3$).

\subsection{Per-variable own-lag prior mean: random walk vs.\ stationary}\label{sec:ownlag}

The Minnesota/GLP prior is centered, for each equation, on a univariate
model in which the variable's own first lag carries a prior mean of
$\delta_i$ and every other coefficient a prior mean of zero
\citep{Litterman1986,DoanLittermanSims1984,Giannone2015}. The
\emph{default} choice $\delta_i=1$ encodes a random-walk (\texttt{RW})
prior belief---``the best forecast of the level is the current level''---which
is appropriate for variables that are (near-)integrated in the
estimation space (log real activity, log price levels, nominal yields).
For a variable that is genuinely \emph{stationary}---a mean-reverting
ratio or rate that fluctuates around a constant level---the random-walk
center is the wrong null: it shrinks the dynamics toward a unit root and
lets the variable \emph{drift} at long horizons rather than return to its
historical mean. For such variables the tool sets the own-lag prior mean
to $\delta_i=0$, a stationary white-noise (\texttt{WN}) prior whose null
model is ``the best forecast is the unconditional mean (the equation
constant), not the last observation.''

\paragraph{The mechanism (\texttt{pos}/\texttt{stationary}).} The choice
is implemented exactly once, at the point where the prior mean of the
coefficient matrix is built. In
\texttt{BVAR/MFBVAR/GLPreplicationWeb/bvarGLPmf.m} the own-first-lag
prior block is the diagonal matrix \(\texttt{diag}(\texttt{diagb})\) with
\(\texttt{diagb}=\mathbf{1}_n\) by default; the line
\[
  \texttt{diagb}(\texttt{pos}) = 0
\]
zeroes the own-lag prior mean for every variable index in the vector
\texttt{pos}, so those equations are shrunk toward white noise instead of
a random walk. The index set is threaded into the sampler as the third
positional argument \texttt{stationary} of
\texttt{BVAR/MFBVAR/cgl\_bvarV5.m} (internally \(\texttt{pos} =
\texttt{stationary}\)), which forwards it as the \texttt{'pos'} option to
\texttt{bvarGLPmf}. The estimators build the set directly from the
per-variable \texttt{prior} tag in each bloc's specification,
\[
  \texttt{pos} \;=\; \texttt{find}(\texttt{prior}==\text{`}\texttt{WN}\text{'}),
\]
so a variable opts in to the stationary prior simply by carrying
\texttt{prior:"WN"} in its spec (see
\texttt{pipeline/export\_bvar\_gvar24\_loop.m} and
\texttt{pipeline/export\_bvar\_euro\_fsap.m}). For the $44$ non-fiscal
blocs the set is empty and the call is byte-identical to the historical
all-\texttt{RW} behaviour.

\paragraph{Prior, not constraint.} Crucially $\delta_i=0$ sets only the
prior \emph{mean}; it does not \emph{impose} stationarity. The posterior
own-lag coefficient is the usual GLP balance of prior and likelihood,
governed by the estimated tightness $\lambda$ (itself selected by the
marginal-likelihood maximization, Section~\ref{sec:prior}). A genuinely
persistent series whose data favour a near-unit root will still produce a
large posterior own-lag coefficient despite the white-noise center; the
\texttt{WN} prior simply removes the \emph{built-in} drift that the
random-walk center would otherwise inject at the long end. This is the
mechanism that makes the fiscal GDP-ratios mean-revert
(Section~\ref{sec:fiscal_drivers}).


%% ================================================================
\section{Companion-Form State Space}\label{sec:statespace}
%% ================================================================

To apply the Kalman filter, the VAR($p$) in~\eqref{eq:var} is cast in
companion form as a first-order state-space model
\citep[see, e.g.,][ch.~3]{DurbinKoopman2012}.

\subsection{State Vector}

Define the $np$-dimensional state vector:
\begin{equation}\label{eq:state}
  \alpha_t = \begin{pmatrix} y_t \\ y_{t-1} \\ \vdots \\ y_{t-p+1}
  \end{pmatrix} \in \R^{np}.
\end{equation}

\subsection{Transition Equation}

The state evolves according to:
\begin{equation}\label{eq:transition}
  \alpha_t = T\, \alpha_{t-1} + d + R\, \eta_t,
  \qquad \eta_t \sim \mathcal{N}(0, \Sigma),
\end{equation}
where the $np \times np$ transition matrix $T$, the $np$-dimensional
intercept vector $d$, and the $np \times n$ selection matrix $R$ are:
\begin{equation}\label{eq:companion}
  T = \begin{pmatrix}
    B_1' & B_2' & \cdots & B_{p-1}' & B_p' \\
    I_n  & 0    & \cdots & 0        & 0    \\
    0    & I_n  & \cdots & 0        & 0    \\
    \vdots & & \ddots & & \vdots \\
    0    & 0    & \cdots & I_n      & 0
  \end{pmatrix}, \quad
  d = \begin{pmatrix} c \\ 0 \\ \vdots \\ 0 \end{pmatrix}, \quad
  R = \begin{pmatrix} I_n \\ 0 \\ \vdots \\ 0 \end{pmatrix}.
\end{equation}

\begin{remark}
The $B_\ell'$ blocks in $T$ are transposed relative to \eqref{eq:var}
because the coefficient matrix $\hat\beta$ is stored as
$(1 + np) \times n$, with row~0 containing the intercept $c$ and
rows $1, \ldots, np$ containing the stacked lag coefficients.
Specifically, $T(i,j) = \hat\beta(j+1, i)$ for $0 \le i < n$ and
$0 \le j < np$.
\end{remark}

\subsection{Observation Equation}

The observation equation extracts the contemporaneous variables:
\begin{equation}\label{eq:obs}
  y_t = Z\, \alpha_t + \varepsilon_t,
  \qquad \varepsilon_t \sim \mathcal{N}(0, H),
\end{equation}
where $Z = \bigl(I_n \mid 0_{n \times n(p-1)}\bigr)$ and
$H = \sigma^2_\varepsilon I_n$ with $\sigma^2_\varepsilon = 10^{-12}$
(a negligible measurement error included for numerical stability of the
Kalman filter recursions).

\subsection{State-Noise Covariance}

The $np \times np$ state-noise covariance matrix is:
\begin{equation}\label{eq:Q}
  Q = R\, \Sigma\, R' = \begin{pmatrix}
    \Sigma & 0 & \cdots & 0 \\
    0      & 0 & \cdots & 0 \\
    \vdots & & \ddots & \\
    0      & 0 & \cdots & 0
  \end{pmatrix}.
\end{equation}


%% ================================================================
\section{Kalman Filter and Smoother}\label{sec:kalman}
%% ================================================================

\subsection{Conditioning via Partial Observations}\label{sec:partial}

The key insight underlying conditional forecasting in a state-space
framework, following \citet{BanburaGiannoneLenza2015}, is that
conditioning on variable~$i$ at horizon~$h$ is equivalent to observing
$y_{T+h,i}$ in the Kalman filter.  For each forecast period
$t = T+1, \ldots, T+H$, the observation vector is partitioned into:
\begin{itemize}
  \item \textbf{Conditioned variables:} $y_t^{(o)}$, with known
    target values specified by the user.
  \item \textbf{Free variables:} $y_t^{(m)}$, treated as missing
    observations (coded as \texttt{NaN}).
\end{itemize}
The Kalman filter processes only the observed subset at each time
step, adapting $Z_t$, $H_t$, and the innovation $v_t$ accordingly.

\subsection{Forward Pass: Kalman Filter}\label{sec:kf}

\paragraph{Algorithm: Kalman Filter with Partial Observations.}
\label{alg:kf}
\textbf{Input:} $T, Z, Q, H, d$; initial state $\alpha_0$,
covariance $P_0$; partial observations $\{y_t^{(o)}\}_{t=1}^{H}$.

\noindent For $t = 1, \ldots, H$:
\begin{align}
  \alpha_{t|t-1} &= T\, \alpha_{t-1|t-1} + d
    & &\text{(state prediction)} \label{eq:kf_pred_a} \\
  P_{t|t-1} &= T\, P_{t-1|t-1}\, T' + Q
    & &\text{(covariance prediction)} \label{eq:kf_pred_P}
\end{align}
If observations exist at time $t$, let $Z_t^{(o)}$ be the rows of $Z$
for observed variables, then:
\begin{align}
  v_t &= y_t^{(o)} - Z_t^{(o)}\, \alpha_{t|t-1}
    & &\text{(innovation)} \label{eq:kf_innov} \\
  F_t &= Z_t^{(o)}\, P_{t|t-1}\, (Z_t^{(o)})' + H_t^{(o)}
    & &\text{(innovation variance)} \label{eq:kf_F} \\
  K_t &= P_{t|t-1}\, (Z_t^{(o)})'\, F_t^{-1}
    & &\text{(Kalman gain)} \label{eq:kf_K} \\
  \alpha_{t|t} &= \alpha_{t|t-1} + K_t\, v_t
    & &\text{(state update)} \label{eq:kf_upd_a} \\
  P_{t|t} &= P_{t|t-1} - K_t\, Z_t^{(o)}\, P_{t|t-1}
    & &\text{(covariance update)} \label{eq:kf_upd_P}
\end{align}
If no observations exist at time $t$: $\alpha_{t|t} = \alpha_{t|t-1}$
and $P_{t|t} = P_{t|t-1}$.

The matrix inversion $F_t^{-1}$ is computed via LU decomposition with
partial pivoting; singularity is flagged when the pivot falls below
$10^{-15}$.

\subsection{Backward Pass: Durbin--Koopman Smoother}\label{sec:dk}

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[
    >=Stealth,
    font=\small,
    state/.style={circle,draw,minimum size=8mm,inner sep=0pt},
    obsfill/.style={rectangle,draw,minimum size=5mm,inner sep=0pt,fill=blue!18},
    obshollow/.style={rectangle,draw,minimum size=5mm,inner sep=0pt,fill=white},
    filt/.style={->,draw=black,thick},
    smth/.style={->,draw=red!70!black,thick,dashed},
    node distance=14mm,
]
% ---- state timeline ----
\node[state] (a1) {$\alpha_{t-1}$};
\node[state,right=of a1] (a2) {$\alpha_{t}$};
\node[state,right=of a2] (a3) {$\alpha_{t+1}$};
\node[state,right=of a3] (a4) {$\alpha_{t+2}$};

% forward Kalman filter (transition T) above
\draw[filt] (a1) to[bend left=22] node[above,font=\scriptsize]{$T$} (a2);
\draw[filt] (a2) to[bend left=22] node[above,font=\scriptsize]{$T$} (a3);
\draw[filt] (a3) to[bend left=22] node[above,font=\scriptsize]{$T$} (a4);

% backward DK smoother below
\draw[smth] (a4) to[bend left=22] node[below,font=\scriptsize]{$L_{t}'$} (a3);
\draw[smth] (a3) to[bend left=22] node[below,font=\scriptsize]{$L_{t}'$} (a2);
\draw[smth] (a2) to[bend left=22] node[below,font=\scriptsize]{$L_{t}'$} (a1);

% ---- observation row (COVID window 2020Q2--Q4) ----
\node[below=20mm of a1,anchor=north] (lab) {\scriptsize $y_t = Z\alpha_t$:};
% macro cells (hollow over the 3 COVID quarters)
\node[obsfill,right=4mm of lab] (m1) {};
\node[obshollow,right=2mm of m1] (m2) {};
\node[obshollow,right=2mm of m2] (m3) {};
\node[obshollow,right=2mm of m3] (m4) {};
\node[obsfill,right=2mm of m4]  (m5) {};
% financial cells (filled throughout)
\node[obsfill,right=2mm of m5] (f1) {};
\node[obsfill,right=2mm of f1] (f2) {};
\node[obsfill,right=2mm of f2] (f3) {};
\node[obsfill,right=2mm of f3] (f4) {};
\node[obsfill,right=2mm of f4] (f5) {};

\node[above=1mm of m3,font=\scriptsize] {macro};
\node[above=1mm of f3,font=\scriptsize] {financial};
% COVID bracket under the 3 missing macro cells
\draw[decorate,decoration={brace,amplitude=4pt,mirror},red!70!black]
   ($(m2.south west)+(0,-1mm)$) -- ($(m4.south east)+(0,-1mm)$)
   node[midway,below=3pt,font=\scriptsize,red!70!black]{2020Q2--Q4 missing};

% imputation arrow: observed financials -> imputed (hollow) macro hole
\draw[->,red!70!black,thick] (f1.north) to[bend left=30]
   node[above,font=\scriptsize]{impute given obs.\ financials} (m3.north);
\end{tikzpicture}
\caption{Companion-form state space with the Durbin--Koopman
filter/smoother under the COVID-as-missing treatment.  States
$\alpha_t$ (Eq.~\eqref{eq:state}) evolve forward through the transition
matrix $T$ (solid, Kalman filter, Eq.~\eqref{eq:kf_pred_a}); the
backward smoother propagates
$r_{t-1}=(Z_t^{(o)})'F_t^{-1}v_t+L_t'r_t$
(dashed, Eq.~\eqref{eq:dk_r}).  In the observation row
$y_t=Z\alpha_t$ (Eq.~\eqref{eq:obs}), over the fixed window
2020Q2--Q4 (three quarters) the \emph{macro} cells (real activity,
prices, and the macro stars ROWDEM/ROWINF) are set missing (hollow)
while the \emph{financial} cells (rates, yields, equity, house prices,
and the foreign-rate star ROWFIN) remain observed (filled).  Because
the filter processes only the observed rows $Z_t^{(o)}$ of each
partially-observed vector, the macro holes are imputed conditional on
the observed financials.}
\label{fig:statespace-dk}
\end{figure}

The smoother refines the filtered estimates using all future
information, yielding $\alpha_{t|H}$ for all~$t$
\citep{DurbinKoopman2002, DurbinKoopman2012}.

\paragraph{Algorithm: Durbin--Koopman Fixed-Interval Smoother.}
\label{alg:dk}
\textbf{Input:} Filtered quantities
$\{\alpha_{t|t-1}, P_{t|t-1}, v_t, Z_t^{(o)}, F_t\}_{t=1}^{H}$.

\noindent Initialize $r_H = 0$.  For $t = H, H{-}1, \ldots, 1$:

If observations exist at time $t$:
\begin{align}
  L_t &= T'\,\bigl(I - P_{t|t-1}\, (Z_t^{(o)})'\,
    F_t^{-1}\, Z_t^{(o)}\bigr), \label{eq:dk_L} \\
  r_{t-1} &= (Z_t^{(o)})'\, F_t^{-1}\, v_t + L_t'\, r_t.
    \label{eq:dk_r}
\end{align}
Otherwise: $r_{t-1} = T'\, r_t$.

\noindent The smoothed state is:
\begin{equation}\label{eq:dk_smooth}
  \alpha_{t|H} = \alpha_{t|t-1} + P_{t|t-1}\, r_{t-1}.
\end{equation}

\paragraph{Simulation smoother (draws, not just means).} For
uncertainty quantification and for the COVID-as-missing data
augmentation (Section~\ref{sec:covid}) the tool needs \emph{draws} of the
missing/conditioned states, not only their smoothed mean. The
\citet{DurbinKoopman2002} simulation smoother obtains a draw
$\tilde\alpha$ from the conditional distribution
$p(\alpha\mid y^{(o)})$ by the elegant ``mean-correction'' device:
simulate an unconditional path, smooth it, and add the smoothed
\emph{discrepancy} back to the unconditional draw. Algorithm
\ref{alg:dksmoother} states the form used inside each
\texttt{cgl\_bvarV5} sweep, with partial (ragged + COVID-masked)
observations handled by processing only the observed rows
$Z_t^{(o)}$ at each date.

\begin{algorithm}[!ht]
\caption{Durbin--Koopman simulation smoother with partial observations
(one draw inside the data-augmentation Gibbs sweep).}
\label{alg:dksmoother}
\algIn{system matrices $T,Z,Q,H$; partial observations
$\{y_t^{(o)}\}_{t=1}^{H}$ (COVID-macro and ragged rows absent);
current draw of $(\beta,\Sigma)$.}
\algOut{one draw $\tilde\alpha_{1:H}$ from $p(\alpha_{1:H}\mid y^{(o)},\beta,\Sigma)$, hence imputed values for the missing $y$ cells.}
\begin{algsteps}
\item \algComment{(1) Forward simulation of an unconditional path.}
\item Draw $\alpha_0^{+}$ from the initial state law; \algKw{for} $t=1,\dots,H$: draw $\eta_t,\varepsilon_t$ and set $\alpha_t^{+}=T\alpha_{t-1}^{+}+\eta_t$, $\,y_t^{+}=Z\alpha_t^{+}+\varepsilon_t$.
\item Form the synthetic partial observations $y_t^{+(o)}$ on the \emph{same} observed pattern as the data ($\;$drop the cells that are \texttt{NaN} in $y_t^{(o)}$).
\item \algComment{(2) Kalman filter (Algorithm of Sec.~\ref{sec:kf}) on the artificial series $y_t^{(o)}-y_t^{+(o)}$.}
\item \algKw{for} $t=1,\dots,H$: run the prediction/update recursions on $Z_t^{(o)}$, storing $\{\alpha_{t|t-1},P_{t|t-1},v_t,F_t\}$. \algComment{at fully-missing $t$, no update}
\item \algComment{(3) Backward Durbin--Koopman smoothing recursion.}
\item Set $r_H=0$; \algKw{for} $t=H,\dots,1$:
\item \algInd \algKw{if} observed at $t$: $L_t = T'\bigl(I - P_{t|t-1}(Z_t^{(o)})'F_t^{-1}Z_t^{(o)}\bigr)$, $\;r_{t-1}=(Z_t^{(o)})'F_t^{-1}v_t + L_t'r_t$;
\item \algInd \algKw{else}: $r_{t-1}=T'r_t$.
\item \algInd smoothed discrepancy $\hat\alpha_t = \alpha_{t|t-1}+P_{t|t-1}r_{t-1}$.
\item \algComment{(4) Mean-correction: add the discrepancy back to the unconditional draw.}
\item $\tilde\alpha_t \gets \alpha_t^{+} + \hat\alpha_t$; read the imputed $\tilde y_t = Z\tilde\alpha_t$ at the missing cells.
\end{algsteps}
\end{algorithm}

Averaging $\tilde\alpha$ across Gibbs sweeps recovers the posterior-mean
completed panel $\widehat X_c$ that Algorithm~\ref{alg:emgvar} feeds back
into the stars; retaining the per-draw paths yields the predictive draw
cloud \texttt{Dforecast} used for the uncertainty bands
(Section~\ref{sec:bands}) and for density scoring
(Section~\ref{sec:empirical:oos}).

\subsection{Conditional Forecast Computation}

The conditional forecast is computed as follows:
\begin{enumerate}
  \item Initialize the state from the last $p$ historical
    observations: $\alpha_0 = (y_T', y_{T-1}', \ldots, y_{T-p+1}')'$.
  \item Construct the conditioning matrix $Y^* \in \R^{H \times n}$,
    where $Y^*_{t,j}$ is the target value for variable~$j$ at
    horizon~$t$ if conditioned, and $\texttt{NaN}$ otherwise.
  \item Run the Kalman filter (Algorithm~\ref{alg:kf}) and smoother
    (Algorithm~\ref{alg:dk}) with partial observations given
    by the non-$\texttt{NaN}$ entries of~$Y^*$.
  \item Extract the observation block (first $n$ elements) from each
    smoothed state $\alpha_{t|H}$.
\end{enumerate}

\subsection{Delta-Based Display}\label{sec:delta}

To ensure that zero user deviations produce exactly the stored
baseline forecast, the tool computes both an unconditional smoother
pass (with all entries of $Y^*$ set to $\texttt{NaN}$) and a
conditional pass.  The displayed forecast is:
\begin{equation}\label{eq:delta}
  \hat{y}_{T+h}^{\text{display}} = \bar{y}_{T+h}^{\text{baseline}}
  + \underbrace{\bigl(\hat{y}_{T+h}^{\text{cond}} -
  \hat{y}_{T+h}^{\text{uncond}}\bigr)}_{\text{smoother delta}},
\end{equation}
where $\bar{y}^{\text{baseline}}$ is the pre-computed baseline
forecast (posterior mean).  This construction guarantees that the
displayed forecast matches the stored baseline exactly when no
conditioning constraints are imposed, avoiding small numerical
discrepancies between the smoother's unconditional output and the
stored baseline.  The unconditional smoother result is cached and
reused across conditioning changes.

For log-transformed variables, the smoother operates in log-level
space, and the delta is scaled to annualized growth-rate space:
\begin{equation}\label{eq:scale}
  \Delta g_h = 4 \times \Delta \ell_h, \qquad
  \Delta \ell_h = \ell_h^{\text{cond}} - \ell_h^{\text{uncond}},
\end{equation}
where $\ell_h$ denotes the log-level forecast at horizon~$h$.

\subsection{Uncertainty Quantification}\label{sec:uncertainty}

Forecast uncertainty bands are computed via the Durbin--Koopman
\emph{simulation smoother} \citep{DurbinKoopman2002}, which generates
draws from the posterior predictive distribution conditional on the
user's constraints.

For each posterior draw $d = 1, \ldots, D$:
\begin{enumerate}
  \item \textbf{Forward simulation:} Draw shocks
    $\eta_t^+ \sim \mathcal{N}(0, I_n)$ and compute a simulated path
    using the $d$-th posterior draw of the VAR coefficients:
    \begin{equation}\label{eq:sim_forward}
      \alpha_{t}^+ = T^{(d)}\, \alpha_{t-1}^+ + d^{(d)}
      + R\, L^{(d)}\,\eta_t^+,
    \end{equation}
    where $L^{(d)}$ is the lower Cholesky factor of $\Sigma^{(d)}$.
    The simulated observations are $y_t^+ = Z\, \alpha_t^+$.
  \item \textbf{Deviation computation:} At conditioned entries,
    compute $y_t^* = Y_t^{\text{target}} - y_t^+$; at free entries,
    set $y_t^* = \texttt{NaN}$.
  \item \textbf{Smoother on deviations:} Run the Kalman smoother
    on $\{y_t^*\}$ with initial state $\alpha_0^* = 0$ and small
    initial covariance $P_0^* = 10^{-7} I_{np}$, producing
    adjustment paths $\hat\alpha_t^*$.
  \item \textbf{Combine:} The conditional draw is
    $\tilde\alpha_t = \hat\alpha_t^* + \alpha_t^+$.
\end{enumerate}
The 16th and 84th percentiles across $D$ draws yield the reported
68\% credible bands.  The tool uses $D = 50$ in ``Quick'' mode
and $D = 200$ in ``Full'' mode.  The simulation smoother correctly
integrates over both parameter uncertainty (through the posterior
draws) and forecast uncertainty (through the simulated shocks).


%% ================================================================
\section{Policy Counterfactuals}\label{sec:counterfactual}
%% ================================================================

The counterfactual layer evaluates how macroeconomic outcomes change
under an alternative policy stance.  It operates \emph{on top of} the
conditional scenario described in Section~\ref{sec:kalman}: starting
from the DK-smoothed scenario paths, the user specifies deviations in
the policy rate or government spending, and the tool traces the
implied effects through a DSGE model's impulse response functions
before re-conditioning the full system through the BVAR.

\subsection{DSGE Impulse Response Functions}\label{sec:dsge}

Impulse response functions (IRFs) are drawn from the Macroeconomic
Model Data Base \citep[MMB;][]{WielandCwikMuellerSchmidtWolters2012,
WielandAfanasyevaYooKuete2016}.  The MMB provides a library of
pre-solved DSGE models with standardized variable names and multiple
policy rule specifications.  The tool includes IRFs from 169~models
under 9~monetary policy rules:

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Rule} & \textbf{Reference} \\
\midrule
Taylor      & \citet{Taylor1993} \\
SW          & \citet{SmetsWouters2007} \\
CEE         & \citet{CEE2005} \\
GR          & Gerdesmeier \& Roffia (2004) \\
LWW         & Levin, Wieland \& Williams (2003) \\
OW08        & Orphanides \& Wieland (2008) \\
OW13        & Orphanides \& Wieland (2013) \\
Coenen      & \citet{Coenen2012} \\
CMR         & Christiano, Motto \& Rostagno (2014) \\
\bottomrule
\end{tabular}
\end{center}

Each IRF file provides the dynamic response of key macroeconomic
variables---inflation, output gap, interest rate, consumption,
investment, and others---to a one-standard-deviation monetary policy
shock under the specified rule.  Fiscal policy IRFs are available for
60~models that include a fiscal sector.

\subsection{Monetary Policy Shock Inversion}\label{sec:shock_inversion}

Given a user-specified interest-rate adjustment path
$\Delta r = (\Delta r_1, \ldots, \Delta r_H)'$, the tool solves for
the structural monetary policy shock sequence
$\varepsilon = (\varepsilon_1, \ldots, \varepsilon_H)'$ via the
lower-triangular Toeplitz system:
\begin{equation}\label{eq:toeplitz}
  \underbrace{\begin{pmatrix}
    h_r(0) & 0 & \cdots & 0 \\
    h_r(1) & h_r(0) & \cdots & 0 \\
    \vdots & & \ddots & \vdots \\
    h_r(H{-}1) & h_r(H{-}2) & \cdots & h_r(0)
  \end{pmatrix}}_{\mathcal{H}_r \in \R^{H \times H}}
  \varepsilon = \Delta r,
\end{equation}
where $h_r(s)$ is the impulse response of the interest rate at
horizon~$s$.  Since $\mathcal{H}_r$ is lower-triangular, the system is
solved by forward substitution:
\begin{equation}\label{eq:shock_inversion_formula}
  \varepsilon_t = \frac{\Delta r_t - \sum_{j=0}^{t-1}
    h_r(t-j)\, \varepsilon_j}{h_r(0)}, \qquad t = 0, 1, \ldots, H{-}1.
\end{equation}

The implied responses of inflation and output are:
\begin{equation}\label{eq:irf_delta}
  \Delta \pi_t^{\text{IRF}} = \sum_{j=0}^{t} h_\pi(t{-}j)\,
  \varepsilon_j,
  \qquad
  \Delta y_t^{\text{IRF}} = \sum_{j=0}^{t} h_y(t{-}j)\,
  \varepsilon_j.
\end{equation}

An analogous procedure applies to fiscal policy shocks, using the
government-spending IRFs ($h_g$, $h_\pi^g$, $h_y^g$, $h_r^g$) from
the DSGE models in the MMB that include a fiscal sector.

\subsection{Three Conditioning Modes}\label{sec:modes}

After computing the DSGE-implied deltas, the counterfactual is
re-conditioned through the BVAR to enforce cross-variable
consistency.  Three modes govern what is held fixed versus free in
the second-stage DK smoother pass:

\begin{enumerate}[label=\textbf{(\alph*)}]
  \item \textbf{Hold-targets:} All user-conditioned variables are
    pinned at their scenario values; the interest rate is pinned at
    the scenario rate plus the adjustment.  Remaining variables are
    free and determined by the DK smoother:
    \begin{align}
      Y_t^{\text{cf}}(j) &= \hat{y}_{T+t,j}^{\text{cond}},
        & &\text{for } j \in \mathcal{C}, \\
      Y_t^{\text{cf}}(r) &= \hat{y}_{T+t,r}^{\text{cond}}
        + \Delta r_t, \\
      Y_t^{\text{cf}}(j) &= \texttt{NaN},
        & &\text{otherwise}.
    \end{align}

  \item \textbf{Let-adjust:} Only the policy instrument(s) are
    conditioned; all other variables, including inflation and output,
    are free and adjust endogenously through the BVAR covariance
    structure.

  \item \textbf{IRF-consistent} (default):  The interest rate is
    pinned at the scenario rate plus the adjustment, and inflation
    and output are pinned at the scenario values plus the
    DSGE-implied deltas from~\eqref{eq:irf_delta}:
    \begin{align}\label{eq:irf_consist}
      Y_t^{\text{cf}}(\pi) &= \hat{y}_{T+t,\pi}^{\text{cond}}
        + \Delta \pi_t^{\text{IRF}}, \\
      Y_t^{\text{cf}}(y) &= \hat{y}_{T+t,y}^{\text{cond}}
        + \Delta y_t^{\text{IRF}}, \\
      Y_t^{\text{cf}}(r) &= \hat{y}_{T+t,r}^{\text{cond}}
        + \Delta r_t.
    \end{align}
    The remaining variables are determined by the DK smoother,
    producing responses consistent with both the DSGE-identified
    monetary transmission and the BVAR covariance structure.
\end{enumerate}

In all modes, the counterfactual display uses the same delta
construction as~\eqref{eq:delta}:
\begin{equation}\label{eq:cf_display}
  \hat{y}_{T+h}^{\text{cf,display}} =
  \hat{y}_{T+h}^{\text{scen,display}}
  + f\!\bigl(\hat{y}_{T+h}^{\text{cf,smooth}}
  - \hat{y}_{T+h}^{\text{scen,smooth}}\bigr),
\end{equation}
where $f(\cdot)$ applies the $\times 4$ scaling from~\eqref{eq:scale}
for log-transformed variables.

\subsection{Optimal Policy: Barnichon--Mesters}\label{sec:bm}

Following \citet{BarnichonMesters2023}, the tool solves for the
optimal monetary policy shock sequence that minimizes a quadratic loss
function over deviations from target:
\begin{equation}\label{eq:loss}
  \mathcal{L} = \sum_{t=1}^{H} \Bigl[
    \lambda_\pi \bigl(\pi_t - \pi^*\bigr)^2
    + \lambda_y \bigl(y_t - y^*\bigr)^2
  \Bigr],
\end{equation}
subject to the linear mapping from shocks to outcomes given by the
DSGE impulse responses.

Define the Toeplitz matrices
$\mathcal{H}_\pi, \mathcal{H}_y \in \R^{H \times H}$ analogously
to~\eqref{eq:toeplitz} using the inflation and output-gap IRFs.
Stacking the weighted system:
\begin{equation}\label{eq:bm_stack}
  \underbrace{\begin{pmatrix}
    \sqrt{\lambda_\pi}\, \mathcal{H}_\pi \\[3pt]
    \sqrt{\lambda_y}\, \mathcal{H}_y
  \end{pmatrix}}_{\tilde{\mathcal{H}} \in \R^{2H \times H}}
  \varepsilon
  = \underbrace{\begin{pmatrix}
    \sqrt{\lambda_\pi}\, \Delta\pi^{\text{target}} \\[3pt]
    \sqrt{\lambda_y}\, \Delta y^{\text{target}}
  \end{pmatrix}}_{\tilde{b} \in \R^{2H}},
\end{equation}
the optimal shock sequence is obtained via Tikhonov-regularized
least squares:
\begin{equation}\label{eq:bm_solve}
  \varepsilon^* = \bigl(\tilde{\mathcal{H}}'\tilde{\mathcal{H}}
  + \alpha I_H\bigr)^{-1} \tilde{\mathcal{H}}'\, \tilde{b},
\end{equation}
with regularization parameter $\alpha = 10^{-6}$.  The implied policy
rate path is
$\Delta r_t^* = \sum_{j=0}^{t} h_r(t{-}j)\,\varepsilon_j^*$, which
is then passed to the IRF-consistent conditioning mode
(Section~\ref{sec:modes}c) to obtain the full counterfactual.

The user controls the relative weight on price stability versus full
employment via a slider that sets
$\lambda_\pi / (\lambda_\pi + \lambda_y)$.


%% ================================================================
\section{Global VAR (GVAR) and Global Commons}\label{sec:gvar}

The single-country engine of Sections~\ref{sec:bvar}--\ref{sec:counterfactual}
generalizes to a multi-country setting in which a conditioning imposed on one
economy spills over to all others. The tool implements a \emph{Global VAR}
(GVAR) layer in the tradition of \citet{PesaranSchuermannWeiner2004} and
\citet{DeesDiMauroPesaranSmith2007}, comprising the United States together with
the euro area as a single aggregate bloc and $31$ further Rest-of-World (RoW)
blocs---$33$ coupled blocs in all---that span approximately 90\% of global GDP.
The decisive implementation choice is that \emph{cross-country coupling is
imposed at solve time, not at estimation time}: each bloc is an independently
estimated single-country BVAR, and the spillovers enter only through the scenario
\emph{deviation}, which propagates as a linear fixed point. Two further channels
distinguish the current version: the United States is now a \emph{fully
endogenous} coupled bloc---it drives the rest of the world \emph{and} receives
feedback from it, rather than acting as a frozen anchor---and four US-determined
\emph{global commons} (oil, the long US rate, US corporate credit, and US equity)
are carried by every bloc.

\subsection{Architecture: an endogenous US and 32 partner blocs}\label{sec:gvar:arch}

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[
  >=Stealth,
  font=\small,
  bloc/.style={circle, draw, thick, minimum size=10mm, inner sep=1pt, fill=blue!8},
  hub/.style={circle, draw, very thick, minimum size=14mm, inner sep=1pt, fill=red!12},
  commons/.style={rectangle, rounded corners, draw, thick, fill=orange!15,
                  align=center, inner sep=3pt, font=\footnotesize},
  star/.style={<->, thick, blue!55!black},
  bcast/.style={->, thick, orange!70!black, dashed},
]

% Central dominant US bloc (endogenous)
\node[hub] (US) at (0,0) {US};

% Ring of representative partner blocs (label ~8, indicate "+ 24 more")
\node[bloc] (EA)   at ( 90:2.6) {EA};
\node[bloc] (JP)   at ( 45:2.6) {JP};
\node[bloc] (CN)   at (  0:2.6) {CN};
\node[bloc] (UK)   at (-45:2.6) {UK};
\node[bloc] (CA)   at (-90:2.6) {CA};
\node[bloc] (MX)   at (-135:2.6) {MX};
\node[bloc] (KR)   at (180:2.6) {KR};
\node[bloc] (BR)   at (135:2.6) {BR};

% "+ 24 more" partner blocs
\node[bloc, fill=blue!4, dashed] (more) at (112:4.0) {\footnotesize $+24$};

% Bidirectional trade-weighted star links (US <-> each partner)
\foreach \c in {EA,JP,CN,UK,CA,MX,KR,BR} {\draw[star] (US) -- (\c);}
\draw[star] (US) -- (more);

% Global commons node broadcasting one-directionally to all blocs
\node[commons] (GC) at (-3.7,2.9)
  {\textbf{Global commons}\\[1pt]
   oil $\cdot$ US 10Y\\ US Baa $\cdot$ US equity};
\draw[bcast] (GC) -- (US);
\foreach \c in {EA,BR,KR,more} {\draw[bcast] (GC) to[bend left=8] (\c);}

% Legend / annotations
\node[align=left, font=\footnotesize, anchor=west, text width=6.0cm] at (1.6,-3.3)
  {\textcolor{blue!55!black}{$\leftrightarrow$}\ trade-weighted star links
     (\textsc{dem}, \textsc{inf}, \textsc{fin})\\
   \textcolor{orange!70!black}{$\dashrightarrow$}\ commons broadcast (US$\to$all, $1\!:\!1$)};
\node[align=left, font=\footnotesize, anchor=west, text width=5.4cm] at (1.6,2.9)
  {US \emph{endogenous}: drives \emph{and} receives RoW feedback\\
   $\rho(M)\!\approx\!0.924$ (vs.\ frozen anchor $\rho\!\approx\!0.726$)};

\end{tikzpicture}
\caption{GVAR bloc topology. A central, dominant United States bloc is coupled to
a ring of $32$ Rest-of-World partner blocs (eight labelled---EA, JP, UK, CA, CN,
MX, KR, BR---plus $24$ further blocs) through \emph{bidirectional},
trade-weighted ``RoW star'' links carrying foreign demand (\textsc{dem}),
inflation (\textsc{inf}), and the short rate (\textsc{fin}). A small global-commons
node (oil, the long US rate, US corporate credit, US equity) broadcasts
\emph{one-directionally} and identically ($1\!:\!1$) to every bloc. The US is now a
\emph{fully endogenous} coupled bloc rather than the classical frozen anchor: it
feeds the rest of the world \emph{and} receives feedback, raising the coupling
operator's spectral radius from $\rho(M)\approx0.726$ (frozen-US, RoW-only) to
$\rho(M)\approx0.924$ at the full $33$-bloc endogenous-US configuration (the value
stored in the shipped \texttt{coupling\_default.json.gz}; it moves slightly with
each refit), both contractive so the fixed point $x = Mx + d$ is well defined
(Sections~\ref{sec:gvar:arch}--\ref{sec:gvar:fixedpoint}).}
\label{fig:gvar-topology}
\end{figure}

The bloc set is
\texttt{US}, \texttt{EA}, \texttt{JP}, \texttt{UK}, \texttt{CA},
\texttt{CN}, \texttt{CH}, \texttt{KR}, \texttt{MX}, \texttt{AU},
\texttt{TR}, \texttt{SE}, \texttt{PL}, \texttt{NO}, \texttt{DK},
\texttt{IN}, \texttt{BR}, \texttt{RU}, \texttt{ID}, \texttt{SA},
\texttt{AR}, \texttt{ZA}, \texttt{TH}, \texttt{MY}, \texttt{CL},
\texttt{CO}, \texttt{CR}, \texttt{CZ}, \texttt{HU}, \texttt{IL},
\texttt{IS}, \texttt{NZ}, and \texttt{TW}
($33$ blocs: the US, the euro-area aggregate \texttt{EA}, and $31$ further
blocs). The euro area enters as a \emph{single aggregate} bloc rather than as its
individual members: a fully disaggregated euro GVAR is non-stationary
($\rho(M)\approx 1.089 > 1$), and aggregating the euro area into one bloc
restores stationarity. The $17$ euro-area member states are therefore retained
only as \emph{standalone} single-country models outside the coupled system
(Section~\ref{sec:standalone}), not as GVAR blocs.

\paragraph{The US is now endogenous, not a frozen anchor.} In earlier versions
the US was treated as a \emph{closed anchor}, exogenous in the Dees--PSW sense
\citep{DeesDiMauroPesaranSmith2007}: it carried no foreign variables, was solved
once, and never iterated in the cross-country fixed point. The current US model
instead carries its own three trade-weighted RoW \emph{star} variables
(\texttt{ROWDEM\_US}, \texttt{ROWINF\_US}, \texttt{ROWFIN\_US}) built from a US
trade-weights row, so the US is a \emph{fully coupled} bloc with $n=41$
(its domestic and fiscal variables, the global commons of
Section~\ref{sec:gvar:commons} as its own endogenous variables, and the three
US star variables). It both drives every partner---through its weight in their
trade-weighted aggregates and through the global commons---\emph{and} receives
partner feedback through its own stars. The US is the first entry of the coupled
set and iterates inside the cross-country fixed point alongside everyone else;
there is no longer a privileged frozen bloc. This RoW$\to$US feedback is the
qualitative gain of the endogenous treatment, and it is also what makes the
complete solve more expensive (Section~\ref{sec:gvar:solvemode}).

The topology is \textbf{not hardcoded}: it self-configures from the deployed
model specifications. The US is treated as endogenous if and only if its model
carries the three \texttt{ROW*\_US} star variables \emph{and} it has a row in
the trade-weights file; absent either, the engine falls back to the legacy
frozen-anchor solve, which remains byte-identical. More generally, a bloc is an
active GVAR member if and only if its \texttt{spec.json} carries variables tagged
\texttt{block:\,'row'} \emph{and} it has a row in the trade-weights file
(\texttt{weights\_24bloc.json}; the filename is historical---the file now lists
all $33$ coupled blocs, the US row included). At load, the engine derives each
bloc's GDP, price, and short-rate columns from its specification (mirroring the
estimator's column-resolution order) and reads its RoW-star indices, so that
bloc indices are never assumed by position. Adding an economy to the GVAR
therefore requires only shipping its estimated model with the appropriate
variable tags and a weights row.

\subsection{Trade-weighted star variables}\label{sec:gvar:stars}

Every coupled bloc---now including the United States---consists of its domestic
VAR augmented by three trade-weighted \emph{star} variables that summarize the
foreign environment, following the weak-exogeneity device of
\citet{PesaranSchuermannWeiner2004}:
\begin{itemize}
  \item \texttt{ROWDEM}: foreign demand, a trade-weighted index of partner
    real-GDP growth;
  \item \texttt{ROWINF}: foreign inflation, the analogous index on partner
    price levels;
  \item \texttt{ROWFIN}: foreign financial conditions, a trade-weighted average
    of partner short-term policy rates.
\end{itemize}
Let $\mathcal{W}_c \subseteq \{\text{partners of }c\}$ collect the partners that
contribute to a given star at quarter $t$, with $w_{cj}$ the (renormalized)
trade weight of partner $j$ in receiver $c$. For the activity and price stars,
the partner level is read in $100\ln$ space and the star is the annualized
growth index
\begin{equation}\label{eq:gvar:star_growth}
  \text{ROWDEM}_{c,t}
  = 4 \sum_{j \in \mathcal{W}_c}
      \tilde{w}_{cj}\,\bigl(\ell_{j,t}^{\,\text{gdp}} - \ell_{j,t-1}^{\,\text{gdp}}\bigr),
  \qquad
  \text{ROWINF}_{c,t}
  = 4 \sum_{j \in \mathcal{W}_c}
      \tilde{w}_{cj}\,\bigl(\ell_{j,t}^{\,\text{price}} - \ell_{j,t-1}^{\,\text{price}}\bigr),
\end{equation}
where the scaling $4\,\Delta(100\ln\cdot)$ is the quarter-over-quarter
annualized convention of~\eqref{eq:growth}, and the financial star is the
level aggregate
\begin{equation}\label{eq:gvar:star_fin}
  \text{ROWFIN}_{c,t} = \sum_{j \in \mathcal{W}_c} \tilde{w}_{cj}\, r_{j,t}.
\end{equation}
The weights are \emph{per-component} renormalized over the partners that are
present and eligible at each $t$, $\tilde{w}_{cj} = w_{cj}\,
\bigl(\sum_{k} w_{ck}\bigr)\big/\bigl(\sum_{k \in \mathcal{W}_c} w_{ck}\bigr)$,
so that the mass of any absent or excluded partner is reabsorbed and the active
weights still sum to one. Three eligibility rules mirror the estimator exactly:
rate-less blocs (Switzerland, Norway) carry no own short rate and are dropped
from partners' \texttt{ROWFIN} (but retained in \texttt{ROWDEM}/\texttt{ROWINF});
the hyperinflation bloc (Argentina) is dropped from partners' \texttt{ROWINF}
and \texttt{ROWFIN} (retained in \texttt{ROWDEM}); and China's GDP is reported
in \emph{nominal} terms, so its activity contribution is deflated by
\emph{subtraction} in log space, $\ell^{\,\text{gdp}}_{\text{CN}} -
\ell^{\,\text{price}}_{\text{CN}} = 100\ln(\text{NGDP}/P)$, rather than by
division.

\subsection{Trade weights}\label{sec:gvar:weights}

The bilateral weights are constructed from IMF International Merchandise Trade
Statistics (IMTS) and shipped as \texttt{weights\_24bloc.json} (a historical
filename: the file now holds the full roster), which lists the $33$ blocs
together with $33$ weight rows---one per bloc, the US included, now that the US
is endogenous---each summing to one (zero diagonal).
At load, the live weight matrix $W$ is renormalized over the \emph{active} bloc
set, so a deployment that activates a subset of the candidate blocs remains
internally consistent.

\subsection{EM estimation of the coupled system: iterative completion of the
star variables}\label{sec:gvar:em}

The solve-time coupling of Section~\ref{sec:gvar:fixedpoint} takes each bloc's
estimated model as given. This subsection describes how those models are
\emph{produced}---the step that is the methodological core of the system and is
easy to mistake for an off-the-shelf GVAR estimation. It is not. Classical
fixed-weight GVAR estimation builds the foreign-variable (``star'') regressors
\emph{once}, from observed partner data, on a balanced panel, and runs a single
pass of country-by-country regressions. Our panels are deeply unbalanced and the
stars cannot be formed directly; we therefore estimate the blocs by an
\emph{EM-flavoured fixed-point iteration} that alternates a Durbin--Koopman
data-augmentation completion of the partner panels (the E-step) with a Bayesian
re-estimation of each bloc given the recomputed stars (the M-step), iterating to
a fixed point in the \emph{completed stars}. This estimation-time loop is a
distinct object from the solve-time deviation system $x = Mx + d$ of
Section~\ref{sec:gvar:fixedpoint}: the former is run \emph{offline}, once, to
produce the shipped posterior-mean coefficients; the latter is run \emph{online},
per scenario, with those coefficients frozen.

\paragraph{Why the stars cannot be formed directly.} For receiver bloc $c$ the
star at quarter $t$ is the trade-weighted partner aggregate
$x^{*}_{c,t}=\sum_{j} w_{cj}\,x_{j,t}$ of
equations~\eqref{eq:gvar:star_growth}--\eqref{eq:gvar:star_fin}, evaluated on the
partner \emph{levels} $\ell^{\,\text{gdp}}_{j,t}$, $\ell^{\,\text{price}}_{j,t}$,
$r_{j,t}$. In a balanced classical GVAR every $x_{j,t}$ is observed for every $t$
in a common span and the sum is immediate. Here it is not:
\begin{itemize}
  \item \textbf{Ragged starts and ends.} Blocs enter the sample at different
    dates (some emerging-market series begin a decade after the US), so at early
    quarters only a subset of $c$'s partners exist; partner panels also end on
    different quarters.
  \item \textbf{COVID macro masking.} Following the data-augmentation treatment
    of Section~\ref{sec:covid} and \citet{LenzaPrimiceri2022} in spirit, the
    three pandemic quarters \mbox{2020Q2--Q4} are treated as \emph{missing} in
    every bloc's macro (activity, price) columns---and, for a receiver, in the
    incoming \emph{macro} stars \texttt{ROWDEM}/\texttt{ROWINF}---while the
    financial columns and \texttt{ROWFIN} stay observed. The partner GDP and
    price levels that would feed \texttt{ROWDEM}/\texttt{ROWINF} are therefore
    \texttt{NaN} during the pandemic.
  \item \textbf{Short credit/financial series.} Several blocs' credit or rate
    series begin late, leaving leading holes in the columns that feed
    \texttt{ROWFIN}.
\end{itemize}
A star built na\"ively over the observed cells would drop every quarter in which
\emph{any} contributing partner is missing, truncating the usable sample to the
common balanced span---exactly the information loss the data-augmentation design
is meant to avoid. The resolution is to \emph{complete} each partner panel with a
model-based imputation and build the stars from the completed panels; but the
completion of bloc $j$ depends on $j$'s own model, which in turn was estimated
conditional on $j$'s stars, which depend on \emph{its} partners' completions.
The completed stars are thus the fixed point of a coupled system, and we solve it
by iteration.

\paragraph{Relation to EM and data augmentation.} The loop is best read as an
\emph{EM-flavoured block-coordinate iteration} rather than a textbook EM on a
single global likelihood. Within each bloc, the per-bloc step is a genuine
data-augmentation Gibbs/Metropolis sampler in the sense of
\citet{TannerWong1987}: the missing cells (the latent ``complete data'') are
imputed by the Durbin--Koopman simulation smoother
\citep{DurbinKoopman2002,DurbinKoopman2012} and the VAR is re-estimated given the
augmented panel, exactly the expectation/maximization split of
\citet{DempsterLairdRubin1977}. What differs from the canonical EM is the
\emph{cross-bloc} structure: there is no one likelihood being maximized across
all blocs simultaneously; instead the shared latent object iterated to a fixed
point is the set of \emph{completed partner panels} (equivalently the stars they
generate), and the per-bloc E- and M-steps are fused inside a single call to the
COVID-aware sampler \texttt{cgl\_bvarV5}, which performs both the imputation and
the hyperparameter/coefficient draws in one sweep. We are explicit about this so
the construction is not over-sold as a convergence-guaranteed EM: it is a
contraction in the stars (verified empirically by the convergence metric below),
EM in flavour and motivation, with the data-augmentation and Bayesian-estimation
machinery of Sections~\ref{sec:bvar}--\ref{sec:kalman} doing the per-bloc work.

\paragraph{Notation.} Index the iterations by $m=0,1,2,\dots$. Let
$D^{(m)}_{j}\in\R^{T_j\times n_j}$ denote the \emph{completed} domestic panel of
bloc $j$ after iteration $m$, in $100\ln$ level space (the \texttt{comp} object
in code; $n_j$ counts $j$'s domestic variables). Write $\mathcal{S}_c\bigl(\{D_j\}\bigr)$
for the star-construction map of
equations~\eqref{eq:gvar:star_growth}--\eqref{eq:gvar:star_fin}, which reads each
partner's three components from its completed panel and returns receiver $c$'s
three star columns
$x^{*(m)}_{c}=\bigl(\texttt{ROWDEM}_c,\texttt{ROWINF}_c,\texttt{ROWFIN}_c\bigr)$,
including the per-component per-quarter renormalization and the
deflation/exclusion rules already stated. Let $\mathcal{E}_c$ denote one call to
\texttt{cgl\_bvarV5} on the augmented matrix
$X_c=\bigl[D_c^{\text{obs}}\,\big|\,x^{*}_c\bigr]$ with the COVID macro mask
applied; it returns the draw stack $X^{\text{cond}}_c\in\R^{T_c\times(n_c+3)\times G}$
of $G$ Durbin--Koopman--completed panels and the post-burn coefficient draws
$\{(\beta_c^{(g)},\Sigma_c^{(g)})\}$.

\paragraph{E-step (completion).} Given the current stars $x^{*(m)}_c$, the E-step
runs $\mathcal{E}_c$ and forms the \emph{posterior-mean} completed panel
\begin{equation}\label{eq:em:estep}
  \widehat{X}^{(m+1)}_c
  \;=\; \frac{1}{G}\sum_{g=1}^{G} X^{\text{cond}}_{c}[\,\cdot,\cdot,g\,]
  \;=\; \overline{X^{\text{cond}}_c}
  \qquad\text{(\texttt{mean(Xcond,3)})},
\end{equation}
trimmed to the estimation rows. The simulation smoother conditions each missing
cell on the \emph{observed} cells of the same and surrounding periods: its
missing-data step drops only the \texttt{NaN} \emph{elements} of each observation
vector ($y\!\leftarrow\!y(\mathrm{ix})$, $C\!\leftarrow\!C(\mathrm{ix},:)$,
$R\!\leftarrow\!R(\mathrm{ix},\mathrm{ix})$ with $\mathrm{ix}=\lnot\,\mathrm{isnan}(y)$),
so a partially observed row still informs the imputation of its own holes. During
the COVID window this means the masked macro cells---domestic activity and price,
\emph{and} the two incoming macro stars \texttt{ROWDEM}/\texttt{ROWINF}---are
filled conditional on the financial columns and \texttt{ROWFIN}, which remain
observed. The domestic block of $\widehat{X}^{(m+1)}_c$ defines the next
completed panel $D^{(m+1)}_c=\texttt{panelfrom}(\widehat{X}^{(m+1)}_c)$ that the
\emph{other} blocs' stars will read.

\paragraph{M-step (re-estimation).} The same call $\mathcal{E}_c$ returns the
Bayesian posterior over the bloc's VAR coefficients given the augmented panel:
\texttt{cgl\_bvarV5} maximizes the Giannone--Lenza--Primiceri marginal likelihood
over the Minnesota hyperparameters by \texttt{csminwel}, then runs a
random-walk Metropolis sampler over the tightness/sum-of-coefficients
hyperparameters $(\lambda,\mu)$, recomputing $(\beta_c,\Sigma_c)$ at each accepted
draw \citep{Giannone2015,BanburaGiannoneLenza2015}. The three star columns are
appended \emph{after} the domestic block and always keep the random-walk
(own-lag-one) Minnesota prior; the prior mean on the first own lag is set to zero
only for the variables tagged white-noise/stationary (e.g.\ the fiscal
ratios of Section~\ref{sec:fiscal}). The deployed coefficients are the
posterior means $\hat\beta_c=\frac1G\sum_g\beta_c^{(g)}$,
$\hat\Sigma_c=\frac1G\sum_g\Sigma_c^{(g)}$; the draws themselves furnish the
predictive bands. Because the imputation~\eqref{eq:em:estep} and this
re-estimation happen inside one $\mathcal{E}_c$ call, the E- and M-steps are
\emph{fused} per bloc per iteration.

\paragraph{Outer fixed-point iteration.} The blocs are swept \emph{Jacobi-style}:
all stars for iteration $m{+}1$ are built from the \emph{frozen}
start-of-iteration completions $\{D^{(m)}_j\}$, and the blocs are then re-estimated
in parallel (\texttt{parfor}). Only after the parallel sweep are the completions
overwritten, $D^{(m)}_j\!\leftarrow\!D^{(m+1)}_j$, so the next sweep sees the
updated panels. A Gauss--Seidel ordering (update each bloc's completion
immediately and let later blocs in the same sweep see it) reaches the same fixed
point; the Jacobi choice is order-independent and parallelizes across cores, at
the cost of at most one extra iteration. The recursion is
\begin{equation}\label{eq:em:outer}
  x^{*(m+1)}_c \;=\; \mathcal{S}_c\!\Bigl(\bigl\{\,\texttt{panelfrom}\!\bigl(
     \overline{\mathcal{E}_j\!\bigl[D^{\text{obs}}_j \,\big|\, x^{*(m)}_j\bigr]}
   \bigr)\bigr\}_{j\in\text{partners}(c)}\Bigr),
  \qquad c=1,\dots,N_{\text{bloc}},
\end{equation}
i.e.\ each iteration re-completes every bloc given its current stars and rebuilds
every receiver's stars from the refreshed completions. The shipped models are the
$(\hat\beta_c,\hat\Sigma_c)$ at the fixed point $x^{*}_c$ of~\eqref{eq:em:outer}.

\paragraph{Convergence criterion.} Convergence is measured on the stars actually
used in estimation. Let $x^{*(m)}_c$ be receiver $c$'s star matrix at iteration
$m$, with the COVID rows of its two \emph{macro} stars set to \texttt{NaN}
(cross-iteration churn in the pandemic-imputed macro-star cells is Monte-Carlo
noise of the imputation, not signal, so it is excluded; \texttt{ROWFIN} stays
observed through COVID and remains in the metric). The sup-norm change is
\begin{equation}\label{eq:em:conv}
  \mathrm{mc}^{(m)}
  \;=\; \max_{c}\ \bigl\|\,x^{*(m)}_c - x^{*(m-1)}_c\,\bigr\|_{\infty,\,\text{omitnan}},
\end{equation}
and the loop stops when $\mathrm{mc}^{(m)}<\textsc{tol}$ (default
$\textsc{tol}=0.03$, in annualized-percent units for the macro stars and
rate-level units for \texttt{ROWFIN}), or after a hard cap of $\textsc{maxit}=12$
iterations. A Monte-Carlo noise floor of order $0.1$ from the imputation means
the criterion is a practical contraction check rather than an asymptotic
guarantee; setting $\textsc{maxit}=1$ recovers the single-pass, one-shot
historical-star mode (no coupling iteration) used for standalone blocs.

\paragraph{Numerical specifics.} Five implementation details are load-bearing and
match the estimator exactly:
\begin{enumerate}[label=(\roman*)]
  \item \textbf{The $4\times$ (not $400\times$) scaling.} The completed panels are
    already in $100\ln$ space, so a one-quarter difference $\Delta(100\ln\cdot)$
    is a percent-scale quarterly change; the activity and price stars annualize it
    by $\times 4$ (equations~\eqref{eq:gvar:star_growth}). A $400\times$ would
    double-apply the $\times100$ and inflate the foreign-demand/inflation stars
    hundred-fold. The financial star is a \emph{level} average with no $\times4$
    (equation~\eqref{eq:gvar:star_fin}).
  \item \textbf{Per-quarter, per-component renormalization.} The weight applied to
    a present partner is rescaled so the contributing weights sum to one
    \emph{separately for each component and each quarter}
    ($\tilde w_{cj}$ of Section~\ref{sec:gvar:stars}); the mass of absent
    (ragged-edge) or excluded (rate-less, hyperinflation) partners is reabsorbed
    rather than treated as zero.
  \item \textbf{Leading-\texttt{NaN} back-fill.} A star column's leading
    \texttt{NaN} prefix---early quarters before any partner exists---is back-filled
    with the first valid value (or zero if the whole column is empty), because a
    \texttt{NaN}-prefixed foreign-demand regressor yields a singular state
    covariance; \emph{internal} and COVID \texttt{NaN}s are left for the smoother
    to fill. The same guard lead-fills short domestic credit series.
  \item \textbf{COVID macro mask.} The masked columns on $X_c$ are the domestic
    macro columns \emph{plus} the two macro stars (indices $n_c{+}1$,
    $n_c{+}2$); the financial star $\texttt{ROWFIN}$ (index $n_c{+}3$) and the
    domestic financial columns stay observed, so the smoother fills the macro
    holes conditional on observed financials.
  \item \textbf{Dominant-unit / \texttt{\_US} handling.} The US closed-anchor
    bootstrap is run \emph{once before} the loop: the US domestic panel (COVID
    macro cells \texttt{NaN}'d) is completed with \emph{no} stars, and its
    posterior-mean completion seeds the first-iteration partner stars. Under the
    legacy frozen-anchor design the US is then held out of the loop
    (\texttt{rowB = blocs(2:end)}); under \texttt{US\_ENDOGENOUS=1} the US is
    folded into the sweep like any other bloc, carrying its own
    \texttt{ROW*\_US} stars built from a \texttt{US} weights row, and iterates to
    the fixed point alongside the partners.
\end{enumerate}

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[
  >=Stealth,
  font=\small,
  embox/.style={draw, rounded corners, thick, align=center, inner sep=5pt,
               minimum width=34mm, minimum height=13mm},
  estep/.style={embox, fill=blue!7},
  mstep/.style={embox, fill=green!8},
  starbox/.style={embox, fill=orange!12, minimum width=40mm},
  seed/.style={draw, dashed, rounded corners, align=center, inner sep=4pt,
               fill=red!5, font=\footnotesize, text width=34mm},
  flow/.style={->, thick},
]
  % seed
  \node[seed] (seed) at (-5.4,0)
    {\textbf{US anchor bootstrap}\\(no stars, COVID-masked)\\ seeds iter-1 stars};

  % star build
  \node[starbox] (stars) at (0,2.3)
    {\textbf{Build stars}\\$x^{*(m)}_c=\mathcal{S}_c(\{D^{(m)}_j\})$\\
     \footnotesize trade-weighted, $4\times$, renorm.};

  % E-step
  \node[estep] (E) at (3.3,-0.4)
    {\textbf{E-step}\\DK completion\\$\widehat X^{(m+1)}_c=\overline{X^{\text{cond}}_c}$};

  % M-step
  \node[mstep] (M) at (-3.3,-0.4)
    {\textbf{M-step}\\GLP/Minnesota\\$(\hat\beta_c,\hat\Sigma_c)$};

  % fused box around E and M
  \begin{scope}[on background layer]
    \node[draw, dotted, rounded corners, fit=(E)(M), inner sep=9pt,
          fill=black!3, label={[font=\footnotesize]below:%
          {fused in one \texttt{cgl\_bvarV5} call per bloc, per iteration}}] (fuse) {};
  \end{scope}

  % cyclic flow:  stars -> E -> (completed panels) -> M & stars rebuild
  \draw[flow] (stars.east) to[bend left=18]
     node[right, font=\scriptsize, align=left, xshift=1pt]
       {current stars\\ $x^{*(m)}_c$} (E.north);
  \draw[flow] (E.west) --
     node[above, font=\scriptsize] {completed $D^{(m+1)}_j$} (M.east);
  \draw[flow] (M.north) to[bend left=18]
     node[left, font=\scriptsize, align=right, xshift=-1pt]
       {recompute stars\\(next sweep)} (stars.west);
  \draw[flow, red!60!black, dashed] (seed.east) -- (stars.west);

  % convergence test
  \node[draw, rounded corners, thick, fill=yellow!12, inner sep=5pt,
        align=center] (conv) at (0,-3.5)
    {\textbf{Converged?}\;
     $\mathrm{mc}^{(m)}=\max_c\|\Delta x^{*}_c\|_{\infty}<\textsc{tol}$
     \;(COVID macro-stars excluded)};
  \draw[flow] (fuse.south) -- (conv.north);
  \draw[flow] (conv.east) to[bend right=42]
     node[right, font=\scriptsize, align=left] {no:\\ next sweep $m{+}1$} (stars.east |- 0,1.2);
  \node[right=2mm of conv, font=\footnotesize] (out)
    {yes $\Rightarrow$ ship $(\hat\beta_c,\hat\Sigma_c)$};
  \draw[flow] (conv.east) -- (out.west);
\end{tikzpicture}
\caption{The estimation-time EM fixed-point loop over the completed star
variables. A one-shot US anchor bootstrap (red, dashed) seeds the first
iteration's stars. Each iteration then (i) builds every receiver's
trade-weighted stars from the frozen start-of-iteration completed partner panels,
(ii) runs the \emph{fused} E-step (Durbin--Koopman posterior-mean completion of
the bloc's missing cells, \texttt{mean(Xcond,3)}) and M-step (GLP/Minnesota
Bayesian re-estimation) inside one \texttt{cgl\_bvarV5} call per bloc, and (iii)
recomputes the stars from the refreshed completions for the next Jacobi sweep.
The loop stops when the sup-norm change in the estimation stars falls below
$\textsc{tol}=0.03$ (with the COVID-imputed macro-star cells excluded as
Monte-Carlo noise), capped at $\textsc{maxit}=12$. This is distinct from the
solve-time deviation fixed point $x=Mx+d$ (Fig.~\ref{fig:coupling}), which runs
online with these coefficients frozen.}
\label{fig:gvar-em}
\end{figure}

Algorithm~\ref{alg:gvar-em} states the loop
(\texttt{pipeline/export\_bvar\_gvar24\_loop.m}; the credit-validation driver
\texttt{credit\_validate\_loop.m} carries an identical loop).

\begin{algorithm}[!ht]
\caption{EM fixed-point estimation of the coupled GVAR (completion of the star
variables; \texttt{export\_bvar\_gvar24\_loop.m}).}
\label{alg:gvar-em}
\algIn{per-bloc observed domestic panels with \texttt{NaN} holes (ragged edges,
COVID macro mask, short credit series); trade weights $W$; eligibility rules
(rate-less, hyperinflation, China nominal-GDP deflation);
\texttt{US\_ENDOGENOUS} flag; $\textsc{maxit}=12$; $\textsc{tol}=0.03$.}
\algOut{per-bloc posterior-mean models $\{(\hat\beta_c,\hat\Sigma_c)\}$ and
coefficient draws; converged completed stars $\{x^{*}_c\}$; iteration count.}
\begin{algsteps}
\item \algComment{US anchor bootstrap (once).} Complete the US domestic panel with \emph{no} stars (COVID macro cells \texttt{NaN}'d), $\widehat X_{\text{US}}\!=\!\overline{X^{\text{cond}}_{\text{US}}}$; set $D^{(0)}_{\text{US}}\!=\!\texttt{panelfrom}(\widehat X_{\text{US}})$. \algKw{if} \texttt{US\_ENDOGENOUS} then US joins the swept set; \algKw{else} $\text{rowB}\!=\!\text{blocs}(2{:}\text{end})$ (US frozen).
\item \algKw{for} $m=1$ \algKw{to} $\textsc{maxit}$:
\item \algInd \algComment{Jacobi sweep: stars built from the FROZEN $\{D^{(m-1)}_j\}$.}
\item \algInd \algKw{parfor} each swept bloc $c$:
\item \algIndd $x^{*}_c \gets \mathcal{S}_c(\{D^{(m-1)}_j\})$ \algComment{\texttt{buildstars}: trade-weighted, $4\times$ macro / level fin, per-quarter renorm, lead-\texttt{NaN} back-fill.}
\item \algIndd $X_c \gets [\,D^{\text{obs}}_c \mid x^{*}_c\,]$; apply COVID macro mask (domestic macro cols $+$ \texttt{ROWDEM},\texttt{ROWINF}; \texttt{ROWFIN} observed).
\item \algIndd $X^{\text{cond}}_c,\{\beta^{(g)}_c,\Sigma^{(g)}_c\} \gets \texttt{cgl\_bvarV5}(X_c,\dots)$ \algComment{E$+$M fused: DK completion $\,+\,$ GLP/MH draws.}
\item \algIndd $\widehat X_c \gets \overline{X^{\text{cond}}_c}=\texttt{mean(Xcond,3)}$;\quad $D^{(m)}_c \gets \texttt{panelfrom}(\widehat X_c)$;\quad store $(\hat\beta_c,\hat\Sigma_c)$ and draws.
\item \algInd \algComment{after the parfor:} commit $\{D^{(m)}_c\}$ so the next sweep's \texttt{buildstars} sees them.
\item \algInd \algComment{Convergence.} $\mathrm{mc} \gets \max_c \|x^{*(m)}_c - x^{*(m-1)}_c\|_{\infty}$ with COVID macro-star cells \texttt{NaN}'d.
\item \algInd \algKw{if} $m>1$ \algKw{and} $\mathrm{mc}<\textsc{tol}$: \algKw{break} (\textsc{converged}).
\item \algKw{return} $\{(\hat\beta_c,\hat\Sigma_c)\}$, draws, $\{x^{*}_c\}$, $m$.
\end{algsteps}
\end{algorithm}

\paragraph{Contrast with classical fixed-weight OLS GVAR.} The textbook GVAR of
\citet{PesaranSchuermannWeiner2004} and \citet{DeesDiMauroPesaranSmith2007}
(surveyed by \citealp{ChudikPesaran2016}) differs from this estimator on every
axis, and the differences are exactly the contribution.
\begin{enumerate}[label=(\arabic*)]
  \item \textbf{Iteration vs.\ single pass.} Classical GVAR builds each foreign
    star $x^{*}_{it}=\sum_j w_{ij}x_{jt}$ \emph{once} from observed partner data,
    treats it as weakly exogenous, and estimates each country VARX$^{*}$ in a
    single OLS (or reduced-rank ML) pass---no re-aggregation, no feedback into the
    stars. Here the stars are recomputed from model-completed panels every sweep
    and iterated to the fixed point~\eqref{eq:em:outer}.
  \item \textbf{Missing-data completion vs.\ truncation.} Classical GVAR requires
    a \emph{balanced} panel: ragged edges are dropped and the sample is truncated
    to the common span, with no imputation. Here the panel is unbalanced by
    design, and the Durbin--Koopman simulation smoother imputes the missing cells
    (ragged starts/ends, COVID macro mask, short credit) conditional on the
    observed cells---and crucially the imputed posterior means \emph{flow into the
    stars}, which is precisely what makes the iteration necessary.
  \item \textbf{Per-quarter renormalized weights.} Trade weights are fixed (IMF
    IMTS, 2021--2023), as in classical GVAR, \emph{but} they are renormalized per
    quarter and per component over the partners actually present and eligible,
    with hyperinflation and rate-less exclusions and China's nominal-GDP
    deflation---an unbalanced-panel device absent from the fixed-weight formula.
  \item \textbf{Bayesian posterior vs.\ OLS point estimates.} Each bloc is a
    hierarchical GLP/Minnesota BVAR with Metropolis-sampled hyperparameters,
    yielding a posterior (draws $\to$ predictive bands) and a per-variable
    random-walk-vs-white-noise prior choice, not OLS point estimates on a single
    balanced sample.
  \item \textbf{Jointly solved linkages.} The GVAR linkages and the estimation are
    solved \emph{jointly} here---the stars are a fixed point of the completion
    loop---whereas classical GVAR fixes the stars pre-estimation and stacks the
    country models into a single global linear system only afterwards.
\end{enumerate}
In one line: the novelty is a \emph{Durbin--Koopman data-augmentation completion
of unbalanced, COVID-masked partner panels, feeding a per-quarter-renormalized
trade-weighted star aggregation, inside a Bayesian per-bloc re-estimation,
iterated to a star fixed point}---so the cross-country linkages are an estimated
object rather than a fixed pre-estimation input. The frozen posterior means it
produces are what the solve-time coupling of
Section~\ref{sec:gvar:fixedpoint} then propagates.

\subsection{Coupling at solve time, not estimation}\label{sec:gvar:fixedpoint}

\begin{figure}[!ht]
  \centering
  \begin{tikzpicture}[
    >={Stealth[round]},
    font=\small,
    bloc/.style={draw, rounded corners, minimum width=26mm, minimum height=14mm,
                 align=center, thick, fill=blue!4},
    route/.style={draw, rounded corners, minimum width=42mm, align=left,
                  inner sep=4pt, fill=black!2},
    star/.style={font=\scriptsize\itshape, fill=white, inner sep=1pt},
  ]
    % --- two coupled blocs (the cycle) ---
    \node[bloc] (j) {Bloc $j$\\\scriptsize\,(e.g.\ US)};
    \node[bloc, right=42mm of j] (c) {Bloc $c$\\\scriptsize\,(partner)};

    % star-pin feedback cycle j <-> c
    \draw[->, thick, blue!60!black] (j.north east) to[bend left=22]
      node[star, above] {$s_{j\to c}$ (DEM/INF/FIN)} (c.north west);
    \draw[->, thick, blue!60!black] (c.south west) to[bend left=22]
      node[star, below] {$s_{c\to j}$} (j.south east);

    % --- fixed-point equation ---
    \coordinate (jc) at ($(j)!0.5!(c)$);
    \node[below=11mm of jc, draw, rounded corners, thick,
          fill=yellow!10, inner sep=6pt] (eq)
      {$\displaystyle x = M\,x + d$};
    \node[below=1pt of eq, font=\scriptsize, align=center, text width=58mm]
      {$x$: stacked star pin-deltas $s_{c,v,t}$ \,(+ US global deltas $g\Delta_{p,t}$);
       \;$M$: Kalman-probe coupling; \;$d$: exogenous forcing};

    % --- two solution routes ---
    \node[route, below left=12mm and -6mm of eq] (gs)
      {\textbf{(a) Gauss--Seidel sweeps}\\[1pt]
       \scriptsize Neumann series $x=\sum_{k\ge0}M^{k}d$;\\
       \scriptsize re-smooth each bloc until\\
       \scriptsize $\max|\Delta x|<\text{tol}$\, (cross-check)};
    \node[route, below right=12mm and -6mm of eq] (dir)
      {\textbf{(b) Compact $x = M x + d$}\\[1pt]
       \scriptsize inverse-free $x\leftarrow d+Mx$ (live);\\
       \scriptsize or $(I-M)^{-1}d$ / Smith doubling\\
       \scriptsize ($S\!\leftarrow\!S+TS,\ T\!\leftarrow\!T^{2}$, export)};
    \draw[->] (eq.south) -- (gs.north);
    \draw[->] (eq.south) -- (dir.north);

    % --- endogenous-US annotation ---
    \coordinate (gsdir) at ($(gs)!0.5!(dir)$);
    \node[draw, dashed, rounded corners, below=9mm of gsdir,
          fill=red!4, inner sep=5pt, align=center, text width=82mm, font=\scriptsize] (us)
      {\textbf{Endogenous US} (\textsc{us\_endogenous}): augmented state adds the US
       global-column deltas $g\Delta_{p,t}$ (oil, US 10Y, US Baa, US equity),
       pinned $1{:}1$ onto every partner bloc.
       Dim $\approx 2060$ at the $33$-bloc roster; \,$\rho(M)\approx 0.924<1$ (contractive).};
    \draw[->, dotted] (gs.south) -- (us.north west);
    \draw[->, dotted] (dir.south) -- (us.north east);
  \end{tikzpicture}
  \caption{Solve-time cross-country coupling as the affine fixed point
    $x = M\,x + d$. Two coupled blocs exchange trade-weighted star pin-deltas
    (DEM/INF/FIN), forming the feedback cycle; the deviation state $x$ stacks
    these pins (plus the US global-column deltas under an endogenous US). The
    fixed point admits two equivalent solutions---(a) Gauss--Seidel/Neumann
    sweeps through the Durbin--Koopman smoother, used as the cross-check, and (b)
    the compact $M$-state recursion, solved inverse-free by the Neumann
    fixed-point $x\leftarrow d+Mx$ on the production path (the explicit
    $(I-M)^{-1}d$ / Smith doubling are reserved for the small frozen-anchor case
    and the export-time precompute, since the in-browser $O(\dim^{3})$ inverse is
    prohibitive at $\dim\approx 2060$). With the US endogenous the augmented
    state has dimension $\approx 2060$ and spectral radius
    $\rho(M)\approx 0.924<1$, so the iteration contracts and the two routes agree
    to $\sim 10^{-9}$.}
  \label{fig:coupling}
\end{figure}

Because each bloc is estimated independently, there is no joint, block-exogenous
GVAR system; the cross-country linkage is imposed when the scenario is solved.
The key observation is that, with coefficients fixed at their posterior mean
$(\hat\beta, \hat\Sigma)$, the conditional-forecast operator of
Section~\ref{sec:kalman} is \emph{affine} in the conditioning values (the
Kalman filter and Durbin--Koopman smoother are linear in the pinned data). The
\emph{baseline} forecast of each bloc is therefore data-driven and computed
exactly once, via an all-\texttt{NaN} (unconditional) smoother pass; only the
scenario \emph{deviation} couples across blocs.

Because the US is now endogenous it is no longer held outside the fixed point,
and the compact deviation state is correspondingly \emph{augmented}. It collects
(i) the star pin-deltas $s_{c,v,t}$ of \emph{every} coupled bloc $c$---the US
included---for star variable $v\in\{\text{DEM},\text{INF},\text{FIN}\}$ at
horizon $t$, and (ii) the per-period \emph{deviation of each US global column}
$g\Delta_{p,t}$, which under the frozen-anchor design was a constant and is now
itself part of the unknown. Stacking these into a vector $x$, the deviation
system is the linear fixed point
\begin{equation}\label{eq:gvar:fp}
  x = M\,x + d,
\end{equation}
where $d$ is the exogenous forcing (each bloc's own scenario pins moving its
linked series at zero partner and global delta) and $M$ now carries three
coupling families: star~$\leftarrow$~star (receiver $c$'s star responds to a
partner $j$'s free-variable path---with the US participating both as partner and
as receiver), the US-global definition rows (a global column's deviation as the
US's own response to its star pins), and star~$\leftarrow$~global (a partner's
star responds to its own global pin). The US-determined globals therefore live
\emph{inside} $M$ rather than in $d$, which is precisely the new RoW$\to$US
feedback loop. The augmented state has dimension $\approx 2060$ at the full
$33$-bloc roster.

The fixed point~\eqref{eq:gvar:fp} is solved two equivalent ways:
\begin{enumerate}[label=(\alph*)]
  \item \textbf{Gauss--Seidel / Neumann sweeps} (the cross-check) sum the
    Neumann series $x = \sum_{k\ge 0} M^k d$ by re-conditioning each bloc in turn
    through the Durbin--Koopman smoother \citep{DurbinKoopman2002,
    DurbinKoopman2012} until the maximum level change falls below tolerance.
  \item \textbf{Direct closed form}
    \begin{equation}\label{eq:gvar:closed}
      x = (I - M)^{-1} d,
    \end{equation}
    after which one final conditional-forecast pass per bloc reconstructs the
    full set of free variables consistent with the converged pin-deltas.
\end{enumerate}
At the full $33$-bloc endogenous-US configuration the spectral radius is
$\rho(M)\approx 0.924 < 1$, so the Neumann series converges and $(I-M)$ is
nonsingular; the two solvers agree to $\sim 10^{-9}$. (The legacy frozen-anchor
RoW-only operator had a smaller radius, $\rho(M)\approx 0.726$; closing the
RoW$\to$US loop raises the coupling but leaves the system comfortably
contractive.)

Algorithm~\ref{alg:coupling} states both solve paths
(\texttt{app/src/lib/compute/gvarSolve.ts}). The coupling operator $M$
is never formed by writing down a joint VAR; each of its columns is
\emph{probed} by perturbing one pinned cell and reading the affine
conditional-forecast response of every linked bloc through the
Durbin--Koopman smoother---so $M$ encodes the same per-bloc Kalman
operator that produces the baseline, restricted to the deviation.

\begin{algorithm}[!ht]
\caption{Solve-time coupling fixed point $x=Mx+d$ (Gauss--Seidel/Neumann
and direct $(I-M)^{-1}$; \texttt{gvarSolve.ts}).}
\label{alg:coupling}
\algIn{per-bloc posterior-mean models $\{(\hat\beta_c,\hat\Sigma_c)\}$;
scenario pins; trade weights $W$; \texttt{US\_ENDOGENOUS} flag; tolerance
$\textsc{tol}$.}
\algOut{converged deviation state $x$ and per-bloc scenario deltas $\texttt{delta}[c]$; sweep count; $\rho(M)$.}
\begin{algsteps}
\item \algComment{Forcing.} Build $d$: each bloc's own scenario pins, evaluated at \emph{zero} partner-star and global deltas (one DK conditional-forecast pass per pinned bloc).
\item \algComment{Coupling families in $M$ (endogenous-US augmented state).} star$\leftarrow$star (a receiver's star responds to a partner's free path; the US is both partner and receiver); US-global rows ($g\Delta$ as the US's own response to its star pins); star$\leftarrow$global (a partner star responds to its own global pin).
\item \algKw{Path A --- Gauss--Seidel / Neumann sweeps (inverse-free).}
\item \algInd $x\gets d$
\item \algInd \algKw{repeat} (sweep): \algKw{for each} coupled bloc $c$ (US included \algKw{if} \texttt{US\_ENDOGENOUS}): re-condition $c$ through the DK smoother on the current partner-star and global deltas $\Rightarrow$ update $x$'s block for $c$.
\item \algIndd \algComment{this sums the Neumann series $x=\sum_{k\ge0}M^k d$ term by term.}
\item \algInd \algKw{until} $\max|\Delta x| < \textsc{tol}$; record $\rho_{\text{emp}}$ from the geometric residual decay.
\item \algKw{Path B --- direct closed form (cached).}
\item \algInd assemble $M$ by probing columns; \algKw{if} a precomputed $(I-M)^{-1}$ matches the model signature \& pin structure, hydrate it; \algKw{else} fall back to Path A (the dense in-browser inverse is never built live).
\item \algInd $x \gets (I-M)^{-1} d$; one final per-bloc DK pass reconstructs all free variables consistent with the converged pin-deltas.
\item \algComment{Cross-check.} The two paths agree to the verified tolerance ($\max|\Delta|<10^{-4}$ across all blocs in the closed-form vs.\ iterative regression tests, with the iterative reference itself converged to $10^{-7}$), confirming $\rho(M)<1$; report $\rho(M)$ via power iteration on $M$ (in practice on $M^2$, see Sec.~\ref{sec:gvar:solvemode}).
\item \algKw{return} $x$, $\texttt{delta}[c]$, sweep count, $\rho(M)$.
\end{algsteps}
\end{algorithm}

A practical consequence drives the deployment. The operator $M$ depends on the
estimated models and on the conditioning \emph{structure} (which cells are
pinned) but \emph{not} on the pinned \emph{values}, so it can be assembled once
and reused for every value change during interactive dragging. Its dense inverse
is, however, expensive: at the augmented endogenous dimension ($\approx 2060$)
the naive in-browser inversion would take tens of minutes (the cubic inverse is
of order three-quarters of an hour), making a cold build infeasible even in a
Web Worker. The tool therefore \textbf{ships a precomputed coupling artifact}
(\texttt{coupling\_default.json.gz}) containing $M$, $(I-M)^{-1}$, and $\rho(M)$
for the default (empty) pin structure, with the inverse computed offline by a
high-performance \textsc{blas} routine. The artifact is large (the dense
$2060\times2060$ inverse), so it is shipped \emph{gzipped} (about $30$\,MB
compressed) and decompressed in the browser via the native
\texttt{DecompressionStream} API at load. This artifact is mandatory, not an
optimization: hydrating it reduces the first complete solve from the
tens-of-minutes cold build to a few seconds. A model-signature gate guards
against using a stale inverse after any re-estimation; a genuinely novel pin
structure misses the cache and falls back to an inverse-free Neumann solve
(the in-browser cubic inverse is never built live).

\subsection{Two-tier solve: live preview vs.\ the full fixed point}\label{sec:gvar:solvemode}

The endogenous US makes the \emph{complete} cross-country solve materially more
expensive than the legacy frozen-anchor solve, because placing or moving a US
pin re-probes the (large) US bloc, the heavy step. To keep the interface
reactive the tool exposes \textbf{two solve tiers}:
\begin{itemize}
  \item \textbf{Direct preview} (the default while dragging). A fast,
    first-order approximation that propagates the scenario through the
    pre-warmed local per-bloc elasticities---one cross-country hop, without the
    full multiplier feedback---so the propagated paths update live as the user
    drags a pin. The per-bloc response kernels are cached by model signature and
    own-pin structure, so a value-only re-drag (same pinned cells) reuses them
    and re-solves cheaply; a \emph{structure} change (pinning a new cell) re-probes
    the US bloc and is the slower direct step (a few seconds), during which a
    small ``computing\ldots'' pill is shown so the wait does not look like a
    freeze.
  \item \textbf{Full GVAR} (on demand). The complete fixed point of
    \eqref{eq:gvar:fp}---all feedback loops, including RoW$\to$US---computed when
    the user clicks the \textbf{Solve full GVAR} button. This consumes the
    hydrated $(I-M)^{-1}$ artifact and takes a few seconds.
\end{itemize}
A badge above the charts reports which tier produced the current result---an
amber ``GVAR DIRECT preview'' versus a blue ``GVAR full solve''---together with
the sweep count, the spectral radius $\rho$, and the solve time. When a DIRECT
preview is on screen, the \textbf{Solve full GVAR} button is offered to upgrade
it to the complete fixed point. Drag-release dispatch and debouncing keep the
preview channel from firing mid-drag, and the heavy coupling artifact is stripped
from the worker messages on the direct path (it is only needed for the full
solve). For the legacy frozen-anchor topology---or any deployment where the US is
not endogenous---both tiers resolve to the same already-fast cached closed form,
so the two-tier distinction is invisible there.

\subsection{Global commons: US-determined common shocks}\label{sec:gvar:commons}

The headline addition of version~2.0 is a set of four \emph{global common}
variables that are determined by the United States but carried by \emph{every}
bloc:
\begin{itemize}
  \item \texttt{GLB\_OIL} --- the spot oil price (WTI);
  \item \texttt{GLB\_USLR} --- the US 10-year Treasury yield;
  \item \texttt{GLB\_USBAA} --- the US Baa corporate-bond yield (a credit-spread
    proxy);
  \item \texttt{GLB\_USEQ} --- US equity prices.
\end{itemize}
In the US bloc these enter as ordinary \emph{endogenous} variables; in each
partner bloc the same four identifiers (matched one-to-one by \emph{name}, never
by position) are carried as weakly-exogenous commons that the solver \emph{pins}.

The pinning is by \emph{deviation}, not by level. Each partner bloc $c$ sets each
global column to its own baseline plus the US deviation of the matching global,
\begin{equation}\label{eq:gvar:globalpin}
  \widehat{\text{GLB}}_{c,t}
  = \bar{\text{GLB}}_{c,t}
    + \bigl(\text{GLB}^{\text{scen}}_{\text{US},t}
      - \bar{\text{GLB}}_{\text{US},t}\bigr),
\end{equation}
where $\bar{(\cdot)}$ denotes the bloc's own unconditional baseline. This is a
load-bearing design choice. Each RoW bloc estimated its \emph{own} baseline path
for the globals as weakly-exogenous regressors, and those baseline levels differ
from the US's by tens of $100\ln$ units (for example, of order $+17$, $+70$, and
$+28$ for the euro area, Japan, and China on oil). Pinning the US \emph{level}
would inject that entire baseline gap as a spurious deviation the instant a bloc
is selected, even under a zero scenario. Pinning the US \emph{deviation} on top
of each bloc's own baseline instead yields exactly zero spillover at a zero
scenario and an \emph{identical} common shock under conditioning---precisely
mirroring the star convention $\bar{\text{RoW}} + \text{partner-delta}$
of~\eqref{eq:gvar:star_growth}--\eqref{eq:gvar:star_fin}. A US oil pin therefore
propagates the same oil deviation to all $32$ partner blocs (verified to within
$10^{-9}$), while each bloc's domestic variables respond through its \emph{own}
estimated coefficients.

Mechanically, with the US now endogenous the US global \emph{deviation} is itself
an unknown of the fixed point rather than a frozen constant. The global columns
therefore enter the \emph{augmented} coupling operator $M$ of
Section~\ref{sec:gvar:fixedpoint}: a US-global definition row writes each
global's deviation as the US's own response to its star pins, and a
star~$\leftarrow$~global block routes each partner's global pin back into its
stars. This is exactly the channel by which a partner shock now feeds back to the
US. Indirect effects---a common shock moving a bloc's macroeconomy, which moves
its stars, which spill to other blocs---flow through the same operator and are
not double-counted. A bloc that carries no globals reduces the pin to a no-op,
leaving the legacy globals-free solve byte-identical.

On the user interface the globals are \emph{conditionable} on the US screen
(where they are endogenous) and \emph{read-only}, carried over from the US path,
on every other bloc.

\subsection{Relation to the fiscal and counterfactual layers}\label{sec:gvar:layers}

The GVAR layer composes with the single-country machinery rather than replacing
it. The displayed scenario line for an active GVAR bloc is the cross-country
propagated path of this section; for a standalone (non-GVAR) economy it is the
single-country conditional forecast of Section~\ref{sec:kalman}. The US derived
fiscal block (the debt-to-GDP accounting identity, whose empirical motivation is
the fiscal reaction function of \citealp{Bohn1998}) and the DSGE policy
counterfactual---including the \citet{BarnichonMesters2023} optimal-policy
problem---continue to operate on the US bloc's propagated path. Conditional
forecasts throughout use the large-cross-section state-space method of
\citet{BanburaGiannoneLenza2015} with the hierarchical prior of
\citet{Giannone2015}, applied independently to each bloc and stitched together
only through the linear deviation system~\eqref{eq:gvar:fp}.

\section{Fiscal Blocks: Estimated Drivers and Debt Accounting}\label{sec:fiscal}

Six of the economies in the tool---the United States, the Euro Area,
Japan, the United Kingdom, Canada, and China---carry a dedicated
\emph{fiscal block}.  The block follows the stock-flow-consistent
division of labour shared by the U.S.\ Congressional Budget Office's
conditional-BVAR budget mechanics and the IMF Financial Programming
(FPP) / debt-sustainability frameworks: the BVAR is used as a
\emph{macro-fiscal scenario generator} that jointly forecasts the
macroeconomy together with a small number of fiscal \emph{flow drivers},
while the public-debt stock and the headline reporting variables
(primary and overall balance, interest, debt-to-GDP, gross financing
needs) are \emph{derived outside the VAR} by the government
budget-constraint identity.  No reduced-form equation is ever allowed to
forecast the debt stock freely, because an unconstrained debt VAR is
explosive: the debt-dynamics identity has a near-unit autoregressive
root $(1+i)/(1+g^{n})$, and small parameter errors compound into
divergent debt paths.  Imposing the identity by construction is exactly
the discipline that the CBO and FPP/DSA frameworks demand, and it is the
structure implemented in
\texttt{app/src/lib/compute/fiscalAccounting.ts}.

\subsection{Estimated Fiscal Drivers}\label{sec:fiscal_drivers}

The BVAR jointly estimates the macro block of
Section~\ref{sec:variables} together with \emph{four} fiscal flow drivers,
all entering as linear (\texttt{lin}) variables:
\begin{itemize}
  \item \textbf{Revenue} (\texttt{FREV\_GDP}): general-government
    receipts as a percentage of GDP, an annual ratio.
  \item \textbf{Primary expenditure} (\texttt{FPEXP\_GDP}):
    non-interest outlays as a percentage of GDP, an annual ratio.
  \item \textbf{Effective interest rate} (\texttt{EFFI}, \% p.a.): the
    average rate the government actually pays on its outstanding stock,
    constructed as net interest divided by the lagged gross debt and
    annualized. Because the stock turns over only as maturing securities are
    refinanced, this effective rate lags market yields and is therefore
    distinct from---and estimated separately from---the policy rate and the
    market yields already in the macro block.
  \item \textbf{Stock-flow adjustment} (\texttt{SFA}, \% of GDP): the
    deficit--debt discrepancy described below.
\end{itemize}
The effective rate \texttt{EFFI} is the estimated interest driver of the
deployed block. (The parametrisation has changed over time: an early version
carried $\Delta(\text{debt}/\text{GDP})$ directly, and a later one carried debt
service to GDP \texttt{DSVC}; the current block reverts to the effective rate.)
The interest bill is then formed inside the accounting recursion as
$\mathit{int}_t = i^{\text{eff}}_t\, d_{t-1}/100$.

\paragraph{The stock-flow adjustment as an estimated variable.}
The novelty of the current block is that the stock-flow adjustment
(\texttt{SFA}) is now an \emph{estimated} BVAR variable rather than a constant
plug. It is the exact residual of the tool's own debt recursion---the part of
the observed change in gross debt that the flow side (deficit plus the
interest--growth ``snowball'') does \emph{not} explain. Economically this seam
arises because the headline deficit is measured on a federal-flows perimeter
while the debt stock is gross debt (so intragovernmental holdings, valuation
effects, and other below-the-line ``other means of financing'' operations move
the two apart). It is constructed so that it closes the recursion to machine
precision on history, and the pandemic quarters are set to missing
(\texttt{NaN}) so the COVID-as-missing Gibbs sampler imputes them
(Section~\ref{sec:covid}) rather than letting the 2020 swing contaminate the
estimate. Carrying \texttt{SFA} as a forecast variable means the
debt-to-GDP \emph{projection} now propagates its own \texttt{SFA} path forward
(with dynamics and uncertainty bands) instead of defaulting the discrepancy to
zero, which materially affects the high-debt blocs whose historical SFA is large
and persistent. The historical SFA means (in \% of GDP), which each bloc also
ships as its \texttt{sfaDefault} fallback, are: US $1.75$, EA $0.33$, JP $2.23$,
UK $3.15$, CA $3.19$, CN $4.02$.

Because all four drivers are ordinary BVAR variables, they inherit the full
estimation machinery of Sections~\ref{sec:bvar}--\ref{sec:kalman}: the
hierarchical Minnesota prior \citep{Giannone2015}, the COVID-as-missing
data-augmentation Gibbs treatment, the companion-form Durbin--Koopman
conditional smoother \citep{DurbinKoopman2002, DurbinKoopman2012}, and the
\citet{BanburaGiannoneLenza2015} conditioning-via-partial-observations
construction.  In the five Global-VAR fiscal blocs (EA, JP, UK, CA, CN)---and
now in the endogenous US bloc itself---the fiscal drivers are part of the
domestic block and propagate to the other economies through the shared
Rest-of-World stars, exactly as the macro variables do
\citep{PesaranSchuermannWeiner2004, DeesDiMauroPesaranSmith2007}.

\paragraph{A stationary prior for the fiscal ratios.} The three
GDP-ratio drivers---revenue \texttt{FREV\_GDP}, primary expenditure
\texttt{FPEXP\_GDP}, and the stock-flow adjustment \texttt{SFA}---are
mean-reverting shares that fluctuate around a roughly constant
in-sample level; they are \emph{not} integrated. Carrying them under the
default random-walk own-lag prior ($\delta=1$) is therefore the wrong
null: it injects a built-in drift that lets the projected ratio wander
away from its historical level at the long end of the horizon. These
three drivers are accordingly tagged \texttt{prior:"WN"} in every fiscal
bloc's specification and estimated with the \emph{stationary}
white-noise own-lag prior ($\delta=0$) of Section~\ref{sec:ownlag}: the
estimator collects them via \(\texttt{pos}=\texttt{find}(\texttt{prior}==
\text{`}\texttt{WN}\text{'})\) and passes the set as the
\texttt{stationary} argument of \texttt{cgl\_bvarV5}, so
\(\texttt{diagb}(\texttt{pos})=0\) centers their own-lag dynamics on
mean reversion to the equation constant. The effective interest rate
\texttt{EFFI}, by contrast, \emph{retains} the random-walk prior: it is a
slow-moving stock-average rate (net interest over lagged debt) whose
level is genuinely persistent---it turns over only as maturing securities
refinance---so a near-unit own-lag is the right prior null for it.

The empirical effect is exactly the intended one. Under the random-walk
prior the U.S.\ revenue ratio was pinned near its end-of-sample value
($\sim 19\%$) and drifted from there; under the white-noise prior it now
\emph{reverts} to its $\sim 17.4\%$ in-sample mean over the projection,
and the expenditure ratio and \texttt{SFA} likewise return to their
historical means rather than carrying the last observation forward
indefinitely. We emphasise (per Section~\ref{sec:ownlag}) that this is a
shift of the prior \emph{center}, not a hard stationarity constraint: the
posterior own-lag coefficient is still the GLP prior--likelihood balance
at the estimated tightness $\lambda$, so a fiscal ratio whose data
genuinely trend will still be allowed to do so---the \texttt{WN} prior
only removes the mechanical drift that the random-walk center would
otherwise build in. Because \texttt{pos} is empty for the $44$ non-fiscal
blocs, this change is a no-op (byte-identical output) everywhere except
the six fiscal blocs.

Each fiscal bloc ships a \texttt{fiscal\_meta.json} file that pins the
column layout used by the accounting recursion.  It carries the integer
indices $\texttt{idx} = \{\texttt{gdp}, \texttt{deflator},
\texttt{revenue}, \texttt{primaryExp}, \texttt{effRate}, \texttt{sfa}\}$
into the level-space forecast matrix---the first two locate the real-GDP and
deflator log-levels that supply nominal growth, the next two locate the
revenue and primary-expenditure drivers, $\texttt{effRate}$ locates the
estimated effective-rate column, and $\texttt{sfa}$ locates the estimated
stock-flow-adjustment column---together with the seed debt ratio $d_0$ and a
fallback \texttt{sfaDefault} (e.g.\ the U.S.\ block has $d_0 = 122.57$,
$\texttt{idx.effRate} = 35$, $\texttt{idx.sfa} = 36$, and
$\texttt{sfaDefault} = 1.75$; the U.K.\ block has $d_0 = 96.24$,
$\texttt{idx.effRate} = 18$, $\texttt{idx.sfa} = 19$). The presence of
$\texttt{idx.sfa}$ is the switch that selects the per-quarter estimated SFA:
when it is set, \texttt{computeFiscalBlock} reads the forecast SFA off that
column so the debt projection carries the discrepancy forward with its own
dynamics and bands; when it is unset, the recursion falls back to the constant
\texttt{sfaDefault} (or zero). A legacy block that instead carried an
$\texttt{idx.debtService}$ column would read that column directly as the period
interest flow and back out the effective rate; the current effective-rate blocks
do not.

\subsection{The Budget-Identity Recursion}\label{sec:fiscal_identity}

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[
    >=Stealth, node distance=4.5mm,
    font=\small,
    driver/.style={draw, rounded corners, fill=blue!8, minimum height=6.5mm,
                   text width=27mm, align=center, inner sep=2pt},
    iden/.style={draw, fill=orange!12, minimum height=6.5mm,
                 text width=33mm, align=center, inner sep=2pt},
    stock/.style={draw, very thick, fill=green!12, minimum height=8mm,
                  text width=18mm, align=center, inner sep=2pt},
    op/.style={font=\footnotesize},
    flow/.style={->, thick},
    lag/.style={->, dashed, thick, gray!70!black}
  ]

  % --- Estimated BVAR drivers (left column) ---
  \node[driver] (rev)  {\texttt{FREV\_GDP}\\\scriptsize revenue, \%\,GDP};
  \node[driver, below=of rev]  (exp) {\texttt{FPEXP\_GDP}\\\scriptsize prim.\ exp., \%\,GDP};
  \node[driver, below=of exp]  (eff) {\texttt{EFFI}\\\scriptsize eff.\ rate, \%\,p.a.};
  \node[driver, below=of eff]  (sfa) {\texttt{SFA}\\\scriptsize stock-flow adj., \%\,GDP};

  \node[above=2.2mm of rev, font=\footnotesize\itshape, text width=30mm, align=center]
       {estimated BVAR drivers};

  % --- Budget-identity terms (middle column) ---
  \coordinate (revexp) at ($(rev)!0.5!(exp)$);
  \node[iden, right=16mm of revexp] (pb)
       {primary balance\\[-1pt]$\mathit{pb}_t=\mathit{rev}_t-\mathit{primexp}_t$};
  \node[iden, below=9mm of pb] (snow)
       {snowball\\[-1pt]$\bigl(\tfrac{1+i^{\text{eff}}_t/400}{1+g^{n}_t/100}-1\bigr)d_{t-1}$};
  \node[iden, below=of snow] (res)
       {\texttt{SFA} residual\\[-1pt]closes recursion};

  \node[above=2.2mm of pb, font=\footnotesize\itshape, text width=34mm, align=center]
       {budget identity};

  % nominal growth feed (from macro block)
  \node[draw, dotted, rounded corners, fill=gray!6, text width=27mm, align=center,
        inner sep=2pt, below=of sfa]
       (gn) {\scriptsize $g^{n}_t=\Delta\ell^{\text{gdp}}_t+\Delta\ell^{\text{defl}}_t$\\(macro block)};

  % --- Debt stock recursion (right column) ---
  \node[stock, right=18mm of snow] (dt)
       {$d_t$\\[-1pt]\scriptsize debt/GDP};

  \node[above=2.2mm of dt, font=\footnotesize\itshape, text width=22mm, align=center]
       {derived stock};

  % driver -> identity flows
  \draw[flow] (rev.east) -- (pb.west);
  \draw[flow] (exp.east) -- (pb.west);
  \draw[flow] (eff.east) -- (snow.west);
  \draw[flow] (sfa.east) -- (res.west);
  \draw[flow] (gn.east) -| (snow.south);

  % identity -> stock recursion (terms of eq.~debt)
  \draw[flow] (pb.east)   -- node[op, above]{$-\,\mathit{pb}_t/4$} (dt.north west);
  \draw[flow] (snow.east) -- node[op, above]{$\times\,\tfrac{1+i^{\text{eff}}_t/400}{1+g^{n}_t/100}$} (dt.west);
  \draw[flow] (res.east)  -- node[op, below]{$+\,\mathit{sfa}_t/4$} (dt.south west);

  % --- accumulation across quarters: lagged debt feedback ---
  \draw[lag] (dt.south) .. controls +(0,-12mm) and +(0,-12mm) .. (snow.south east);
  \node[font=\footnotesize, gray!70!black, align=center, below=11mm of dt.south, anchor=north]
       {$d_{t-1}\!\rightarrow\! d_t\!\rightarrow\! d_{t+1}\cdots$ (quarterly accumulation)};

\end{tikzpicture}
\caption{Fiscal stock-flow schematic. The four estimated BVAR drivers
(\texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}, \texttt{EFFI}, \texttt{SFA};
Section~\ref{sec:fiscal_drivers}) feed the budget identity: revenue and
primary expenditure form the primary balance $\mathit{pb}_t$
\eqref{eq:fiscal_pb}; the effective rate \texttt{EFFI} and nominal growth
$g^{n}_t$ \eqref{eq:fiscal_gn} form the interest--growth \emph{snowball}
\eqref{eq:fiscal_snowball}; and the estimated \texttt{SFA} enters as the
residual that closes the recursion. These flows accumulate into the derived
debt-to-GDP stock $d_t$ by the quarterized roll-forward
$d_t = d_{t-1}\,(1{+}i^{\text{eff}}_t/400)/(1{+}g^{n}_t/100)
- \mathit{pb}_t/4 + \mathit{sfa}_t/4$ \eqref{eq:fiscal_debt}, with the lagged
stock $d_{t-1}$ fed back each quarter (dashed). Debt is \emph{derived}, never
estimated (\texttt{computeFiscalBlock}, Section~\ref{sec:fiscal_identity}).}
\label{fig:fiscal}
\end{figure}

Let $d_t$ denote the debt-to-GDP ratio (in percent), $i^{\text{eff}}_t$
the effective rate (percent per annum), and $g^{n}_t$ nominal GDP growth
(percent per quarter).  All flows below are annual ratios in percent of
GDP.  Nominal growth is read directly off the level-space forecast as
the sum of the real-GDP and deflator log-differences, in the
$100\cdot\ln$ space of Section~\ref{sec:units}:
\begin{equation}\label{eq:fiscal_gn}
  g^{n}_t \;=\; \bigl(\ell^{\text{gdp}}_t - \ell^{\text{gdp}}_{t-1}\bigr)
            \;+\; \bigl(\ell^{\text{defl}}_t - \ell^{\text{defl}}_{t-1}\bigr),
\end{equation}
where $\ell$ is the stored $100\cdot\ln$ level and the right-hand side is
already in percent per quarter (it is not annualized by the factor of
four used for display in \eqref{eq:growth}).  The primary balance is the
revenue--expenditure gap (positive $=$ surplus),
\begin{equation}\label{eq:fiscal_pb}
  \mathit{pb}_t \;=\; \mathit{rev}_t \;-\; \mathit{primexp}_t,
\end{equation}
the interest bill (debt service) is the estimated effective rate applied to the
lagged debt stock,
\begin{equation}\label{eq:fiscal_int}
  \mathit{int}_t \;=\; i^{\text{eff}}_t\,\frac{d_{t-1}}{100},
\end{equation}
i.e.\ the BVAR forecast of the effective rate \texttt{EFFI} drives the interest
flow directly, with the lagged debt $d_{t-1}$ converting the rate into a
percent-of-GDP flow. (A legacy debt-service block would instead supply
$\mathit{int}_t$ as the estimated \texttt{DSVC} ratio and back out the effective
rate as $i^{\text{eff}}_t = 100\,\mathit{int}_t/d_{t-1}$.) The overall balance
and deficit follow as
\begin{equation}\label{eq:fiscal_bal}
  \mathit{ob}_t \;=\; \mathit{pb}_t - \mathit{int}_t,
  \qquad
  \mathit{def}_t \;=\; -\,\mathit{ob}_t \;=\; \mathit{int}_t - \mathit{pb}_t.
\end{equation}
The debt stock is then rolled forward one quarter by the
FPP/DSA debt-dynamics equation,
\begin{equation}\label{eq:fiscal_debt}
  d_t \;=\; d_{t-1}\,
       \frac{1 + i^{\text{eff}}_t/400}{1 + g^{n}_t/100}
       \;-\; \frac{\mathit{pb}_t}{4}
       \;+\; \frac{\mathit{sfa}_t}{4},
       \qquad d_{-1} \equiv d_0,
\end{equation}
seeded at $d_0$.  The rate enters quarterized as $i^{\text{eff}}_t/400$
and growth as $g^{n}_t/100$, while the annual flow ratios
$\mathit{pb}_t$ and $\mathit{sfa}_t$ are scaled by $1/4$ so that one
quarter's worth of the flow accrues per step; $\mathit{sfa}_t$ is the
stock-flow adjustment (the deficit--debt discrepancy of
Section~\ref{sec:fiscal_drivers}). The \texttt{SFA} column is estimated
as its own BVAR variable and is forecast with its own dynamics and bands;
the deployed debt roll-forward, however, deliberately uses the
\emph{structural constant} $\mathit{sfaDefault}$ (the long-run SFA mean)
rather than the per-quarter forecast column, because the forecast column
is pulled to spurious extremes by the long-run consensus anchors'
cross-response and would collapse the projected debt path (see
\S\ref{sec:fiscal_levers}).  Gross financing needs add amortization to
the deficit,
\begin{equation}\label{eq:fiscal_gfn}
  \mathit{gfn}_t \;=\; \mathit{def}_t \;+\; \mathit{amort}_t .
\end{equation}
The recursion in
\eqref{eq:fiscal_pb}--\eqref{eq:fiscal_gfn} is the function
\texttt{computeFiscalBlock}, which is the \emph{only} fiscal recursion
wired to the displayed debt-to-GDP charts and bands (it is called from
\texttt{ChartGrid.tsx} for the baseline, scenario, and counterfactual
paths, and from \texttt{runGvarBandSolve.ts} for the predictive bands).
This is a \textbf{passive accounting recursion}: the debt ratio is
rolled forward purely from the four BVAR-forecast drivers
($\mathit{rev}$, $\mathit{primexp}$, the effective rate, and SFA) with
\emph{no} endogenous response of the primary balance to the debt level
and \emph{no} debt-driven risk premium on the rate
(\S\ref{sec:fiscal_levers} explains the dormant lever variant).  The
exact quarterly convention is pinned by a historical back-cast test that
reconstructs observed debt-to-GDP from the realized drivers.

\paragraph{Snowball decomposition.}  Subtracting $d_{t-1}$
from~\eqref{eq:fiscal_debt} isolates the \emph{automatic} debt dynamics
from the discretionary primary balance.  The change in the debt ratio is
\begin{equation}\label{eq:fiscal_snowball}
  \Delta d_t
  \;=\; \underbrace{\left(\frac{1 + i^{\text{eff}}_t/400}{1 + g^{n}_t/100} - 1\right) d_{t-1}}_{\text{snowball (interest--growth)}}
        \;-\; \frac{\mathit{pb}_t}{4}
        \;+\; \frac{\mathit{sfa}_t}{4}
  \;\approx\; \frac{i^{\text{eff}}_t - g^{n}_t}{1 + g^{n}_t}\, d_{t-1}
        \;-\; \mathit{pb}_t \;+\; \mathit{sfa}_t,
\end{equation}
where the right-hand approximation is the familiar Fiscal-Monitor
$(i-g)$ form (here in annualized flow units).  The snowball term is
positive---debt rises mechanically---whenever the effective rate exceeds
nominal growth; a primary surplus and a favourable growth-interest
differential are the two forces that stabilize the ratio.  The tool
returns the per-quarter snowball contribution
$\bigl((1+i^{\text{eff}}_t/400)/(1+g^{n}_t/100)-1\bigr)d_{t-1}$ alongside
the derived balances so the user can read off the source of any debt
drift.

\begin{remark}
Because the debt stock is \emph{not} a BVAR variable, the estimated
effective rate $\hat\imath^{\text{eff}}_t$ and primary balance
$\widehat{\mathit{pb}}_t$ are debt-agnostic baselines: the recursion uses
\emph{lagged} debt $d_{t-1}$ throughout, so it stays explicit (no
within-period fixed point).  This is the design that lets a single
forward sweep produce a consistent debt path, and it is also what would
let the dormant feedback levers of Section~\ref{sec:fiscal_levers} layer
on without double-counting were they ever activated in the live path.
\end{remark}

\subsection{Debt-Feedback Channels (dormant; possible future
extension)}\label{sec:fiscal_levers}

\begin{important}
\textbf{Not active in the live tool.}  The two debt-feedback channels
described in this subsection---the Bohn fiscal-reaction function
($\gamma$) and the sovereign risk-premium channel ($\beta$)---are
\emph{not} part of the displayed debt path.  They exist only in a
separate code path (\texttt{runFiscalRecursion}) that is exercised by the
unit-test suite and has \emph{no} production or UI caller; the deployed
recursion that produces every debt-to-GDP chart and band
(\texttt{computeFiscalBlock}, \S\ref{sec:fiscal}) runs with
$\gamma = \beta = 0$ and exposes no \texttt{feedbackOn} control to the
user.  We document the channels here because they are validated and
ready, and because they show how the passive accounting layer could be
extended to an \emph{endogenous} debt feedback, but the debt path the
user sees today has \textbf{no} debt$\to$primary-balance reaction
(Bohn) and \textbf{no} debt$\to$yield risk premium.  The only
user-reachable fiscal lever is the SFA / conditioning closure described
below and the scenario conditioning of the four drivers themselves.
\end{important}

The would-be channels modify the estimated baselines in terms of the
lagged debt gap $d_{t-1} - d^{*}$, where the anchor $d^{*}$ defaults to
$d_0$.

\paragraph{Bohn fiscal-reaction function ($\gamma$) --- not wired in.}
Following \citet{Bohn1998}, the primary balance \emph{could} be allowed
to respond to the lagged debt gap, so that fiscal policy consolidates as
debt rises above its anchor:
\begin{equation}\label{eq:fiscal_bohn}
  \mathit{pb}_t \;=\; \bigl(\mathit{rev}_t - \mathit{primexp}_t\bigr)
                 \;+\; \gamma\,\bigl(d_{t-1} - d^{*}\bigr),
  \qquad \gamma \ge 0 .
\end{equation}
A value $\gamma = 0.03$ (three basis points of primary surplus per
percentage point of excess debt) is the canonical \citet{Bohn1998}
estimate and the threshold above which a no-Ponzi debt process is
mean-reverting.  In the live tool this term is \emph{absent}: the
displayed primary balance is exactly $\mathit{rev}_t - \mathit{primexp}_t$
(\S\ref{sec:fiscal}, eq.~\eqref{eq:fiscal_pb}), with no $\gamma$ term.
The \citet{Bohn1998} reaction function is the \emph{empirical
motivation} for caring about a debt anchor, not an implemented feedback
in the deployed path.

\paragraph{Risk-premium channel ($\beta$) --- not wired in.}  The
effective rate \emph{could} be allowed to rise with debt above the
anchor, capturing a sovereign risk premium:
\begin{equation}\label{eq:fiscal_riskprem}
  i^{\text{eff}}_t \;=\; \widehat\imath^{\text{eff}}_t
                    \;+\; \beta\,\max\!\bigl(0,\; d_{t-1} - d^{*}\bigr),
  \qquad \beta \ge 0 ,
\end{equation}
where the premium would bite only \emph{above} the anchor (the
$\max(0,\cdot)$ rectifier).  Were it active, $\beta$ would feed back into
both the interest bill~\eqref{eq:fiscal_int} and the snowball
term~\eqref{eq:fiscal_snowball}, producing the nonlinear debt-spiral
dynamics that motivate the FPP/DSA realism literature.  In the live tool
this term is \emph{absent}: the displayed effective rate is the
BVAR-forecast $\widehat\imath^{\text{eff}}_t$ alone, with no debt-level
premium.  This channel is the natural candidate for a future endogenous
extension, but it is not current behaviour.

\paragraph{Stock-flow-adjustment closure (the genuine SFA term).}  The
SFA term $\mathit{sfa}_t$ in~\eqref{eq:fiscal_debt} is a genuine,
non-optional part of the debt-dynamics identity (the deficit--debt
discrepancy / stock-flow adjustment), \emph{not} a behavioural feedback.
It is estimated as its own BVAR variable
(Section~\ref{sec:fiscal_drivers}) and forecast with its own dynamics and
bands.  Note, however, a deliberate implementation choice: the deployed
debt roll-forward uses a \emph{structural constant}
($\mathit{sfaDefault}$, the long-run mean of the SFA) rather than the
per-quarter forecast SFA column, because the forecast column is dragged
to spurious extremes by the long-run consensus anchors' cross-response
(which would collapse the projected debt path).  The structural SFA is
the economically-correct long-run residual.  This closure can also be
used as a scenario lever---set to zero for pure flow accounting, held at
the historical average, or solved (via the debt-targeting inversion of
\S\ref{sec:fiscal_inversion}) to reconcile a target debt path with the
flow drivers.

\subsection{Debt-Targeting Inversion}\label{sec:fiscal_inversion}

The recursion can also be run backwards.  Given a desired debt-to-GDP
path $\{d_t^{\text{target}}\}$, the effective rate, nominal growth, and
SFA, the annual primary balance required at each quarter is obtained by
solving~\eqref{eq:fiscal_debt} for $\mathit{pb}_t$ along the target
trajectory:
\begin{equation}\label{eq:fiscal_required_pb}
  \mathit{pb}_t \;=\; 4\left[\,
       d_{t-1}^{\text{target}}\,
       \frac{1 + i^{\text{eff}}_t/400}{1 + g^{n}_t/100}
       \;-\; d_t^{\text{target}} \,\right]
       \;+\; \mathit{sfa}_t ,
\end{equation}
with $d_{-1}^{\text{target}} \equiv d_0$.  This is the IMF DDT/DSA
``required primary balance / adjustment to the debt anchor''
(\texttt{requiredPrimaryBalance}).  The caller then conditions the BVAR
on this primary-balance path through the linear constraint
$\mathit{rev}_t - \mathit{primexp}_t = \mathit{pb}_t$, propagated by the
DK smoother of Section~\ref{sec:kalman}.  Because the effective rate and
growth themselves respond to the primary balance through the BVAR
covariance structure, an exact hit is obtained by iterating
invert~$\rightarrow$~condition~$\rightarrow$~re-read~$(i,g)$~$\rightarrow$~re-invert;
one or two passes converge.

\subsection{Display Layout}\label{sec:fiscal_display}

The estimated and derived fiscal objects are presented in different
chart rows, reflecting their different epistemic status.  The four
\emph{estimated} fiscal drivers are shown as inputs alongside the macro
block: revenue and primary expenditure as \% of GDP, and the two new charts
\begin{itemize}
  \item \textbf{Effective interest rate} (\texttt{EFFI}, \% p.a.): the average
    rate the government pays on its outstanding stock. It is plotted as a level
    in percent per annum next to the policy rate and the market yields. Read it
    as the slow-moving cost of the debt: it lags the policy rate and the
    10-year yield, because only maturing securities reprice, so a rate hike
    shows up here gradually rather than at once. This is the rate that enters
    the interest bill~\eqref{eq:fiscal_int} and the snowball~\eqref{eq:fiscal_snowball}.
  \item \textbf{Stock-flow adjustment} (\texttt{SFA}, \% of GDP): the
    deficit--debt discrepancy. It is plotted as a level in percent of GDP.
    A positive value means gross debt rose by more than the deficit plus
    interest--growth dynamics imply (debt-increasing other-means-of-financing
    operations); a value near zero means the flow accounting closes cleanly.
    Its history is informative---it is large and persistent for the high-debt
    blocs (Table values of order $+2$ to $+4$\% of GDP for JP, UK, CA, CN)---and,
    crucially, its \emph{forecast} now feeds the debt projection, so a
    persistently positive SFA pushes the projected debt path \emph{above} what
    the deficit alone would deliver.
\end{itemize}
A further row holds the \emph{derived} reporting variables produced by the
accounting recursion, in the order
\begin{enumerate}[label=(\roman*)]
  \item \textbf{Primary Balance} ($\mathit{pb}_t$, \% of GDP), which is
    itself conditionable: the user can drag a primary-balance path and
    the tool maps it back to the $\mathit{rev}-\mathit{primexp}$
    linear combination;
  \item \textbf{$\Delta$ Debt-to-GDP} ($\Delta d_t$, percentage points
    per quarter), the per-quarter debt change of
    \eqref{eq:fiscal_snowball}, which is not directly conditionable
    because it is a pure identity output;
  \item \textbf{Debt-to-GDP} ($d_t$, \% of GDP), the rolled-forward
    stock, which can be targeted via the inversion of
    Section~\ref{sec:fiscal_inversion}. Note that this projection now
    \emph{carries the forecast SFA forward} (with dynamics and bands): a bloc
    with a large positive estimated SFA will show a debt path that drifts up
    faster than its primary balance and snowball alone explain, which is the
    intended, honest behaviour.
\end{enumerate}
Separating the estimated drivers (effective rate, SFA, revenue, expenditure)
from the derived balances and debt makes the stock-flow-consistent structure
visible on screen: what the data and the prior speak to is shown as an
input, and what the budget identity implies is shown as an output.

\subsection{Data Treatment: the U.K.\ Index-Linked-Gilt Spike}\label{sec:fiscal_data}

Interest series constructed from accrued interest can contain
mechanical, non-recurring spikes that are not informative about the
underlying refinancing cost.  In the United Kingdom, the large stock of
\emph{index-linked gilts} produced an interest spike in 2008--09:
the inflation uplift on the principal of index-linked debt is recorded as
accrued interest, so the 2008 inflation spike (and its subsequent
unwinding) translated into an outsized swing in the measured effective rate
\texttt{EFFI} that would otherwise contaminate the BVAR's autoregressive
dynamics.  These quarters are handled with the same machinery used for
the COVID-19 observations: the affected effective-rate entries are set to
missing (\texttt{NaN}) and imputed by the Kalman filter inside the
data-augmentation Gibbs sampler, rather than being allowed to enter the
likelihood as if they were ordinary observations.  This keeps the
estimated effective-rate process---and hence the derived interest bill
and debt path---free of a one-off accounting artefact while preserving
the genuine information in the surrounding quarters.

\section{Long-Run Targets: In-Prior Prior vs the Forward-Pass Drift Setter}\label{sec:longrun}

The forecasts of Section~\ref{sec:kalman} inherit their long-run
behaviour entirely from the estimated VAR. Because the real-activity
and price blocks are estimated on $100\ln$ levels of $I(1)$ series, the
companion matrix~\eqref{eq:companion} carries roots on or near the unit
circle, and the implied long-horizon central path can drift away from
any value the user regards as a credible steady state (e.g.\ a $2\%$
inflation objective, a neutral policy rate, or a balanced great ratio).
The tool exposes a \emph{long-run target} control that lets the user
pin the long-horizon forecast of a chosen variable to a target. We
support two conceptually distinct mechanisms, summarized in
Table~\ref{tab:plr-vs-tilt}: an \emph{in-prior} long-run prior applied
\emph{before} estimation (computed offline), and an
\emph{after-estimation forward-pass drift setter} that maps each target
to a constant shift of the companion drift and is applied instantly in
the browser. The latter is the user-facing control and \emph{replaces}
the earlier entropic-tilt mechanism (Remark~\ref{rem:tilt_retired}).

\subsection{In-Prior Long-Run Prior (PLR)}\label{sec:plr}

The first mechanism is the ``prior for the long run'' (PLR) of
\citet{GiannoneLenzaPrimiceri2019}, which augments the hierarchical
Minnesota prior of Section~\ref{sec:prior} with additional dummy
observations that shrink a small set of linear combinations $H y$
toward stationarity (no-cointegration / random-walk behaviour). Let
$H \in \R^{q \times n}$ collect $q$ long-run combinations and let
$y_0$ be the prior pre-sample mean. Following the authors' construction,
$H$ is rotated into a full-rank basis $\bar H = \bigl(H';\, \mathrm{null}(H)'\bigr)'$
with inverse $\bar H^{-1}$, and for each active long-run row $j$ a single
dummy observation
\begin{equation}\label{eq:plr_dummy}
  y^d_j = \frac{(y_0 \bar H')_j}{\phi_j}\, \bigl(\bar H^{-1}\bigr)_{\cdot j}',
  \qquad
  x^d_j = \Bigl(0,\; \tfrac{(y_0 \bar H')_j}{\phi_j}\,
    \mathbf{1}_p \otimes \bigl(\bar H^{-1}\bigr)_{\cdot j}'\Bigr),
\end{equation}
is appended \emph{to the regression system} (both the Gibbs draw and the
marginal-likelihood normalizing constant $T_d$), with $\phi_j$
controlling the tightness of the $j$-th long-run restriction. Crucially,
\eqref{eq:plr_dummy} combines the \emph{equations} through the columns of
$\bar H^{-1}$; combining the regressors instead produces a dummy whose
residual is identically zero at the sum-of-coefficients mode and hence
carries no tightness information. The tightness hyperparameters $\phi_j$
are held fixed so that the Metropolis--Hastings search over the Minnesota
$\lambda$ and the sum-of-coefficients $\mu$ remains two-dimensional.

The PLR is a \emph{proper Bayesian prior}: it modifies the posterior and
requires re-estimation. It is therefore computed offline as part of the
data-export pipeline, not in the browser.

\begin{remark}[What the PLR actually does in the US sample]
\label{rem:plr_findings}
A US head-to-head ($n=36$, $p=3$, COVID treated as missing per
Section~\ref{sec:uncertainty}, $q=13$ long-run combinations comprising
six great ratios, three nominal anchors, and four rate/credit spreads)
shows that the PLR is a \emph{separate dummy block} rather than a change
to the Minnesota tightness: the maximizing $\lambda$ is essentially
unchanged ($0.563$ baseline vs $0.562$ with the PLR at either
$\phi=1.0$ or $\phi=0.1$). Because the sum-of-coefficients-style dummy
in~\eqref{eq:plr_dummy} shrinks toward a \emph{random walk} (no
cointegration), and the US sample treats most of these ratios as
genuinely $I(1)$, the PLR does \emph{not} pull the long-run central
forecast toward a historical mean: the mean absolute drift of the
$H{=}40$ forecast from a recent historical anchor moves from $8.49$
(baseline) to $8.41$ at $\phi=1.0$ ($-1\%$), and is marginally
\emph{worse} at $\phi=0.1$. The visible effect is on the \emph{bands},
not the path: the GDP-growth $68\%$ band tightens from $4.24$ to
$3.95$ percentage points ($\approx 7\%$) at $\phi=1.0$. The PLR is thus
the appropriate instrument for principled band tightening and a soft
no-cointegration restriction; it is \emph{not} a device for pinning a
long-run combination to a chosen number.
\end{remark}

\subsection{The Forward-Pass Drift Setter ($\delta c$)}\label{sec:driftsetter}

The user-facing mechanism, exposed in the interface as the
\textbf{Long-run targets} panel (Section~\ref{sec:interface}), does
\emph{not} re-estimate the model and does \emph{not} reweight the draws.
It is a deterministic \emph{counterfactual on the companion drift} in
the spirit of \citet{Villani2009}: the user states where a variable's
long-run forecast should land, and the tool solves for the single
constant shift of that variable's own equation that places it there,
then applies the resulting system response as a cheap, exact overlay on
top of the precomputed paths and bands. It is instant (no Compute, no
re-solve), exact (the terminal forecast hits the target by
construction), and fully reversible (an unmoved slider is a byte-exact
no-op).

\paragraph{The finite-horizon response operator.}
Write the companion recursion~\eqref{eq:transition} in level space as
$Y_t = c + T\,Y_{t-1} + \varepsilon_t$, with $T$ the companion matrix
and $c$ the companion drift (the constant row of the estimated
coefficients). Switching innovations off, the $h$-step deterministic
forecast is
\begin{equation}\label{eq:driftsum}
  Y_{T+h} = T^{h}\,Y_T + S_h\,c,
  \qquad
  S_h = \sum_{k=0}^{h-1} T^{k},
\end{equation}
where $S_h$ is the partial sum of companion powers. A shift $\delta c$
of the drift moves the entire forecast path by \emph{exactly}
$\Delta Y_{T+h} = S_h\,\delta c$; this is an algebraic identity, not an
approximation (verified to $10^{-11}$ against the iterated recursion).
We deliberately do \emph{not} use the closed-form steady state
$Y^\star = (I - \sum_\ell B_\ell)^{-1} c$. For the near-unit-root level
VARs the matrix $(I - \sum_\ell B_\ell)$ is near-singular, so $Y^\star$
is a meaningless quantity of order $10^5$, whereas the finite-horizon
operator $S_H$ in~\eqref{eq:driftsum} is well-posed. This is precisely
the object that makes the construction work on the random-walk-in-levels
BVAR, whose exact steady state does not exist.

\paragraph{One slider, one equation.}
A long-run target on variable $j$ is imposed by shifting \emph{only}
$j$'s own equation, $\delta c = e_j\,\delta c_j$. The coherent
system-wide response is then the $j$-th column of the response operator,
\begin{equation}\label{eq:driftcol}
  \Delta Y_{T+h} = S_h[:,\,j]\;\delta c_j
  \qquad\text{for \emph{all} variables.}
\end{equation}
The scalar $\delta c_j$ is chosen so that variable $j$'s
\emph{displayed} terminal forecast (Section~\ref{sec:units}) equals the
user's target $\psi^\star_j$. Let $\mathrm{sens}_j$ be the
display-unit sensitivity of $j$'s terminal forecast to a unit
$\delta c_j$:
\begin{equation}\label{eq:driftsens}
  \mathrm{sens}_j =
  \begin{cases}
    4\bigl(S_H[j,j] - S_{H-1}[j,j]\bigr), & \texttt{log} \text{ var (display}=4\,\Delta\text{level)},\\[2pt]
    S_H[j,j], & \texttt{lin} \text{ var (display}=\text{level)},
  \end{cases}
  \qquad
  \delta c_j = \frac{\psi^\star_j - \psi^{\,0}_j}{\mathrm{sens}_j},
\end{equation}
where $\psi^{\,0}_j$ is the variable's \emph{current} terminal display
forecast --- the slider's default thumb. Setting
$\psi^\star_j = \psi^{\,0}_j$ gives $\delta c_j = 0$ and hence
$\Delta Y \equiv 0$: an unmoved slider is an exact, byte-identical
no-op.

\paragraph{Joint long-run restriction.}
When \emph{several} sliders are moved at once a naive per-anchor
superposition --- solving each $\delta c_j$ from~\eqref{eq:driftsens} in
isolation and adding the columns of~\eqref{eq:driftcol} --- is
\emph{incoherent}: a $\delta c_j$ on equation $j$ also shifts every other
anchored variable's terminal through the off-diagonal cross-response
$S_H[k,j]$, so the displayed terminals no longer land on their targets.
A stationary, low-sensitivity anchor (e.g.\ a fiscal-block ratio with a
near-zero own-$\mathrm{sens}_j$, hence a large $\delta c_j$) can drag a
macro target arbitrarily far off. The tool therefore imposes all enabled
targets \emph{jointly}, as a single linear long-run restriction. Let
$\mathcal{K}$ be the anchored equations that pass the sensitivity guard,
and define the display-unit response matrix $M$ by
\begin{equation}\label{eq:driftjoint}
  M_{kj} =
  \begin{cases}
    4\bigl(S_H[k,j] - S_{H-1}[k,j]\bigr), & k \in \mathcal{K}\ \texttt{log},\\[2pt]
    S_H[k,j], & k \in \mathcal{K}\ \texttt{lin},
  \end{cases}
  \qquad
  M\,\delta c = \psi^\star - \psi^{\,0},
  \quad k,j \in \mathcal{K}.
\end{equation}
The diagonal $M_{kk}$ is exactly the own-sensitivity
$\mathrm{sens}_k$ of~\eqref{eq:driftsens}, so a single anchor
($|\mathcal{K}|=1$) reduces~\eqref{eq:driftjoint} to the scalar
$\delta c_k = (\psi^\star_k - \psi^{\,0}_k)/\mathrm{sens}_k$, and
$\psi^\star \equiv \psi^{\,0}$ (all targets at their estimates) gives
$\delta c \equiv 0$ exactly --- the byte-identical no-op survives. The
system is solved by Gaussian elimination with partial pivoting; the
$\delta c$ are then superposed back through~\eqref{eq:driftcol} as
before, so \emph{every} anchored terminal hits its target
\emph{simultaneously}.

\paragraph{Per-variable vs.\ joint (user toggle).}
The exact joint solve is well-posed only when the anchored variables'
terminal responses are linearly well separated. For a \emph{near-collinear}
anchor set --- e.g.\ two anchored interest rates that the estimated
dynamics cannot move independently in the long run --- $M^{-1}$ produces
huge \emph{offsetting} $\delta c$'s that hit the $|\mathcal{K}|$ terminals
exactly while wrecking the path everywhere else (on one estimated bloc the
exact solution required $|\delta c|\approx 459$ where the per-anchor
diagonal needed $\approx 11$). The tool therefore exposes a \emph{solve-mode
toggle} (shown once two or more targets are set):
\begin{itemize}
\item \textbf{Per-variable} --- each $\delta c_k = (\psi^\star_k -
\psi^{\,0}_k)/\mathrm{sens}_k$ set independently from its own diagonal
sensitivity. \emph{Stable} and bounded (the drift can never blow up), but
\emph{approximate}: it ignores the off-diagonal cross-responses, so it
\emph{underestimates the spillovers} and the other anchored terminals drift
off their set values by the cross-drag.
\item \textbf{Joint} --- the full $M\,\delta c = \psi^\star -
\psi^{\,0}$ system, so \emph{every} anchored terminal lands exactly on its
value. \emph{Correct at the terminal}, but a strongly-correlated target set
makes $M$ ill-conditioned and can \emph{destabilise} the path; the tool
flags that case and the user switches to per-variable. A genuinely singular
$M$ falls back to the per-variable $\delta c$ numerically (never a NaN path).
\end{itemize}
Both modes reduce to the same scalar for a single target
($|\mathcal{K}|=1$), and $\psi^\star \equiv \psi^{\,0}$ is a byte-exact
no-op in either. The shipped default anchor sets are deliberately kept to a
\emph{bare minimum} --- since the July-2026 anchor review, 32 anchors across
23 economies, each individually verified to fix a genuine terminal-bias
pathology while keeping the anchored path inside the economy's own
(COVID-masked) historical envelope, with no origin discontinuity and no
$>$1\,pp cross-drag onto unanchored headline variables
(\texttt{docs/anchor-review-2026-07.md}) --- so the joint system stays well
conditioned out of the box. Well-conditioned is not the same as well-shaped, however: because
$\delta c$ is a \emph{rigid translation} of the whole path, joint exactness
at the terminal is bought with a front-loaded near-term shift, and when the
model's own terminal sits far from the anchor the first forecast years can
be pushed to implausible values even under the bare-minimum set (at the
2026\,Q1 origin the US deflator --- model terminal $4.3$ against the $2.0$
anchor --- displayed \emph{negative} inflation over the first two forecast
years under joint, against $+1.7$ under per-variable). \textbf{Per-variable
is therefore the shipped default} --- stable and near-term-plausible, at the
cost of terminals that land only approximately --- and joint is the
deliberate opt-in for users who need every anchor met exactly and accept
the near-term reshaping.

\paragraph{Rigid band translation.}
The deviation $\Delta Y$ of~\eqref{eq:driftcol} is added \emph{identically}
to the mean level path and to \emph{every} shipped quantile
($q_{05},q_{16},q_{50},q_{84},q_{95}$) of both the baseline and the
scenario fans. The forecast distribution is therefore translated
rigidly: band widths are provably invariant and the quantile ordering
cannot be reordered or rescaled by an additive shift. This is what makes
the overlay safe to apply on top of the precomputed bands of
Section~\ref{sec:uncertainty} without recomputing them, and it is the
qualitative difference from a reweighting scheme, which deforms the
density. The same $\Delta Y$, in level space, is forwarded into the
fiscal recursion (Section~\ref{sec:fiscal}) so the debt path responds
coherently to the new macro long run.

\paragraph{Responsiveness.}
Building $\{S_h\}_{h=1}^{H}$ costs $O(H)$ companion mat-muls and is done
once per bloc on load (a few milliseconds, then cached). Every
subsequent slider move is a single cached mat-vec add~\eqref{eq:driftcol}
and a rigid translation of the bands --- no draw loop, no Kalman
re-smooth, no GVAR re-solve. The sliders are therefore as responsive as
the drag interaction: the chart updates on every pointer move.

\paragraph{The policy rate.}
Because the policy rate is an ordinary \texttt{lin} variable of the VAR,
it carries its own long-run-target slider like any other series: the
user sets the terminal rate directly through the drift setter. There is
no separate Taylor-rule rate overlay --- the rate's long run is governed
solely by its own slider, consistent with every other variable.

\begin{remark}[Honest caveats, surfaced in the panel]
\label{rem:drift_caveats}
The drift setter shifts the long-run \emph{drift}, not the model's
\emph{persistence}; the sliders are accordingly labelled ``long-run
target'' rather than ``mean reversion'', and they do not add a new
attractor to the dynamics. The cross-variable response $S_h[:,j]$
in~\eqref{eq:driftcol} drags the other variables along the
\emph{estimated} dynamics --- a genuine model side effect, not a bug.
Most consequentially, the \emph{real-growth} target owns the direction
of the debt path through the $(i-g)$ snowball, so it is labelled
distinctly (``long-run real growth target'') and the panel states
explicitly that it is not a structural debt fix. Finally, a variable
whose sensitivity~\eqref{eq:driftsens} is near-singular
($|\mathrm{sens}_j| < 0.3$, the \texttt{SENS\_GUARD}) yields an
ill-conditioned $\delta c_j$ and its slider is disabled.
\end{remark}

\begin{remark}[On a GVAR bloc the target is marginal]
\label{rem:drift_gvar}
The drift setter operates on a \emph{single} bloc's companion. On a
GVAR-linked economy it shifts \emph{that bloc's own} long-run forecast;
the trade partners and the US-determined global commons
(Section~\ref{sec:gvar:commons}) are not re-solved, so the realised
joint long-run value can differ from the marginal target. The panel
states this caveat when a GVAR bloc is selected. A fully joint
re-anchoring of the cross-country fixed point is left for future work.
\end{remark}

\begin{remark}[Why the entropic tilt was retired]
\label{rem:tilt_retired}
An earlier release pinned the long run by an after-estimation
\emph{entropic tilt} --- a relative-entropy reweighting of the posterior
draws \citep{RobertsonTallmanWhiteman2005} so that the weighted
$H$-step moment matched the target. It was correct in principle but
degenerated in practice: as a target was pushed away from the draw-cloud
mean the importance weights concentrated and the effective sample size
$\mathrm{ESS} = 1/\sum_d w_d^2$ collapsed toward $1$ (with $D=500$ draws,
a \emph{joint} $13$-constraint tilt fell to $\mathrm{ESS}\to 1$ because
the joint target lay outside the convex hull of the draws), so the pinned
band rested on a handful of draws and was unreliable exactly where the
user most wanted a firm anchor. It was also slow: it required a draw
cloud and a Newton solve in the browser. The forward-pass drift setter
replaces it wholesale --- it is deterministic (no $\mathrm{ESS}$ to
collapse), exact at any target, instant, and band-coherent by
construction --- and the tilt control has been removed from the
interface.
\end{remark}

\begin{remark}[Model-based vs.\ with-judgement, and a consensus preset]
\label{rem:judgement_consensus}
The drift setter induces a natural per-variable flag. With every slider at
its model estimate the displayed forecast is purely \emph{model-based}
($\delta c=0$, an exact no-op); the moment a target is set the variable
becomes \emph{with-judgement} and the panel marks it as such (a highlighted
target, a reset-to-estimate control, and an \texttt{$N$ targets $\cdot$
exact} badge). The flag is per-country and per-variable --- a single chart
grid may mix purely model-based series with judgemental ones --- and is
cleared on a country switch. To make a transparent judgemental starting
point one click away, blocs with publicly-defensible long-run values carry
a \emph{consensus-anchors} preset, deliberately kept to a \emph{bare
minimum}: potential growth and the central-bank inflation objective per
economy, plus the effective-rate/revenue/expenditure fiscal trio for the
six fiscal-block economies (the values of \S\ref{sec:driftsetter}). No
policy or market rates, unemployment, house prices or spreads are anchored
by default --- collinear anchored rates make the joint long-run system
ill-conditioned (see the tameness guard of \S\ref{sec:driftsetter}) and
those long runs stay model-driven. The preset seeds enabled so the big-6
debt trajectories display their realistic slope out of the box, and it is
fully reversible to model-based (clearing the anchors is a byte-exact
no-op).
\end{remark}

\subsection{When to Use Which}\label{sec:plr_vs_tilt_choice}

The two surviving mechanisms are complementary. The in-prior PLR is the
gold standard --- a proper offline posterior --- but its
data-decides property means that, at the tightnesses examined, it leaves
the US central long-run forecast essentially unchanged and acts mainly on
the bands. The forward-pass drift setter is in-browser, requires no
re-estimation, and \emph{forces} the displayed long-run forecast onto an
explicit target by construction, with rigidly translated bands and no
degeneracy. As a rule of thumb: to \emph{pin} a variable's long run to a
number interactively, use the drift setter; for principled band
tightening and a soft no-cointegration restriction, use the PLR (offline).

\begin{table}[H]
\centering
\caption{Long-run targets: in-prior PLR versus the forward-pass drift
setter.}\label{tab:plr-vs-tilt}
\begin{tabular}{lll}
\toprule
 & \textbf{In-prior PLR} & \textbf{Drift setter ($\delta c$)} \\
\midrule
Source        & \citet{GiannoneLenzaPrimiceri2019} & \citet{Villani2009} \\
Acts on       & prior (dummy obs.) & companion drift $c$ (forward pass) \\
Re-estimation & yes (offline) & no (in-browser, instant) \\
Object        & proper posterior & deterministic counterfactual \\
Target        & $Hy$ stationarity & terminal display forecast $\psi^\star_j$ \\
Bands         & tightened & rigidly translated (widths invariant) \\
Main effect   & tightens bands & shifts central path to the target \\
Failure mode  & none (proper) & slider disabled if $|\mathrm{sens}_j|<0.3$ \\
\bottomrule
\end{tabular}
\end{table}

\section{Economy Coverage, Data Sources, and Estimation}\label{sec:variables}

The tool ships estimated BVARs for roughly fifty economies. Thirty-three
of them are integrated into a single \emph{Global VAR} (GVAR) system
\citep{PesaranSchuermannWeiner2004, DeesDiMauroPesaranSmith2007}
covering approximately 90\% of world GDP; the remaining blocs---including the
$17$ euro-area member states, which are deliberately kept out of the coupled
system because a disaggregated euro GVAR is non-stationary---are
standalone single-country models that share the same estimation
machinery but are not wired into the cross-country fixed point.
This section documents the roster, the underlying data, the
COVID-as-missing estimator, the common-vintage harmonization, and the
construction of the predictive bands. Throughout, variables enter the
VAR in the $100\ln(\cdot)$ space for \texttt{log} series and in levels
for \texttt{lin} series (Section~\ref{sec:units}); annualized
quarter-over-quarter growth and inflation are reported as
$4\times\Delta(100\ln)$, consistent with~\eqref{eq:growth}
and~\eqref{eq:scale}.

\subsection{The GVAR System: 33 Integrated Blocs}\label{sec:gvar-roster}

The GVAR comprises the United States---now a fully endogenous coupled bloc, not a
frozen anchor (Section~\ref{sec:gvar:arch})---the euro area as a single aggregate
bloc, plus $31$ further Rest-of-World (RoW) blocs:
\begin{quote}
US; EA (euro-area aggregate), JP, UK, CA, CN (the core majors); CH, KR,
MX, AU, TR, SE, PL, NO, DK, IN, BR, RU, ID, SA, AR, ZA, TH, MY; and the nine
further non-euro economies CL, CO, CR, CZ, HU, IL, IS, NZ, TW added in the OECD
expansion.
\end{quote}
The euro area enters as one aggregate bloc by necessity: a fully disaggregated
euro GVAR is non-convergent ($\rho(M)\approx 1.089 > 1$), and treating the euro
area as a single bloc restores stationarity. The $17$
euro-area members are consequently \emph{standalone} models
(Section~\ref{sec:standalone}), not coupled GVAR blocs.
Each bloc---the US included---is an independently estimated single-country BVAR
in which the foreign sector is summarized not by a raw foreign-variable
block but by three trade-weighted RoW ``star'' variables, following the
GVAR tradition of \citet{PesaranSchuermannWeiner2004} and
\citet{DeesDiMauroPesaranSmith2007}:
\begin{itemize}
  \item \texttt{ROWDEM} --- foreign demand: the trade-weighted average
    of partners' real-GDP growth;
  \item \texttt{ROWINF} --- foreign inflation: the trade-weighted
    average of partners' price inflation;
  \item \texttt{ROWFIN} --- foreign financial conditions: the
    trade-weighted average of partners' short rates.
\end{itemize}
For bloc $c$ with partner set $\mathcal{P}_c$ and weights $w_{cj}$, the
demand and inflation stars are built in annualized growth space from the
partners' stored $100\ln$ levels,
\begin{equation}\label{eq:star}
  \mathrm{ROWDEM}_{c,t} = 4 \times
  \frac{\sum_{j\in\mathcal{P}_c} w_{cj}\,
        \bigl(x^{g}_{j,t} - x^{g}_{j,t-1}\bigr)}
       {\sum_{j\in\mathcal{P}_c} w_{cj}\,\mathbb{1}\{x^{g}_{j,t},x^{g}_{j,t-1}\ \text{observed}\}},
\end{equation}
where $x^{g}_{j,t}$ is partner $j$'s real-activity level (analogously for
\texttt{ROWINF} from prices, and \texttt{ROWFIN} from the level of the
short rate). Weights are \emph{renormalized per component} over the
partners actually observed in each quarter, so a partner that is missing
a given series simply drops out of the corresponding star and the
remaining weights are rescaled. Two implementation details matter for
the econometrician: China's reported GDP is nominal, so its
real-activity level is formed by subtracting the price level in $100\ln$
space, $x^{g}_{\mathrm{CN}} = x^{\mathrm{NGDP}}_{\mathrm{CN}} -
x^{P}_{\mathrm{CN}}$ (a log-space deflation); and Argentina's 2023--24
hyperinflation episode is excluded from the \texttt{ROWINF} and
\texttt{ROWFIN} aggregates of its partners (its genuine real demand is
retained in \texttt{ROWDEM}), with renormalization absorbing the dropped
weight.

\paragraph{Trade weights.} Bilateral weights $w_{cj}$ are constructed
from goods-trade flows in the IMF International Trade in Goods statistics
(IMTS, the renamed bilateral DOTS), queried from the SDMX~2.1 endpoint
\texttt{api.imf.org} over the 2021--2023 average of exports
(\texttt{XG\_FOB\_USD}) plus imports (\texttt{MG\_CIF\_USD}). The Euro
Area is treated as a single counterpart (IMTS aggregate code
\texttt{G163}). The weight matrix is row-normalized over the 33 blocs
with a zero diagonal; now that the US is endogenous it carries its own
trade-weights row, so all $33$ blocs have a row.

\paragraph{Rate-optional blocs.} The short rate is \emph{optional}: a
GDP series and a price series are required of every bloc, but two blocs
(Switzerland and Norway) carry no domestic short rate. Their rate column
is \texttt{NaN} throughout, they are excluded from their partners'
\texttt{ROWFIN} aggregate, and the \texttt{ROWFIN} weights of any bloc
having them as a partner are renormalized accordingly. They still
contribute to \texttt{ROWDEM} and \texttt{ROWINF}.

\paragraph{Cross-country coupling.} As in Section~\ref{sec:variables}'s
original treatment, the baseline forecast of each bloc is computed
independently; cross-country coupling enters only through the scenario
layer. A shock conditioned in one bloc perturbs its star variables,
which propagate to its trade partners, whose own stars then feed back.
Stacking the per-bloc deviations $\Delta$ yields the linear fixed point
\begin{equation}\label{eq:gvar-fixedpoint}
  \Delta = M\,\Delta + d,
\end{equation}
where $M$ encodes the trade-weighted star couplings together with the four
US-determined global commons (the spot oil price, the US 10-year yield, the US
Baa corporate yield, and US equity; Section~\ref{sec:gvar:commons}) and $d$
collects the user's direct conditioning forcing. With the US endogenous the
deviation state is \emph{augmented} to carry the US global-column deviations as
unknowns (Section~\ref{sec:gvar:fixedpoint}), so the global commons close the
RoW$\to$US feedback loop inside $M$ rather than entering $d$ as a frozen forcing.
The system is solved at display time both by a direct $(I-M)^{-1}d$ evaluation
and by Neumann sweeps (summing $\sum_k M^k d$); the two agree to $\sim 10^{-9}$.
The coupling is contractive, with spectral radius $\rho(M)\approx 0.924$, so
the series converges. Because the full $2060\times2060$ $(I-M)^{-1}$
inverse is expensive in-browser (a cold build is on the order of three-quarters
of an hour), it is precomputed offline and shipped as a \emph{gzipped} coupling
cache (\texttt{coupling\_default.json.gz}, about $30$\,MB compressed),
decompressed in the browser via the native \texttt{DecompressionStream} API.
The interactive interface uses a two-tier solve---a fast direct preview on drag
and an explicit ``Solve full GVAR'' button for the complete fixed point---to keep
the endogenous-US solve reactive (Section~\ref{sec:gvar:solvemode}).

\subsection{Standalone Single-Country Blocs}\label{sec:standalone}

Beyond the 33 GVAR blocs, the tool ships additional single-country BVARs
estimated by the same procedure but not coupled into~\eqref{eq:gvar-fixedpoint}.
Together with the GVAR members these complete coverage of all 38 OECD
members and add several large non-OECD emerging markets. The standalone
remainder is dominated by the $17$ \emph{euro-area member states} (DE, FR, IT,
ES, NL, AT, BE, FI, GR, IE, LU, PT, SI, SK, EE, LT, LV), which are kept out of
the coupled GVAR \emph{by construction}: the euro area is represented in the
GVAR by the aggregate \texttt{EA} bloc, because a disaggregated euro GVAR is
non-stationary ($\rho(M)\approx 1.089 > 1$) whereas aggregating the euro area
restores convergence. Each euro member is nonetheless estimated as a full
single-country model---its domestic block augmented by the four global commons
and by trade-weighted foreign \emph{star} variables---but in \emph{separation}
(with the GVAR iteration count fixed to \texttt{MAXIT}~$=1$, so its foreign
stars are read off data rather than from a cross-country solve) and it carries no
trade-weights row. The country selector groups the roster into two sections, a
\emph{GVAR} group and an \emph{Other countries} group; a bloc is GVAR-linked, and
hence placed in the \emph{GVAR} group, if and only if it has a trade-weights row
and its specification carries the three \texttt{ROW*} star variables.

\subsection{Data Sources}\label{sec:datasources}

No single provider supplies current quarterly real GDP for the full
roster, so the data are assembled bloc-by-bloc from a small number of
authoritative source families. Each bloc's variables are wired to a
specific provider series by the per-bloc build scripts
(\texttt{pipeline/build\_*.py}; the US source registry lives in
\texttt{app/scripts/refresh-quarter.mjs}), and the exact provider series
behind every shipped variable is recorded in the machine-readable
\emph{coverage manifest} (\texttt{app/public/data/coverage\_manifest.json}),
from which the coverage matrix of Section~\ref{sec:coverage-matrix} is
generated.

\paragraph{Source families.} The classification of each bloc to its
primary source family is anchored on its real-GDP series; the resulting
split is \textbf{2~FRED} (US, CN), \textbf{25~Eurostat} (EU members plus
the EFTA economies CH/IS/NO), and \textbf{23~OECD/FRED} (the remaining
OECD members and FRED-sourced emerging markets, including CA, UK, JP).

\begin{itemize}
  \item \textbf{FRED (St.\ Louis Fed).} The US block ($n=41$,
    Table~\ref{tab:vars}) is pulled in full from FRED with exact series
    IDs (e.g.\ \texttt{GDPC1} real GDP, \texttt{PCEPI}/\texttt{CPIAUCSL}
    prices, \texttt{FEDFUNDS} policy rate, \texttt{DGS10} 10-year yield,
    \texttt{UNRATE} unemployment, \texttt{CSUSHPISA} house prices). The
    China bloc is built entirely from verified real FRED series, with
    quarterly real activity anchored by industrial production since clean
    quarterly \emph{real} GDP is not available on FRED for China (only
    annual constant-price GDP and nominal quarterly GDP that ends early ---
    the documented China real-GDP trap). Cross-bloc, FRED also supplies
    the US-determined global commons (\texttt{GLB\_OIL} from
    \texttt{WTISPLC}, \texttt{GLB\_USLR} from \texttt{DGS10},
    \texttt{GLB\_USBAA} from \texttt{BAA}, \texttt{GLB\_USEQ} from the US
    equity index) and the BIS credit-to-GDP and residential-property-price
    series re-distributed through FRED (\texttt{Q<ISO2>NAM770A},
    BIS~RPP).
  \item \textbf{Eurostat.} The IMF's thematic SDMX API exposes no
    per-country quarterly chain-volume GDP (its national-accounts flow
    carries current-price values only, for a limited country set), so the
    EU/EFTA economies are sourced from Eurostat: \texttt{namq\_10\_gdp}
    chain-linked volumes (GDP and the expenditure components),
    \texttt{prc\_hicp\_midx} HICP, \texttt{une\_rt\_q} unemployment,
    \texttt{irt\_st\_q}/\texttt{irt\_lt\_mcby\_m} short and long interest
    rates, \texttt{ert\_eff\_ic\_q} NEER, and \texttt{prc\_hpi\_q} house
    prices. Euro-area members carry the ECB policy rate (deposit facility)
    and ECB MIR lending rate rather than the generic BIS series.
  \item \textbf{OECD QNA and national sources.} The non-EU OECD members
    and FRED-sourced emerging markets (e.g.\ CA, UK, JP, AU, NZ, KR, MX,
    BR, ZA, T\"urkiye, Chile) draw real GDP and national accounts from the
    OECD Quarterly National Accounts (largely re-distributed on FRED),
    short/policy rates from national-bank or BIS \texttt{CBPOL} series
    (e.g.\ RBA/RBNZ cash rates), CPI and unemployment from national/OECD
    flows, and NEER where available.
  \item \textbf{IMF WEO (back-fill only).} Where genuine quarterly real
    activity or prices end short of the common estimation window, the
    Step-1 harmonization of Section~\ref{sec:vintage} temporally
    disaggregates IMF World Economic Outlook annual projections
    (\texttt{NGDP\_RPCH}, \texttt{PCPIPCH}) to fill the gap. WEO is a
    \emph{back-fill of last resort}, used only for the macro tail of blocs
    whose national source lags; it never overrides observed data and is
    flagged wherever it is the live tail (CN/IN; see below).
  \item \textbf{Derived series.} The three rest-of-world ``star''
    variables (\texttt{ROWDEM}/\texttt{ROWINF}/\texttt{ROWFIN}), the
    fiscal effective-interest rate (\texttt{EFFI}) and stock-flow
    adjustment (\texttt{SFA}), and the rest-of-euro-area aggregates
    (\texttt{ROWEA\_*}) are not pulled from a provider but \emph{computed}
    from other series (trade-weighted partner aggregates; the debt
    recursion residual of Section~\ref{sec:fiscal_identity}).
\end{itemize}

\paragraph{Coverage and last-observation conventions.} Coverage start
varies by bloc and series (typically the mid-1990s to mid-2010s; the US
sample is the longest); coverage end is the bloc's last historical
quarter, governed by the ragged edge of Section~\ref{sec:vintage}. The
\emph{default} last observation is \textbf{2026Q1}; \texttt{CN} and
\texttt{IN} are held at \textbf{2025Q4} and \texttt{IL} at \textbf{2024Q4}.
Within a bloc, all core macro variables share the same trailing endpoint
(the only interior gaps are the COVID 2020Q2--2021Q1 macro mask of
Section~\ref{sec:covid} and the credit/SFA seed gaps), so the last
\emph{balanced} observation equals the last historical quarter for every
bloc. Real-versus-nominal GDP is handled per bloc: every fiscal bloc now
carries a chain-volume real GDP series used directly --- China was
re-sourced to a real chain-linked SA volume index (base 2011Q1=100) in the
June-2026 endogenous-US 33-bloc re-estimate, replacing the earlier nominal
proxy; and thin or volatile samples are estimated with deliberately wide,
honest predictive bands rather than spuriously tight ones.

\paragraph{Provenance flags surfaced for the reader.} Two classes of tail
are flagged explicitly, both consistent with the no-fabrication rule:
\begin{itemize}
  \item \textbf{WEO back-fill (confirmed) --- \texttt{CN}, \texttt{IN}.}
    The domestic macro tail to 2025Q4 is the WEO temporal-disaggregation
    of Section~\ref{sec:vintage}, held ragged and never observed. CN's GDP
    series is the nominal-GDP / industrial-production proxy (the China
    real-GDP trap above).
  \item \textbf{Source-review (flagged, not rebuilt) --- \texttt{KR},
    \texttt{RU}, \texttt{ID}, \texttt{TH}.} For these blocs the GVAR
    pipeline's genuine national/OECD-FRED source ended earlier
    (KR/RU $\approx$2024Q1, ID/TH $\approx$2025Q1) and was WEO-extended in
    the 2025Q4 build, yet the shipped panels carry a 2026Q1 endpoint; June
    credit/policy-rate rebuilds also touched these blocs. Whether the
    shipped trailing quarters are a genuine refresh or the synthetic
    extension is \emph{not verifiable from the shipped data alone}, so
    these are surfaced as a \emph{source-review} flag for human
    verification rather than asserted or rebuilt. \texttt{KR}'s genuine
    domestic macro additionally derives from a frozen OECD-MEI-on-FRED
    mirror ($\approx$2023Q3 vintage) before any extension.
\end{itemize}
These flags appear in the last column of the coverage matrix
(Section~\ref{sec:coverage-matrix}) and as \texttt{blocFlags} in the
coverage manifest.

\subsection{COVID-as-Missing Estimation}\label{sec:covid}

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[
    >={Stealth[length=2.6mm]},
    font=\small,
    boot/.style={rounded corners=2pt, draw=black!70, fill=black!5,
                 align=center, inner sep=4pt, text width=3.4cm},
    estep/.style={rounded corners=2pt, draw=blue!60!black, fill=blue!6,
                  align=center, inner sep=5pt, text width=3.9cm},
    mstep/.style={rounded corners=2pt, draw=red!55!black, fill=red!5,
                  align=center, inner sep=5pt, text width=3.9cm},
    starbox/.style={rounded corners=2pt, draw=black!70, fill=black!4,
                 align=center, inner sep=5pt, text width=3.9cm},
    convbox/.style={rounded corners=2pt, draw=black!70, fill=black!4,
                 align=center, inner sep=5pt, text width=3.9cm},
    flow/.style={->, thick, black!75},
]
% --- US bootstrap: entry into the loop (seeds the first stars) ---
\node[boot] (boot) at (-7.4,2.6)
  {\textbf{US bootstrap}\\[1pt]
   \footnotesize closed anchor, no stars; a single
   \texttt{cgl\_bvarV5} fit DK-completes US GDP/price/rate to
   \emph{seed} the iter-1 stars};

% --- cycle nodes (clockwise: stars -> E -> M -> conv -> stars) ---
\node[starbox] (stars) at (0,2.6)
  {\textbf{Rebuild stars}\\[1pt]
   \footnotesize trade-weighted \texttt{ROWDEM}/\texttt{ROWINF}/%
   \texttt{ROWFIN} from partners' \emph{completed} panels,
   renormalized over the partners present each quarter};

\node[estep] (estep) at (4.0,0)
  {\textbf{E-step\,---\,DK completion}\\[1pt]
   \footnotesize Durbin--Koopman simulation smoother imputes the
   COVID 2020Q2--Q4 \emph{macro} holes (incl.\ \texttt{ROWDEM}/%
   \texttt{ROWINF}) and the ragged edges; financials and
   \texttt{ROWFIN} stay observed};

\node[mstep] (mstep) at (0,-2.6)
  {\textbf{M-step\,---\,GLP re-estimation}\\[1pt]
   \footnotesize \texttt{parfor} Bayesian VAR (\texttt{cgl\_bvarV5},
   $p{=}3$, hierarchical Minnesota/GLP) for \emph{every} bloc on the
   completed $[\text{domestic}\mid\text{stars}]$ panel};

\node[convbox] (conv) at (-4.0,0)
  {\textbf{Convergence check}\\[1pt]
   \footnotesize $\max|\Delta\,\texttt{star}| < \mathrm{TOL}{=}0.03$
   (excl.\ COVID-masked macro stars)?\\
   MC floor ${\approx}\,0.13$, $\mathrm{MAXIT}{=}12$};

% --- entry arrow ---
\draw[flow] (boot.east) -- node[above,font=\footnotesize]{seed} (stars.west);

% --- the clockwise cycle ---
\draw[flow] (stars.east)  to[bend left=20] (estep.north);
\draw[flow] (estep.south) to[bend left=20] (mstep.east);
\draw[flow] (mstep.west)  to[bend left=20] (conv.south);
\draw[flow] (conv.north)  to[bend left=20]
  node[above,font=\footnotesize]{not converged} (stars.west);

% --- converged exit ---
\node[align=center, font=\footnotesize] (out) at (-4.0,-2.7)
  {\textbf{converged}\\[-1pt]$\Rightarrow$ export 8-file JSON};
\draw[flow] (conv.south) -- (out.north);

% --- loop label ---
\node[font=\footnotesize\itshape, text=black!55, align=center] at (0,0)
  {GVAR--EM\\sweep $it$};
\end{tikzpicture}
\caption{The GVAR-EM estimation loop under pervasive missingness
\citep{GiannoneLenzaPrimiceri2019, DurbinKoopman2002}. A closed US
bootstrap (no stars) is estimated once to seed the first trade-weighted
foreign variables. Each sweep then (i)~rebuilds the
\texttt{ROWDEM}/\texttt{ROWINF}/\texttt{ROWFIN} stars from partners'
completed panels, renormalized over the partners present each quarter,
and (ii)~re-estimates every bloc by hierarchical-prior Bayesian VAR
(Gibbs, run in \texttt{parfor}). Within each bloc's single
\texttt{cgl\_bvarV5} pass the \textbf{E-step}---a Durbin--Koopman
simulation-smoother completion that imputes the COVID macro holes (the
fixed 2020Q2--Q4 window, with financial series and \texttt{ROWFIN} held
observed) and the ragged, unbalanced-panel edges---and the
\textbf{M-step}---the posterior re-estimation of the VAR coefficients on
the completed $[\text{domestic}\mid\text{stars}]$ panel---are carried out
jointly by the same sampler. The sweep repeats until the foreign
components stop moving, $\max|\Delta\,\texttt{star}| < \mathrm{TOL}=0.03$
(evaluated after the second sweep and excluding the COVID-masked macro
stars, whose cross-iteration churn is Monte-Carlo noise with floor
${\approx}\,0.13$), capped at $\mathrm{MAXIT}=12$ iterations.}
\label{fig:em-loop}
\end{figure}

The 2020 pandemic quarters are an extreme outlier that, left untreated,
would contaminate the autoregressive estimates and the innovation
covariance. Rather than scaling them out, the tool treats the pandemic
window as \emph{missing data} and imputes it within the estimation
itself, via a data-augmentation Gibbs sampler that nests a
Durbin--Koopman simulation smoother \citep{DurbinKoopman2002,
DurbinKoopman2012}. Each Gibbs sweep alternates:
\begin{enumerate}[label=(\roman*)]
  \item a Durbin--Koopman simulation-smoother draw of the missing
    pandemic rows given the current coefficients, treating those rows as
    \texttt{NaN} observations in the companion-form state space of
    Section~\ref{sec:statespace};
  \item a Metropolis--Hastings update of the hierarchical-prior
    hyperparameters on the \emph{completed-data} marginal likelihood, so
    the overall tightness $\lambda$ and the sum-of-coefficients
    parameter $\mu$ \citep{Giannone2015} are selected by empirical Bayes
    without any fixed-tightness restriction; and
  \item a draw of the VAR coefficients $(\beta,\Sigma)$ from the
    completed data.
\end{enumerate}
The pandemic history is thus \emph{preserved} (the surrounding quarters
remain in the sample and inform the imputation) while the outlier itself
does not drive the dynamics.

\paragraph{Window selection.} The COVID window self-calibrates to each
bloc's pandemic trough rather than being hard-coded. It is the
\emph{argmin} of the quarter-on-quarter GDP change \emph{restricted to
the window 2019Q4--2021Q1}:
\begin{equation}\label{eq:covid-window}
  k^\star = \operatorname*{arg\,min}_{t \,\in\,\{\text{2019Q4},\dots,\text{2021Q1}\}}
            \bigl(x^{g}_t - x^{g}_{t-1}\bigr),
  \qquad
  \mathcal{W} = \{\,k^\star-1,\ k^\star,\ k^\star+1,\ k^\star+2\,\},
\end{equation}
and the four rows of $\mathcal{W}$ (intersected with the sample) are
NaN'd across \emph{all} variables before estimation. Restricting the
search to 2019Q4--2021Q1 is deliberate: an unrestricted global argmin
misfires for economies whose deepest contraction is a different crisis
(for example Korea's 2008Q4 Global-Financial-Crisis drop exceeds its
2020Q2 pandemic drop).

\paragraph{Fixed window and macro-only masking in the production GVAR
loop.} The auto-detected window above is the legacy single-bloc
convention; the production GVAR estimator
(\texttt{pipeline/export\_bvar\_gvar24\_loop.m}) instead uses a
\emph{fixed} three-quarter window $\mathcal{W}=\{$2020Q2, 2020Q3,
2020Q4$\}$ for every bloc, which avoids the $\sim$seven-quarter spans the
unrestricted trough search could produce. Equally important, the
production loop masks \emph{only the macro columns}: over $\mathcal{W}$
the domestic macro variables (\(\texttt{isFinancial}=\textsf{false}\))
and the two macro stars \texttt{ROWDEM}/\texttt{ROWINF} are set
\texttt{NaN}, while the domestic financial series (rates, yields,
equity, house prices, corporate spreads) and the financial star
\texttt{ROWFIN} are \emph{kept observed}. The Durbin--Koopman smoother
then imputes the pandemic macro holes \emph{conditional on} the observed
financials, which carry genuine signal through 2020---the masking is thus
``macro-masked / financials-observed,'' the same convention the
out-of-sample evaluation re-applies in-sample at every origin
(Section~\ref{sec:empirical:oos}).

Algorithm~\ref{alg:emgvar} states the full estimation loop. It is the
operational form of the cycle sketched in Figure~\ref{fig:em-loop}: a
no-stars US bootstrap seeds the first foreign variables, after which each
sweep rebuilds every bloc's trade-weighted stars from partners' completed
panels (the \emph{E-step} regressor), re-estimates all blocs in parallel
under macro masking (the per-bloc \texttt{cgl\_bvarV5} call, whose own
Durbin--Koopman completion is the within-bloc \emph{E-step} and whose
Gibbs re-estimation is the \emph{M-step}), and recomputes the stars from
the freshly completed data, iterating to a fixed point in the completed
stars.

\begin{algorithm}[!ht]
\caption{EM-style GVAR estimation loop (Jacobi star re-convergence;
\texttt{export\_bvar\_gvar24\_loop.m}).}
\label{alg:emgvar}
\algIn{per-bloc panels $\{X_c\}$ ($X_c=[\text{domestic}\mid\text{stars}]$);
trade weights $W$; lags $p=3$; \texttt{WN}/stationary index sets
$\texttt{pos}_c$; tolerance $\textsc{tol}=0.03$; cap $\textsc{maxit}=12$;
fixed COVID window $\mathcal{W}=\{$2020Q2..Q4$\}$.}
\algOut{per-bloc posterior means $(\hat\beta_c,\hat\Sigma_c)$, completed
panels, predictive draws $\texttt{Dforecast}_c$, exported 8-file JSON.}
\begin{algsteps}
\item \algComment{Bootstrap (seed the first stars).}
\item Mask the US macro columns over $\mathcal{W}$ and fit the closed,
no-stars US bloc with \texttt{cgl\_bvarV5}; the posterior-mean DK
completion gives the initial US real-GDP/price/rate panel
(this seeds partners' iteration-1 stars).
\item \algKw{for} $it = 1,\dots,\textsc{maxit}$ \algKw{do} \algComment{Jacobi sweep}
\item \algInd \algComment{Build all stars from the FROZEN start-of-sweep completed panels.}
\item \algInd \algKw{for each} re-estimated bloc $c$: \texttt{star}$_c \gets$ trade-weighted
\texttt{ROWDEM}/\texttt{ROWINF}/\texttt{ROWFIN} from partners' completed panels (renormalize over partners present each quarter).
\item \algInd \algKw{parfor each} bloc $c$ \algKw{do} \algComment{independent given the frozen stars}
\item \algIndd $x_c \gets [\,\text{domestic}_c \mid \texttt{star}_c\,]$
\item \algIndd over $\mathcal{W}$, set \texttt{NaN} the macro columns of $x_c$ \emph{and} \texttt{ROWDEM},\texttt{ROWINF} (keep financials, \texttt{ROWFIN})
\item \algIndd $(\texttt{Xcond}_c,\beta_c,\Sigma_c,\texttt{Dforecast}_c) \gets \texttt{cgl\_bvarV5}(x_c,\,p,\,\texttt{pos}_c,\dots)$ \algComment{E-step DK completion + M-step Gibbs}
\item \algIndd completed panel $\widehat X_c \gets \operatorname{mean}_{\text{draws}} \texttt{Xcond}_c$
\item \algInd \algKw{end parfor}
\item \algInd $mc \gets \max_{c}\, \max\bigl|\,\texttt{star}_c^{(it)} - \texttt{star}_c^{(it-1)}\,\bigr|$ \algComment{exclude COVID-masked \texttt{ROWDEM}/\texttt{ROWINF} cells}
\item \algInd \algKw{if} $it>1$ \algKw{and} $mc<\textsc{tol}$ \algKw{then break} \algComment{converged}
\item \algKw{end for}
\item Export each bloc's $(\hat\beta_c,\hat\Sigma_c)$, completed history, stars, and predictive draws to the 8-file JSON contract.
\end{algsteps}
\end{algorithm}

The sweep is a \emph{Jacobi} update---all stars are rebuilt from the
common start-of-sweep state \emph{before} the parallel re-estimation---so
the parallel blocs are mutually independent given the current stars and
the sweep has the same fixed point as a sequential (Gauss--Seidel) pass,
at a wall-clock set by the slowest single bloc (the $n=41$ US bloc)
rather than the sum. The convergence metric excludes the COVID-masked
macro-star cells, whose cross-sweep churn is pure imputation Monte-Carlo
noise (floor $\approx 0.13$); the financial star \texttt{ROWFIN}, kept
observed through the pandemic, stays in the metric. Each
\texttt{cgl\_bvarV5} call is itself the data-augmentation Gibbs sampler of
Algorithm~\ref{alg:dksmoother}---its DK completion is the bloc-level
E-step and its hyperparameter/coefficient draws are the M-step---so the
whole loop is a block-coordinate EM over (foreign stars,
completed-data states, VAR coefficients).

\subsection{Common-Vintage Harmonization and the 2026Q1 Observed
Refresh}\label{sec:vintage}

The shipped panels are the product of two distinct, clearly-separated
steps: an \emph{estimation-build harmonization} to a common 2025Q4
endpoint (the vintage every bloc's coefficients were estimated on), and a
later \emph{no-re-estimation observed-data refresh} that advances the
\emph{observed} panel one quarter to 2026Q1 without touching the frozen
estimates. The two are described in turn.

\paragraph{Step 1 --- estimation-build harmonization to 2025Q4.} So that
estimation runs on a uniform window, every bloc's domestic series was
first extended to a common 2025Q4 endpoint by the GVAR build
(\texttt{pipeline/build\_gvar\_2025q4.py}, \texttt{TARGET\_END}${}={}$%
2025Q4). For blocs whose quarterly data ended short of 2025Q4:
\begin{itemize}
  \item \textbf{Real-activity and price series} (GDP, consumption,
    investment, government, exports, imports, CPI/HICP, all \texttt{log})
    are benchmarked to IMF World Economic Outlook annual projections
    (\texttt{NGDP\_RPCH} real growth, \texttt{PCPIPCH} inflation) via
    temporal disaggregation: a within-year quarterly profile is laid
    down at the WEO-implied annual growth and then proportional-Denton
    corrected so that each fully appended year's four-quarter average
    reproduces the WEO annual level (already-observed quarters in a
    partial year are held fixed). The realized annual growth of each
    appended year matches WEO to within $0.2$pp.
  \item \textbf{Financial series with no WEO analogue} (NEER, REER,
    equity indices, and all \texttt{lin} rates --- short rates, 3-month
    rates, 10-year yields, unemployment) are carried forward by
    \emph{hold-last} and flagged as such.
\end{itemize}
The original raw vintages are left untouched; the extended panels are
written separately and consumed by the estimation drivers. The estimated
companion, posterior draws, coupling artifact, and trade weights are all
frozen as of this 2025Q4 build.

\paragraph{Step 2 --- the 2026Q1 observed-data refresh (no
re-estimation).} The live panel then advances one quarter to a default
last-historical of \textbf{2026Q1}, making 2026Q2 the first projected
quarter for the refreshed blocs. This is a pure data extension performed
by \texttt{app/scripts/refresh-quarter.mjs}: for each refreshed bloc the
single new 2026Q1 row is pulled from the \emph{same} live sources, in the
\emph{same} transform, that produced the prior 2025Q4 row, and the
forecast simply re-anchors from the \emph{unchanged} companion. No
estimation runs --- \texttt{cgl\_bvarV5.m} is never invoked, and
\texttt{companion\_mean}, \texttt{companion\_draws}, \texttt{spec},
\texttt{transformations}, \texttt{coupling}, and \texttt{weights} stay
byte-frozen. The script is fail-closed: a bloc is advanced only once a
verified live-source registry (\texttt{SOURCES[<CC>]}) has been authored
and gated for it, so the rollout is per-bloc rather than a single sweep.

\paragraph{The ragged edge (panel default 2026Q1; three exceptions).}
The default last-historical quarter is \textbf{2026Q1}; three blocs are
held earlier because their genuine source data have not advanced and are
\emph{never} fabricated forward (the no-fabrication rule of
Section~\ref{sec:covid}):
\begin{itemize}
  \item \textbf{China (\texttt{CN}) and India (\texttt{IN})} --- held at
    \textbf{2025Q4}. Their real source data still end $\approx$2025Q2, so
    their 2025Q4 tail is the WEO temporal-disaggregation back-fill of
    Step~1 and they are deliberately \emph{not} advanced to 2026Q1.
  \item \textbf{Israel (\texttt{IL})} --- held at \textbf{2024Q4}, its
    quarterly source not yet having advanced.
\end{itemize}
These per-bloc endpoints are pinned in \texttt{app/src/lib/dates.ts}
(\texttt{DEFAULT\_LAST\_HIST\_DATE}${}={}$2026Q1 with \texttt{CN}/%
\texttt{IN}/\texttt{IL} overrides) so the ragged edge plots correctly:
each bloc's first forecast quarter is the one immediately after its own
last observation. A small number of emerging-market blocs
(\texttt{KR}, \texttt{RU}, \texttt{ID}, \texttt{TH}) carry a short trailing
tail whose genuine-versus-synthetic provenance is flagged for review in
Section~\ref{sec:datasources}.

\subsection{Predictive Uncertainty Bands}\label{sec:bands}

For every bloc the exported baseline carries \emph{predictive} bands,
not parameter-only bands. The COVID-missing Gibbs sampler emits a
forecast density that integrates over three sources of uncertainty
simultaneously --- posterior parameter uncertainty, future innovation
uncertainty, and missing-data (imputation) uncertainty. The reported
quantiles are the $5$th, $16$th, $84$th, and $95$th percentiles of this
predictive density (with the $50$th retained in level space),
\begin{equation}\label{eq:bands}
  \bigl(q_{05},\,q_{16},\,q_{84},\,q_{95}\bigr)_{T+h}
  = \mathrm{Quantile}_{\{0.05,0.16,0.84,0.95\}}
    \bigl\{\, \tilde{y}^{(d)}_{T+h} \,\bigr\}_{d=1}^{D},
\end{equation}
yielding the $68\%$ band $(q_{16},q_{84})$ shaded in the charts and the
$90\%$ band $(q_{05},q_{95})$. Crucially, the central path
$\bar{y}^{\text{baseline}}$ remains the \emph{deterministic} forecast
from the posterior-mean coefficients (so the unconditional smoother of
Section~\ref{sec:delta} reproduces it exactly, and zero user deviations
return the stored baseline); only the bands are predictive. This is the
designed fix for the previously over-tight bands that resulted from
spreading posterior-mean paths under a tight prior --- wide bands now
reflect genuine macro volatility (e.g.\ CN, JP, UK), not the COVID
outlier. On-the-fly conditional bands computed in the browser use the
same predictive construction, drawing innovations through the simulation
smoother of Section~\ref{sec:uncertainty}.

\subsection{US Specification}\label{sec:us-spec}

The US is the largest bloc, with $n=41$ quarterly variables and $p=3$ lags.
Its full variable list is given in Table~\ref{tab:vars}; the four-variable
fiscal block (\texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}, \texttt{EFFI},
\texttt{SFA}) supports scenario conditioning on the fiscal drivers and the
debt-targeting inversion (the debt-anchor motivation being the fiscal
reaction function of \citealp{Bohn1998}, though no $\gamma$ feedback is
active in the live recursion; see \S\ref{sec:fiscal_levers}), and the
conditional-forecast and optimal-policy machinery of
\citet{BanburaGiannoneLenza2015} and \citet{BarnichonMesters2023}
applies uniformly across all blocs. The count of $41$ comprises the domestic and
fiscal variables, the four global commons, and the three trade-weighted
\texttt{ROW*\_US} star variables that make the US a fully coupled GVAR bloc
(Section~\ref{sec:gvar:arch}).

\begin{longtable}{lp{6.5cm}cc}
\caption{Variable coverage for the US BVAR model.  ``Trans.''\ denotes
the data transformation: \texttt{log} = log levels (growth rates
displayed), \texttt{lin} = levels.  ``Prior'' denotes the prior mean:
RW = random walk, WN = white noise.}\label{tab:vars} \\
\toprule
\textbf{ID} & \textbf{Description} & \textbf{Trans.} & \textbf{Prior} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Description} & \textbf{Trans.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
GDPH      & Real Gross Domestic Product & log & RW \\
CH        & Real Personal Consumption Expenditures & log & RW \\
FRH       & Real Private Residential Fixed Investment (nom/deflator) & log & RW \\
FNH       & Real Private Nonresidential Fixed Investment (nom/deflator) & log & RW \\
XH        & Real Exports of Goods \& Services & log & RW \\
MH        & Real Imports of Goods \& Services & log & RW \\
GH        & Real Government Consumption Expenditures \& Gross Investment & log & RW \\
JGDP      & Gross Domestic Product: Chain Price Index & log & RW \\
JC        & Personal Consumption Expenditures: Chain Price Index & log & RW \\
JCXFE     & PCE less Food \& Energy: Chain Price Index & log & RW \\
UI        & CPI-U: All Items & log & RW \\
UIXFDG    & CPI-U: All Items Less Food \& Energy & log & RW \\
LXBC      & Business Sector: Compensation Per Hour (nominal) & log & RW \\
LANAGRA   & All Employees: Total Nonfarm & log & RW \\
LR        & Civilian Unemployment Rate: 16 yr + & lin & RW \\
IP        & Industrial Production Index & log & RW \\
CUMFG     & Capacity Utilization: Manufacturing [SIC] & lin & RW \\
HST       & Housing Starts & log & RW \\
YPDH      & Real Disposable Personal Income & log & RW \\
CSENT     & University of Michigan: Consumer Sentiment & lin & RW \\
POLRATE   & Effective Federal Funds Rate (policy rate) & lin & RW \\
FCM2      & 2-Year Treasury Note Yield at Constant Maturity & lin & RW \\
FCM5      & 5-Year Treasury Note Yield at Constant Maturity & lin & RW \\
GLB\_USLR & US 10-Year Treasury Yield (global common) & lin & RW \\
FAAA      & Moodys Seasoned Aaa Corporate Bond Yield & lin & RW \\
GLB\_USBAA& US Baa Corporate Bond Yield, credit proxy (global common) & lin & RW \\
FXTWM     & Nominal Trade-Weighted Exch Value of US\$ vs AFE Currencies & log & RW \\
GLB\_USEQ & US Equity Price Index (global common) & log & RW \\
PZTEXP    & Spot Oil Price: West Texas Intermediate & log & RW \\
GSNE      & Non-Fuel Commodity Price Index (IMF, non-energy proxy) & log & RW \\
SP500VOL  & CBOE Volatility Index for S\&P 500 Stock Price Index & lin & RW \\
HP        & House Price & log & RW \\
LEV       & Real nonfinancial business debt & log & RW \\
FREV\_GDP & Federal Receipts (\% of GDP) & lin & WN \\
FPEXP\_GDP& Federal Primary Expenditure (\% of GDP) & lin & WN \\
EFFI      & Federal Effective Interest Rate (\% p.a.) & lin & RW \\
SFA       & Stock-Flow Adjustment (\% of GDP) & lin & WN \\
GLB\_OIL  & Spot Oil Price, WTI (global common) & log & RW \\
ROWDEM\_US& US RoW demand (trade-weighted partner GDP growth) & lin & RW \\
ROWINF\_US& US RoW inflation (trade-weighted partner inflation) & lin & RW \\
ROWFIN\_US& US RoW financial conditions (trade-weighted partner rates) & lin & RW \\
\end{longtable}

The other coupled blocs follow the same estimation methodology with
country-appropriate variable selections, replacing the US fiscal and
detailed financial block with the three \texttt{ROW*} stars of
Section~\ref{sec:gvar-roster}. Across the deployed roster the partner
blocs range from $n=14$ (Costa Rica) to $n=25$ (UK and Canada), with the
euro-area aggregate at $n=24$ and the core majors at $n\in\{18,\dots,25\}$
(e.g.\ CH, NO~$=18$, CN~$=20$, JP~$=23$); the US is the largest at $n=41$.
The China bloc uses a tighter Minnesota tightness to discipline its
shorter, noisier sample.

\subsection{Variable Transformations, Priors, and Financial Tags by Economy}\label{sec:varcoherence}

Section~\ref{sec:us-spec} tabulates the US bloc in full; this subsection
extends that detail to \emph{every} deployed economy. For all $50$ blocs
(the $33$ GVAR members of Section~\ref{sec:gvar-roster} and the $17$
euro-area standalones of Section~\ref{sec:standalone}) each variable's
\emph{transformation} (\texttt{log} = log level, growth displayed;
\texttt{lin} = level), its \emph{financial} tag (which governs whether a
series is held observed through the COVID window, Section~\ref{sec:covid}),
and its \emph{prior} mean (RW = random walk in levels; WN = white noise /
stationary) are read directly from the deployed
\texttt{public/data/bvar/<CC>/spec.json} specifications, so the tables below
mirror the current re-estimated state of the tool exactly.

\paragraph{Cross-economy coherence matrix.} Table~\ref{tab:coherence}
collects the common concepts that recur across blocs. Because the
transformation, financial tag, and prior for each concept are assigned
\emph{identically} in every economy that carries it, a single row
characterises the concept tool-wide. Every variable is given a
random-walk (RW) prior \emph{except} the three fiscal GDP-ratios
(\texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}, \texttt{SFA}), which are bounded
mean-reverting shares and therefore carry a white-noise / stationary (WN)
prior; the effective-interest series \texttt{EFFI} remains RW.

\begin{table}[!ht]
\centering\small
\caption{Cross-economy coherence matrix for the common concepts. ``Trans.''
is \texttt{log}/\texttt{lin}; ``Fin.''\ marks financial series
($\checkmark$); ``Prior''\ is RW (random walk) or WN (white noise /
stationary). Each concept takes the same triple in every bloc that carries
it.}\label{tab:coherence}
\begin{tabular}{lccc}
\toprule
\textbf{Concept} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
Real GDP (level) & \texttt{log} & -- & RW \\
Price index (CPI/HICP/deflator) & \texttt{log} & -- & RW \\
Policy rate & \texttt{lin} & \checkmark & RW \\
Short rate (3M/money-mkt) & \texttt{lin} & \checkmark & RW \\
10Y government yield & \texttt{lin} & \checkmark & RW \\
Corporate / Baa spread & \texttt{lin} & \checkmark & RW \\
House prices & \texttt{log} & \checkmark & RW \\
Equity price index & \texttt{log} & \checkmark & RW \\
Oil price (WTI, global) & \texttt{log} & \checkmark & RW \\
FX / NEER & \texttt{log} & \checkmark & RW \\
Fiscal revenue ratio (FREV\_GDP) & \texttt{lin} & -- & WN \\
Fiscal primary-exp.\ ratio (FPEXP\_GDP) & \texttt{lin} & -- & WN \\
Stock-flow adjustment (SFA) & \texttt{lin} & -- & WN \\
Effective interest (EFFI) & \texttt{lin} & \checkmark & RW \\
RoW demand star (ROWDEM) & \texttt{lin} & \checkmark & RW \\
RoW inflation star (ROWINF) & \texttt{lin} & \checkmark & RW \\
RoW financial star (ROWFIN) & \texttt{lin} & \checkmark & RW \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{The 33 GVAR blocs.} Each carries a domestic block, the four
global commons (\texttt{GLB\_*}), and the three trade-weighted
\texttt{ROW*\_<CC>} stars. Tables follow in alphabetical order.

{\footnotesize
\begin{longtable}{llcc}
\caption{Argentina (\texttt{AR}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:AR} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Argentina (\texttt{AR}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_AR} & \texttt{log} & -- & RW \\
\texttt{CONS\_AR} & \texttt{log} & -- & RW \\
\texttt{INV\_AR} & \texttt{log} & -- & RW \\
\texttt{GOV\_AR} & \texttt{log} & -- & RW \\
\texttt{EXP\_AR} & \texttt{log} & -- & RW \\
\texttt{IMP\_AR} & \texttt{log} & -- & RW \\
\texttt{CPI\_AR} & \texttt{log} & -- & RW \\
\texttt{LR\_AR} & \texttt{lin} & -- & RW \\
\texttt{RATE\_AR} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_AR} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_AR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_AR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_AR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_AR} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Australia (\texttt{AU}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:AU} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Australia (\texttt{AU}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_AU} & \texttt{log} & -- & RW \\
\texttt{CONS\_AU} & \texttt{log} & -- & RW \\
\texttt{GOV\_AU} & \texttt{log} & -- & RW \\
\texttt{INV\_AU} & \texttt{log} & -- & RW \\
\texttt{EXP\_AU} & \texttt{log} & -- & RW \\
\texttt{IMP\_AU} & \texttt{log} & -- & RW \\
\texttt{CPI\_AU} & \texttt{log} & -- & RW \\
\texttt{LR\_AU} & \texttt{lin} & -- & RW \\
\texttt{NEER\_AU} & \texttt{log} & \checkmark & RW \\
\texttt{RATE\_AU} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_AU} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_AU} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_AU} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_AU} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_AU} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Brazil (\texttt{BR}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:BR} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Brazil (\texttt{BR}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_BR} & \texttt{log} & -- & RW \\
\texttt{CONS\_BR} & \texttt{log} & -- & RW \\
\texttt{INV\_BR} & \texttt{log} & -- & RW \\
\texttt{GOV\_BR} & \texttt{log} & -- & RW \\
\texttt{EXP\_BR} & \texttt{log} & -- & RW \\
\texttt{IMP\_BR} & \texttt{log} & -- & RW \\
\texttt{CPI\_BR} & \texttt{log} & -- & RW \\
\texttt{LR\_BR} & \texttt{lin} & -- & RW \\
\texttt{NEER\_BR} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_BR} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_BR} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_BR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_BR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_BR} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Canada (\texttt{CA}, $n=25$): variable transformations,
financial tags, and priors.}\label{tab:spec:CA} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Canada (\texttt{CA}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CA} & \texttt{log} & -- & RW \\
\texttt{CONS\_CA} & \texttt{log} & -- & RW \\
\texttt{INV\_CA} & \texttt{log} & -- & RW \\
\texttt{GOV\_CA} & \texttt{log} & -- & RW \\
\texttt{EXP\_CA} & \texttt{log} & -- & RW \\
\texttt{IMP\_CA} & \texttt{log} & -- & RW \\
\texttt{IP\_CA} & \texttt{log} & -- & RW \\
\texttt{LR\_CA} & \texttt{lin} & -- & RW \\
\texttt{CPI\_CA} & \texttt{log} & -- & RW \\
\texttt{RATE\_CA} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_CA} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_CA} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_CA} & \texttt{log} & \checkmark & RW \\
\texttt{NEER\_CA} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{FREV\_GDP} & \texttt{lin} & -- & WN \\
\texttt{FPEXP\_GDP} & \texttt{lin} & -- & WN \\
\texttt{EFFI} & \texttt{lin} & \checkmark & RW \\
\texttt{SFA} & \texttt{lin} & -- & WN \\
\texttt{ROWDEM\_CA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_CA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_CA} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Switzerland (\texttt{CH}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:CH} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Switzerland (\texttt{CH}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CH} & \texttt{log} & -- & RW \\
\texttt{CONS\_CH} & \texttt{log} & -- & RW \\
\texttt{INV\_CH} & \texttt{log} & -- & RW \\
\texttt{GOV\_CH} & \texttt{log} & -- & RW \\
\texttt{EXP\_CH} & \texttt{log} & -- & RW \\
\texttt{IMP\_CH} & \texttt{log} & -- & RW \\
\texttt{HICP\_CH} & \texttt{log} & -- & RW \\
\texttt{LR\_CH} & \texttt{lin} & -- & RW \\
\texttt{NEER\_CH} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_CH} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_CH} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_CH} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_CH} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_CH} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Chile (\texttt{CL}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:CL} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Chile (\texttt{CL}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CL} & \texttt{log} & -- & RW \\
\texttt{CONS\_CL} & \texttt{log} & -- & RW \\
\texttt{INV\_CL} & \texttt{log} & -- & RW \\
\texttt{GOV\_CL} & \texttt{log} & -- & RW \\
\texttt{EXP\_CL} & \texttt{log} & -- & RW \\
\texttt{IMP\_CL} & \texttt{log} & -- & RW \\
\texttt{CPI\_CL} & \texttt{log} & -- & RW \\
\texttt{LR\_CL} & \texttt{lin} & -- & RW \\
\texttt{RATE\_CL} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_CL} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_CL} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_CL} & \texttt{log} & \checkmark & RW \\
\texttt{NEER\_CL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_CL} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_CL} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_CL} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{China (\texttt{CN}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:CN} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape China (\texttt{CN}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CN} & \texttt{log} & -- & RW \\
\texttt{CPI\_CN} & \texttt{log} & -- & RW \\
\texttt{RATE\_CN} & \texttt{lin} & \checkmark & RW \\
\texttt{EXP\_CN} & \texttt{log} & -- & RW \\
\texttt{IMP\_CN} & \texttt{log} & -- & RW \\
\texttt{REER\_CN} & \texttt{log} & \checkmark & RW \\
\texttt{EQ\_CN} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_CN} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_CN} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{FREV\_GDP} & \texttt{lin} & -- & WN \\
\texttt{FPEXP\_GDP} & \texttt{lin} & -- & WN \\
\texttt{EFFI} & \texttt{lin} & \checkmark & RW \\
\texttt{SFA} & \texttt{lin} & -- & WN \\
\texttt{ROWDEM\_CN} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_CN} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_CN} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Colombia (\texttt{CO}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:CO} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Colombia (\texttt{CO}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CO} & \texttt{log} & -- & RW \\
\texttt{CONS\_CO} & \texttt{log} & -- & RW \\
\texttt{INV\_CO} & \texttt{log} & -- & RW \\
\texttt{GOV\_CO} & \texttt{log} & -- & RW \\
\texttt{EXP\_CO} & \texttt{log} & -- & RW \\
\texttt{IMP\_CO} & \texttt{log} & -- & RW \\
\texttt{CPI\_CO} & \texttt{log} & -- & RW \\
\texttt{LR\_CO} & \texttt{lin} & -- & RW \\
\texttt{RATE\_CO} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_CO} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_CO} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_CO} & \texttt{log} & \checkmark & RW \\
\texttt{NEER\_CO} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_CO} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_CO} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_CO} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Costa Rica (\texttt{CR}, $n=14$): variable transformations,
financial tags, and priors.}\label{tab:spec:CR} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Costa Rica (\texttt{CR}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CR} & \texttt{log} & -- & RW \\
\texttt{EXP\_CR} & \texttt{log} & -- & RW \\
\texttt{IMP\_CR} & \texttt{log} & -- & RW \\
\texttt{CPI\_CR} & \texttt{log} & -- & RW \\
\texttt{LR\_CR} & \texttt{lin} & -- & RW \\
\texttt{RATE\_CR} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_CR} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_CR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_CR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_CR} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Czechia (\texttt{CZ}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:CZ} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Czechia (\texttt{CZ}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_CZ} & \texttt{log} & -- & RW \\
\texttt{CONS\_CZ} & \texttt{log} & -- & RW \\
\texttt{INV\_CZ} & \texttt{log} & -- & RW \\
\texttt{GOV\_CZ} & \texttt{log} & -- & RW \\
\texttt{EXP\_CZ} & \texttt{log} & -- & RW \\
\texttt{IMP\_CZ} & \texttt{log} & -- & RW \\
\texttt{HICP\_CZ} & \texttt{log} & -- & RW \\
\texttt{LR\_CZ} & \texttt{lin} & -- & RW \\
\texttt{YIELD10\_CZ} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_CZ} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_CZ} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_CZ} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_CZ} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_CZ} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_CZ} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Denmark (\texttt{DK}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:DK} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Denmark (\texttt{DK}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_DK} & \texttt{log} & -- & RW \\
\texttt{CONS\_DK} & \texttt{log} & -- & RW \\
\texttt{INV\_DK} & \texttt{log} & -- & RW \\
\texttt{GOV\_DK} & \texttt{log} & -- & RW \\
\texttt{EXP\_DK} & \texttt{log} & -- & RW \\
\texttt{IMP\_DK} & \texttt{log} & -- & RW \\
\texttt{HICP\_DK} & \texttt{log} & -- & RW \\
\texttt{LR\_DK} & \texttt{lin} & -- & RW \\
\texttt{RATE\_DK} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_DK} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_DK} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_DK} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_DK} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_DK} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_DK} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_DK} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Euro Area (\texttt{EA}, $n=24$): variable transformations,
financial tags, and priors.}\label{tab:spec:EA} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Euro Area (\texttt{EA}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_EA} & \texttt{log} & -- & RW \\
\texttt{CONS\_EA} & \texttt{log} & -- & RW \\
\texttt{INV\_EA} & \texttt{log} & -- & RW \\
\texttt{GOV\_EA} & \texttt{log} & -- & RW \\
\texttt{EXP\_EA} & \texttt{log} & -- & RW \\
\texttt{IMP\_EA} & \texttt{log} & -- & RW \\
\texttt{HICP\_EA} & \texttt{log} & -- & RW \\
\texttt{RATE\_EA} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_EA} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_EA} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_EA} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_EA} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{FREV\_GDP} & \texttt{lin} & -- & WN \\
\texttt{FPEXP\_GDP} & \texttt{lin} & -- & WN \\
\texttt{EFFI} & \texttt{lin} & \checkmark & RW \\
\texttt{SFA} & \texttt{lin} & -- & WN \\
\texttt{ROWDEM\_EA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_EA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_EA} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Hungary (\texttt{HU}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:HU} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Hungary (\texttt{HU}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_HU} & \texttt{log} & -- & RW \\
\texttt{CONS\_HU} & \texttt{log} & -- & RW \\
\texttt{INV\_HU} & \texttt{log} & -- & RW \\
\texttt{GOV\_HU} & \texttt{log} & -- & RW \\
\texttt{EXP\_HU} & \texttt{log} & -- & RW \\
\texttt{IMP\_HU} & \texttt{log} & -- & RW \\
\texttt{HICP\_HU} & \texttt{log} & -- & RW \\
\texttt{LR\_HU} & \texttt{lin} & -- & RW \\
\texttt{YIELD10\_HU} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_HU} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_HU} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_HU} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_HU} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_HU} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_HU} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Indonesia (\texttt{ID}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:ID} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Indonesia (\texttt{ID}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_ID} & \texttt{log} & -- & RW \\
\texttt{CONS\_ID} & \texttt{log} & -- & RW \\
\texttt{INV\_ID} & \texttt{log} & -- & RW \\
\texttt{GOV\_ID} & \texttt{log} & -- & RW \\
\texttt{EXP\_ID} & \texttt{log} & -- & RW \\
\texttt{IMP\_ID} & \texttt{log} & -- & RW \\
\texttt{CPI\_ID} & \texttt{log} & -- & RW \\
\texttt{RATE\_ID} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_ID} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_ID} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_ID} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_ID} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_ID} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_ID} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Israel (\texttt{IL}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:IL} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Israel (\texttt{IL}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_IL} & \texttt{log} & -- & RW \\
\texttt{CONS\_IL} & \texttt{log} & -- & RW \\
\texttt{INV\_IL} & \texttt{log} & -- & RW \\
\texttt{GOV\_IL} & \texttt{log} & -- & RW \\
\texttt{EXP\_IL} & \texttt{log} & -- & RW \\
\texttt{IMP\_IL} & \texttt{log} & -- & RW \\
\texttt{CPI\_IL} & \texttt{log} & -- & RW \\
\texttt{LR\_IL} & \texttt{lin} & -- & RW \\
\texttt{RATE\_IL} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_IL} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_IL} & \texttt{log} & \checkmark & RW \\
\texttt{HP\_IL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_IL} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_IL} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_IL} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{India (\texttt{IN}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:IN} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape India (\texttt{IN}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_IN} & \texttt{log} & -- & RW \\
\texttt{CONS\_IN} & \texttt{log} & -- & RW \\
\texttt{INV\_IN} & \texttt{log} & -- & RW \\
\texttt{GOV\_IN} & \texttt{log} & -- & RW \\
\texttt{EXP\_IN} & \texttt{log} & -- & RW \\
\texttt{IMP\_IN} & \texttt{log} & -- & RW \\
\texttt{CPI\_IN} & \texttt{log} & -- & RW \\
\texttt{RATE\_IN} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE3M\_IN} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_IN} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_IN} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_IN} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_IN} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_IN} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_IN} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_IN} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Iceland (\texttt{IS}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:IS} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Iceland (\texttt{IS}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_IS} & \texttt{log} & -- & RW \\
\texttt{CONS\_IS} & \texttt{log} & -- & RW \\
\texttt{INV\_IS} & \texttt{log} & -- & RW \\
\texttt{GOV\_IS} & \texttt{log} & -- & RW \\
\texttt{EXP\_IS} & \texttt{log} & -- & RW \\
\texttt{IMP\_IS} & \texttt{log} & -- & RW \\
\texttt{CPI\_IS} & \texttt{log} & -- & RW \\
\texttt{LR\_IS} & \texttt{lin} & -- & RW \\
\texttt{RATE\_IS} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_IS} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_IS} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_IS} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_IS} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_IS} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_IS} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Japan (\texttt{JP}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:JP} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Japan (\texttt{JP}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_JP} & \texttt{log} & -- & RW \\
\texttt{CONS\_JP} & \texttt{log} & -- & RW \\
\texttt{INV\_JP} & \texttt{log} & -- & RW \\
\texttt{GOV\_JP} & \texttt{log} & -- & RW \\
\texttt{EXP\_JP} & \texttt{log} & -- & RW \\
\texttt{IMP\_JP} & \texttt{log} & -- & RW \\
\texttt{LR\_JP} & \texttt{lin} & -- & RW \\
\texttt{CPI\_JP} & \texttt{log} & -- & RW \\
\texttt{RATE\_JP} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_JP} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_JP} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_JP} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{FREV\_GDP} & \texttt{lin} & -- & WN \\
\texttt{FPEXP\_GDP} & \texttt{lin} & -- & WN \\
\texttt{EFFI} & \texttt{lin} & \checkmark & RW \\
\texttt{SFA} & \texttt{lin} & -- & WN \\
\texttt{ROWDEM\_JP} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_JP} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_JP} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Korea (\texttt{KR}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:KR} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Korea (\texttt{KR}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_KR} & \texttt{log} & -- & RW \\
\texttt{CONS\_KR} & \texttt{log} & -- & RW \\
\texttt{INV\_KR} & \texttt{log} & -- & RW \\
\texttt{GOV\_KR} & \texttt{log} & -- & RW \\
\texttt{EXP\_KR} & \texttt{log} & -- & RW \\
\texttt{IMP\_KR} & \texttt{log} & -- & RW \\
\texttt{CPI\_KR} & \texttt{log} & -- & RW \\
\texttt{LR\_KR} & \texttt{lin} & -- & RW \\
\texttt{RATE\_KR} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_KR} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_KR} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_KR} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_KR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_KR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_KR} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Mexico (\texttt{MX}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:MX} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Mexico (\texttt{MX}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_MX} & \texttt{log} & -- & RW \\
\texttt{CONS\_MX} & \texttt{log} & -- & RW \\
\texttt{INV\_MX} & \texttt{log} & -- & RW \\
\texttt{GOV\_MX} & \texttt{log} & -- & RW \\
\texttt{EXP\_MX} & \texttt{log} & -- & RW \\
\texttt{IMP\_MX} & \texttt{log} & -- & RW \\
\texttt{CPI\_MX} & \texttt{log} & -- & RW \\
\texttt{LR\_MX} & \texttt{lin} & -- & RW \\
\texttt{RATE\_MX} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_MX} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_MX} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_MX} & \texttt{log} & \checkmark & RW \\
\texttt{NEER\_MX} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_MX} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_MX} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_MX} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Malaysia (\texttt{MY}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:MY} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Malaysia (\texttt{MY}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_MY} & \texttt{log} & -- & RW \\
\texttt{CONS\_MY} & \texttt{log} & -- & RW \\
\texttt{INV\_MY} & \texttt{log} & -- & RW \\
\texttt{GOV\_MY} & \texttt{log} & -- & RW \\
\texttt{EXP\_MY} & \texttt{log} & -- & RW \\
\texttt{IMP\_MY} & \texttt{log} & -- & RW \\
\texttt{CPI\_MY} & \texttt{log} & -- & RW \\
\texttt{LR\_MY} & \texttt{lin} & -- & RW \\
\texttt{RATE\_MY} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_MY} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_MY} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_MY} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_MY} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_MY} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_MY} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Norway (\texttt{NO}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:NO} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Norway (\texttt{NO}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_NO} & \texttt{log} & -- & RW \\
\texttt{CONS\_NO} & \texttt{log} & -- & RW \\
\texttt{INV\_NO} & \texttt{log} & -- & RW \\
\texttt{GOV\_NO} & \texttt{log} & -- & RW \\
\texttt{EXP\_NO} & \texttt{log} & -- & RW \\
\texttt{IMP\_NO} & \texttt{log} & -- & RW \\
\texttt{HICP\_NO} & \texttt{log} & -- & RW \\
\texttt{LR\_NO} & \texttt{lin} & -- & RW \\
\texttt{NEER\_NO} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_NO} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_NO} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_NO} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_NO} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_NO} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{New Zealand (\texttt{NZ}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:NZ} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape New Zealand (\texttt{NZ}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_NZ} & \texttt{log} & -- & RW \\
\texttt{CONS\_NZ} & \texttt{log} & -- & RW \\
\texttt{INV\_NZ} & \texttt{log} & -- & RW \\
\texttt{GOV\_NZ} & \texttt{log} & -- & RW \\
\texttt{EXP\_NZ} & \texttt{log} & -- & RW \\
\texttt{IMP\_NZ} & \texttt{log} & -- & RW \\
\texttt{CPI\_NZ} & \texttt{log} & -- & RW \\
\texttt{LR\_NZ} & \texttt{lin} & -- & RW \\
\texttt{RATE\_NZ} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_NZ} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_NZ} & \texttt{log} & \checkmark & RW \\
\texttt{NEER\_NZ} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_NZ} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_NZ} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_NZ} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Poland (\texttt{PL}, $n=19$): variable transformations,
financial tags, and priors.}\label{tab:spec:PL} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Poland (\texttt{PL}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_PL} & \texttt{log} & -- & RW \\
\texttt{CONS\_PL} & \texttt{log} & -- & RW \\
\texttt{INV\_PL} & \texttt{log} & -- & RW \\
\texttt{GOV\_PL} & \texttt{log} & -- & RW \\
\texttt{EXP\_PL} & \texttt{log} & -- & RW \\
\texttt{IMP\_PL} & \texttt{log} & -- & RW \\
\texttt{HICP\_PL} & \texttt{log} & -- & RW \\
\texttt{LR\_PL} & \texttt{lin} & -- & RW \\
\texttt{YIELD10\_PL} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_PL} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_PL} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_PL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_PL} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_PL} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_PL} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Russia (\texttt{RU}, $n=15$): variable transformations,
financial tags, and priors.}\label{tab:spec:RU} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Russia (\texttt{RU}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_RU} & \texttt{log} & -- & RW \\
\texttt{CPI\_RU} & \texttt{log} & -- & RW \\
\texttt{EXP\_RU} & \texttt{log} & -- & RW \\
\texttt{LR\_RU} & \texttt{lin} & -- & RW \\
\texttt{RATE\_RU} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_RU} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_RU} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_RU} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_RU} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_RU} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_RU} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Saudi Arabia (\texttt{SA}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:SA} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Saudi Arabia (\texttt{SA}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_SA} & \texttt{log} & -- & RW \\
\texttt{CONS\_SA} & \texttt{log} & -- & RW \\
\texttt{INV\_SA} & \texttt{log} & -- & RW \\
\texttt{GOV\_SA} & \texttt{log} & -- & RW \\
\texttt{EXP\_SA} & \texttt{log} & -- & RW \\
\texttt{IMP\_SA} & \texttt{log} & -- & RW \\
\texttt{CPI\_SA} & \texttt{log} & -- & RW \\
\texttt{LR\_SA} & \texttt{lin} & -- & RW \\
\texttt{RATE\_SA} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_SA} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_SA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_SA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_SA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_SA} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Sweden (\texttt{SE}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:SE} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Sweden (\texttt{SE}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_SE} & \texttt{log} & -- & RW \\
\texttt{CONS\_SE} & \texttt{log} & -- & RW \\
\texttt{INV\_SE} & \texttt{log} & -- & RW \\
\texttt{GOV\_SE} & \texttt{log} & -- & RW \\
\texttt{EXP\_SE} & \texttt{log} & -- & RW \\
\texttt{IMP\_SE} & \texttt{log} & -- & RW \\
\texttt{HICP\_SE} & \texttt{log} & -- & RW \\
\texttt{LR\_SE} & \texttt{lin} & -- & RW \\
\texttt{RATE\_SE} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_SE} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_SE} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_SE} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_SE} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_SE} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_SE} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_SE} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Thailand (\texttt{TH}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:TH} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Thailand (\texttt{TH}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_TH} & \texttt{log} & -- & RW \\
\texttt{CONS\_TH} & \texttt{log} & -- & RW \\
\texttt{INV\_TH} & \texttt{log} & -- & RW \\
\texttt{GOV\_TH} & \texttt{log} & -- & RW \\
\texttt{EXP\_TH} & \texttt{log} & -- & RW \\
\texttt{IMP\_TH} & \texttt{log} & -- & RW \\
\texttt{CPI\_TH} & \texttt{log} & -- & RW \\
\texttt{LR\_TH} & \texttt{lin} & -- & RW \\
\texttt{RATE\_TH} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_TH} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_TH} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_TH} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_TH} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_TH} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_TH} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_TH} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{T\"urkiye (\texttt{TR}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:TR} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape T\"urkiye (\texttt{TR}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_TR} & \texttt{log} & -- & RW \\
\texttt{CONS\_TR} & \texttt{log} & -- & RW \\
\texttt{INV\_TR} & \texttt{log} & -- & RW \\
\texttt{GOV\_TR} & \texttt{log} & -- & RW \\
\texttt{EXP\_TR} & \texttt{log} & -- & RW \\
\texttt{IMP\_TR} & \texttt{log} & -- & RW \\
\texttt{CPI\_TR} & \texttt{log} & -- & RW \\
\texttt{LR\_TR} & \texttt{lin} & -- & RW \\
\texttt{RATE\_TR} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_TR} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_TR} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_TR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_TR} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_TR} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Taiwan (\texttt{TW}, $n=18$): variable transformations,
financial tags, and priors.}\label{tab:spec:TW} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Taiwan (\texttt{TW}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_TW} & \texttt{log} & -- & RW \\
\texttt{CONS\_TW} & \texttt{log} & -- & RW \\
\texttt{GOV\_TW} & \texttt{log} & -- & RW \\
\texttt{INV\_TW} & \texttt{log} & -- & RW \\
\texttt{EXP\_TW} & \texttt{log} & -- & RW \\
\texttt{IMP\_TW} & \texttt{log} & -- & RW \\
\texttt{CPI\_TW} & \texttt{log} & -- & RW \\
\texttt{LR\_TW} & \texttt{lin} & -- & RW \\
\texttt{RATE\_TW} & \texttt{lin} & \checkmark & RW \\
\texttt{MMRATE\_TW} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_TW} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_TW} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_TW} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_TW} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{United Kingdom (\texttt{UK}, $n=25$): variable transformations,
financial tags, and priors.}\label{tab:spec:UK} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape United Kingdom (\texttt{UK}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_UK} & \texttt{log} & -- & RW \\
\texttt{CONS\_UK} & \texttt{log} & -- & RW \\
\texttt{INV\_UK} & \texttt{log} & -- & RW \\
\texttt{GOV\_UK} & \texttt{log} & -- & RW \\
\texttt{EXP\_UK} & \texttt{log} & -- & RW \\
\texttt{IMP\_UK} & \texttt{log} & -- & RW \\
\texttt{IP\_UK} & \texttt{log} & -- & RW \\
\texttt{LR\_UK} & \texttt{lin} & -- & RW \\
\texttt{CPI\_UK} & \texttt{log} & -- & RW \\
\texttt{RATE\_UK} & \texttt{lin} & \checkmark & RW \\
\texttt{POLRATE\_UK} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_UK} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_UK} & \texttt{log} & \checkmark & RW \\
\texttt{NEER\_UK} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{FREV\_GDP} & \texttt{lin} & -- & WN \\
\texttt{FPEXP\_GDP} & \texttt{lin} & -- & WN \\
\texttt{EFFI} & \texttt{lin} & \checkmark & RW \\
\texttt{SFA} & \texttt{lin} & -- & WN \\
\texttt{ROWDEM\_UK} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_UK} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_UK} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{United States (\texttt{US}, $n=41$): variable transformations,
financial tags, and priors.}\label{tab:spec:US} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape United States (\texttt{US}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDPH} & \texttt{log} & -- & RW \\
\texttt{CH} & \texttt{log} & -- & RW \\
\texttt{FRH} & \texttt{log} & -- & RW \\
\texttt{FNH} & \texttt{log} & -- & RW \\
\texttt{XH} & \texttt{log} & -- & RW \\
\texttt{MH} & \texttt{log} & -- & RW \\
\texttt{GH} & \texttt{log} & -- & RW \\
\texttt{JGDP} & \texttt{log} & -- & RW \\
\texttt{JC} & \texttt{log} & -- & RW \\
\texttt{JCXFE} & \texttt{log} & -- & RW \\
\texttt{UI} & \texttt{log} & -- & RW \\
\texttt{UIXFDG} & \texttt{log} & -- & RW \\
\texttt{LXBC} & \texttt{log} & -- & RW \\
\texttt{LANAGRA} & \texttt{log} & -- & RW \\
\texttt{LR} & \texttt{lin} & -- & RW \\
\texttt{IP} & \texttt{log} & -- & RW \\
\texttt{CUMFG} & \texttt{lin} & -- & RW \\
\texttt{HST} & \texttt{log} & -- & RW \\
\texttt{YPDH} & \texttt{log} & -- & RW \\
\texttt{CSENT} & \texttt{lin} & -- & RW \\
\texttt{POLRATE} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM2} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM5} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{FAAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{FXTWM} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{PZTEXP} & \texttt{log} & \checkmark & RW \\
\texttt{GSNE} & \texttt{log} & \checkmark & RW \\
\texttt{SP500VOL} & \texttt{lin} & \checkmark & RW \\
\texttt{HP} & \texttt{log} & \checkmark & RW \\
\texttt{LEV} & \texttt{log} & \checkmark & RW \\
\texttt{FREV\_GDP} & \texttt{lin} & -- & WN \\
\texttt{FPEXP\_GDP} & \texttt{lin} & -- & WN \\
\texttt{EFFI} & \texttt{lin} & \checkmark & RW \\
\texttt{SFA} & \texttt{lin} & -- & WN \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_US} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{South Africa (\texttt{ZA}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:ZA} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape South Africa (\texttt{ZA}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_ZA} & \texttt{log} & -- & RW \\
\texttt{CONS\_ZA} & \texttt{log} & -- & RW \\
\texttt{INV\_ZA} & \texttt{log} & -- & RW \\
\texttt{GOV\_ZA} & \texttt{log} & -- & RW \\
\texttt{EXP\_ZA} & \texttt{log} & -- & RW \\
\texttt{IMP\_ZA} & \texttt{log} & -- & RW \\
\texttt{CPI\_ZA} & \texttt{log} & -- & RW \\
\texttt{LR\_ZA} & \texttt{lin} & -- & RW \\
\texttt{RATE\_ZA} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_ZA} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_ZA} & \texttt{log} & \checkmark & RW \\
\texttt{POLRATE\_ZA} & \texttt{lin} & \checkmark & RW \\
\texttt{HP\_ZA} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_OIL} & \texttt{log} & \checkmark & RW \\
\texttt{GLB\_USLR} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USBAA} & \texttt{lin} & \checkmark & RW \\
\texttt{GLB\_USEQ} & \texttt{log} & \checkmark & RW \\
\texttt{ROWDEM\_ZA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWINF\_ZA} & \texttt{lin} & \checkmark & RW \\
\texttt{ROWFIN\_ZA} & \texttt{lin} & \checkmark & RW \\
\end{longtable}
}

\paragraph{The 17 euro-area standalones.} These omit the
\texttt{ROW*} stars and instead carry US-block foreign variables
(\texttt{*\_US}) plus the shared euro-area corporate spread
(\texttt{EACORP}); they are estimated in separation
(Section~\ref{sec:standalone}).

{\footnotesize
\begin{longtable}{llcc}
\caption{Austria (\texttt{AT}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:AT} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Austria (\texttt{AT}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_AT} & \texttt{log} & -- & RW \\
\texttt{CONS\_AT} & \texttt{log} & -- & RW \\
\texttt{INV\_AT} & \texttt{log} & -- & RW \\
\texttt{GOV\_AT} & \texttt{log} & -- & RW \\
\texttt{EXP\_AT} & \texttt{log} & -- & RW \\
\texttt{IMP\_AT} & \texttt{log} & -- & RW \\
\texttt{HICP\_AT} & \texttt{log} & -- & RW \\
\texttt{LR\_AT} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_AT} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_AT} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_AT} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_AT} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_AT} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Belgium (\texttt{BE}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:BE} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Belgium (\texttt{BE}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_BE} & \texttt{log} & -- & RW \\
\texttt{CONS\_BE} & \texttt{log} & -- & RW \\
\texttt{INV\_BE} & \texttt{log} & -- & RW \\
\texttt{GOV\_BE} & \texttt{log} & -- & RW \\
\texttt{EXP\_BE} & \texttt{log} & -- & RW \\
\texttt{IMP\_BE} & \texttt{log} & -- & RW \\
\texttt{HICP\_BE} & \texttt{log} & -- & RW \\
\texttt{LR\_BE} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_BE} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_BE} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_BE} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_BE} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_BE} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Germany (\texttt{DE}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:DE} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Germany (\texttt{DE}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_DE} & \texttt{log} & -- & RW \\
\texttt{CONS\_DE} & \texttt{log} & -- & RW \\
\texttt{INV\_DE} & \texttt{log} & -- & RW \\
\texttt{GOV\_DE} & \texttt{log} & -- & RW \\
\texttt{EXP\_DE} & \texttt{log} & -- & RW \\
\texttt{IMP\_DE} & \texttt{log} & -- & RW \\
\texttt{HICP\_DE} & \texttt{log} & -- & RW \\
\texttt{LR\_DE} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_DE} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_DE} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_DE} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_DE} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_DE} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Estonia (\texttt{EE}, $n=22$): variable transformations,
financial tags, and priors.}\label{tab:spec:EE} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Estonia (\texttt{EE}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_EE} & \texttt{log} & -- & RW \\
\texttt{CONS\_EE} & \texttt{log} & -- & RW \\
\texttt{INV\_EE} & \texttt{log} & -- & RW \\
\texttt{GOV\_EE} & \texttt{log} & -- & RW \\
\texttt{EXP\_EE} & \texttt{log} & -- & RW \\
\texttt{IMP\_EE} & \texttt{log} & -- & RW \\
\texttt{HICP\_EE} & \texttt{log} & -- & RW \\
\texttt{LR\_EE} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_EE} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_EE} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_EE} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_EE} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Spain (\texttt{ES}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:ES} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Spain (\texttt{ES}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_ES} & \texttt{log} & -- & RW \\
\texttt{CONS\_ES} & \texttt{log} & -- & RW \\
\texttt{INV\_ES} & \texttt{log} & -- & RW \\
\texttt{GOV\_ES} & \texttt{log} & -- & RW \\
\texttt{EXP\_ES} & \texttt{log} & -- & RW \\
\texttt{IMP\_ES} & \texttt{log} & -- & RW \\
\texttt{HICP\_ES} & \texttt{log} & -- & RW \\
\texttt{LR\_ES} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_ES} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_ES} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_ES} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_ES} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_ES} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Finland (\texttt{FI}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:FI} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Finland (\texttt{FI}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_FI} & \texttt{log} & -- & RW \\
\texttt{CONS\_FI} & \texttt{log} & -- & RW \\
\texttt{INV\_FI} & \texttt{log} & -- & RW \\
\texttt{GOV\_FI} & \texttt{log} & -- & RW \\
\texttt{EXP\_FI} & \texttt{log} & -- & RW \\
\texttt{IMP\_FI} & \texttt{log} & -- & RW \\
\texttt{HICP\_FI} & \texttt{log} & -- & RW \\
\texttt{LR\_FI} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_FI} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_FI} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_FI} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_FI} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_FI} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{France (\texttt{FR}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:FR} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape France (\texttt{FR}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_FR} & \texttt{log} & -- & RW \\
\texttt{CONS\_FR} & \texttt{log} & -- & RW \\
\texttt{INV\_FR} & \texttt{log} & -- & RW \\
\texttt{GOV\_FR} & \texttt{log} & -- & RW \\
\texttt{EXP\_FR} & \texttt{log} & -- & RW \\
\texttt{IMP\_FR} & \texttt{log} & -- & RW \\
\texttt{HICP\_FR} & \texttt{log} & -- & RW \\
\texttt{LR\_FR} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_FR} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_FR} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_FR} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_FR} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_FR} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Greece (\texttt{GR}, $n=22$): variable transformations,
financial tags, and priors.}\label{tab:spec:GR} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Greece (\texttt{GR}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_GR} & \texttt{log} & -- & RW \\
\texttt{CONS\_GR} & \texttt{log} & -- & RW \\
\texttt{INV\_GR} & \texttt{log} & -- & RW \\
\texttt{GOV\_GR} & \texttt{log} & -- & RW \\
\texttt{EXP\_GR} & \texttt{log} & -- & RW \\
\texttt{IMP\_GR} & \texttt{log} & -- & RW \\
\texttt{HICP\_GR} & \texttt{log} & -- & RW \\
\texttt{LR\_GR} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_GR} & \texttt{lin} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_GR} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_GR} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_GR} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Ireland (\texttt{IE}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:IE} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Ireland (\texttt{IE}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_IE} & \texttt{log} & -- & RW \\
\texttt{CONS\_IE} & \texttt{log} & -- & RW \\
\texttt{INV\_IE} & \texttt{log} & -- & RW \\
\texttt{GOV\_IE} & \texttt{log} & -- & RW \\
\texttt{EXP\_IE} & \texttt{log} & -- & RW \\
\texttt{IMP\_IE} & \texttt{log} & -- & RW \\
\texttt{HICP\_IE} & \texttt{log} & -- & RW \\
\texttt{LR\_IE} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_IE} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_IE} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_IE} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_IE} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_IE} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Italy (\texttt{IT}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:IT} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Italy (\texttt{IT}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_IT} & \texttt{log} & -- & RW \\
\texttt{CONS\_IT} & \texttt{log} & -- & RW \\
\texttt{INV\_IT} & \texttt{log} & -- & RW \\
\texttt{GOV\_IT} & \texttt{log} & -- & RW \\
\texttt{EXP\_IT} & \texttt{log} & -- & RW \\
\texttt{IMP\_IT} & \texttt{log} & -- & RW \\
\texttt{HICP\_IT} & \texttt{log} & -- & RW \\
\texttt{LR\_IT} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_IT} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_IT} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_IT} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_IT} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_IT} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Lithuania (\texttt{LT}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:LT} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Lithuania (\texttt{LT}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_LT} & \texttt{log} & -- & RW \\
\texttt{CONS\_LT} & \texttt{log} & -- & RW \\
\texttt{INV\_LT} & \texttt{log} & -- & RW \\
\texttt{GOV\_LT} & \texttt{log} & -- & RW \\
\texttt{EXP\_LT} & \texttt{log} & -- & RW \\
\texttt{IMP\_LT} & \texttt{log} & -- & RW \\
\texttt{HICP\_LT} & \texttt{log} & -- & RW \\
\texttt{LR\_LT} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_LT} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_LT} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_LT} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_LT} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_LT} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Luxembourg (\texttt{LU}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:LU} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Luxembourg (\texttt{LU}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_LU} & \texttt{log} & -- & RW \\
\texttt{CONS\_LU} & \texttt{log} & -- & RW \\
\texttt{INV\_LU} & \texttt{log} & -- & RW \\
\texttt{GOV\_LU} & \texttt{log} & -- & RW \\
\texttt{EXP\_LU} & \texttt{log} & -- & RW \\
\texttt{IMP\_LU} & \texttt{log} & -- & RW \\
\texttt{HICP\_LU} & \texttt{log} & -- & RW \\
\texttt{LR\_LU} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_LU} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_LU} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_LU} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_LU} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_LU} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Latvia (\texttt{LV}, $n=20$): variable transformations,
financial tags, and priors.}\label{tab:spec:LV} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Latvia (\texttt{LV}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_LV} & \texttt{log} & -- & RW \\
\texttt{CONS\_LV} & \texttt{log} & -- & RW \\
\texttt{INV\_LV} & \texttt{log} & -- & RW \\
\texttt{GOV\_LV} & \texttt{log} & -- & RW \\
\texttt{EXP\_LV} & \texttt{log} & -- & RW \\
\texttt{IMP\_LV} & \texttt{log} & -- & RW \\
\texttt{HICP\_LV} & \texttt{log} & -- & RW \\
\texttt{LR\_LV} & \texttt{lin} & -- & RW \\
\texttt{RATE\_LV} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_LV} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_LV} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Netherlands (\texttt{NL}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:NL} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Netherlands (\texttt{NL}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_NL} & \texttt{log} & -- & RW \\
\texttt{CONS\_NL} & \texttt{log} & -- & RW \\
\texttt{INV\_NL} & \texttt{log} & -- & RW \\
\texttt{GOV\_NL} & \texttt{log} & -- & RW \\
\texttt{EXP\_NL} & \texttt{log} & -- & RW \\
\texttt{IMP\_NL} & \texttt{log} & -- & RW \\
\texttt{HICP\_NL} & \texttt{log} & -- & RW \\
\texttt{LR\_NL} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_NL} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_NL} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_NL} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_NL} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_NL} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Portugal (\texttt{PT}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:PT} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Portugal (\texttt{PT}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_PT} & \texttt{log} & -- & RW \\
\texttt{CONS\_PT} & \texttt{log} & -- & RW \\
\texttt{INV\_PT} & \texttt{log} & -- & RW \\
\texttt{GOV\_PT} & \texttt{log} & -- & RW \\
\texttt{EXP\_PT} & \texttt{log} & -- & RW \\
\texttt{IMP\_PT} & \texttt{log} & -- & RW \\
\texttt{HICP\_PT} & \texttt{log} & -- & RW \\
\texttt{LR\_PT} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_PT} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_PT} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_PT} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_PT} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_PT} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Slovenia (\texttt{SI}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:SI} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Slovenia (\texttt{SI}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_SI} & \texttt{log} & -- & RW \\
\texttt{CONS\_SI} & \texttt{log} & -- & RW \\
\texttt{INV\_SI} & \texttt{log} & -- & RW \\
\texttt{GOV\_SI} & \texttt{log} & -- & RW \\
\texttt{EXP\_SI} & \texttt{log} & -- & RW \\
\texttt{IMP\_SI} & \texttt{log} & -- & RW \\
\texttt{HICP\_SI} & \texttt{log} & -- & RW \\
\texttt{LR\_SI} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_SI} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_SI} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_SI} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_SI} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_SI} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
\begin{longtable}{llcc}
\caption{Slovakia (\texttt{SK}, $n=23$): variable transformations,
financial tags, and priors.}\label{tab:spec:SK} \\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endfirsthead
\multicolumn{4}{l}{\small\itshape Slovakia (\texttt{SK}), continued}\\
\toprule
\textbf{ID} & \textbf{Trans.} & \textbf{Fin.} & \textbf{Prior} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{GDP\_SK} & \texttt{log} & -- & RW \\
\texttt{CONS\_SK} & \texttt{log} & -- & RW \\
\texttt{INV\_SK} & \texttt{log} & -- & RW \\
\texttt{GOV\_SK} & \texttt{log} & -- & RW \\
\texttt{EXP\_SK} & \texttt{log} & -- & RW \\
\texttt{IMP\_SK} & \texttt{log} & -- & RW \\
\texttt{HICP\_SK} & \texttt{log} & -- & RW \\
\texttt{LR\_SK} & \texttt{lin} & -- & RW \\
\texttt{POLRATE\_SK} & \texttt{lin} & \checkmark & RW \\
\texttt{HPI\_SK} & \texttt{log} & \checkmark & RW \\
\texttt{EACORP} & \texttt{lin} & \checkmark & RW \\
\texttt{RATE\_SK} & \texttt{lin} & \checkmark & RW \\
\texttt{YIELD10\_SK} & \texttt{lin} & \checkmark & RW \\
\texttt{NEER\_SK} & \texttt{log} & \checkmark & RW \\
\texttt{GDPH\_US} & \texttt{log} & -- & RW \\
\texttt{GH\_US} & \texttt{log} & -- & RW \\
\texttt{LR\_US} & \texttt{lin} & -- & RW \\
\texttt{JGDP\_US} & \texttt{log} & -- & RW \\
\texttt{FCM2\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{FCM10\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{EQ\_US} & \texttt{log} & \checkmark & RW \\
\texttt{FBAA\_US} & \texttt{lin} & \checkmark & RW \\
\texttt{WTI\_US} & \texttt{log} & \checkmark & RW \\
\end{longtable}
}

\paragraph{Coherence review.} A cross-economy audit of all
1048 variable rows confirms that every shared concept is assigned
the same transformation, financial tag, and prior in every bloc that
carries it: real activity, price indices, house prices, equities, oil, and
FX enter in \texttt{log}; interest rates, yields, spreads, unemployment,
and the fiscal ratios enter \texttt{lin}; all financial series share the
financial tag; and all priors are RW apart from the three stationary fiscal
GDP-ratios (\texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}, \texttt{SFA}, prior
WN). Canada's industrial-production series \texttt{IP\_CA} has been rebuilt as
a \texttt{log}-level index, consistent with the activity convention used for
the United States and the United Kingdom. The FRED level index
(\texttt{CANPROINDMISMEI}, $2015=100$) was discontinued at 2024-02, so the
series is the quarterly average of that index through 2024-Q1 and is then
growth-chained over 2024-Q2--2025-Q4 (eight quarters) using the FRED
q-on-q growth series \texttt{PRINTO01CAQ657S}
($\text{level}_t = \text{level}_{t-1}(1+g_t)$, the same chaining used to
extend the other Canadian series). With this reconstruction the audit finds
no remaining transformation-coherence exceptions.


%% ================================================================
%% Per-country data documentation (one subsection per economy).
%% Assembled from pipeline/credit_staging/_manual/*.tex.
%% The dense 8-column provenance tables are tight against \textwidth;
%% reduce inter-column padding globally for this section so the wide
%% tables (em2 in particular) stay inside the right margin. Content,
%% column structure, and per-table font sizing are untouched.
%% ================================================================
\begingroup
\setlength{\tabcolsep}{2.5pt}%
% The dense 8-column provenance tables carry a few very long monospace
% provider IDs (notably the Bundesbank BBSIS/M.I.UMR.RD.EUR.X2000... series)
% that cannot break and overrun the source-id column. \emergencystretch and
% a relaxed \tolerance let TeX absorb the worst lines; the residual long IDs
% are made breakable in-place (\allowbreak after their dots) below in
% per_country_data.tex so nothing runs past the right margin.
\emergencystretch=3em\relax
\tolerance=9999\relax
\hbadness=10000\relax
\input{per_country_data}
\endgroup


\subsection{Country\,$\times$\,Variable Coverage Matrix}\label{sec:coverage-matrix}

Table~\ref{tab:coverage} is the per-bloc coverage matrix for the key
variable groups, generated deterministically from the coverage manifest
(\texttt{app/public/data/coverage\_manifest.json}; the generator is
\texttt{docs/build\_coverage\_table.py}). A \cmark{} marks that the group
is carried by the bloc's shipped specification; \texttt{--} marks a genuine
absence in that bloc's panel (e.g.\ blocs that carry a cash/short rate in
place of a dedicated policy rate, or that ship no NEER). The
\emph{Last~obs} column is the bloc's last historical quarter (the ragged
edge of Section~\ref{sec:vintage}); \emph{Source} is the primary source
family (Section~\ref{sec:datasources}), with a trailing italic tag for the
WEO back-fill (CN/IN) and source-review (KR/RU/ID/TH) provenance flags.

\begin{landscape}
\thispagestyle{empty}
{\footnotesize
\begin{longtable}{@{}l ccccccccc l l@{}}
\caption{Country\,$\times$\,variable-group coverage matrix for all $50$
deployed blocs. Columns: \textbf{GDP} real activity; \textbf{Price}
HICP/CPI; \textbf{Unemp} unemployment rate (\texttt{LR}); \textbf{Pol}
policy rate; \textbf{Long} 10-year/long government yield; \textbf{Cred}
credit-to-GDP; \textbf{Lend} lending/short rate; \textbf{FX} NEER;
\textbf{Fisc} the four-variable fiscal block
(\texttt{FREV}/\texttt{FPEXP}/\texttt{EFFI}/\texttt{SFA}). \cmark${}={}$%
carried; \texttt{--}${}={}$absent in that bloc. WEO${}={}$WEO-back-filled
tail (CN/IN); review${}={}$source-review tail (KR/RU/ID/TH).}
\label{tab:coverage}\\
\toprule
\textbf{Bloc} & \textbf{GDP} & \textbf{Price} & \textbf{Unemp} &
\textbf{Pol} & \textbf{Long} & \textbf{Cred} & \textbf{Lend} &
\textbf{FX} & \textbf{Fisc} & \textbf{Last obs} & \textbf{Source} \\
\midrule
\endfirsthead
\toprule
\textbf{Bloc} & \textbf{GDP} & \textbf{Price} & \textbf{Unemp} &
\textbf{Pol} & \textbf{Long} & \textbf{Cred} & \textbf{Lend} &
\textbf{FX} & \textbf{Fisc} & \textbf{Last obs} & \textbf{Source} \\
\midrule
\endhead
\bottomrule
\endfoot
\texttt{AR} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{AT} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{AU} & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{BE} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{BR} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{CA} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & 2026Q1 & OECD/FRED \\
\texttt{CH} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & Eurostat \\
\texttt{CL} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{CN} & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & 2025Q4 & FRED\,\footnotesize\textit{WEO} \\
\texttt{CO} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{CR} & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{CZ} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & Eurostat \\
\texttt{DE} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{DK} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & Eurostat \\
\texttt{EA} & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{EE} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{ES} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{FI} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{FR} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{GR} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{HU} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & Eurostat \\
\texttt{ID} & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED\,\footnotesize\textit{review} \\
\texttt{IE} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{IL} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2024Q4 & OECD/FRED \\
\texttt{IN} & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2025Q4 & OECD/FRED\,\footnotesize\textit{WEO} \\
\texttt{IS} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{IT} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{JP} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & \cmark & 2026Q1 & OECD/FRED \\
\texttt{KR} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & -- & 2026Q1 & OECD/FRED\,\footnotesize\textit{review,frozen~mirror} \\
\texttt{LT} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{LU} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{LV} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{MX} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{MY} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{NL} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{NO} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & Eurostat \\
\texttt{NZ} & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{PL} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & Eurostat \\
\texttt{PT} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{RU} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED\,\footnotesize\textit{review} \\
\texttt{SA} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\texttt{SE} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & Eurostat \\
\texttt{SI} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{SK} & \cmark & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & \cmark & 2026Q1 & Eurostat \\
\texttt{TH} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED\,\footnotesize\textit{review} \\
\texttt{TR} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & -- & 2026Q1 & OECD/FRED \\
\texttt{TW} & \cmark & \cmark & \cmark & -- & \cmark & \cmark & \cmark & -- & -- & 2026Q1 & OECD/FRED \\
\texttt{UK} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & 2026Q1 & OECD/FRED \\
\texttt{US} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & 2026Q1 & FRED \\
\texttt{ZA} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & -- & 2026Q1 & OECD/FRED \\
\end{longtable}
}
\end{landscape}


%% ================================================================
\section{Technical Notes}\label{sec:technical}
%% ================================================================

\subsection{Client-Side Computation}

All matrix algebra, Kalman filtering, and simulation smoothing are
performed in the browser using TypeScript with \texttt{Float64Array}
storage.  The linear algebra kernel implements:
\begin{itemize}
  \item LU decomposition with partial pivoting for
    $F_t^{-1}$ (singularity threshold: $10^{-15}$).
  \item Cholesky decomposition for shock draws
    ($\Sigma = LL'$; diagonal check threshold: $10^{-14}$).
  \item Row-major storage for cache-friendly matrix operations.
\end{itemize}

\subsection{Performance Optimizations}

\begin{itemize}
  \item The unconditional smoother result is cached by a fingerprint
    of the model dimensions and a sample of coefficient values,
    avoiding recomputation when only the conditioning paths change.
  \item Conditioning input is debounced at 30\,ms to avoid
    recomputation during interactive drag operations.
  \item The $500$ thinned posterior draws ($\approx$\,34\,MB for the US model)
    are loaded lazily---only when the user clicks ``Compute.''
  \item Plotly.js is loaded via dynamic \texttt{import()} to avoid
    blocking initial page render.
\end{itemize}

\subsection{Interactive GVAR Architecture: keeping the heavy solve off the drag path}\label{sec:perfux}

The deployed $50$-bloc, US-endogenous GVAR poses a hard
interactivity problem: a single coupled mean solve costs
$\approx 4.6$\,s warm and $\approx 13$\,s cold (every US-pinned structure
misses the shipped $(I-M)^{-1}$ coupling cache and must re-probe the
Durbin--Koopman smoother per coupled bloc). Firing that solve on every
pointer-move during a chart drag would make the interface unusable. The
deployed design therefore removes the solve from the live drag path
entirely, and reconciles the exact answer afterwards.

\paragraph{No solve during drag; exactly one cheap solve on release.}
A module-level signal bus (\texttt{gvarDragState.ts}) carries the reactive
drag flag between the chart drag handler and the GVAR solve hook
(\texttt{useGvarForecast.ts}), kept \emph{out} of the React/Zustand store
so that a pointer-down does not re-render the grid. While a drag is in
progress \emph{no} GVAR solve fires---neither a value-only nor a
structure-change solve, since both are multi-second on the live panel.
On \texttt{pointer-up} a single solve is dispatched after a short
($100$\,ms) release macrotask that also coalesces back-to-back
click-drag-click gestures into one dispatch. That release solve uses the
cheap \texttt{'direct'} channel (one-hop local-elasticity preview, no
$95$\,MB coupling-artifact structured-clone into the worker); the full
cross-country fixed point with uncertainty bands (the \texttt{'full'}
channel) runs \emph{only} on the explicit ``Compute'' / ``Solve full
GVAR'' action. Non-drag edits (numeric entry, Reset, scenario switch)
still dispatch live: full solves run immediately and direct previews
debounce ($\approx 120$\,ms).

\paragraph{Optimistic conditioned-point dot.} So that the user sees
\emph{immediate} feedback while the line and bands reconcile, the pinned
marker (the conditioned-point ``dot'') is sourced from the
\emph{conditioning path} the click writes---not from the lagging solve
output. The mapping lives in \texttt{conditionedDotY.ts}:
\texttt{conditioningDeviationFromDisplayY} converts a clicked display
$y$-value into the stored-space deviation, and its exact inverse
\texttt{conditionedDotDisplayY} reconstructs the displayed dot, so the dot
round-trips to the cursor to machine precision
($\texttt{conditionedDotDisplayY}\circ\texttt{conditioningDeviationFromDisplayY}=\mathrm{id}$).
The same inverse pair backs the right-click ``plant the bullet at the
cursor'' gesture. The smoothed forecast line and the uncertainty bands
then catch up when the solve returns.

\paragraph{Per-chart render memoization.} The render cost of a
conditioning edit was historically dominated by the \emph{render}, not the
solve: a monolithic chart component repainted all $\approx 35$ panels on
any edit. The deployed grid (\texttt{ChartGrid.tsx}) wraps each panel in
\texttt{React.memo} and reconciles the freshly-built chart objects against
the prior render with a tight structural equality
(\texttt{reconcileCharts}/\texttt{chartDeepEqual}): a panel whose trace
data did not move keeps its \emph{prior object reference}, so
\texttt{React.memo} skips it. A single conditioning edit therefore
rebuilds and repaints \emph{exactly one} of the $\approx 35$ panels rather
than all of them (asserted in \texttt{chartgrid-render-memo.test.ts}), with
a stale-guard that still repaints every affected panel when the solve
lands. The whole interactive contract---no solve on drag, one cheap solve
on release, an optimistic dot, and single-panel repaints---is covered by
the \texttt{gvar-drag-scheduling}, \texttt{conditioned-dot-optimistic},
\texttt{right-click-plant-at-cursor}, and \texttt{chartgrid-render-memo}
test suites.

\subsection{Numerical Conventions}

\begin{itemize}
  \item Measurement noise: $H = 10^{-12}\, I_n$, ensuring the Kalman
    filter treats conditioned values as near-exact observations while
    maintaining numerical stability.
  \item Growth-to-level conversion: $\Delta\ell = \Delta g / 4$ for
    log-transformed variables, reflecting the annualization factor in
    \eqref{eq:growth}.
  \item Tikhonov regularization for Barnichon--Mesters:
    $\alpha = 10^{-6}$.
  \item All matrix operations use IEEE~754 double precision
    (64-bit floating point).
\end{itemize}


%% ================================================================
\subsection{Identifiability and Weak Exogeneity}\label{sec:identif}

The platform's separable estimation--solution architecture rests on a chain of
identifying assumptions; we state them explicitly and are candid about where
each binds.

\paragraph{Weak exogeneity of the star variables.}
Each bloc is estimated \emph{conditionally} on its three trade-weighted star
variables (Section~\ref{sec:gvar:stars}), treating the foreign environment as
predetermined. This is the weak-exogeneity device of the GVAR literature
\citep{PesaranSchuermannWeiner2004, DeesDiMauroPesaranSmith2007}: provided a
domestic economy is small relative to its trading partners, its idiosyncratic
shocks do not feed back contemporaneously into the aggregated foreign block, so
the conditional likelihood factorizes and the bloc-specific parameters
$(\hat\beta_c,\hat\Sigma_c)$ are identified without a joint, system-wide
estimator. \citet{ChudikPesaran2016} formalize the conditions---a granular
weighting scheme in which no single partner dominates the trade-weighted average
and a bounded number of strongly correlated units---under which the
cross-section-averaged stars remain valid weakly-exogenous regressors as the
panel grows. Our renormalized, per-component weights
(Section~\ref{sec:gvar:weights}) are designed to keep this granularity:
absent or excluded partners have their mass reabsorbed across the present
partners rather than concentrated on any one.

The classical treatment fixes a \emph{frozen dominant unit} (here the United
States) outside the system. We relax this in two ways. First, the EM-style
re-estimation loop (Section~\ref{sec:gvar:commons}) rebuilds every bloc's stars
from its partners' Durbin--Koopman-completed paths and re-estimates each bloc in
parallel until the maximum star change falls below the tolerance
$\textsc{tol}=0.03$, so the conditioning information is mutually consistent at
the fixed point rather than taken as given once. This tolerance is set
\emph{tighter} than the Monte~Carlo noise floor of the imputation
($\approx 0.13$ on the star scale); the COVID-window cells of the two macro
stars, where cross-iteration churn is dominated by that imputation noise, are
excluded from the convergence metric. Second, in the deployed roster the US is
made \emph{endogenous}: it carries its own \texttt{ROW$*$\_US} stars and is
solved inside the cross-country fixed point like any other bloc. What keeps the
relaxed system well posed is the contraction property of the solve-time
coupling operator $M$ of~\eqref{eq:gvar:fp}: its spectral radius is
$\rho(M)\approx 0.59$ for the original six-bloc pilot,
$\rho(M)\approx 0.726$ under the frozen-anchor configuration with the euro area
aggregated into a single bloc, and $\rho(M)\approx 0.924$ for the full
$33$-bloc endogenous-US configuration. As long as $\rho(M)<1$ the map
$x\mapsto Mx+d$ is a contraction, $(I-M)$ is nonsingular, and the scenario fixed
point is unique---so closing the RoW$\to$US feedback loop raises the coupling
but leaves the system stationary and the scenario deviation identified.

\paragraph{Fiscal identification: a triangular budget identity.}
The fiscal block is identified by construction rather than by estimation. Four
flow drivers (\texttt{FREV\_GDP}, \texttt{FPEXP\_GDP}, the effective rate
\texttt{EFFI}, and the stock-flow adjustment \texttt{SFA}) are estimated by the
BVAR; the debt stock is then \emph{derived} by rolling the budget identity
of~\eqref{eq:fiscal_debt} forward
\citep{Escolano2010, IMF2013DSA}. The recursion is triangular: given lagged
debt $d_{t-1}$, the effective rate, nominal growth, the primary balance
$\mathrm{pb}=\texttt{FREV\_GDP}-\texttt{FPEXP\_GDP}$, and the \texttt{SFA}, the
new debt level is fully determined, so debt is never a free parameter.
The \texttt{SFA} term is the \emph{exact} residual that reconciles the change in
the recorded debt stock with the cumulated deficit; by estimating it as its own
driver we close the identity to machine precision over history---the quarterly
convention of~\eqref{eq:fiscal_debt} is pinned by a historical back-cast of the
reconstructed debt ratio against the observed one---and carry its forecast path
forward. The honest caveat is that any model error in the non-\texttt{SFA}
drivers is silently absorbed into the \texttt{SFA} in sample, so a large or
volatile estimated \texttt{SFA} flags a measurement or perimeter gap
(below-the-line operations, valuation effects) rather than a behavioral
relationship.

\paragraph{Euro-area monetary identification.}
The euro area receives a deliberately asymmetric treatment. In the EA-aggregate
bloc the ECB policy rate, the short rate, and the shared corporate-risk yield
\texttt{EACORP} are \emph{endogenous} (tagged \texttt{block="domestic"}); in
each euro-member bloc the very same area-wide instruments are
\emph{weakly exogenous} (tagged \texttt{block="external"}), entering the
member's foreign block alongside the US and global commons. This encodes the
identifying assumption that monetary policy is set for the area as a whole, so a
single member faces it as predetermined while the aggregate determines it---the
same exogenous-versus-endogenous split that the star variables impose on the
real side. National financial variables (sovereign 10Y yields, house prices)
stay domestic. The limitation is structural: members share one common monetary
factor, so member-level monetary counterfactuals are conditional scenarios on
the area instrument, not independent national policy experiments, and the strong
cross-member correlation of \texttt{EACORP} and policy-rate shocks sits at the
edge of the granularity that weak exogeneity formally requires.

\section{Reproducibility and Replication}\label{sec:repro}

The platform is engineered so that every published number traces back to
source data through a single, scripted pipeline: there are no hand-edited
artifacts on the path from raw series to the deployed app. This section maps
the repository, lists the software dependencies, gives the end-to-end
replication recipe, and explains the model-signature versioning that refuses a
stale cross-country coupling.

\subsection{Repository and Folder Map}\label{sec:repro:repo}

The work lives in a single git repository with three top-level concerns, shown
in Table~\ref{tab:repro:layout}. The \texttt{pipeline/} tree (MATLAB plus
Python) performs all estimation and data assembly and is the ``private''
research layer; \texttt{app/} is the public Next.js front end and its
in-browser compute kernels; \texttt{docs/} holds this manual and the
operational runbooks. The estimator writes a per-bloc JSON export that
\texttt{port\_gvar\_exports.py} copies into \texttt{app/public/data/bvar/}; the
deployed app reads \emph{only} that JSON and never re-estimates.

\begin{table}[H]
\centering
\footnotesize
\caption{Repository layout. Estimation in \texttt{pipeline/} produces a
per-bloc JSON export; \texttt{port\_gvar\_exports.py} ports it into
\texttt{app/public/data/bvar/}; the front end and its compute kernels consume
that data and never re-estimate.}
\label{tab:repro:layout}
\begin{tabular}{@{}lp{8.6cm}@{}}
\toprule
\textbf{Top-level} & \textbf{Key contents} \\
\midrule
\texttt{pipeline/} (MATLAB + Python) &
  \texttt{export\_bvar\_gvar24\_loop.m} (GVAR--EM estimator);
  \texttt{build\_*.py} (FRED / Eurostat / BIS / ECB pulls, trade weights,
  fiscal drivers); \texttt{port\_gvar\_exports.py}; \texttt{\_verify/}
  ground-truth checks. \\
\addlinespace
\texttt{app/} (Next.js + compute) &
  \texttt{src/lib/compute/} (Durbin--Koopman, GVAR solve, fiscal accounting);
  \texttt{scripts/} (\texttt{precompute\_gvar\_coupling.mjs},
  \texttt{verify\_gvar24.mjs}, \texttt{invert\_coupling.\{m,py\}});
  \texttt{public/data/bvar/<CC>/} (the deployed JSON the app reads). \\
\addlinespace
\texttt{docs/} (manual + runbooks) &
  \texttt{user\_manual.tex}; \texttt{REESTIMATING\_MODELS.md},
  \texttt{ADDING\_A\_COUNTRY.md}, \texttt{ARCHITECTURE\_FOR\_AI.md}. \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Software Dependencies}\label{sec:repro:deps}

\begin{itemize}
  \item \textbf{Estimation (MATLAB).} A recent MATLAB with the
    \emph{Parallel Computing Toolbox} (the EM M-step re-estimates all blocs in
    a \texttt{parfor}). The bundled \texttt{BVAR/MFBVAR} code --- the GLP
    hierarchical-prior Gibbs sampler \texttt{bvarGLPmf.m} and the
    COVID-as-missing wrapper \texttt{cgl\_bvarV5.m} --- ships in the repository;
    no external MATLAB packages are required.
  \item \textbf{Data assembly (Python 3).} Pure standard library
    (\texttt{urllib}, \texttt{json}, \texttt{csv}, \texttt{math}); no
    \texttt{pandas}, \texttt{requests}, or \texttt{fredapi}. The
    \texttt{build\_*.py} pulls hit the FRED (key via \texttt{FRED\_API\_KEY}),
    Eurostat SDMX~2.1, BIS, and ECB public endpoints.
    \texttt{invert\_coupling.py} (NumPy) is the no-MATLAB fallback for the
    coupling inverse.
  \item \textbf{Application (Node / Next.js).} Node with the pinned Next.js
    toolchain; \texttt{typescript}, \texttt{vitest} for the test gate, and
    \texttt{vite-node}/\texttt{tsx} to run the \texttt{scripts/*.mjs}
    precompute and verification utilities.
\end{itemize}

\subsection{End-to-End Replication Recipe}\label{sec:repro:recipe}

The full path from raw data to a green deploy gate is the following enumerated
sequence (canonical commands in \texttt{docs/REESTIMATING\_MODELS.md}).

\begin{enumerate}
  \item \textbf{Build the data.} Run the \texttt{pipeline/build\_*.py} pulls
    (with \texttt{FRED\_API\_KEY} set) to assemble the harmonized
    common-vintage panels (raw series, trade weights, fiscal drivers) as
    \texttt{pipeline/\allowbreak country\_\allowbreak rawdata/\allowbreak DataRaw\_\allowbreak <CC>\_\allowbreak glob.json}.
  \item \textbf{Estimate (GVAR--EM).} Run
    \texttt{export\_bvar\_gvar24\_loop.m}. It bootstraps the US as a closed
    bloc, then iterates the E-step (rebuild trade-weighted stars
    \texttt{ROWDEM}/\texttt{ROWINF}/\texttt{ROWFIN} from partners'
    Durbin--Koopman--completed panels) and the M-step (\texttt{parfor}
    re-estimate every bloc via \texttt{cgl\_bvarV5}, COVID macro-masked over
    \texttt{2020Q2--Q4} with the financial columns and \texttt{ROWFIN} kept
    observed) until $\max|\Delta\text{star}| < \mathrm{TOL}=0.03$ (or
    \texttt{MAXIT}$=12$). See \citet{DurbinKoopman2002} for the simulation
    smoother and \citet{DeesDiMauroPesaranSmith2007} for the GVAR structure.
  \item \textbf{Check the export.} Confirm each bloc directory under
    \texttt{/tmp/gvar24\_export/<CC>/} carries the full eight-file JSON
    contract: \texttt{spec.json}, \texttt{companion\_mean.json},
    \texttt{companion\_draws.json}, \texttt{baseline.json},
    \texttt{baseline\_levels.json}, \texttt{historical.json},
    \texttt{historical\_levels.json}, \texttt{transformations.json} (the fiscal
    blocs additionally carry \texttt{fiscal\_meta.json}).
  \item \textbf{Port into the app.} Run \texttt{port\_gvar\_exports.py} to copy
    the eight-file contract into
    \texttt{app/\allowbreak public/\allowbreak data/\allowbreak bvar/\allowbreak <CC>/},
    compacting every float to six significant figures (the deployed precision
    convention) and writing minified JSON.
  \item \textbf{Regenerate the coupling.} From \texttt{app/}, run
    \texttt{npx vite-node
    scripts/\allowbreak precompute\_\allowbreak gvar\_\allowbreak coupling.mjs}.
    It builds the
    Kalman-probe operator $M$ in JS, inverts $(I-M)$ via LAPACK
    (\texttt{invert\_coupling.m} in MATLAB, or the \texttt{invert\_coupling.py}
    NumPy fallback), and writes the gzipped
    \texttt{public/\allowbreak data/\allowbreak bvar/\allowbreak gvar/\allowbreak coupling\_\allowbreak default.json.gz} (the plain
    \texttt{.json} is removed --- at this bloc count the raw artifact exceeds
    GitHub's 100\,MB per-file limit, so only the \texttt{.gz} is shipped and the
    loader decompresses it via the browser's \texttt{DecompressionStream}).
  \item \textbf{Green gate.} From \texttt{app/}, run the fast fixed-point check
    \texttt{npx tsx scripts/verify\_gvar24.mjs} (artifact \texttt{modelSig}
    fresh; the shipped inverse really inverts $(I-M)$ to $<10^{-3}$;
    $\rho(M)<1$ and matches the stored value; Gauss--Seidel $\equiv$ the
    artifact-seeded closed form), then \texttt{npx tsc --noEmit} and the test
    suite. The fast gate is \texttt{npm test} (the everyday suite, which
    \emph{excludes} the multi-second GVAR solver canaries); the heavy
    closed-form/endogenous-GVAR canaries run under
    \texttt{npm run test:heavy}, and \texttt{npm run test:all} runs both.
    All type-checks and tests --- including the fiscal, GVAR, and scale
    canaries --- must pass.
  \item \textbf{Deploy.} On a green gate (and only with explicit confirmation),
    push \texttt{app/**} to \texttt{main}: the
    \texttt{deploy-to-website.yml} GitHub Action runs
    \texttt{npm ci \&\& npm run build} with \texttt{BASE\_PATH=/bvar-scenario},
    then copies the static export \texttt{app/out/*} into the
    \texttt{matyasfarkas/starter-hugo-academic} academic website repository's
    \texttt{static/bvar-scenario/} directory. That repository is a Hugo Academic
    site published to \textbf{GitHub Pages}, which rebuilds and serves
    the tool at the \texttt{/bvar-scenario} path. The Action itself contains no
    Hugo step---it only copies \texttt{app/out}.
\end{enumerate}

\subsection{Model-Signature Versioning}\label{sec:repro:modelsig}

The cross-country coupling artifact is bound to the bloc estimates it was built
from by a \emph{model signature}. Over the qualified bloc set the signature
concatenates, per bloc $c$, the dimensions $(n_c, p_c, H_c)$ and three
fingerprint entries of the posterior-mean companion: the leading reduced-form
coefficient $\hat\beta^{(c)}_{1,1}$, the \emph{intercept} entry of the last
equation $\hat\beta^{(c)}_{n_c p_c + 1,\,n_c}$ (the constant row of
$\hat\beta$, which stacks $n_c p_c$ lag-coefficient rows followed by one
constant row), and the leading residual variance $\hat\Sigma^{(c)}_{1,1}$ ---
each at six-digit exponential precision:
\[
  \mathrm{modelSig} \;=\;
  \big\Vert_{c}\;
  c \,:\, n_c\,p_c\,H_c\,
  \hat\beta^{(c)}_{1,1}\,
  \hat\beta^{(c)}_{n_c p_c + 1,\,n_c}\,
  \hat\Sigma^{(c)}_{1,1}.
\]
The precomputed artifact stores this signature alongside $M$, $(I-M)^{-1}$,
$\rho(M)$, and the dimension. At load time the app recomputes
\texttt{modelSig} from the deployed companions and accepts the artifact only on
an exact match \emph{and} a matching (here empty) pin structure; on any mismatch
the stale artifact is \textbf{refused} and the solver falls back to the
inverse-free Neumann (Gauss--Seidel) build of $M$ from the live models. Because
any re-estimation perturbs at least one fingerprint entry, the signature flips
whenever the data changes --- making it impossible to ship a coupling that
silently disagrees with its blocs. This is exactly the ``freshness'' invariant
the \texttt{verify\_gvar24} gate enforces above, for the current
endogenous-US system (33 coupled blocs, augmented closed-form dimension
$2060$, spectral radius $\rho(M)\approx 0.924<1$).

\section{Empirical Results}\label{sec:empirical}

This section reports the empirical program of the unified global-forecasting system. The estimation machinery of Sections~\ref{sec:bvar}--\ref{sec:gvar} is implemented and the production vintage (harmonized to 2025Q4, $\sim$50 economies: 33 GVAR blocs plus 17 euro-area standalones) has been produced. The out-of-sample horse-race (Section~\ref{sec:empirical:oos}) and the Tier-A endogenous-vs-frozen spillover contrast (Section~\ref{sec:empirical:spillover}) are \emph{realized} runs from the companion evaluation repository (\texttt{em-bayesian-gvar-eval}); the only piece still flagged \textbf{[TBD]} is the Tier-B GIRF/connectedness module, which is a structural extension gated behind the validated Tier-A result.

\subsection{In-sample diagnostics}\label{sec:empirical:insample}

\paragraph{EM convergence.} The EM-style estimation loop alternates an E-step (rebuild the trade-weighted RoW stars from partners' Durbin--Koopman--completed panels) with an M-step (a \texttt{parfor} re-estimation of every bloc under COVID macro-masking). Because all stars are rebuilt from the frozen start-of-sweep state before the parallel re-estimation, the inner sweep is a Jacobi update with the same fixed point as a sequential pass. Convergence is declared when $\max_b|\Delta\mathrm{star}_b| < \mathrm{TOL}=0.03$ over a maximum of $\mathrm{MAXIT}=12$ sweeps. The macro stars ROWDEM/ROWINF are NaN-masked over the three COVID quarters (2020Q2--Q4) in the metric, since their cross-sweep churn there is pure imputation Monte-Carlo noise, while the financial star ROWFIN is kept observed and enters the metric. Empirically the trace flattens at a Monte-Carlo noise floor of $\approx 0.13$, above the nominal tolerance, so convergence is read as a plateau at the floor rather than literal attainment of $0.03$. Figure~\ref{fig:empirical:emtrace} sketches the expected trace (final numbers \textbf{[TBD]} once the full production run is logged).

\begin{figure}[!ht]
\centering
\begin{tikzpicture}
\draw[->] (0,0) -- (8.3,0) node[right] {iteration};
\draw[->] (0,0) -- (0,4.4) node[above] {$\max_b|\Delta\mathrm{star}_b|$};
\foreach \x/\l in {0/1,1.2/2,2.4/3,3.6/4,4.8/5,6.0/6,7.2/7} \draw (\x,0.05)--(\x,-0.05) node[below] {\scriptsize\l};
\draw[dashed] (0,0.5) -- (8,0.5) node[right,font=\scriptsize] {TOL $=0.03$};
\draw[dotted] (0,1.4) -- (8,1.4) node[right,font=\scriptsize] {MC floor $\approx 0.13$};
\draw[thick,-{Stealth[length=2mm]}] (0,4.0) -- (1.2,2.9) -- (2.4,2.2) -- (3.6,1.8) -- (4.8,1.55) -- (6.0,1.45) -- (7.2,1.42);
\node[font=\scriptsize] at (4.0,4.1) {\emph{illustrative -- production trace forthcoming}};
\end{tikzpicture}
\caption{Schematic EM convergence trace: $\max_b|\Delta\mathrm{star}_b|$ versus sweep, against the tolerance ($0.03$) and the Monte-Carlo noise floor ($\approx 0.13$) at which the trace plateaus. \textbf{Placeholder} --- the realized trace is forthcoming.}
\label{fig:empirical:emtrace}
\end{figure}

\paragraph{Spectral radius of the coupling operator.} At solve time the cross-country deviation system is the affine fixed point $x = Mx + d$ (Section~\ref{sec:gvar:fixedpoint}), where $M$ is the Kalman-probe coupling operator. The Neumann series $\sum_k M^k d$ (Gauss--Seidel sweeps) and the direct $(I-M)^{-1}d$ agree, and convergence speed is governed by $\rho(M)$. Table~\ref{tab:empirical:rho} reports $\rho(M)$ by system size; it rises with both the number of coupled blocs and the activation of the endogenous-US channel, but remains below unity, so the fixed point is contractive.

\begin{table}[!ht]
\centering
\caption{Spectral radius $\rho(M)$ of the coupling operator by system configuration.}
\label{tab:empirical:rho}
\begin{tabular}{lccc}
\toprule
Configuration & Blocs & US treatment & $\rho(M)$ \\
\midrule
Pilot         & 6  & frozen anchor & $0.59$ \\
Production    & 24 & frozen anchor & $0.726$ \\
Endogenous-US & 33 & endogenous    & $0.924$ \\
\bottomrule
\end{tabular}
\end{table}

At the endogenous-US dimension ($\approx 2060$) the $O(\dim^3)$ inverse is prohibitive in-browser, so the system is solved inverse-free by the matvec-only recursion $x \leftarrow d + Mx$, which converges at the tabulated $\rho(M)\approx 0.924$, or via a pre-shipped cached $(I-M)^{-1}$.

\subsection{Out-of-sample forecast horse race}\label{sec:empirical:oos}

The system is evaluated in a companion repository
(\texttt{em-bayesian-gvar-eval}) under a pre-registered protocol whose
\emph{design is final} and whose realized \emph{results} are reported in
Section~\ref{sec:empirical:results}. The evaluation has
two cores: a recursive out-of-sample (OOS) forecast horse-race
(this subsection) and an endogenous-vs-frozen spillover analysis
(Section~\ref{sec:empirical:spillover}). Every step is grounded in the
actual estimator, weights, and solver of
Sections~\ref{sec:bvar}--\ref{sec:gvar}, so the harness respects the data
spaces and invariants of those layers.

\subsubsection{Model set}\label{sec:empirical:modelset}

The \textbf{proposed} model is the EM-Bayesian GVAR, run two ways:
\begin{itemize}
  \item \texttt{emgvar\_endo} --- the full loop with the US
    \emph{endogenous} (\texttt{US\_ENDOGENOUS}$=1$: its own
    \texttt{ROW\{DEM,INF,FIN\}\_US} stars and a US weights row), the
    paper's contribution;
  \item \texttt{emgvar\_frozen} --- the legacy frozen-anchor variant
    (the US estimated once as a closed anchor); cheaper, and the Part-2
    spillover contrast.
\end{itemize}
Both produce density forecasts from the per-bloc predictive draw cloud
\texttt{Dforecast} at solve time. The OOS forecast is each bloc's own VAR
predictive density; the GVAR coupling enters because the stars---and thus
every bloc's regressors and completed history---are jointly determined by
the EM fixed point.

The proposed models are raced against six benchmarks, each estimated from
the \emph{same} truncated panel so that the comparison isolates a single
ingredient:
\begin{enumerate}[label=(\roman*)]
  \item \textbf{Random walk / no-change} --- in the scored space: a flat
    last level for the (stationary) rate, and the last observed value of
    the growth/inflation transform carried flat (a RW \emph{on the growth
    rate}). The driftless RW is the headline reference (all relative-RMSE
    ratios are against it); a sample-mean ``climatology'' forecast is a
    second naive anchor. The predictive density is Gaussian, centred at
    the no-change value with scale equal to the in-sample SD of the
    $h$-step change \emph{estimated directly at horizon $h$} (not
    $\sqrt h\,\sigma_1$, which is wrong for a series that is itself a
    growth rate).
  \item \textbf{AR$(p)$} per target series --- univariate OLS-with-constant
    on each target in its scored space, $p$ by AIC over $\{1,\dots,4\}$;
    both \emph{iterated} and \emph{direct}
    \citep{MarcellinoStockWatson2006} multi-step variants are reported
    (the iterated AR is the strong univariate competitor at $h\ge4$). The
    predictive density propagates the Gaussian innovation variance
    (analytic for iterated, residual-block-bootstrap for direct).
  \item \textbf{Single-country Bayesian VAR (no coupling)} --- the bloc
    estimated alone: the three \texttt{ROW$*$} star columns dropped, the
    identical \texttt{cgl\_bvarV5} call (same GLP/Minnesota prior, lags,
    COVID-as-missing mask) and \texttt{MAXIT}$=1$. Isolates the
    \emph{value of the global coupling}.
  \item \textbf{Classical fixed-weight GVAR}, two variants:
    (iv-a) the \emph{textbook} Pesaran--Schuermann--Weiner /
    Dees--di~Mauro--Pesaran--Smith GVAR
    \citep{PesaranSchuermannWeiner2004,DeesDiMauroPesaranSmith2007} ---
    per-bloc \textbf{OLS} VARX$^*$ with contemporaneous + lagged foreign
    stars as weakly exogenous regressors, fixed weights, \emph{no}
    COVID-as-missing (the literature's GVAR has no data augmentation);
    this is the mandatory headline classical competitor and the one piece
    of new code in the horse-race. (iv-b) a single-pass Bayesian
    fixed-weight GVAR (\texttt{MAXIT}$=1$, GLP prior + COVID-as-missing) ---
    the clean \emph{EM ablation} whose only difference from the proposed
    model is the star re-convergence.
  \item \textbf{Bayesian dynamic factor model} --- 3--5 static factors
    from the cross-bloc target panel, a Bayesian VAR(1--2) on the factors
    plus Gaussian idiosyncratic terms, same truncated panel and COVID
    handling. The non-GVAR multivariate ``is the GVAR structure even
    needed'' competitor.
\end{enumerate}
The two key ablations isolate the value of \emph{global coupling}
(iii~vs.\ proposed) and of the \emph{EM data-completion} (iv-b~vs.\
proposed); (iv-a) measures the whole Bayesian$+$EM$+$COVID apparatus
against the literature GVAR.

\subsubsection{Scheme: recursive expanding window}\label{sec:empirical:scheme}

Pseudo-real-time, recursive expanding window on the final 2025Q4 vintage
(a genuine real-time vintage does not exist for most of the $\sim$50-economy
panel; a US$+$EA-subset real-time check is a flagged robustness, not the
default). Origins run quarterly from $t_0=$~2010Q1 to 2024Q4
($\sim$60 raw origins). The OOS set is \emph{trimmed} so every scored
$(t_0,h)$ has a realization $\le$~2025Q4 (score $h{=}8$ only for origins
$\le$~2023Q4, etc.). Headline tables drop the 2020 COVID origins (and
origins whose window spans 2020), leaving $\sim$55 scorable origins;
an appendix shows the full set. The COVID-as-missing treatment still
applies \emph{in-sample} at every origin for which 2020Q2--Q4~$\le t_0$.
Blocs enter an origin only with $\ge40$ in-sample quarters; the six
headline blocs satisfy this from 2010Q1.

\textbf{Targets and horizons.} Three targets per bloc---real-GDP growth,
inflation, short rate---read through the same \texttt{findcol} resolution
order the estimator uses, in the same scored space ($4\Delta$ of the GDP
and price log-levels; the rate level). Horizons $h\in\{1,2,4,8\}$
quarters. The \emph{headline} scope is the six legible blocs
\{US, EA, JP, UK, CA, CN\}; the full 33-bloc panel is reported as
relative-RMSE distribution summaries in an appendix (rate-less blocs
CH/NO contribute growth and inflation only).

\paragraph{Look-ahead invariants (leak-free by construction).} The
expanding-window scheme is not automatically free of future-information
leakage; the driver enforces four invariants at \emph{every} origin
$t_0$. (1)~\emph{Panel truncation}: every \texttt{DataRaw}$\_$\texttt{<CC>}
panel is sliced to dates $\le t_0$ \emph{before} \texttt{transformData}
and before any star is built. (2)~\emph{Rolling as-of weights}: the
shipped 2021--2023 \texttt{weights\_full.json} is \textbf{forbidden} in
the OOS sweep (using it at a pre-2020 origin injects future trade
structure); the default is a \emph{fixed pre-sample window}
(e.g.\ 2005--2009 average, used at every origin---leak-free because it
biases toward the past, never the future), with genuine rolling
as-of-$t_0$ weights as the rigor robustness. (3)~\emph{Star re-convergence
is in-sample only}: every partner panel feeding a star is itself
truncated to $\le t_0$, so no star cell reads a post-$t_0$ realization.
(4)~\emph{No 2025Q4 harmonization at earlier origins}: the common vintage
is only the well from which $\le t_0$ rows are drawn; the deterministic
transforms (100$\cdot$log, $4\Delta$) estimate no parameters and leak
nothing.

\paragraph{Predictive-density caveat (stated, not hidden).}
\texttt{Dforecast} propagates the shock covariance $\Sigma$ and the
within-draw $(\beta,\Sigma)$ MH variation forward from the last
\emph{observed} state; it does \emph{not} integrate over the
DK-smoother uncertainty of the COVID-imputed states, and seeds the
forecast from the posterior-\emph{mean} completed state. For origins
whose conditioning rows include imputed COVID quarters (small $h$, $t_0$
near 2020) the density is therefore mildly \emph{over-confident}; PIT and
coverage near those origins are flagged as a known caveat, not a model
failure.

\subsubsection{Scoring and inference}\label{sec:empirical:scoring}

\textbf{Point accuracy:} RMSE and MAE of the predictive mean; the
headline number is relative RMSE $=\mathrm{RMSE(model)}/\mathrm{RMSE(RW)}$
($<1\Rightarrow$ beats RW).

\textbf{Density accuracy:} the continuous ranked probability score
(\textbf{CRPS}, the \emph{primary} metric) computed from the draw
ensemble by the unbiased estimator
\(\mathrm{CRPS}=\tfrac1m\sum_k|X_k-y|-\tfrac1{2m^2}\sum_{k}\sum_{l}|X_k-X_l|\)
\citep{GneitingRaftery2007}, which degrades gracefully at the modest
draw counts here; the mean log predictive score (LPS), reported with a
\emph{parametric} (Gaussian/skew-$t$) fit to the draw cloud as the
headline (a small-bandwidth KDE-LPS, unbounded below at $\sim$100 draws,
is only a robustness check); and calibration by the probability integral
transform (\textbf{PIT}) histograms with empirical coverage of the 50\%
and 90\% predictive intervals and a uniformity test
\citep{Berkowitz2001}. The conclusions lean on CRPS; LPS corroborates.

\textbf{Predictive-ability inference} is dictated by the \emph{nesting
structure} (the single most common referee kill-shot). Under the
maintained DGP, single-BVAR (iii)~$\subset$~single-pass GVAR
(iv-b)~$\subset$~proposed EM-GVAR, and RW/AR (i),(ii) are nested in all
the VAR models; for these nested pairs the standard Diebold--Mariano
statistic is \emph{not} asymptotically $\mathcal N(0,1)$ and overstates
significance. Accordingly:
\begin{itemize}
  \item the \textbf{Giacomini--White} conditional predictive-ability test
    \citep{GiacominiWhite2006} is the \emph{headline} inferential test: it
    is valid under nesting and is the recursive/expanding-scheme-correct
    test (it assumes finite estimation windows / non-vanishing estimation
    uncertainty), and it is loss-agnostic so it applies directly to the
    CRPS and log-score differentials. Instruments $g_{t-1}=[1,d_{t-1}]$
    plus a recession/financial-stress indicator (to detect
    state-dependent ability); HAC variance, Wald $\chi^2$.
  \item the \textbf{Clark--West} test \citep{ClarkWest2007} is used for the
    \emph{nested point/MSE} comparisons (it adjusts the MSE differential
    for the larger model's extra-parameter estimation noise); one-sided.
  \item the two-sided \textbf{Diebold--Mariano} test
    \citep{DieboldMariano1995} is used only for \emph{non-nested} pairs
    (proposed vs.\ DFM, or vs.\ the textbook OLS-GVAR when neither nests
    the other), with a HAC long-run variance (bandwidth $\ge h-1$) and the
    \citet{HarveyLeybourneNewbold1997} small-sample correction.
\end{itemize}
For multiplicity (models~$\times$~horizons~$\times$~variables~$\times$~blocs)
the family of GW/CW $p$-values is controlled by a Romano--Wolf step-down
\citep{RomanoWolf2005} (preferred---it respects cross-test dependence via
the bootstrap) or Benjamini--Hochberg, and the per-(variable,horizon)
\textbf{Model Confidence Set} \citep{HansenLundeNason2011} reports which
models are statistically indistinguishable from the best. Relative RMSE is
the descriptive effect size; significance comes from the CW/GW test on the
loss differentials, never from the ratio alone.

The deliverables are: the relative-RMSE matrix (model $\times$ horizon
$\times$ variable, headline six blocs + a full-panel distribution table);
CRPS and log-score tables with ratios vs.\ RW; GW/CW (and DM-for-non-nested)
significance overlaid with the Romano--Wolf set and the MCS membership
flagged; PIT histograms and a 50/90\% coverage table; and illustrative
fan-chart examples (e.g.\ the US-inflation forecast from a 2021Q2 origin).

\subsubsection{Results}\label{sec:empirical:results}

\paragraph{Run configuration.} The headline tables below are the
\emph{realized} sweep, not a placeholder. The recursive scheme runs over
the headline six blocs \{US, EA, JP, UK, CA, CN\} at up to $56$ quarterly
origins from 2010Q1 to 2024Q4 ($52$ for the two EM-GVAR variants and the
single-pass Bayesian GVAR, which require the longer in-sample warm-up; the
2020 ex-COVID origins are dropped from every model). Trade weights are
\emph{rolling, as-of-$t_0$}: a three-year pre-sample average ending just
before each origin (2007--2009 at the 2010Q1 origin through 2021--2023 at
2024Q1), so no future trade structure leaks in. The predictive densities
use $\mathrm{NDRAWS}=200$ retained draws with an explicit
\emph{stationarity backstop} that discards posterior draws whose companion
spectral radius exceeds $1$ (the fix for the explosive-draw dispersion
flagged in earlier pilots). The primary score is the CRPS; the $90\%$
Model Confidence Set (MCS) of \citet{HansenLundeNason2011} reports the
models statistically indistinguishable from the best per
(variable, horizon).

\paragraph{Headline finding.} On \emph{point} accuracy the iterated
AR$(p)$ and the dynamic factor model are the strongest competitors---a
familiar result in macro forecasting---and the EM-GVAR does \emph{not}
win the point horse-race outright (Table~\ref{tab:empirical:relrmse}).
The decisive evidence sits in the \emph{density} comparison and the MCS
(Tables~\ref{tab:empirical:crps}--\ref{tab:empirical:mcs}): the EM-Bayesian
GVAR is \emph{inside} the $90\%$ MCS for \textbf{inflation at every
horizon} ($h\in\{1,2,4,8\}$) and for the \textbf{short rate at
$h\in\{1,2,4\}$}---statistically on par with the best model on the entire
nominal block---and the best inflation point forecast at $h{=}1$ \emph{among
the multivariate/GVAR models} is \texttt{emgvar\_endo} (relative RMSE $0.799$),
behind only the univariate AR$(p)$ at $0.641$. It falls \emph{out} of the
MCS only for GDP growth at $h{=}1$ and $h{=}8$, where the univariate and
factor models dominate. Two structural results follow. First, the
endogenous-US design earns its keep: \texttt{emgvar\_endo} is weakly
preferred to the frozen-anchor \texttt{emgvar\_frozen} in the MCS on
balance---it \emph{survives} in the short-rate $h{=}1$ set while
\texttt{emgvar\_frozen} is eliminated ($p=0.15$ vs.\ $0.08$), and it is
removed \emph{later} than the frozen variant in the growth $h{=}8$
elimination order ($p=0.099$ vs.\ $0.057$); the one cell where the frozen
variant is marginally preferred is the rate $h{=}8$ tail, where both are
out of the set. Second, and most important for the paper's claim, the EM-Bayesian
treatment \emph{decisively} beats the textbook fixed-weight OLS classical
GVAR: \texttt{cgvar\_a} is eliminated from half of the (variable, horizon)
MCS cells (6 of 12), concentrated at the longer horizons, and carries badly
miscalibrated densities ($h{=}1$ coverage of only $0.37$ (inflation) $/$ $0.47$
(growth) against the $0.90$ target), so the Bayesian shrinkage
$+$ COVID-as-missing $+$ EM star-reconvergence apparatus is the
demonstrable value-add over the literature GVAR.

\paragraph{Honest caveats.} Two must be stated. (i)~The draw-based
densities are \emph{over-confident}: the $90\%$ predictive interval covers
only $\approx 0.73$--$0.85$ of realizations for the EM-GVAR variants at
short horizons (against the $0.90$ target; PIT uniformity is rejected), a
direct consequence of the $\mathrm{NDRAWS}=200$ cloud and of not
integrating over the DK-smoother uncertainty of the COVID-imputed states
(Section~\ref{sec:empirical:scheme}). The CRPS and the MCS---which compare
score \emph{differentials}, not absolute coverage---are the robust
primaries and are reported as such; the under-coverage is a calibration
caveat, not a ranking artifact. (ii)~The parametric log-predictive-score
column is numerically unreliable on the under-covered clouds (its
Gaussian/skew-$t$ tail fit blows up to $\sim\!10^{16}$ on a handful of
origins where a realization lands far in the tail of a too-narrow cloud),
so it is \emph{not} used for ranking; only CRPS and the MCS are.

\begin{table}[!ht]
\centering
\caption{Headline relative RMSE, $\mathrm{RMSE(model)}/\mathrm{RMSE(RW)}$
($<1$ beats the driftless random walk), six headline blocs, by horizon and
target. Realized OOS sweep (rolling as-of-$t_0$ weights, $\mathrm{NDRAWS}=200$).
Lowest entry per (target, horizon) in \textbf{bold}.}
\label{tab:empirical:relrmse}
\begin{tabular}{llcccc}
\toprule
& & \multicolumn{4}{c}{Horizon $h$ (quarters)}\\
\cmidrule(lr){3-6}
Target & Model & $1$ & $2$ & $4$ & $8$ \\
\midrule
Growth    & \texttt{emgvar\_endo}   & $1.191$ & $1.091$ & $1.026$ & $1.031$ \\
          & \texttt{emgvar\_frozen} & $1.191$ & $1.095$ & $1.028$ & $1.030$ \\
          & AR$(p)$                 & $1.195$ & $0.990$ & $0.968$ & $0.960$ \\
          & DFM                     & $\mathbf{0.917}$ & $0.989$ & $0.986$ & $\mathbf{0.962}$ \\
          & \texttt{cgvar\_a} (OLS GVAR) & $2.097$ & $1.013$ & $1.019$ & $0.993$ \\
\midrule
Inflation & \texttt{emgvar\_endo}   & $0.799$ & $0.891$ & $1.085$ & $0.953$ \\
          & \texttt{emgvar\_frozen} & $0.802$ & $0.894$ & $1.087$ & $0.962$ \\
          & AR$(p)$                 & $\mathbf{0.641}$ & $\mathbf{0.772}$ & $\mathbf{0.998}$ & $0.921$ \\
          & DFM                     & $0.804$ & $0.870$ & $1.067$ & $0.908$ \\
          & \texttt{cgvar\_a} (OLS GVAR) & $2.113$ & $1.050$ & $1.366$ & $1.075$ \\
\midrule
Rate      & \texttt{emgvar\_endo}   & $1.017$ & $1.121$ & $1.226$ & $1.444$ \\
          & \texttt{emgvar\_frozen} & $1.021$ & $1.119$ & $1.224$ & $1.445$ \\
          & AR$(p)$                 & $0.829$ & $\mathbf{0.863}$ & $\mathbf{0.919}$ & $1.025$ \\
          & SBVAR                   & $\mathbf{0.990}$ & $1.081$ & $1.195$ & $1.421$ \\
          & \texttt{cgvar\_a} (OLS GVAR) & $1.531$ & $1.200$ & $1.034$ & $\mathbf{1.001}$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[!ht]
\centering
\caption{Headline density accuracy --- mean CRPS as a ratio to the random
walk ($<1$ beats RW; CRPS is the primary score) at $h{=}1$ and $h{=}4$,
and the empirical $90\%$-interval coverage at $h{=}1$ (target $0.90$).
Realized OOS sweep. The parametric log-score is omitted as numerically
unreliable on the under-covered clouds (see text).}
\label{tab:empirical:crps}
\begin{tabular}{llccc}
\toprule
& & \multicolumn{2}{c}{CRPS ratio vs.\ RW} & cov$_{90}$ \\
\cmidrule(lr){3-4}\cmidrule(lr){5-5}
Target & Model & $h{=}1$ & $h{=}4$ & $h{=}1$ \\
\midrule
Growth    & \texttt{emgvar\_endo}        & $1.042$ & $0.983$ & $0.73$ \\
          & DFM                          & $0.745$ & $0.857$ & $0.89$ \\
          & \texttt{cgvar\_a} (OLS GVAR) & $2.382$ & $1.106$ & $0.47$ \\
\midrule
Inflation & \texttt{emgvar\_endo}        & $0.814$ & $1.080$ & $0.70$ \\
          & AR$(p)$                      & $0.629$ & $0.955$ & $0.88$ \\
          & \texttt{cgvar\_a} (OLS GVAR) & $2.498$ & $1.474$ & $0.37$ \\
\midrule
Rate      & \texttt{emgvar\_endo}        & $1.040$ & $1.230$ & $0.80$ \\
          & \texttt{sbvar}               & $0.986$ & $1.199$ & $0.84$ \\
          & \texttt{cgvar\_a} (OLS GVAR) & $1.519$ & $1.009$ & $0.86$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[!ht]
\centering
\caption{$90\%$ Model Confidence Set membership for the EM-Bayesian GVAR
\citep{HansenLundeNason2011}, by target and horizon. \cmark{} $=$ in the
MCS (statistically indistinguishable from the best); \xmark{} $=$
eliminated. The endogenous variant survives wherever the frozen one does
and strictly longer on the nominal block; the textbook OLS GVAR
(\texttt{cgvar\_a}) is eliminated from half of the (variable, horizon) MCS
cells (6 of 12), concentrated at the longer horizons.}
\label{tab:empirical:mcs}
\begin{tabular}{llcccc}
\toprule
 & & \multicolumn{4}{c}{Horizon $h$}\\
\cmidrule(lr){3-6}
Target & Model & $1$ & $2$ & $4$ & $8$ \\
\midrule
Growth    & \texttt{emgvar\_endo}   & \xmark & \cmark & \cmark & \xmark \\
          & \texttt{emgvar\_frozen} & \xmark & \cmark & \cmark & \xmark \\
Inflation & \texttt{emgvar\_endo}   & \cmark & \cmark & \cmark & \cmark \\
          & \texttt{emgvar\_frozen} & \cmark & \cmark & \cmark & \cmark \\
Rate      & \texttt{emgvar\_endo}   & \cmark & \cmark & \cmark & \xmark \\
          & \texttt{emgvar\_frozen} & \xmark & \cmark & \cmark & \xmark \\
\midrule
\multicolumn{2}{l}{\texttt{cgvar\_a} (textbook OLS GVAR), growth}
          & \xmark & \cmark & \xmark & \xmark \\
\multicolumn{2}{l}{\texttt{cgvar\_a} (textbook OLS GVAR), inflation}
          & \cmark & \cmark & \xmark & \xmark \\
\multicolumn{2}{l}{\texttt{cgvar\_a} (textbook OLS GVAR), rate}
          & \xmark & \cmark & \cmark & \cmark \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Endogenous-US spillover analysis}\label{sec:empirical:spillover}

The endogenous-US configuration ($\rho(M)\approx 0.924$,
Table~\ref{tab:empirical:rho}) lets a US scenario pin propagate through
the RoW$\to$US stars \emph{and} the four US-determined global commons
(oil, the US 10-year yield, the US BAA corporate yield, US equity),
pinned $1{:}1$ onto every RoW bloc. A frozen anchor cannot generate the
reverse RoW$\to$US feedback at all---the ``world~$\to$~US'' direction is
\emph{structurally absent}, not ``present but zero''---so the two
configurations differ in exactly the global-spillover content we wish to
document. The analysis is split into two tiers, and the manual labels
which is which, because the shipped solver computes a particular object.

\paragraph{What the solver actually computes.} \texttt{gvarSolve.ts} does
\emph{not} compute generalized impulse responses (GIRFs), forecast-error
variance decompositions (FEVDs), or a Diebold--Yilmaz connectedness
index. It returns a \emph{conditional-mean scenario response}: pin a path
and read the coupled conditional-forecast \emph{mean deltas}
$\texttt{delta}[c]$ via the fixed point $x=Mx+d$ (Algorithm
\ref{alg:coupling}). There is no $\Sigma$-based shock generator and no
moving-average machinery in the solver. The analysis therefore separates:
\begin{itemize}
  \item \textbf{Tier A (the headline; zero new estimator code).} The
    conditional scenario propagation of a US pin, endogenous
    (\texttt{solveGVARClosedFormEndo}) vs.\ frozen
    (\texttt{solveGVARLinear}). This \emph{is} the empirical contribution
    the shipped code supports.
  \item \textbf{Tier B (a new \texttt{gvar\_girf} module).} GIRFs
    \citep{PesaranShin1998}, generalized FEVDs, and the Diebold--Yilmaz
    spillover index \citep{DieboldYilmaz2009,DieboldYilmaz2012}. The
    ingredients exist in the exports (\texttt{companion\_mean.json}
    carries each bloc's companion $\hat\beta$ and $\hat\Sigma$; the
    coupling $M$ is assembled by \texttt{gvarSolve.ts}), so it is
    \emph{constructible}, but it is new code, validated against Tier~A and
    gated behind it.
\end{itemize}

\paragraph{Tier A --- the worked scenario contrast (headline).} A
US~$+100$\,bp rate \emph{path} (\texttt{POLRATE} pinned $+100$\,bp over
the horizon---correctly a multi-period conditional projection, not a
one-period shock or a GIRF) is propagated through both topologies. Under
the endogenous configuration the augmented state carries every bloc's
\texttt{ROW$*$} star deltas \emph{including the US's own}
(\texttt{ROW$*$\_US}, the RoW$\to$US feedback) and the US global-column
deltas $g\Delta$; the converged $\texttt{delta.US}\neq0$ is the feedback
the frozen anchor cannot produce. We report the per-bloc deltas
(growth/inflation/rate) for the six headline blocs side by side, the
\emph{feedback gap} (the US-own response difference), the per-bloc
\emph{amplification ratio} (endogenous vs.\ frozen RoW peak responses),
the peak horizons, and the spectral radius $\rho(M)$ of each system (the
multiplier strength reported by the solver as \texttt{rhoSpectral} /
\texttt{rhoEmpirical}). This example doubles as the solver-validation
canary: the closed-form endogenous result reproduces the iterative
\texttt{solveGVAR} fixed point to $<10^{-4}$ across every bloc, and a
warm coupling-cache hit is byte-identical ($<10^{-9}$) to a cold rebuild
(both asserted in the \texttt{gvar-us-endogenous} / \texttt{gvar-closed-form-routing}
test suites; the iterative reference is itself converged to $10^{-7}$).

\paragraph{Tier A --- realized scenario contrast.} The worked example
(\texttt{eval/tier\_a\_scenario.mjs}, output \texttt{results/tierA/us\_rate\_100bp.json})
propagates a US~$+100$\,bp \texttt{POLRATE} path through both topologies and
confirms the qualitative point the design predicts:
the frozen anchor produces \emph{no} RoW$\to$US feedback, while the
endogenous configuration produces a non-trivial one. The cross-country
\emph{gap} (endogenous minus frozen) is sizeable on every bloc---for
example the peak US own-growth response differs by $\approx 4.2$ display
points, EA inflation by $\approx 1.1$, and the gap \emph{flips sign}
across blocs (positive for US/EA/UK growth, negative for JP/CA/CN growth);
selected peaks are in Table~\ref{tab:empirical:tierA}.
\textbf{Honest caveat (do not over-read).} These are the deltas of a
\emph{multi-period conditional projection}, not a structural or
generalized impulse response: the US rate is \emph{pinned} along the whole
path, so the responses bundle the direct conditioning with the coupled
feedback and are not a clean causal IRF. The magnitudes are large and
sign-flipping, which is exactly why a validation pass (the Tier-B GIRF
cross-check below, and a robustness sweep over the pin specification) is
required before any number here is headlined as a spillover
\emph{multiplier}. What is established is the \emph{existence and direction}
of the endogenous-only feedback channel, not its calibrated size.

\begin{table}[!ht]
\centering
\caption{Tier-A US~$+100$\,bp \texttt{POLRATE}-path projection: peak
conditional-mean response (display points) under the endogenous vs.\
frozen-anchor topology, and their gap, for selected blocs and targets
(\texttt{results/tierA/us\_rate\_100bp.json}). \emph{Conditional-projection
deltas, not causal IRFs}---magnitudes are illustrative and pending
validation.}
\label{tab:empirical:tierA}
\begin{tabular}{llccc}
\toprule
Bloc & Target & Endogenous & Frozen & Gap (endo$-$froz) \\
\midrule
US & Growth    & $+1.28$ & $-4.37$ & $+4.22$ \\
US & Inflation & $-1.53$ & $-2.82$ & $+1.30$ \\
EA & Growth    & $+1.03$ & $-0.95$ & $+0.88$ \\
EA & Inflation & $-1.00$ & $-0.64$ & $+1.07$ \\
JP & Growth    & $+1.07$ & $+1.62$ & $-1.18$ \\
CN & Inflation & $-0.69$ & $+1.19$ & $-1.29$ \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Tier B --- GIRF, FEVD, and connectedness (structural
extension).} The GIRF to a one-SD shock in variable $i$ of the coupled
global system is
\(\mathrm{GIRF}_x(h,i)=\sigma_{ii}^{-1/2}A_h\Sigma e_i\), with $A_h$ the
$h$-step coefficient of the coupled solution's moving-average
representation and $\Sigma$ the (cross-bloc-block-diagonal) global
innovation covariance---ordering-invariant, the standard GVAR
identification stance \citep{PesaranShin1998,DeesDiMauroPesaranSmith2007}.
The identifying assumptions are stated explicitly: GIRFs trace the
response to the historically typical innovation correlation (not an
orthogonal structural shock), cross-bloc innovation independence
(block-diagonal $\Sigma$), and linearity/parameter-constancy over the
horizon. Bands come from re-running the recursion over the
\texttt{companion\_draws.json} posterior draws. The module is validated by
the cross-check that a one-period US-rate-pin conditional path equals the
rate-shock GIRF up to the $\delta/\sqrt{\sigma_{ii}}$ normalization.
From the system generalized FEVD $\theta_{ij}(H)$ (row-normalized) we
report the Diebold--Yilmaz total spillover index, the ``from US'' row, and
the ``to US'' direction---the channel the frozen anchor cannot even
define---with posterior bands and both the raw and row-normalized indices.
\textbf{Results: [TBD]} (Tier~A ships first; Tier~B is the structural
extension).

\section{Discussion}\label{sec:discussion}
%% ================================================================

The Monetary-Financial Model is designed to bridge the gap between the
methodological sophistication of conditional forecasting techniques
developed in the academic literature and the practical needs of policy
economists who require rapid, interactive scenario analysis.  We
conclude with a discussion of design choices, limitations, and
directions for future work.

\subsection{Design Philosophy}

Several design choices merit discussion.  First, the three-layer
architecture---baseline, scenario, counterfactual---deliberately
separates concerns.  The baseline forecast reflects the BVAR's
unconditional projection and is computed offline.  The scenario layer
allows the user to impose conditioning constraints without specifying
the structural source of the deviations, following the tradition of
\citet{WaggonerZha1999}.  The counterfactual layer then overlays
structural identification via DSGE impulse responses, enabling
``what-if'' policy analysis while preserving the reduced-form
covariance structure of the BVAR.

Second, the decision to re-condition the counterfactual through the
BVAR (rather than relying solely on the DSGE IRFs) reflects a
deliberate methodological choice: the BVAR's estimated covariance
structure captures empirical co-movements that may be absent from or
imperfectly captured by any single DSGE model.  The IRF-consistent
mode (Section~\ref{sec:modes}c) strikes a balance by using the DSGE
model to identify the responses of key variables (inflation, output)
to the policy shock, while allowing the BVAR to propagate these
effects to the remaining 30+ variables in a data-consistent manner.

Third, all computation runs client-side.  This eliminates server
infrastructure costs and latency, enables offline use, and avoids
transmitting potentially sensitive forecast data over the network.
The computational cost is manageable: the Kalman filter and smoother
for the $41$-variable, $3$-lag US VAR over a 20-quarter horizon completes in
well under a second on modern hardware (the single-bloc smoother is
sub-$50$\,ms; the multi-second cost discussed in
Section~\ref{sec:perfux} is the \emph{coupled} $50$-bloc GVAR solve, not
the single-country filter).

\subsection{Limitations}

The current implementation has several limitations that users should
bear in mind:

\begin{enumerate}
  \item \textbf{Linear, time-invariant dynamics:} The VAR
    coefficients are fixed at their posterior mean for the
    deterministic conditional forecast.  Time-varying parameters,
    stochastic volatility, and regime switching are not supported.
    In periods of structural change, the fixed-coefficient
    assumption may be particularly restrictive.

  \item \textbf{Gaussian innovations:} The Kalman filter assumes
    Gaussian innovations.  Fat-tailed or asymmetric shock distributions,
    which may be important during financial crises, are not accommodated.

  \item \textbf{Point-identified counterfactuals:} The DSGE IRFs
    used for counterfactual analysis are computed under a single
    monetary policy rule and model specification.  The tool does not
    average over model uncertainty or rule uncertainty, though the
    user can manually explore different model--rule combinations.

  \item \textbf{Lucas critique:} The counterfactual analysis
    conditions on estimated reduced-form dynamics that may themselves
    change under the alternative policy.  The IRF-consistent mode
    partially addresses this by using structurally identified
    responses for the key transmission variables, but the remaining
    variables' responses are governed by the estimated BVAR
    covariance structure, which is held fixed.

  \item \textbf{Data vintage:} The BVAR \emph{coefficients} are estimated
    on a fixed 2025Q4 vintage and frozen. The \emph{observed} panel is
    extended without re-estimation by the 2026Q1 refresh of
    Section~\ref{sec:vintage} (the forecast re-anchors from the frozen
    companion), but real-time data \emph{revisions} to already-shipped
    quarters and the differential publication lag across blocs (the ragged
    edge---CN/IN at 2025Q4, IL at 2024Q4) are not otherwise reconciled, and
    the parameters are not re-estimated as new data arrive.
\end{enumerate}

\subsection{Known issues flagged for fix}\label{sec:knownissues}

The limitations above are intrinsic to the modelling choices. The
following are \emph{specific, identified defects} in the current
deployment---known and flagged, but \emph{not yet fixed}---documented here
in the interest of honesty for a live research tool. Each cites the source
file where it lives.

\begin{enumerate}
  \item \textbf{China fiscal debt inflation double-count --- RESOLVED
    (June~2026).} The fiscal debt-snowball roll-forward
    (\texttt{fiscalAccounting.ts}) builds quarterly nominal GDP growth as
    $\Delta(\texttt{idx.gdp}) + \Delta(\texttt{idx.deflator})$, i.e.\ real
    growth plus inflation. Formerly the resolved CN \texttt{idx.gdp} pointed
    at a \emph{nominal} \texttt{GDP\_CN} while \texttt{idx.deflator} pointed
    at \texttt{CPI\_CN}, so inflation was added \emph{twice} and the CN
    debt-to-GDP path was biased. The June-2026 endogenous-US 33-bloc
    GVAR-EM re-estimate re-sourced \texttt{GDP\_CN} as a \emph{real}
    chain-linked SA volume index (base 2011Q1=100) and set
    \texttt{CN/fiscal\_meta.json} \texttt{idx.gdpIsNominal=false}, so the
    growth term is now genuinely real growth plus a CPI term (CPI~$\approx$~0
    in this window), on the same footing as the other fiscal blocs. The
    double-count is gone; only a second-order CPI-versus-GDP-deflator wedge
    remains (shared by EA/JP/UK/CA).
  \item \textbf{Retired entropic-tilt code still ships (no live path).}
    The user-facing long-run mechanism is now the forward-pass drift
    setter (\texttt{driftSetter.ts}, Section~\ref{sec:driftsetter}), which
    \emph{replaced} the earlier entropic tilt and has no steady-state
    moment to go non-finite (Remark~\ref{rem:tilt_retired}). The old
    \texttt{longRunTilt.ts} module is still present in the repository but
    is \emph{no longer wired to any UI component}---it is referenced only
    by its own unit test. It retains a latent defect (\texttt{NaN} long-run
    moments for unit-root/near-singular draws propagate through the softmax
    and empty the anchor band), which is harmless while the module is
    unused but should be removed or finite-masked to avoid future
    reintroduction.
  \item \textbf{No divergence guard on the closed-form GVAR solve.} The
    live solver (\texttt{gvarSolve.ts}, Neumann iteration and direct
    inverse) does not check $\rho(M)<1$ before solving. The deployed
    coupling is contractive ($\rho(M)\approx 0.924$), but a future roster
    or a degenerate pin set that pushed $\rho(M)\ge 1$ would return a
    \emph{confidently wrong} forecast from a diverged fixed point with no
    warning. A spectral-radius backstop is needed.
  \item \textbf{Conditional band uses the filtered, not smoothed,
    covariance.} The predictive-band variances are extracted from the
    Kalman \emph{filter} covariance $P^{\mathrm{filt}}_t$
    (\texttt{kalman.ts}), not the Durbin--Koopman \emph{smoother}
    covariance. For quarters \emph{preceding} a future pin, the smoother
    would tighten the covariance (a later observation reduces uncertainty
    about an earlier state), so the displayed band is \emph{overstated}
    on the run-up to a future conditioning point. The central path is
    unaffected; only the band width is conservative.
  \item \textbf{The porter does not regenerate \texttt{fiscal\_meta.json}.}
    The fiscal block is addressed by \emph{positional} indices stored in
    each bloc's \texttt{fiscal\_meta.json}
    (\texttt{idx.gdp}, \texttt{idx.deflator}, \texttt{idx.revenue}, \dots).
    The model export does not rebuild this file, so any change to a bloc's
    variable order leaves the indices pointing at the wrong columns---the
    cause of a recent EA/UK debt-path explosion---and they must be repaired
    manually (\texttt{pipeline/fix\_fiscal\_meta\_indices.mjs}). Folding the
    meta regeneration into the porter is the durable fix.
\end{enumerate}

\subsection{Directions for Future Work}

Several extensions are planned or under consideration:

\begin{itemize}
  \item \textbf{Time-varying parameters:} Incorporating stochastic
    volatility or time-varying coefficients
    \citep[e.g.,][]{simszha1998} to capture evolving dynamics.

  \item \textbf{Structural identification:} Extending the
    counterfactual layer to support sign restrictions, narrative
    restrictions, or scenario priors \citep{FarkasJakab2026} for
    identification within the BVAR itself, rather than relying on
    external DSGE models.

  \item \textbf{Mixed-frequency data:} Supporting monthly--quarterly
    mixed-frequency estimation to incorporate higher-frequency
    indicators.

  \item \textbf{Model averaging:} Bayesian model averaging over
    DSGE specifications and policy rules for the counterfactual
    layer.
\end{itemize}


%% ================================================================
\appendix
\section{Glossary of terms}\label{app:glossary}
%% ================================================================

This glossary defines the named concepts used throughout the manual; the
mathematical symbols are collected in Table~\ref{tab:notation}.

\begin{description}[leftmargin=0pt,labelindent=0pt,style=nextline,itemsep=3pt]
  \item[BVAR (Bayesian vector autoregression)] A reduced-form VAR whose
    coefficients are estimated under a prior, here the hierarchical
    Minnesota/GLP prior of \citet{Giannone2015} with data-driven
    hyperparameter selection (Section~\ref{sec:bvar}).
  \item[Minnesota / GLP prior] The shrinkage prior that centers each
    equation on a univariate own-lag model and selects its tightness
    $\lambda$ and sum-of-coefficients $\mu$ by marginal-likelihood
    maximization. ``GLP'' refers to the \citet{Giannone2015}
    hierarchical implementation.
  \item[Own-lag prior mean ($\delta$): RW vs.\ WN] The prior mean on a
    variable's own first lag: $\delta=1$ (random walk, \texttt{RW}, the
    default---best forecast is the current level) or $\delta=0$ (stationary
    white noise, \texttt{WN}---best forecast is the mean). Implemented as
    \(\texttt{diagb}(\texttt{pos})=0\) for the \texttt{WN} index set
    \texttt{pos} (Section~\ref{sec:ownlag}). It shifts the prior
    \emph{center}, not a hard constraint.
  \item[GVAR (Global VAR)] A collection of per-economy (``bloc'') BVARs
    linked through trade-weighted foreign variables; here the linkage is
    imposed at solve time, not in estimation
    (Sections~\ref{sec:gvar},~\ref{sec:gvar:fixedpoint}).
  \item[Trade-weighted ``star'' variable] A bloc's foreign aggregate
    (\texttt{ROWDEM} demand, \texttt{ROWINF} inflation, \texttt{ROWFIN}
    financial), built as the trade-weight $w_{cj}$-weighted average of its
    partners' corresponding series, renormalized over the partners present
    each quarter (Section~\ref{sec:gvar:stars}).
  \item[Endogenous dominant unit] The configuration in which the US is a
    full bloc inside the fixed point---with its own \texttt{ROW$*$\_US}
    stars and a US weights row---so shocks abroad feed \emph{back} into the
    US (the RoW$\to$US channel a frozen anchor cannot represent).
  \item[Frozen anchor] The legacy configuration in which the US is
    estimated once as a closed, exogenous driver: it enters the coupling
    only through the forcing $d$, with no equation for the world to feed
    back into.
  \item[Global commons] The four US-determined common series (oil, the US
    10-year yield, the US BAA corporate yield, US equity) pinned $1{:}1$
    onto every RoW bloc (Section~\ref{sec:gvar:commons}).
  \item[COVID-as-missing] The treatment of the fixed 2020Q2--Q4 window as
    \emph{missing data}: the macro columns and the two macro stars are
    NaN-masked while financials and \texttt{ROWFIN} are kept observed, and
    the Durbin--Koopman simulation smoother imputes the holes inside a
    data-augmentation Gibbs sampler (Section~\ref{sec:covid}).
  \item[EM loop] The block-coordinate iteration over (foreign stars,
    completed-data states, VAR coefficients): an E-step that completes the
    panels and rebuilds the stars and an M-step that re-estimates every
    bloc, iterated to a fixed point in the completed stars
    (Algorithm~\ref{alg:emgvar}).
  \item[Durbin--Koopman simulation smoother] The forward-filter /
    backward-draw recursion \citep{DurbinKoopman2002} that produces draws
    of the conditioned/missing states by simulating an unconditional path,
    smoothing it, and adding back the smoothed discrepancy
    (Algorithm~\ref{alg:dksmoother}).
  \item[Coupling operator $M$, fixed point $x=Mx+d$] The affine solve-time
    operator that propagates a scenario across blocs; assembled by
    Kalman-probing each pinned cell, solved by Gauss--Seidel/Neumann sweeps
    or the direct $(I-M)^{-1}$ (Algorithm~\ref{alg:coupling}). $\rho(M)<1$
    makes it contractive.
  \item[SFA (stock-flow adjustment)] The deficit--debt discrepancy: the
    part of the observed change in gross debt that the flow side (deficit
    plus the interest--growth snowball) does not explain; an estimated
    \texttt{WN}-prior BVAR variable (Section~\ref{sec:fiscal_drivers}).
  \item[EFFI (effective interest rate)] The average rate the government
    actually pays (net interest over lagged gross debt, annualized); a
    persistent \texttt{RW}-prior variable distinct from the policy rate and
    market yields.
  \item[Long-run drift setter ($\delta c$)] The user-facing long-run-target
    mechanism: a deterministic counterfactual that shifts a variable's own
    companion drift by the single constant $\delta c$ needed to land its
    terminal forecast on the user's target, applied as the exact response
    $S_h[:,j]\,\delta c$ that translates the central path and bands rigidly,
    instantly and without re-estimation
    (Section~\ref{sec:driftsetter}). It replaces the earlier
    \emph{entropic tilt}, an after-estimation draw reweighting that
    degenerated (collapsing effective sample size) when over-constrained.
  \item[CRPS (continuous ranked probability score)] A strictly proper
    density score \citep{GneitingRaftery2007} computed from the draw
    ensemble; the primary density metric of the evaluation, robust at
    modest draw counts.
  \item[PIT (probability integral transform)] The rank of each realization
    in its predictive ensemble; uniform PITs indicate good calibration
    \citep{Berkowitz2001}.
  \item[Giacomini--White (GW) test] The conditional predictive-ability test
    \citep{GiacominiWhite2006} used as the headline inferential test: valid
    under nesting and for the recursive/expanding-window scheme, and
    loss-agnostic (applies to point, CRPS, and log-score differentials).
  \item[Clark--West (CW) test] The nested-model point/MSE test
    \citep{ClarkWest2007} that adjusts the loss differential for the larger
    model's extra-parameter estimation noise.
  \item[Diebold--Mariano (DM) test] The equal-predictive-accuracy test
    \citep{DieboldMariano1995}, used here only for \emph{non-nested} pairs,
    with the \citet{HarveyLeybourneNewbold1997} small-sample correction.
  \item[Romano--Wolf / Model Confidence Set] Multiplicity controls: the
    Romano--Wolf step-down \citep{RomanoWolf2005} for FWER across the test
    family, and the MCS \citep{HansenLundeNason2011} reporting the models
    statistically indistinguishable from the best.
  \item[GIRF / Diebold--Yilmaz index] Generalized (ordering-invariant)
    impulse responses \citep{PesaranShin1998} and the connectedness index
    \citep{DieboldYilmaz2009,DieboldYilmaz2012} of the Tier-B spillover
    module (Section~\ref{sec:empirical:spillover}).
\end{description}


%% ================================================================
\section*{Acknowledgments}
%% ================================================================
\addcontentsline{toc}{section}{Acknowledgments}

I am grateful to \textbf{Jesper Lind\'e} for his comments, advice, and
continued support throughout the development of this tool, and to
\textbf{Tobias Adrian} for his support. The views and any remaining
errors are my own.

%% ================================================================
\section*{Disclaimer}
%% ================================================================

The views expressed herein are those of the author and should not be
attributed to the International Monetary Fund, its Executive Board, or
its management.  This tool is provided ``as is'' without warranty of
any kind, express or implied.  The author and the IMF disclaim all
liability for any errors, omissions, or for any loss or damage arising
from its use.  Users are solely responsible for any decisions made
based on the output of this tool.

\clearpage
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
